### 2019-04-17 AnalysisCode/ms1_analyses.Rmd
continued code development

---
title: 'Q1: Are lake and terrestrial primary productivity coherent?'
author: "Jonathan Walter, Grace Wilkinson, Rachel Fleck, Michael Pace"
date: "4/17/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(aqts)
library(wsyn)
library(rgdal)
library(LAGOSNE)

rm(list=ls())

```

# Data important and formatting

```{r data import and formatting, echo=TRUE}

lakes_to_get<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/lakes20yrs_chla.csv")$x

lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, tsvars=c("chla"), minmos=3, minobs=3)
lagoslakes.cln<-cleanAnnualts(lagoslakes.raw) #69 lakes here

```

### 2019-04-17 AnalysisCode/DataExploration/lakes20yrsIDs.R

@@ -1,0 +1,43 @@
+### get LAGOS R package from CRAN and explore it to determine how many lakes appear to be useable
+
+
+rm(list=ls())
+
+#install.packages("LAGOSNE")
+
+library(LAGOSNE)
+library(lubridate)
+
+#lagosne_get(version="1.087.1") #only need to run once or to update to new database version
+
+dt<-lagosne_load(version = "1.087.1")
+
+lakeinfo<-lagosne_select(table="locus", vars=c("lagoslakeid","gnis_name"))
+
+
+vars.raw<-lagosne_select(table="epi_nutr", vars=c("lagoslakeid","chla","sampledate"))
+
+vars<-vars.raw #make a copy to manipulate
+vars<-vars[complete.cases(vars),] #remove obs with missing data
+
+
+###############################################################################
+## Do some first-pass data checks
+###############################################################################
+length(unique(vars$lagoslakeid))
+
+check.20yrs<-NULL #these lakes have data spanning at least 20 years
+
+
+for(id in unique(vars$lagoslakeid)){
+  vars.sub<-vars[vars$lagoslakeid == id,]
+  #id lakes with data spanning >= 20 years, 
+  vars.sub$year<-as.numeric(simplify2array(strsplit(as.character(vars.sub$sampledate),"/"))[3,])
+  if(max(vars.sub$year)-min(vars.sub$year) >= 20) 
+  {
+    check.20yrs<-c(check.20yrs, id)
+  }
+  
+}
+
+write.csv(check.20yrs, file="~/GitHub/AquaTerrSynch/AnalysisCode/lakes20yrs_chla.csv", row.names=F)

### 2019-04-17 R Package/aqts/R/cleanAnnualts.R

@@ -43,6 +43,11 @@ cleanAnnualts<-function(indat, ymin=20, maxNA=2, timespan=NULL, fill.method="med
     
     dat.lind<-indat$lakedata[[lind]]
     
+    if(all(is.na(dat.lind))){
+      droplakes<-c(droplakes,lind)
+      next
+    }
+    
     if(!is.null(timespan)){ #if necessary, limit data to selected timespan
       dat.lind<-dat.lind[,colnames(dat.lind)>=min(timespan) &
                            colnames(dat.lind)<=max(timespan)]
@@ -55,7 +60,7 @@ cleanAnnualts<-function(indat, ymin=20, maxNA=2, timespan=NULL, fill.method="med
     
     #check for ymin
     
-    if(diff(range(as.numeric(colnames(dat.lind)))) < ymin){
+    if(diff(range(as.numeric(colnames(dat.lind)))) < (ymin-1)){
       droplakes<-c(droplakes,lind)
     }
     
@@ -76,6 +81,11 @@ cleanAnnualts<-function(indat, ymin=20, maxNA=2, timespan=NULL, fill.method="med
       }
       if(!is.null(dropvars)){dat.lind<-dat.lind[-dropvars,]}
       
+      if(nrow(dat.lind)==0){
+        droplakes<-c(droplakes, lind)
+        next
+      }
+      
       #fill time series if sporadic NAs
       for(vind in 1:nrow(dat.lind)){
         if(fill.method!="median"){stop("only fill.method=median is implemented")}
@@ -87,6 +97,7 @@ cleanAnnualts<-function(indat, ymin=20, maxNA=2, timespan=NULL, fill.method="med
     cleandat[[lind]]<-dat.lind
     if(length(dat.lind)==0){droplakes<-c(droplakes, lind)}
   }
+  
   if(!is.null(droplakes)){
     cleandat<-cleandat[-droplakes]
     cleaninfo<-cleaninfo[-droplakes,]

### 2019-04-17 R Package/aqts/R/makeLAGOSannualts.R

@@ -38,14 +38,14 @@ makeLAGOSannualts<-function(lakes, tsvars=c("chla"), infovars=NULL, aggfun="gsme
   
   dt<-lagosne_load(version = lagosversion)
   
-  tsvars<-unique(c("lagoslakeid","sampledate",getvars)) #makesure lagoslakeid and sampledate are always pulled
+  tsvars<-unique(c("lagoslakeid","sampledate",tsvars)) #makesure lagoslakeid and sampledate are always pulled
   
   infovars<-unique(c("lagoslakeid","gnis_name","nhd_lat","nhd_long", infovars)) #make sure some vars are always pulled
   
-  epidat<-lagosne_select(table="epi_nutr", vars=getvars[getvars != "secchi"]) #pull lake ecological data
+  epidat<-lagosne_select(table="epi_nutr", vars=tsvars[tsvars != "secchi"]) #pull lake ecological data
   info<-lagosne_select(table="locus", vars=infovars) #pull lake info
   
-  if("secchi" %in% getvars){ #add secchi depth information stored in separate table
+  if("secchi" %in% tsvars){ #add secchi depth information stored in separate table
     secchi<-lagosne_select(table="secchi",vars=c("lagoslakeid","sampledate","secchi"))
     secchi$lakedate<-paste(secchi$lagoslakeid,secchi$sampledate,sep="_")
     epidat$lakedate<-paste(epidat$lagoslakeid,epidat$sampledate,sep="_")
@@ -100,9 +100,9 @@ makeLAGOSannualts<-function(lakes, tsvars=c("chla"), infovars=NULL, aggfun="gsme
     aggdat<-cbind(aggdat,ydat)  
     }#close year loop
     aggdat[is.nan(aggdat)]<-NA
-    rownames(aggdat)<-getvars[!getvars %in% c("sampledate","lagoslakeid")]
+    rownames(aggdat)<-tsvars[!tsvars %in% c("sampledate","lagoslakeid")]
     colnames(aggdat)<-lakeyears
-    lakedata[[paste0(lakeinfo$gnis_name[lakeinfo$lagoslakeid==ii])]]<-aggdat
+    lakedata[[paste0(ii)]]<-aggdat
     lakeinfo$start[lakeinfo$lagoslakeid==ii]<-min(lakeyears)
     lakeinfo$end[lakeinfo$lagoslakeid==ii]<-max(lakeyears)
[…]

### 2019-04-17 R Package/aqts/R/makeMNMPCAannualts.R

@@ -1,0 +1,54 @@
+#' Create annualized time series from MN MPCA data
+#' 
+#' \code{makeMNMPCAannualts} formats MN MPCA data to match output from \code{makeLAGOSannualts}.
+#' 
+#' @param dir a file path where the data files are stored
+#' @param tsvars a character vector of variables to extract and construct time series from.
+#' @param infovars a character vector of lake characteristic variables to include in \code{lakeinfo}. See details.
+#' @param aggfun a string indicating how to summarize multiple observations to an annual timescale. See details.
+#' @param timespan a vector giving the min and max of a range of years which data will be restricted to.
+#' @param minmos the minimum number of months required to have data from for an annual value to be computed.
+#' @param minobs the minimum number of observations, spread over \code{>= minmos}, for an annual value to be computed
+#' 
+#' @return \code{makeIowaALMannualts} returns an object of class \code{list}. Slots are:
+#' \item{lakeinfo}{A data frame of lake information.}
+#' \item{lakedata}{A list of data frames containing the lake data.}
+#' 
+#' @details These are data partly contained in LAGOS-NE that we obtained in order to grow our list of lakes with >=20 years of data.
+#' Currently, the only accepted value of \code{aggfun} is \code{"gsmean"}, corresponding to the growing season mean.
+#' We consider the growing season to last May to September. Output \code{lakeinfo} is a data frame containing the numeric id code, name, 
+#' and geographic coordinates of lakes, plus any further variables listed in \code{infovars}. Each element of \code{lakedata} corresponds to a lake
+#' in \code{lakes} and is a data frame in which columns are variables in \code{tsvars} and rows correspond to years.
+#' 
+#' Options for \code{infovars} are "Phosphorus as P", "Orthophosphate as P", "Inorganic nitrogen (nitrate and nitrite) as N",
+#' "Ammonia-nitrogen as N", "Nitrate as N", "Chloride", "Total suspended solids", "Chlorophyll a, corrected for pheophytin",
+#' "Chlorophyll a, uncorrected for pheophytin", "Depth, Secchi disk depth", "Temperature, water", "Specific conductance",
+#' "pH", "Dissolved oxygen (DO)".
+#' 
[…]

### 2019-04-18 AnalysisCode/ms1_analyses.Rmd
continued code development

@@
 
+This document organizes for openness and reproducibility analyses of the temporal coherence of interannual variation in lake primary productivity with terrestrial primary productivity in the landscape surrounding the lake.
+
 # Data important and formatting
@@
 lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, tsvars=c("chla"), minmos=3, minobs=3)
-lagoslakes.cln<-cleanAnnualts(lagoslakes.raw) #69 lakes here
+lagoslakes.cln<-cleanAnnualts(lagoslakes.raw) #73 lakes here
 

### 2019-04-18 R Package/aqts/R/fixNamestoLAGOS.R

@@ -1,0 +1,1 @@
+#' Fix variables names to LAGOS conventions

### 2019-04-18 R Package/aqts/R/makeIowaALMannualts.R

@@ -76,7 +76,7 @@ makeIowaALMannualts<-function(almdat, lakechar, getvars, aggfun="gsmean", timesp
           #compute variable
           for(nn in 1:ncol(tmp.yy)){
             if(colnames(tmp.yy)[nn] %in% c("sampledate","LakeName","SampleDate","LakeID")){next}
-            if(nrow(tmp.yy)>=minobs & length(unique(month(tmp.yy$sampledate)))>=minobs){
+            if(nrow(tmp.yy)>=minobs & length(unique(month(tmp.yy$sampledate)))>=minmos){
               ydat<-c(ydat,mean(tmp.yy[,nn], na.rm=TRUE))
             }
             else(ydat<-c(ydat,NA))

### 2019-04-18 R Package/aqts/R/makeLAGOSannualts.R

@@ -89,7 +89,7 @@ makeLAGOSannualts<-function(lakes, tsvars=c("chla"), infovars=NULL, aggfun="gsme
           #compute variable
           for(nn in 1:ncol(tmp.yy)){
             if(colnames(tmp.yy)[nn] %in% c("sampledate","lagoslakeid")){next}
-            if(nrow(tmp.yy)>=minobs & length(unique(month(tmp.yy$sampledate)))>=minobs){
+            if(nrow(tmp.yy)>=minobs & length(unique(month(tmp.yy$sampledate)))>=minmos){
               ydat<-c(ydat,mean(tmp.yy[,nn], na.rm=TRUE))
             }
             else(ydat<-c(ydat,NA))

### 2019-04-18 R Package/aqts/R/makeMNMPCAannualts.R

@@ -20,7 +20,7 @@
 #' and geographic coordinates of lakes, plus any further variables listed in \code{infovars}. Each element of \code{lakedata} corresponds to a lake
 #' in \code{lakes} and is a data frame in which columns are variables in \code{tsvars} and rows correspond to years.
 #' 
-#' Options for \code{infovars} are "Phosphorus as P", "Orthophosphate as P", "Inorganic nitrogen (nitrate and nitrite) as N",
+#' Options for \code{tsvars} are "Phosphorus as P", "Orthophosphate as P", "Inorganic nitrogen (nitrate and nitrite) as N",
 #' "Ammonia-nitrogen as N", "Nitrate as N", "Chloride", "Total suspended solids", "Chlorophyll a, corrected for pheophytin",
 #' "Chlorophyll a, uncorrected for pheophytin", "Depth, Secchi disk depth", "Temperature, water", "Specific conductance",
 #' "pH", "Dissolved oxygen (DO)".
@@ -36,7 +36,7 @@
 
 dir<-"~/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/MN_MPCA"
 
-makeLAGOSannualts<-function(dir, tsvars=c("chla"), infovars=NULL, aggfun="gsmean", timespan=NULL,
+makeLAGOSannualts<-function(dir, tsvars="Chlorophyll a, corrected for pheophytin", infovars=NULL, aggfun="gsmean", timespan=NULL,
                             minmos=3, minobs=5, lagosversion="1.087.1"){
   library(dplyr) #load library dependencies
   library(LAGOSNE)
@@ -46,9 +46,57 @@ makeLAGOSannualts<-function(dir, tsvars=c("chla"), infovars=NULL, aggfun="gsmean
   flist<-list.files(path=dir)
   lagosids<-as.numeric(unlist(regmatches(flist, gregexpr("[[:digit:]]+", flist))))
 
+  lakedata<-list()
+  
   for(ff in 1:length(flist)){
     
+    lakedata.ff<-NULL
+    
     dat.ff<-read.csv(paste(dir,flist[ff],sep="/"),stringsAsFactors = F)
+    dat.ff<-dat.ff[dat.ff$parameter %in% tsvars,colnames(dat.ff) %in% c("parameter","result","sampleDate","resultUnit")]
+    
+    #fix date format and convert to POSICXct
[…]

### 2019-05-14 AnalysisCode/ms1_analyses.Rmd
limno data import functions and code

@@
 
-```{r data import and formatting, echo=TRUE}
+```{r limno import and formatting, echo=TRUE, cache=TRUE}
 
@@
 lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, tsvars=c("chla"), minmos=3, minobs=3)
-lagoslakes.cln<-cleanAnnualts(lagoslakes.raw) #73 lakes here
+lagoslakes.cln<-cleanAnnualts(lagoslakes.raw)
+
+rm(lakes_to_get)
+
+MNMPCAlakes.raw<-makeMNMPCAannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/MN_MPCA",
+                                    minmos=3, minobs=3)
+MNMPCAlakes.raw<-fixNamestoLAGOS(MNMPCAlakes.raw,"Minnesota MPCA")
+MNMPCAlakes.cln<-cleanAnnualts(MNMPCAlakes.raw)
+
+WIDNRlakes.raw<-makeWIDNRannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/WI_DNR",
+                                   minmos=3, minobs=3)
+WIDNRlakes.raw<-fixNamestoLAGOS(WIDNRlakes.raw, "Wisconsin DNR")
+WIDNRlakes.cln<-cleanAnnualts(WIDNRlakes.raw)
+
+analysislakes<-list(lakeinfo=rbind(lagoslakes.cln$lakeinfo,MNMPCAlakes.cln$lakeinfo,WIDNRlakes.cln$lakeinfo),
+                    lakedata<-c(lagoslakes.cln$lakedata, MNMPCAlakes.cln$lakedata, WIDNRlakes.cln$lakedata))
+
+any(duplicated(analysislakes$lakeinfo$lagoslakeid)) #no duplicates
 
 ```
+
+```{r AVHRR data import, echo=TRUE}
+
+#Add the AVHRR data
+
+```

### 2019-05-14 Old/cleanAnnualts.R

@@ -30,9 +30,11 @@
 #' 
 #' @export
 
-cleanAnnualts<-function(indat, ymin=20, maxNA=2, optim="chla", timespan=NULL, fill.method="median"){
+cleanAnnualts<-function(indat, ymin=20, maxNA=2, timespan=NULL, fill.method="median"){
   
-  cleandat<-indat$lakedata
+  library(zoo)
+  
+  cleandat<-indat$lakedat
   cleaninfo<-indat$lakeinfo
   
   droplakes<-NULL
@@ -42,7 +44,6 @@ cleanAnnualts<-function(indat, ymin=20, maxNA=2, optim="chla", timespan=NULL, fi
   for(lind in 1:length(indat$lakedata)){
     
     dat.lind<-indat$lakedata[[lind]]
-    if(maxNA < 1){maxNA<-ceiling(ncol(dat.lind)*maxNA)}
     
     if(all(is.na(dat.lind))){
       droplakes<-c(droplakes,lind)
@@ -54,88 +55,57 @@ cleanAnnualts<-function(indat, ymin=20, maxNA=2, optim="chla", timespan=NULL, fi
                            colnames(dat.lind)<=max(timespan)]
     }
     
-    #Find optimal time series for the focal variable
-    optvar<-dat.lind[rownames(dat.lind)==optim,]
-    rle.opt<-rle(!is.na(optvar))
-    maxsteps<-length(rle.opt$lengths)
-    opt.out<-optvar
+    #Drop leading or trailing NAs
+    dat.lind<-t(na.trim(t(dat.lind),sides="both",is.na="all"))
     
-    nacheck<-function(rle.opt){
-      if(!any(!rle.opt$values)){return(TRUE)}
-      else if(max(rle.opt$lengths[!rle.opt$values])==1){return(TRUE)}
-      else{return(FALSE)}    
+    if(maxNA < 1){maxNA<-ceiling(ncol(dat.lind)*maxNA)}
+    
+    #check for ymin
+    
+    if(diff(range(as.numeric(colnames(dat.lind)))) < (ymin-1)){
+      droplakes<-c(droplakes,lind)
     }
     
-    for(step in 1:maxsteps){
-      if(sum(rle.opt$lengths[rle.opt$values])<(ymin-maxNA)){
-        droplakes<-c(droplakes, lind)
-        break
+    else{
+      #check for max NA
+      dropvars<-NULL
+      for(vind in 1:nrow(dat.lind)){
+        if(sum(is.na(dat.lind[vind,]))>maxNA){
[…]

### 2019-05-14 Old/optimal_ts_dev.R

@@ -2,13 +2,15 @@
 
 
 xx<-rnorm(30)
-xx[1]<-NA
-xx[2]<-NA
-xx[3]<-NA
-xx[6]<-NA
+# xx[1]<-NA
+# xx[2]<-NA
+# xx[3]<-NA
+# xx[6]<-NA
 xx[7]<-NA
 xx[19]<-NA
 #xx[20]<-NA
+xx[28]<-NA
+xx[29]<-NA
 
 plot(xx, type="l")
 
@@ -18,23 +20,25 @@ rle.xx$values
 lmin=20
 max.na=floor(lmin*.1)
 
-## Attempt 2
+## Attempt 3
 rle.xx<-rle(!is.na(xx))
 nsteps<-length(rle.xx$lengths)
+xx.out<-xx
 for(step in 1:nsteps){
   if(sum(rle.xx$lengths[rle.xx$values])<(lmin-max.na)){stop("too few observations")}
   #find out if there are consecutive NAs, and if so take the longer segment
   if(any(rle.xx$lengths[rle.xx$values==FALSE]>1)){
-    cut<-min(which(rle.xx$lengths[rle.xx$values==FALSE]>1))
+    cut<-min(which(rle.xx$lengths>1 & !rle.xx$values))
     end<-length(rle.xx$lengths)
     if(sum(rle.xx$lengths[1:cut]) > sum(rle.xx$lengths[(cut+1):length(rle.xx$lengths)])){
       #take the early segment
-      rle.xx$lengths<-rle.xx$lengths[1:cut]
-      rle.xx$values<-rle.xx$values[1:cut]
+      xx.out<-xx.out[1:sum(rle.xx$lengths[1:(cut-1)])]
+      rle.xx$lengths<-rle.xx$lengths[1:(cut-1)]
+      rle.xx$values<-rle.xx$values[1:(cut-1)]
     }
-    if(sum(rle.xx$lengths[1:cut]) <= sum(rle.xx$lengths[(cut+1):length(rle.xx$lengths)])){
+    else if(sum(rle.xx$lengths[1:cut]) <= sum(rle.xx$lengths[(cut+1):length(rle.xx$lengths)])){
       #take the late segment
-      
+      xx.out<-xx.out[(sum(rle.xx$lengths[1:cut])+1):sum(rle.xx$lengths)]
       rle.xx$lengths<-rle.xx$lengths[(cut+1):end]
[…]

### 2019-05-14 R Package/aqts/R/fixNamestoLAGOS.R

@@ -23,7 +23,7 @@
 fixNamestoLAGOS<-function(datalist, origin){
   
   #Check inputs
-  if(!all(names(datalist) %in% c("lakedata","lakeinfo")){
+  if(!all(names(datalist) %in% c("lakedata","lakeinfo"))){
     stop("invalid datalist object")
   }
   if(length(origin)!=1){
@@ -48,32 +48,51 @@ fixNamestoLAGOS<-function(datalist, origin){
         if(oldnames[vind]=="SRP"){newnames<-c(newnames,"srp")}
         if(oldnames[vind]=="Secchi"){newnames<-c(newnames,"secchi")}
       }
-      rownames(datalist.out$lakedata[[lind]]<-newnames
+      rownames(datalist.out$lakedata[[lind]])<-newnames
     }
 
   }
   
   #Minnesota MPCA
   if(origin=="Minnesota MPCA"){
+    for(lind in 1:length(datalist.out$lakedata)){
     oldnames<-rownames(datalist.out$lakedata[[lind]])
     newnames<-NULL
-    for(vind in 1:length(oldnames)){
-      if(oldnames[vind]=="Chlorophyll a, uncorrected for pheophytin"){
-        warning("using uncorrected Chlorophyll a")
-        newnames<-c(newnames,"chla")
+      for(vind in 1:length(oldnames)){
+        if(oldnames[vind]=="Chlorophyll a, uncorrected for pheophytin"){
+          warning("using uncorrected Chlorophyll a")
+          newnames<-c(newnames,"chla")
+        }
+        if(oldnames[vind]=="Chlorophyll a, corrected for pheophytin"){newnames<-c(newnames, "chla")}
+        if(oldnames[vind]=="Depth, Secchi disk depth"){newnames<-c(newnames, "secchi")}
+        if(oldnames[vind]=="Inorganic nitrogen (nitrate and nitrite) as N"){newnames<-c(newnames, "no2no3")}
+        if(oldnames[vind]=="Kjeldahl nitrogen as N"){newnames<-c(newnames, "tkn")}
+        #if(oldnames[vind]=="Phosphorous as P"){newnames<-c(newnames, "tp")} #<----------------Check this!
+        #if(oldnames[vind]=="Nutrient-nitrogen as N"]){newnames<-c(newnames, "tn")}<-----------Check this!
       }
[…]

### 2019-05-14 R Package/aqts/R/makeWIDNRannualts.R

@@ -32,8 +32,6 @@
 #' 
 #' @export
 
-dir<-"/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/WI_DNR"
- 
 makeWIDNRannualts<-function(dir, tsvars="Chlorophyll.ug.l.", infovars=NULL, aggfun="gsmean", timespan=NULL,
                              minmos=3, minobs=3, lagosversion="1.087.1"){
   library(dplyr) #load library dependencies
@@ -111,4 +109,3 @@ makeWIDNRannualts<-function(dir, tsvars="Chlorophyll.ug.l.", infovars=NULL, aggf
   return(list(lakeinfo=lakeinfo, lakedata=lakedata))  
 }
 
-test<-makeWIDNRannualts(dir)

### 2019-05-20 AnalysisCode/ms1_analyses.Rmd
coherence analyses

--- 2019-04-18 AnalysisCode/ms1_analyses.Rmd
@@
 library(LAGOSNE)
+library(raster)
+library(MuMIn)
+library(dplyr)
+library(nlme)
 
@@
 
-lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, tsvars=c("chla"), minmos=3, minobs=3)
-lagoslakes.cln<-cleanAnnualts(lagoslakes.raw) #73 lakes here
+lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), tsvars=c("chla"), 
+                                  minmos=3, minobs=3, timespan=c(1989,2018))
+lagoslakes.cln<-cleanAnnualts(lagoslakes.raw)
+
+rm(lakes_to_get)
+
+MNMPCAlakes.raw<-makeMNMPCAannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/MN_MPCA",
+                                    infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), minmos=3, minobs=3, timespan=c(1989,2018))
+MNMPCAlakes.raw<-fixNamestoLAGOS(MNMPCAlakes.raw,"Minnesota MPCA")
+MNMPCAlakes.cln<-cleanAnnualts(MNMPCAlakes.raw)
+
+WIDNRlakes.raw<-makeWIDNRannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/WI_DNR",
+                                  infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), minmos=3, minobs=3, timespan=c(1989,2018))
+WIDNRlakes.raw<-fixNamestoLAGOS(WIDNRlakes.raw, "Wisconsin DNR")
+WIDNRlakes.cln<-cleanAnnualts(WIDNRlakes.raw)
+
+analysislakes<-list(lakeinfo=rbind(lagoslakes.cln$lakeinfo,MNMPCAlakes.cln$lakeinfo,WIDNRlakes.cln$lakeinfo),
+                    lakedata=c(lagoslakes.cln$lakedata, MNMPCAlakes.cln$lakedata, WIDNRlakes.cln$lakedata))
+
+any(duplicated(analysislakes$lakeinfo$lagoslakeid)) #no duplicates
 
 ```
+
+```{r AVHRR data import, echo=FALSE, cache=TRUE}
+
+dbuff<-calcBufferDist(sa=analysislakes$lakeinfo$lake_area_ha, ltype=analysislakes$lakeinfo$nhd_ftype, minbuff=2500)
+
+accndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/accvi1989_2018.img")
+maxndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/mxvi1989_2018.img")
+
+nlcdwater<-raster("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/landcover/nlcd2011_cls11.img")
+watermask<-nlcdwater<0.05
+
+accndvi<-mask(accndvi,watermask,maskvalue=0) #mask out pixels that have too much water in them
+maxndvi<-mask(maxndvi,watermask,maskvalue=0)
+
+analysislakes<-addAVHRRannualts(analysislakes, accndvi, dbuff)
+analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)
+
+save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1.RData")
+
+```
+
+```{r examine missing values, echo=TRUE, cache=FALSE}
+any(sapply(analysislakes$lakedata, function(x){any(is.infinite(x))}))
+any(sapply(analysislakes$lakedata, function(x){any(is.na(x))}))
+which(sapply(analysislakes$lakedata, function(x){any(is.na(x))}))
+analysislakes$lakeinfo[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))})),]
+
+image(accndvi)
+points(lakepts.prj[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))})),])
+
+dbuff[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))}))]
+
+analysislakes$lakeinfo<-analysislakes$lakeinfo[!sapply(analysislakes$lakedata, function(x){any(is.na(x))}),]
+analysislakes$lakedata<-analysislakes$lakedata[!sapply(analysislakes$lakedata, function(x){any(is.na(x))})]
+```
+
+```{r compute coherences, echo=TRUE, cache=FALSE}
+
+source("~/GitHub/AquaTerrSynch/AnalysisCode/bandtest_coh.R")
+
+tsranges<-rbind(c(2,4),c(4,Inf),c(2,Inf))
+
+coh.chlaXaccndvi<-NULL
+coh.chlaXmaxndvi<-NULL
+
+for(lind in 1:length(analysislakes$lakedata)){
+  lakedat.ii<-cleandat(analysislakes$lakedata[[lind]], as.numeric(colnames(analysislakes$lakedata[[lind]])), clev=5)$cdat
+  chlaXaccndvi<-coh(lakedat.ii[1,], lakedat.ii[2,], as.numeric(colnames(analysislakes$lakedata[[lind]])),
+                    norm="powall", sigmethod="fast", nrand=10000)
+  chlaXmaxndvi<-coh(lakedat.ii[1,], lakedat.ii[3,], as.numeric(colnames(analysislakes$lakedata[[lind]])),
+                    norm="powall", sigmethod="fast", nrand=10000)
+  for(rind in 1:nrow(tsranges)){
+    chlaXaccndvi<-bandtest.coh(chlaXaccndvi, tsranges[rind,])
+    chlaXmaxndvi<-bandtest.coh(chlaXmaxndvi, tsranges[rind,])
+  }
+  coh.chlaXaccndvi<-rbind(coh.chlaXaccndvi, c(t(as.matrix(chlaXaccndvi$bandp[,3:5]))))
+  coh.chlaXmaxndvi<-rbind(coh.chlaXmaxndvi, c(t(as.matrix(chlaXmaxndvi$bandp[,3:5]))))
+
+}
+
+coh.chlaXaccndvi<-as.data.frame(coh.chlaXaccndvi)
+coh.chlaXmaxndvi<-as.data.frame(coh.chlaXmaxndvi)
+
+colnames(coh.chlaXaccndvi)<-paste0("accndvi",c("p.ts1","phi.ts1","coh.ts1","p.ts2","phi.ts2","coh.ts2","p.ts3","phi.ts3","coh.ts3"))
+colnames(coh.chlaXmaxndvi)<-paste0("maxndvi",c("p.ts1","phi.ts1","coh.ts1","p.ts2","phi.ts2","coh.ts2","p.ts3","phi.ts3","coh.ts3"))
+
+coh.chlaXaccndvi$lagoslakeid<-analysislakes$lakeinfo$lagoslakeid
+coh.chlaXmaxndvi$lagoslakeid<-analysislakes$lakeinfo$lagoslakeid
+
+```
+
+```{r summarize coherences, echo=TRUE, cache=FALSE}
+#short timescales
+hist(coh.chlaXaccndvi$accndvicoh.ts1)
+hist(coh.chlaXmaxndvi$maxndvicoh.ts1)
+
+quantile(coh.chlaXaccndvi$accndvip.ts1)
+quantile(coh.chlaXmaxndvi$maxndvip.ts1)
+
+alpha=0.05
+sum(coh.chlaXaccndvi$accndvip.ts1<alpha)/nrow(coh.chlaXaccndvi)
+sum(coh.chlaXmaxndvi$maxndvip.ts1<alpha)/nrow(coh.chlaXmaxndvi)
+
+print(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<alpha]/pi) #only pattern is that lakes don't lead the landscape
+print(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<alpha]/pi)
+
+#long timescales
+hist(coh.chlaXaccndvi$accndvicoh.ts2)
+hist(coh.chlaXmaxndvi$maxndvicoh.ts2)
+
+quantile(coh.chlaXaccndvi$accndvip.ts2)
+quantile(coh.chlaXmaxndvi$maxndvip.ts2)
+
+alpha=0.05
+sum(coh.chlaXaccndvi$accndvip.ts2<alpha)/nrow(coh.chlaXaccndvi)
+sum(coh.chlaXmaxndvi$maxndvip.ts2<alpha)/nrow(coh.chlaXmaxndvi)
+
+print(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<alpha]/pi)
+print(coh.chlaXmaxndvi$maxndviphi.ts2[coh.chlaXmaxndvi$maxndvip.ts2<alpha]/pi)
+
+#all timescales
+hist(coh.chlaXaccndvi$accndvicoh.ts3)
+hist(coh.chlaXmaxndvi$maxndvicoh.ts3)
+
+quantile(coh.chlaXaccndvi$accndvip.ts3)
+quantile(coh.chlaXmaxndvi$maxndvip.ts3)
+
+alpha=0.05
+sum(coh.chlaXaccndvi$accndvip.ts3<alpha)/nrow(coh.chlaXaccndvi)
+sum(coh.chlaXmaxndvi$maxndvip.ts3<alpha)/nrow(coh.chlaXmaxndvi)
+
+print(coh.chlaXaccndvi$accndviphi.ts3[coh.chlaXaccndvi$accndvip.ts3<alpha]/pi)
+print(coh.chlaXmaxndvi$maxndviphi.ts3[coh.chlaXmaxndvi$maxndvip.ts3<alpha]/pi)
+
+```
+
+```{r add vars for modelling, echo=TRUE, cache=FALSE}
+
+#Need to add: depth, average growing season Chlorophyll-a, TSI(chla) categories, pct ag
+
+#agriculture -- is 500m buffer best? Other options include 100m buffer (probably too small) and hu12 watershed
+pct.ag<-lagosne_select(table="buffer500m.lulc", vars=c("lagoslakeid","buffer500m_nlcd2001_pct_82","buffer500m_nlcd2006_pct_82","buffer500m_nlcd2011_pct_82"))
+pct.ag<-pct.ag[pct.ag$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
+pct.ag.avg<-data.frame(lagoslakeid=pct.ag$lagoslakeid, pct.ag=rowMeans(pct.ag[,2:4]))
+
+#depth
+depth<-lagosne_select(table="lakes_limno", vars=c("lagoslakeid","maxdepth"))
+depth<-depth[depth$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,] #use max depth because it's more complete
+
+#growing season Chlorophyll-a
+chla<-lagosne_select(table="epi_nutr", vars=c("lagoslakeid","samplemonth","chla"))
+chla<-chla[chla$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
+gs.chla<-chla[chla$samplemonth %in% 5:9,]
+avg.chla<-aggregate(chla ~ lagoslakeid, data=gs.chla, FUN=mean, na.rm=T)
+
+#Chlorophyll-a TSI class
+#TSI(CHL) = 9.81 ln(CHL) + 30.6
+tsi.chl<-data.frame(lagoslakeid=avg.chla$lagoslakeid, tsi=9.81 * log(avg.chla$chla) + 30.6)
+tsi.chl$tsi.cat<-rep("lake",nrow(tsi.chl))
+
+tsi.chl$tsi.cat[tsi.chl$tsi < 40]<-"oligotrophic"
+tsi.chl$tsi.cat[tsi.chl$tsi >=40 & tsi.chl$tsi < 50]<-"mesotrophic"
+tsi.chl$tsi.cat[tsi.chl$tsi >=50 & tsi.chl$tsi < 70]<-"eutrophic"
+tsi.chl$tsi.cat[tsi.chl$tsi >= 70] <-"hypereutrophic"
+
+#huc2 and huc4 watershed codes
+huc_codes<-read.csv("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
+
+predictors<-analysislakes$lakeinfo
+predictors$tslength<-predictors$end-predictors$start+1
+predictors<-left_join(predictors, depth, by="lagoslakeid")
+predictors<-left_join(predictors, pct.ag.avg, by="lagoslakeid")
+predictors<-left_join(predictors, avg.chla, by="lagoslakeid")
+predictors<-left_join(predictors, tsi.chl, by="lagoslakeid")
+predictors<-left_join(predictors, huc_codes, by="hu4_zoneid")
+
+modvars.accndvi<-left_join(predictors, coh.chlaXaccndvi, by="lagoslakeid")
+modvars.accndvi$nhd_ftype<-factor(modvars.accndvi$nhd_ftype)
+modvars.accndvi$tsi.cat<-factor(modvars.accndvi$tsi.cat)
+```
+
+```{r linear modelling, echo=TRUE, cache=FALSE}
+
+modvars.accndvi<-modvars.accndvi[!is.na(modvars.accndvi$maxdepth),]
+modvars.accndvi<-modvars.accndvi[!is.na(modvars.accndvi$pct.ag),]
+
+#short timescales
+fm.coh.accndvi.st<-gls(accndvicoh.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+                       correlation=corExp(form = ~ nhd_lat + nhd_long))
+dredge.coh.accndvi.st<-dredge(fm.coh.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+print(dredge.coh.accndvi.st)
+
+fm.p.accndvi.st<-gls(accndvip.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+                       correlation=corExp(form = ~ nhd_lat + nhd_long))
+dredge.p.accndvi.st<-dredge(fm.p.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+print(dredge.p.accndvi.st)
+
+#long timescales
+fm.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+                       correlation=corExp(form = ~ nhd_lat + nhd_long))
+dredge.coh.accndvi.lt<-dredge(fm.coh.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+print(dredge.coh.accndvi.lt)
+
+fm.p.accndvi.lt<-gls(accndvip.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+                       correlation=corExp(form = ~ nhd_lat + nhd_long))
+dredge.p.accndvi.lt<-dredge(fm.p.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+print(dredge.p.accndvi.lt)
+```

### 2019-05-20 AnalysisCode/DataExploration/huc_codes.R

@@ -1,0 +1,9 @@
+load(url("https://github.com/limnoliver/CSI-Nutrient-Time-Series/blob/72c8269902e53c7ec6a2cfbe13a0239d13062dc8/Data/huc4.RData?raw=true"))
+plot(huc4, lty = 1, lwd=1, border=TRUE, col = "lightgray")
+head(huc4@data)
+
+out<-data.frame(hu4_zoneid=huc4@data$ZoneID, huc4_code=as.character(huc4@data$HUC4), huc2_code=as.character(substr(huc4@data$HUC4,1,2)))
+
+write.csv(out, "~/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", row.names=FALSE)
+
+test<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')

### 2019-05-20 R Package/aqts/R/addAVHRRannualts.R

@@ -24,7 +24,7 @@
 #' 
 #' @export
 
-makeAVHRRannualts<-function(lakelist, avhrrdata, buffdist=5000, aggfun="mean"){
+addAVHRRannualts<-function(lakelist, avhrrdata, buffdist=5000, aggfun="mean"){
   
   library(raster)
   library(rgdal)
@@ -33,29 +33,34 @@ makeAVHRRannualts<-function(lakelist, avhrrdata, buffdist=5000, aggfun="mean"){
   lakeinfo<-lakelist$lakeinfo
   lakedata<-lakelist$lakedata
   
-  #make lake points and buffer
+  if(length(buffdist)==1){buffdist<-rep(buffdist, nrow(lakelist$lakeinfo))}
+  if(length(buffdist)!=nrow(lakelist$lakeinfo)){
+    stop("length(buffdist) must be 1 or equal to the number of lakes")
+  }
+  
+  #make lake points 
   lakepts<-SpatialPoints(coords=data.frame(x=lakeinfo$nhd_long,y=lakeinfo$nhd_lat),
                             proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs"))
   avhrrproj<-crs(avhrrdata)
   lakepts.prj<-spTransform(lakepts, avhrrproj)
-  lakebuffer<-buffer(lakepts.prj, width=buffdist, dissolve=FALSE)
+  
   
   #loop through lakes and extract AVHRR time series
   for(ii in 1:nrow(lakeinfo)){
-    lakebuffer.ii<-lakebuffer[ii,]
-    avhrrstack.ii<-mask(avhrrdata,lakebuffer.ii)
+    lakebuffer.ii<-buffer(lakepts.prj[ii,], width=buffdist[ii], dissolve=FALSE)
+    #avhrrstack.ii<-mask(avhrrdata,lakebuffer.ii)
     
     if(!aggfun %in% c("mean","median")){stop("aggfun argument must be 'mean' or 'median'.")}
     else if(aggfun=="mean"){
-      ts.ii<-cellStats(avhrrstack.ii, mean, na.rm=TRUE)
+      ts.ii<-cellStats(avhrrdata, mean, na.rm=TRUE)
     }
     else if(aggfun=="median"){
-      ts.ii<-cellStats(avhrrstack.ii, median, na.rm=TRUE)
[…]

### 2019-05-20 R Package/aqts/R/calcBufferDist.R

@@ -1,0 +1,42 @@
+#' Create annualized time series from the LAGOSNE database
+#' 
+#' \code{calcBufferDist} calculates a buffer distance based on lake surface area
+#' 
+#' @param sa a numeric vector of lake surface areas (hectares)
+#' @param ltype lake type; see details
+#' @param minbuff the minimum buffer radius (meters)
+#' 
+#' @return \code{calcBufferDist} returns a numeric vector of buffer distances (meters)
+#' 
+#' @details Computed buffer distances are based on a log-linear relationship between lake surface area and watershed area,
+#' parameterized on empirical data (Walter, et al., unpublished data) with a further simplifying assumption that lakes are circular. 
+#' Setting a minimum buffer radius is useful for cases when lakes are small relative to the grain size of satellite data.
+#' 
+#' @author Jonathan Walter, \email{jaw3es@@virginia.edu}
+#' 
+#' @seealso \code{\link{makeIowaALMannualts},\link{addAVHRRannualts}}
+#' 
+#' @examples
+#' #need to add some
+#' 
+#' @export
+
+calcBufferDist<-function(sa, ltype, minbuff=2500){
+  
+  out<-rep(NA, length(sa))
+  for(ii in 1:length(sa)){
+    if(ltype[ii]==436){#reservoirs
+      wa.ii = (10^(1.8 + 1.05*log10(sa[ii])))*10000 #watershed area in square meters
+      buff.ii = sqrt(wa.ii/pi)
+    }
+    
+    if(ltype[ii]==390){#lakes
+      wa.ii = (10^(1.4 + 1.05*log10(sa[ii])))*10000
+      buff.ii = sqrt(wa.ii/pi)
+    }
+    out[ii]<-buff.ii
+  }
+  
+  out[out<minbuff]<-minbuff
+  return(out)
+}

### 2019-05-21 AnalysisCode/ms1_analyses.Rmd
ms1 analyses v1 not so good

@@
 
-# Data important and formatting
+# Data import
 
-```{r limno import and formatting, echo=TRUE, cache=TRUE}
+Data produced in 'ms1_prep.Rmd' are loaded.
 
-lakes_to_get<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/lakes20yrs_chla.csv")$x
+```{r load workspace, echo=TRUE, cache=FALSE}
 
-lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), tsvars=c("chla"), 
-                                  minmos=3, minobs=3, timespan=c(1989,2018))
-lagoslakes.cln<-cleanAnnualts(lagoslakes.raw)
-
-rm(lakes_to_get)
-
-MNMPCAlakes.raw<-makeMNMPCAannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/MN_MPCA",
-                                    infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), minmos=3, minobs=3, timespan=c(1989,2018))
-MNMPCAlakes.raw<-fixNamestoLAGOS(MNMPCAlakes.raw,"Minnesota MPCA")
-MNMPCAlakes.cln<-cleanAnnualts(MNMPCAlakes.raw)
-
-WIDNRlakes.raw<-makeWIDNRannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/WI_DNR",
-                                  infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), minmos=3, minobs=3, timespan=c(1989,2018))
-WIDNRlakes.raw<-fixNamestoLAGOS(WIDNRlakes.raw, "Wisconsin DNR")
-WIDNRlakes.cln<-cleanAnnualts(WIDNRlakes.raw)
-
-analysislakes<-list(lakeinfo=rbind(lagoslakes.cln$lakeinfo,MNMPCAlakes.cln$lakeinfo,WIDNRlakes.cln$lakeinfo),
-                    lakedata=c(lagoslakes.cln$lakedata, MNMPCAlakes.cln$lakedata, WIDNRlakes.cln$lakedata))
-
-any(duplicated(analysislakes$lakeinfo$lagoslakeid)) #no duplicates
-
-```
-
-```{r AVHRR data import, echo=FALSE, cache=TRUE}
-
-dbuff<-calcBufferDist(sa=analysislakes$lakeinfo$lake_area_ha, ltype=analysislakes$lakeinfo$nhd_ftype, minbuff=2500)
-
-accndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/accvi1989_2018.img")
-maxndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/mxvi1989_2018.img")
-
-nlcdwater<-raster("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/landcover/nlcd2011_cls11.img")
-watermask<-nlcdwater<0.05
-
-accndvi<-mask(accndvi,watermask,maskvalue=0) #mask out pixels that have too much water in them
-maxndvi<-mask(maxndvi,watermask,maskvalue=0)
-
-analysislakes<-addAVHRRannualts(analysislakes, accndvi, dbuff)
-analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)
-
-save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1.RData")
+load("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1.RData")
 
@@
 
-image(accndvi)
-points(lakepts.prj[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))})),])
+# image(accndvi)
+# points(lakepts.prj[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))})),])
 
@@
 
-```{r compute coherences, echo=TRUE, cache=FALSE}
+```{r compute coherences, echo=TRUE, cache=TRUE}
 
@@
 modvars.accndvi$tsi.cat<-factor(modvars.accndvi$tsi.cat)
+modvars.accndvi$tslength<-modvars.accndvi$end-modvars.accndvi$start + 1
 ```
@@
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(fm.coh.accndvi.st)
 dredge.coh.accndvi.st<-dredge(fm.coh.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
-print(dredge.coh.accndvi.st)
+print(head(dredge.coh.accndvi.st))
 
-fm.p.accndvi.st<-gls(accndvip.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+fm.p.accndvi.st<-gls(accndvip.ts1 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(fm.p.accndvi.st)
 dredge.p.accndvi.st<-dredge(fm.p.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
-print(dredge.p.accndvi.st)
+print(head(dredge.p.accndvi.st))
+
+fm.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+                       correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(fm.phi.accndvi.st)
+dredge.phi.accndvi.st<-dredge(fm.phi.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+print(head(dredge.phi.accndvi.st))
 
@@
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(fm.coh.accndvi.lt)
 dredge.coh.accndvi.lt<-dredge(fm.coh.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
-print(dredge.coh.accndvi.lt)
+print(head(dredge.coh.accndvi.lt))
 
-fm.p.accndvi.lt<-gls(accndvip.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+fm.p.accndvi.lt<-gls(accndvip.ts2 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(fm.p.accndvi.lt)
 dredge.p.accndvi.lt<-dredge(fm.p.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
-print(dredge.p.accndvi.lt)
+print(head(dredge.p.accndvi.lt))
+
+fm.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+                       correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(fm.phi.accndvi.lt)
+dredge.phi.accndvi.lt<-dredge(fm.phi.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+print(head(dredge.phi.accndvi.lt))
 ```

### 2019-05-21 AnalysisCode/ms1_prep.Rmd
ms1 analyses v1 not so good

---
title: 'Q1: Are lake and terrestrial primary productivity coherent?'
author: "Jonathan Walter, Grace Wilkinson, Rachel Fleck, Michael Pace"
date: "4/17/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(aqts)
library(wsyn)
library(rgdal)
library(LAGOSNE)
library(raster)
library(MuMIn)
library(dplyr)
library(nlme)

rm(list=ls())

```

This document organizes for openness and reproducibility analyses of the temporal coherence of interannual variation in lake primary productivity with terrestrial primary productivity in the landscape surrounding the lake.

# Data important and formatting

```{r limno import and formatting, echo=TRUE, cache=TRUE}

lakes_to_get<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/lakes20yrs_chla.csv")$x

lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), tsvars=c("chla"), 
                                  minmos=3, minobs=3, timespan=c(1989,2018))
lagoslakes.cln<-cleanAnnualts(lagoslakes.raw)

rm(lakes_to_get)

MNMPCAlakes.raw<-makeMNMPCAannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/MN_MPCA",
                                    infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), minmos=3, minobs=3, timespan=c(1989,2018))
MNMPCAlakes.raw<-fixNamestoLAGOS(MNMPCAlakes.raw,"Minnesota MPCA")
MNMPCAlakes.cln<-cleanAnnualts(MNMPCAlakes.raw)

WIDNRlakes.raw<-makeWIDNRannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/WI_DNR",
                                  infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), minmos=3, minobs=3, timespan=c(1989,2018))
WIDNRlakes.raw<-fixNamestoLAGOS(WIDNRlakes.raw, "Wisconsin DNR")
WIDNRlakes.cln<-cleanAnnualts(WIDNRlakes.raw)

analysislakes<-list(lakeinfo=rbind(lagoslakes.cln$lakeinfo,MNMPCAlakes.cln$lakeinfo,WIDNRlakes.cln$lakeinfo),
                    lakedata=c(lagoslakes.cln$lakedata, MNMPCAlakes.cln$lakedata, WIDNRlakes.cln$lakedata))

any(duplicated(analysislakes$lakeinfo$lagoslakeid)) #no duplicates

```

```{r AVHRR data import, echo=FALSE, cache=FALSE}

dbuff<-calcBufferDist(sa=analysislakes$lakeinfo$lake_area_ha, ltype=analysislakes$lakeinfo$nhd_ftype, minbuff=2500)

accndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/accvi1989_2018.img")
maxndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/mxvi1989_2018.img")

nlcdwater<-raster("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/landcover/nlcd2011_cls11.img")
watermask<-nlcdwater<0.05

accndvi<-mask(accndvi,watermask,maskvalue=0) #mask out pixels that have too much water in them
maxndvi<-mask(maxndvi,watermask,maskvalue=0)

analysislakes<-addAVHRRannualts(analysislakes, accndvi, dbuff)
analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)

save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1.RData")

```

### 2019-05-21 AnalysisCode/ms1_analyses.Rmd
ms1 analyses v2 slightly better

@@
 library(nlme)
+library(lmerTest)
 
@@
 #short timescales
-hist(coh.chlaXaccndvi$accndvicoh.ts1)
-hist(coh.chlaXmaxndvi$maxndvicoh.ts1)
+hist(coh.chlaXaccndvi$accndvicoh.ts1, main="Accumulated NDVI, short timescales", xlab="Coherence", ylab="Frequency")
+hist(coh.chlaXmaxndvi$maxndvicoh.ts1, main="Maximum NDVI, short timescales", xlab="Coherence", ylab="Frequency")
 
-quantile(coh.chlaXaccndvi$accndvip.ts1)
-quantile(coh.chlaXmaxndvi$maxndvip.ts1)
+quantile(coh.chlaXaccndvi$accndvicoh.ts1)
+quantile(coh.chlaXmaxndvi$maxndvicoh.ts1)
 
@@
 
+phicls<-c(-1,-.75,-0.25,0.25,0.75,1)
+
+hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.2]/pi, main="Accumulated NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
+#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<0.2]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
+
 #long timescales
-hist(coh.chlaXaccndvi$accndvicoh.ts2)
-hist(coh.chlaXmaxndvi$maxndvicoh.ts2)
+hist(coh.chlaXaccndvi$accndvicoh.ts2, main="Accumulated NDVI, long timescales", xlab="Coherence", ylab="Frequency")
+hist(coh.chlaXmaxndvi$maxndvicoh.ts2, main="Maximum NDVI, long timescales", xlab="Coherence", ylab="Frequency")
 
-quantile(coh.chlaXaccndvi$accndvip.ts2)
-quantile(coh.chlaXmaxndvi$maxndvip.ts2)
+quantile(coh.chlaXaccndvi$accndvicoh.ts2)
+quantile(coh.chlaXmaxndvi$maxndvicoh.ts2)
 
@@
 
-#all timescales
-hist(coh.chlaXaccndvi$accndvicoh.ts3)
-hist(coh.chlaXmaxndvi$maxndvicoh.ts3)
-
-quantile(coh.chlaXaccndvi$accndvip.ts3)
-quantile(coh.chlaXmaxndvi$maxndvip.ts3)
-
-alpha=0.05
-sum(coh.chlaXaccndvi$accndvip.ts3<alpha)/nrow(coh.chlaXaccndvi)
-sum(coh.chlaXmaxndvi$maxndvip.ts3<alpha)/nrow(coh.chlaXmaxndvi)
-
-print(coh.chlaXaccndvi$accndviphi.ts3[coh.chlaXaccndvi$accndvip.ts3<alpha]/pi)
-print(coh.chlaXmaxndvi$maxndviphi.ts3[coh.chlaXmaxndvi$maxndvip.ts3<alpha]/pi)
+hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts2<0.2]/pi, main="Accumulated NDVI, long timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
+#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvicoh.ts2>0.6]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
 
@@
 modvars.accndvi$tslength<-modvars.accndvi$end-modvars.accndvi$start + 1
-```
-
-```{r linear modelling, echo=TRUE, cache=FALSE}
 
@@
 
+modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.2,]
+modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.2,]
+```
+
+```{r gls modelling, echo=TRUE, cache=FALSE}
 #short timescales
-fm.coh.accndvi.st<-gls(accndvicoh.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(fm.coh.accndvi.st)
-dredge.coh.accndvi.st<-dredge(fm.coh.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+summary(gls.coh.accndvi.st)
+dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
 print(head(dredge.coh.accndvi.st))
 
-fm.p.accndvi.st<-gls(accndvip.ts1 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+gls.p.accndvi.st<-gls(accndvip.ts1 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(fm.p.accndvi.st)
-dredge.p.accndvi.st<-dredge(fm.p.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+summary(gls.p.accndvi.st)
+dredge.p.accndvi.st<-dredge(gls.p.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
 print(head(dredge.p.accndvi.st))
 
-fm.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
-                       correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(fm.phi.accndvi.st)
-dredge.phi.accndvi.st<-dredge(fm.phi.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+gls.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ maxdepth + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi.phist) #remove ftype b/c only lakes
+summary(gls.phi.accndvi.st)
+dredge.phi.accndvi.st<-dredge(gls.phi.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
 print(head(dredge.phi.accndvi.st))
@@
 #long timescales
-fm.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(fm.coh.accndvi.lt)
-dredge.coh.accndvi.lt<-dredge(fm.coh.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+summary(gls.coh.accndvi.lt)
+dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
 print(head(dredge.coh.accndvi.lt))
 
-fm.p.accndvi.lt<-gls(accndvip.ts2 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+gls.p.accndvi.lt<-gls(accndvip.ts2 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(fm.p.accndvi.lt)
-dredge.p.accndvi.lt<-dredge(fm.p.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+summary(gls.p.accndvi.lt)
+dredge.p.accndvi.lt<-dredge(gls.p.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
 print(head(dredge.p.accndvi.lt))
 
-fm.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+gls.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi.philt,
                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(fm.phi.accndvi.lt)
-dredge.phi.accndvi.lt<-dredge(fm.phi.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+summary(gls.phi.accndvi.lt)
+dredge.phi.accndvi.lt<-dredge(gls.phi.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
 print(head(dredge.phi.accndvi.lt))
 ```
+
+GLS models sucked, but inspection of results suggested that mixed effects models with random effects of region on the intercept may likely be an improvement.
+
+```{r mixed modelling, echo=TRUE, cache=FALSE}
+lme.coh.accndvi.st<-lmer(accndvicoh.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi, na.action="na.fail")
+summary(lme.coh.accndvi.st)
+dredge.coh.accndvi.st<-dredge(lme.coh.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+print(head(dredge.coh.accndvi.st))
+
+lme.p.accndvi.st<-lmer(accndvip.ts1 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi, na.action="na.fail")
+summary(lme.p.accndvi.st)
+dredge.p.accndvi.st<-dredge(lme.p.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+print(head(dredge.p.accndvi.st))
+
+lme.phi.accndvi.st<-lmer(accndviphi.ts1 ~ maxdepth + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi.phist, na.action="na.fail")
+summary(lme.phi.accndvi.st)
+dredge.phi.accndvi.st<-dredge(lme.phi.accndvi.st, beta="sd") #model with TSI is unconvincingly better than intercept-only (dAIC = 0.92)
+print(head(dredge.phi.accndvi.st))
+
+lme.coh.accndvi.lt<-lmer(accndvicoh.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi, na.action="na.fail")
+summary(lme.coh.accndvi.lt)
+dredge.coh.accndvi.lt<-dredge(lme.coh.accndvi.lt, beta="sd") #lake type is marginal improvement over intercept only (dAIC = 0.1)
+print(head(dredge.coh.accndvi.lt))
+
+lme.p.accndvi.lt<-lmer(accndvip.ts2 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi, na.action="na.fail")
+summary(lme.p.accndvi.lt)
+dredge.p.accndvi.lt<-dredge(lme.p.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+print(head(dredge.p.accndvi.lt))
+
+lme.phi.accndvi.lt<-lmer(accndviphi.ts2 ~ maxdepth + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi.philt, na.action="na.fail")
+summary(lme.phi.accndvi.lt)
+dredge.phi.accndvi.lt<-dredge(lme.phi.accndvi.lt, beta="sd") #model with TSI is unconvincingly better than intercept-only (dAIC = 0.92)
+print(head(dredge.phi.accndvi.lt))
+
+```
+
+Adding random effects of huc2 region on intercept helped somewhat. Some possibilities are to add more detailed lake type classes, and to model 2-3 regions separately.

### 2019-05-30 AnalysisCode/ms1_analyses.Rmd
add maps to analyses

@@
 library(lmerTest)
+library(viridis)
+library(fields)
 
@@
 
+```{r mapping, echo=TRUE, cache=FALSE}
+
+states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020.shp")
+getstates<-c("Minnesota", "Iowa", "Wisconsin", "Illinois", "Missouri", "Michigan", "Indiana", "Ohio", "Pennsylvania", "New York", "New Jersey", "Connecticut", "New Hampshire", "Rhode Island", "Massachusetts", "Vermont", "Maine")
+lagosstates<-states[states@data$STATE %in% getstates,]
+
+plot(lagosstates, main="Lakes selected for analysis")
+points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=16, cex=1, col="blue")
+
+cohplotdata<-left_join(analysislakes$lakeinfo, coh.chlaXaccndvi, by="lagoslakeid")
+
+pal<-viridis(100)
+
+par(mar=c(1,0,2,0))
+
+plot(lagosstates, main="Lakes by short timescale coherence")
+points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
+colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)
+
+plot(lagosstates, main="Lakes by long timescale coherence")
+points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
+colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)
+
+```
+
 ```{r add vars for modelling, echo=TRUE, cache=FALSE}
@@
 pct.ag<-lagosne_select(table="buffer500m.lulc", vars=c("lagoslakeid","buffer500m_nlcd2001_pct_82","buffer500m_nlcd2006_pct_82","buffer500m_nlcd2011_pct_82"))
+# pct.ag<-lagosne_select(table="hu12.lulc", vars=c("lagoslakeid","hu12_nlcd2001_pct_82","hu12_nlcd2006_pct_82","hu12_nlcd2011_pct_82"))
 pct.ag<-pct.ag[pct.ag$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
@@
 summary(gls.coh.accndvi.st)
-dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.coh.accndvi.st))
@@
 summary(gls.p.accndvi.st)
-dredge.p.accndvi.st<-dredge(gls.p.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+suppressWarnings(dredge.p.accndvi.st<-dredge(gls.p.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.p.accndvi.st))
@@
 summary(gls.phi.accndvi.st)
-dredge.phi.accndvi.st<-dredge(gls.phi.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+suppressWarnings(dredge.phi.accndvi.st<-dredge(gls.phi.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.phi.accndvi.st))
@@
 summary(gls.coh.accndvi.lt)
-dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.coh.accndvi.lt))
@@
 summary(gls.p.accndvi.lt)
-dredge.p.accndvi.lt<-dredge(gls.p.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+suppressWarnings(dredge.p.accndvi.lt<-dredge(gls.p.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.p.accndvi.lt))
@@
 summary(gls.phi.accndvi.lt)
-dredge.phi.accndvi.lt<-dredge(gls.phi.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+suppressWarnings(dredge.phi.accndvi.lt<-dredge(gls.phi.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.phi.accndvi.lt))
@@
 summary(lme.coh.accndvi.st)
-dredge.coh.accndvi.st<-dredge(lme.coh.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+suppressWarnings(dredge.coh.accndvi.st<-dredge(lme.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.coh.accndvi.st))
@@
 summary(lme.p.accndvi.st)
-dredge.p.accndvi.st<-dredge(lme.p.accndvi.st, beta="sd") #intercept only is best model. Disappointing.
+suppressWarnings(dredge.p.accndvi.st<-dredge(lme.p.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.p.accndvi.st))
@@
 summary(lme.phi.accndvi.st)
-dredge.phi.accndvi.st<-dredge(lme.phi.accndvi.st, beta="sd") #model with TSI is unconvincingly better than intercept-only (dAIC = 0.92)
+suppressWarnings(dredge.phi.accndvi.st<-dredge(lme.phi.accndvi.st, beta="sd")) #model with TSI is unconvincingly better than intercept-only (dAIC = 0.92)
 print(head(dredge.phi.accndvi.st))
@@
 summary(lme.coh.accndvi.lt)
-dredge.coh.accndvi.lt<-dredge(lme.coh.accndvi.lt, beta="sd") #lake type is marginal improvement over intercept only (dAIC = 0.1)
+suppressWarnings(dredge.coh.accndvi.lt<-dredge(lme.coh.accndvi.lt, beta="sd")) #lake type is marginal improvement over intercept only (dAIC = 0.1)
 print(head(dredge.coh.accndvi.lt))
@@
 summary(lme.p.accndvi.lt)
-dredge.p.accndvi.lt<-dredge(lme.p.accndvi.lt, beta="sd") #intercept only is best model. Disappointing.
+suppressWarnings(dredge.p.accndvi.lt<-dredge(lme.p.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.p.accndvi.lt))
@@
 summary(lme.phi.accndvi.lt)
-dredge.phi.accndvi.lt<-dredge(lme.phi.accndvi.lt, beta="sd") #model with TSI is unconvincingly better than intercept-only (dAIC = 0.92)
+suppressWarnings(dredge.phi.accndvi.lt<-dredge(lme.phi.accndvi.lt, beta="sd")) #model with TSI is unconvincingly better than intercept-only (dAIC = 0.92)
 print(head(dredge.phi.accndvi.lt))

### 2019-05-30 AnalysisCode/ThinkPiece/displayItems.R
rough think piece display items

@@ -12,11 +12,52 @@ y1<-b1*tt-mean(b1*tt)
 plot(y1,type="l")
 
 #10-year oscillation
-p1<-10
+p1<-11
 y2<-sin(seq(0,2*pi*(max(tt)/p1),length.out=length(tt)))
 plot(y2, type="l")
 
 #4-year oscillation
-p2<-4
+p2<-3
 y3<-sin(seq(0,2*pi*(max(tt)/p2),length.out=length(tt)))
 plot(y3, type="l")
+
+#white noise
+sig<-0.1
+y4<-rnorm(length(tt),0,sig)
+
+plot(tt,y1+y2+y3+y4, type="l")
+
+png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/ThinkPiece/superimposed_signals_v1.png", units="in",
+    height=5, width=3.25, res=300)
+
+par(mfrow=c(4,1), mar=c(2,4,0,1), xpd=T, oma=c(2,0,1,0))
+plot(tt,y1+y2+y3+y4, type="l",xaxt="n", xlab="")
+axis(1,at=c(1,5,10,15,20,25,30),labels=FALSE)
+plot(tt,y1,type="l",xaxt="n",xlab="")
+axis(1,at=c(1,5,10,15,20,25,30),labels=FALSE)
+plot(tt,y2,type="l",xaxt="n",xlab="")
+axis(1,at=c(1,5,10,15,20,25,30),labels=FALSE)
+plot(tt,y3,type="l",xaxt="n",xlab="")
+axis(1,at=c(1,5,10,15,20,25,30),labels=TRUE)
+mtext("Timestep",1,outer=T,cex=0.8,line=0.4)
+
+dev.off()
+
+
+## 2. A long-timescale oscillation where if you catch a particular few years you get a very different answer.
+
+p3<-12
+res=0.1
+tmax=20
+tt<-seq(1,tmax,length.out=tmax/res)
+
+y5<-sin(seq(0,2*pi*(tmax/p3), length.out=tmax/res))
+
+plot(tt,y5,type="l")
+
+rect(4,-1.05,7,1.05)
+rect(8,-1.05,11,1.05)
+rect(12,-1.05,15,1.05)
+
+lm.w1<-lm(y5[tt>4&tt<7]~tt[tt>4&tt<7])
+lm.w2<-lm(y5[tt>8&tt<11]~tt[tt>8&tt<11])        

### 2019-05-30 AnalysisCode/ThinkPiece/displayItems.R
minor think peice display item changes

@@ -53,11 +53,21 @@ tt<-seq(1,tmax,length.out=tmax/res)
 
 y5<-sin(seq(0,2*pi*(tmax/p3), length.out=tmax/res))
 
-plot(tt,y5,type="l")
+png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/ThinkPiece/cycle_trends_v1.png", units="in",
+    height=2.5, width=6.5, res=300)
+par(mar=c(4,2.5,2,2), mgp=c(2,0.8,0))
+plot(tt,y5,type="l", ylab="", xlab="Timestep")
 
-rect(4,-1.05,7,1.05)
-rect(8,-1.05,11,1.05)
-rect(12,-1.05,15,1.05)
+rect(4,-1.05,7,1.05, border="grey")
+rect(8,-1.05,11,1.05, border="grey")
+rect(12,-1.05,15,1.05, border="grey")
 
 lm.w1<-lm(y5[tt>4&tt<7]~tt[tt>4&tt<7])
 lm.w2<-lm(y5[tt>8&tt<11]~tt[tt>8&tt<11])        
+lm.w3<-lm(y5[tt>12&tt<15]~tt[tt>12&tt<15])
+
+lines(tt[tt>4&tt<7], predict(lm.w1), col="red")
+lines(tt[tt>8&tt<11], predict(lm.w2), col="red")
+lines(tt[tt>12&tt<15], predict(lm.w3), col="red")
+
+dev.off()

### 2019-06-05 AnalysisCode/ms1_analyses.Rmd
ms1 result updates by region

@@
 
-```{r compute coherences, echo=TRUE, cache=TRUE}
+```{r compute coherences, echo=TRUE, cache=FALSE}
 
@@
 #agriculture -- is 500m buffer best? Other options include 100m buffer (probably too small) and hu12 watershed
-pct.ag<-lagosne_select(table="buffer500m.lulc", vars=c("lagoslakeid","buffer500m_nlcd2001_pct_82","buffer500m_nlcd2006_pct_82","buffer500m_nlcd2011_pct_82"))
-# pct.ag<-lagosne_select(table="hu12.lulc", vars=c("lagoslakeid","hu12_nlcd2001_pct_82","hu12_nlcd2006_pct_82","hu12_nlcd2011_pct_82"))
-pct.ag<-pct.ag[pct.ag$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
-pct.ag.avg<-data.frame(lagoslakeid=pct.ag$lagoslakeid, pct.ag=rowMeans(pct.ag[,2:4]))
+# pct.ag<-lagosne_select(table="buffer500m.lulc", vars=c("lagoslakeid","buffer500m_nlcd2001_pct_82","buffer500m_nlcd2006_pct_82","buffer500m_nlcd2011_pct_82"))
+pct.ag<-lagosne_select(table="hu12.lulc", vars=c("hu12_zoneid","hu12_nlcd2001_pct_82","hu12_nlcd2006_pct_82","hu12_nlcd2011_pct_82"))
+pct.ag<-pct.ag[pct.ag$hu12_zoneid %in% analysislakes$lakeinfo$hu12_zoneid,]
+pct.ag.avg<-data.frame(hu12_zoneid=pct.ag$hu12_zoneid, pct.ag=rowMeans(pct.ag[,2:4]))
 
@@
 
+#state info
+states<-lagosne_select(table="state", vars=c("state_zoneid","state_name"))
+
 predictors<-analysislakes$lakeinfo
@@
 predictors<-left_join(predictors, depth, by="lagoslakeid")
-predictors<-left_join(predictors, pct.ag.avg, by="lagoslakeid")
+predictors<-left_join(predictors, pct.ag.avg, by="hu12_zoneid")
 predictors<-left_join(predictors, avg.chla, by="lagoslakeid")
 predictors<-left_join(predictors, tsi.chl, by="lagoslakeid")
-predictors<-left_join(predictors, huc_codes, by="hu4_zoneid")
+predictors<-left_join(predictors, states, by="state_zoneid")
+#predictors<-left_join(predictors, huc_codes, by="hu4_zoneid")
+
+for(nn in 1:ncol(predictors)){
+
+  if(is.factor(predictors[,nn])){
+    predictors[,nn]<-factor(predictors[,nn])
+  }
+
+}
+
+str(predictors)
+hist(predictors$lake_area_ha)
+hist(log10(predictors$lake_area_ha))
+hist(predictors$lake_perim_meters)
+hist(log10(predictors$lake_perim_meters))
+table(predictors$nhd_fcode)
+table(predictors$hu12_zoneid)
+hist(predictors$elevation_m)
+hist(predictors$maxdepth)
+hist(log10(predictors$maxdepth))
+hist(predictors$pct.ag)
+hist(log10(predictors$pct.ag))
+hist(predictors$chla)
+hist(log10(predictors$chla))
+hist(predictors$tsi)
+table(predictors$tsi.cat)
+
+predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha)
+predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
+predictors$log10_maxdepth<-log10(predictors$maxdepth)
+predictors$log10_pct.ag<-log10(predictors$pct.ag+1)
+predictors$log10_chla<-log10(predictors$chla)
 
@@
 modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.2,]
+
 ```
@@
 #short timescales
-gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+                        data=modvars.accndvi,
                         correlation=corExp(form = ~ nhd_lat + nhd_long))
@@
 
-gls.p.accndvi.st<-gls(accndvip.ts1 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
-                       correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.p.accndvi.st)
-suppressWarnings(dredge.p.accndvi.st<-dredge(gls.p.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.p.accndvi.st))
-
-gls.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ maxdepth + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi.phist) #remove ftype b/c only lakes
+gls.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+                        data=modvars.accndvi.phist,
+                        correlation=corExp(form = ~ nhd_lat + nhd_long)) #remove ftype b/c only lakes
 summary(gls.phi.accndvi.st)
@@
 #long timescales
-gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
+gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+                        data=modvars.accndvi,
                         correlation=corExp(form = ~ nhd_lat + nhd_long))
@@
 
-gls.p.accndvi.lt<-gls(accndvip.ts2 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi,
-                       correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.p.accndvi.lt)
-suppressWarnings(dredge.p.accndvi.lt<-dredge(gls.p.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.p.accndvi.lt))
-
-gls.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + huc2_code, data=modvars.accndvi.philt,
+gls.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+                        data=modvars.accndvi.philt,
                         correlation=corExp(form = ~ nhd_lat + nhd_long))
@@
 ```
+That turned up astonishingly little, so now try breaking down by region. 
+The regions are: 1) Missouri; 2) Minnesota, Wisconsin, and Michigan; 3) Pennsylvania, New York, Rhode Island, Vermont, New Hampshire, Maine.
 
-GLS models sucked, but inspection of results suggested that mixed effects models with random effects of region on the intercept may likely be an improvement.
+```{r gls modeling r1, echo=TRUE, cache=FALSE}
+#Region 1: Missouri
 
-```{r mixed modelling, echo=TRUE, cache=FALSE}
-lme.coh.accndvi.st<-lmer(accndvicoh.ts1 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi, na.action="na.fail")
-summary(lme.coh.accndvi.st)
-suppressWarnings(dredge.coh.accndvi.st<-dredge(lme.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
+modvars.accndvi.r1<-modvars.accndvi[modvars.accndvi$state_name=="Missouri",]
+# modvars.accndvi.philt.r1<-modvars.accndvi.philt[modvars.accndvi.philt$state_name=="Missouri",]
+# modvars.accndvi.phist.r1<-modvars.accndvi.phist[modvars.accndvi.phist$state_name=="Missouri",]
+
+#short timescales
+gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+                        data=modvars.accndvi.r1,
+                        correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(gls.coh.accndvi.st)
+suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.coh.accndvi.st))
 
-lme.p.accndvi.st<-lmer(accndvip.ts1 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi, na.action="na.fail")
-summary(lme.p.accndvi.st)
-suppressWarnings(dredge.p.accndvi.st<-dredge(lme.p.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.p.accndvi.st))
-
-lme.phi.accndvi.st<-lmer(accndviphi.ts1 ~ maxdepth + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi.phist, na.action="na.fail")
-summary(lme.phi.accndvi.st)
-suppressWarnings(dredge.phi.accndvi.st<-dredge(lme.phi.accndvi.st, beta="sd")) #model with TSI is unconvincingly better than intercept-only (dAIC = 0.92)
-print(head(dredge.phi.accndvi.st))
-
-lme.coh.accndvi.lt<-lmer(accndvicoh.ts2 ~ maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi, na.action="na.fail")
-summary(lme.coh.accndvi.lt)
-suppressWarnings(dredge.coh.accndvi.lt<-dredge(lme.coh.accndvi.lt, beta="sd")) #lake type is marginal improvement over intercept only (dAIC = 0.1)
+#long timescales
+gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+                        data=modvars.accndvi.r1,
+                        correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(gls.coh.accndvi.lt)
+suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
 print(head(dredge.coh.accndvi.lt))
-
-lme.p.accndvi.lt<-lmer(accndvip.ts2 ~ tslength + maxdepth + nhd_ftype + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi, na.action="na.fail")
-summary(lme.p.accndvi.lt)
-suppressWarnings(dredge.p.accndvi.lt<-dredge(lme.p.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.p.accndvi.lt))
-
-lme.phi.accndvi.lt<-lmer(accndviphi.ts2 ~ maxdepth + lake_area_ha + pct.ag + chla + tsi.cat + (1|huc2_code), data=modvars.accndvi.philt, na.action="na.fail")
-summary(lme.phi.accndvi.lt)
-suppressWarnings(dredge.phi.accndvi.lt<-dredge(lme.phi.accndvi.lt, beta="sd")) #model with TSI is unconvincingly better than intercept-only (dAIC = 0.92)
-print(head(dredge.phi.accndvi.lt))
 
@@
 
-Adding random effects of huc2 region on intercept helped somewhat. Some possibilities are to add more detailed lake type classes, and to model 2-3 regions separately.
+```{r gls modeling r2, echo=TRUE, cache=FALSE}
+#Region 2: Minnesota, Wisconsin, Michigan
+
+modvars.accndvi.r2<-modvars.accndvi[modvars.accndvi$state_name %in% c("Minnesota","Wisconsin","Michigan"),]
+
+#short timescales
+gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+                        data=modvars.accndvi.r2,
+                        correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(gls.coh.accndvi.st)
+suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
+print(head(dredge.coh.accndvi.st))
+
+#long timescales
+gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+                        data=modvars.accndvi.r2,
+                        correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(gls.coh.accndvi.lt)
+suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
+print(head(dredge.coh.accndvi.lt))
+
+```
+```{r gls modeling r3, echo=TRUE, cache=FALSE}
+#Region 2: Minnesota, Wisconsin, Michigan
+
+modvars.accndvi.r3<-modvars.accndvi[modvars.accndvi$state_name %in% c("Pennsylvania","New York","Rhode Island","Vermont","New Hampshire","Maine"),]
+
+#short timescales
+gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+                        data=modvars.accndvi.r3,
+                        correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(gls.coh.accndvi.st)
+suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
+print(head(dredge.coh.accndvi.st))
+
+#long timescales
+gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+                        data=modvars.accndvi.r3,
+                        correlation=corExp(form = ~ nhd_lat + nhd_long))
+summary(gls.coh.accndvi.lt)
+suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
+print(head(dredge.coh.accndvi.lt))
+
+```

### 2019-06-05 AnalysisCode/ms1_prep.Rmd
rough think piece display items
ms1 result updates by region

@@
 
+##updated cleanAnnualts on 5/5/19
+
 lakes_to_get<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/lakes20yrs_chla.csv")$x
 
-lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), tsvars=c("chla"), 
+lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "nhd_fcode", "hu4_zoneid", 
+                                                           "hu12_zoneid", "state_zoneid", "elevation_m"), tsvars=c("chla"), 
                                   minmos=3, minobs=3, timespan=c(1989,2018))
@@
 MNMPCAlakes.raw<-makeMNMPCAannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/MN_MPCA",
-                                    infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), minmos=3, minobs=3, timespan=c(1989,2018))
+                                   infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "nhd_fcode", "hu4_zoneid","hu12_zoneid", 
+                                              "state_zoneid", 
+                                              "elevation_m"), minmos=3, minobs=3, timespan=c(1989,2018))
 MNMPCAlakes.raw<-fixNamestoLAGOS(MNMPCAlakes.raw,"Minnesota MPCA")
@@
 WIDNRlakes.raw<-makeWIDNRannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/WI_DNR",
-                                  infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "hu4_zoneid"), minmos=3, minobs=3, timespan=c(1989,2018))
+                                  infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "nhd_fcode", "hu4_zoneid","hu12_zoneid", 
+                                             "state_zoneid", 
+                                             "elevation_m"), minmos=3, minobs=3, timespan=c(1989,2018))
 WIDNRlakes.raw<-fixNamestoLAGOS(WIDNRlakes.raw, "Wisconsin DNR")
 WIDNRlakes.cln<-cleanAnnualts(WIDNRlakes.raw)
+
+#IowaALMlakes<-makeIowaALMannualts(almdat="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/Iowa Synchrony Lakes.csv")
 

### 2019-06-05 AnalysisCode/PreliminaryAnalyses/PrelimAnalyses_IowaALM_20190530.R

@@ -1,0 +1,77 @@
+rm(list=ls())
+
+#you all are working on PCs so your file paths will start differently than mine
+setwd("~/Box Sync/NSF EAGER Synchrony/")
+
+library(wsyn) #this package is currently on github. To install, run devtools::install_github("reumandc/wsyn")
+library(raster) #these packages are on CRAN, install like normal
+library(rgdal)
+library(aqts)
+
+almdat<-read.csv("./Data/Iowa Lakes Data/Iowa Synchrony Lakes.csv", stringsAsFactors=F)
+lakechar<-read.csv("./Data/Iowa Lakes Data/Iowa Lake Characteristics.csv", stringsAsFactors=F)
+
+almdat<-almdat[almdat$LakeID %in% lakechar$LakeID[lakechar$Include=="Y"],]
+lakechar<-lakechar[lakechar$Include=="Y",]
+
+IowaALM.raw<-makeIowaALMannualts(almdat,lakechar,getvars=c("Chlorophyll"))
+IowaALM.raw<-fixNamestoLAGOS(IowaALM.raw, origin="Iowa ALM")
+IowaALM.cln<-cleanAnnualts(IowaALM.raw, ymin=19)
+
+lakechar$lake_area_ha<-lakechar$SA * 100
+lakechar$nhd_ftype<-rep(390, nrow(lakechar))
+
+dbuff<-calcBufferDist(sa=lakechar$lake_area_ha, ltype=lakechar$nhd_ftype, minbuff=2500)
+
+accndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/accvi1989_2018.img")
+maxndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/mxvi1989_2018.img")
+
+nlcdwater<-raster("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/landcover/nlcd2011_cls11.img")
+watermask<-nlcdwater<0.05
+
+accndvi<-mask(accndvi,watermask,maskvalue=0) #mask out pixels that have too much water in them
[…]

### 2019-06-05 AnalysisCode/coh_false_negs.R

@@ -1,0 +1,76 @@
+## What is the false negative rate for coherences measured between short (20 year) time series?
+
+library(wsyn)
+
+nreps=1000
+tmax=20
+
+pvals<-NULL
+shifts<-NULL
+
+
+
+for(ii in 1:nreps){
+  
+  tt=1:tmax
+  
+  env<-rnorm(tmax)
+  y1<-arima.sim(tmax, model=list(ar=0.5), innov=env, n.start=1)
+  y2<-arima.sim(tmax, model=list(ar=0.5), innov=env, n.start=1)
+  
+  shift<-round(runif(1,0,2.49))
+  #shift=0
+  if(shift==0){y2=y1}
+  if(shift==1){y2=c(y1[2:tmax],y1[1])}
+  if(shift==2){y2=c(y1[3:tmax],y1[1:2])}
+  
+  y1<-cleandat(y1, tt, clev=2)$cdat
+  y2<-cleandat(y2, tt, clev=2)$cdat
+  
+  tmp<-coh(y1,y2,tt,norm="powall",sigmethod="fast")
+  tmp<-bandtest(tmp,c(2,20))
+  
+  pvals<-c(pvals, tmp$bandp$p_val[1])
+  shifts<-c(shifts,shift)
+}
+
+false.neg<-sum(pvals>0.05)/nreps
+print(false.neg)
+
+#####################################################
+
+nreps=1000
+tmax=50
+
+pvals<-NULL
+shifts<-NULL
+
+
+
+for(ii in 1:nreps){
+  
+  tt=1:tmax
+  
+  env<-rnorm(tmax)
+  y1<-arima.sim(tmax, model=list(ar=0.5), innov=env, n.start=1)
+  y2<-arima.sim(tmax, model=list(ar=0.5), innov=env, n.start=1)
+  
+  shift<-round(runif(1,0,2.49))
+  #shift=0
+  if(shift==0){y2=y1}
+  if(shift==1){y2=c(y1[2:tmax],y1[1])}
+  if(shift==2){y2=c(y1[3:tmax],y1[1:2])}
+  
+  y1<-cleandat(y1, tt, clev=2)$cdat
+  y2<-cleandat(y2, tt, clev=2)$cdat
+  
+  tmp<-coh(y1,y2,tt,norm="powall",sigmethod="fast")
+  tmp<-bandtest(tmp,c(2,20))
+  
[…]

### 2019-06-05 R Package/aqts/R/cleanAnnualts.R

@@ -90,6 +90,7 @@ cleanAnnualts<-function(indat, ymin=20, maxNA=2, optim="chla", timespan=NULL, fi
       }
       if(sum(rle.opt$lengths[rle.opt$values])>(ymin-maxNA) & 
          sum(rle.opt$lengths[!rle.opt$values])<=maxNA &
+         sum(rle.opt$lenghts)>ymin &
          nacheck(rle.opt)){break}
     }
     

### 2019-06-12 AnalysisCode/ms1_analyses_randforest.Rmd
ms1 analysis updates

--- 2019-06-05 AnalysisCode/ms1_analyses.Rmd
@@
 analysislakes$lakedata<-analysislakes$lakedata[!sapply(analysislakes$lakedata, function(x){any(is.na(x))})]
+
+analysislakes$lakeinfo$tslength<-analysislakes$lakeinfo$end-analysislakes$lakeinfo$start+1
+# analysislakes$lakedata<-analysislakes$lakedata[!analysislakes$lakeinfo$tslength < 20]
+# analysislakes$lakeinfo<-analysislakes$lakeinfo[!analysislakes$lakeinfo$tslength < 20,]
+
 ```
@@
 
+#CV of terrestrial NDVI
+cv.accndvi<-NULL
+for(lake in 1:length(analysislakes$lakedata)){
+  tmp<-analysislakes$lakedata[[lake]][rownames(analysislakes$lakedata[[lake]])=="accndvi",]
+  cv.accndvi<-c(cv.accndvi, sd(tmp)/mean(tmp))  
+ # rm(tmp)
+}
+cv.accndvi<-data.frame(lagoslakeid=as.numeric(names(analysislakes$lakedata)), cv.accndvi=cv.accndvi)
+
 #huc2 and huc4 watershed codes
@@
 predictors<-analysislakes$lakeinfo
-predictors$tslength<-predictors$end-predictors$start+1
 predictors<-left_join(predictors, depth, by="lagoslakeid")
@@
 predictors<-left_join(predictors, states, by="state_zoneid")
+predictors<-left_join(predictors, cv.accndvi, by="lagoslakeid")
 #predictors<-left_join(predictors, huc_codes, by="hu4_zoneid")
@@
 str(predictors)
+hist(predictors$tslength)
 hist(predictors$lake_area_ha)
@@
 table(predictors$tsi.cat)
+hist(predictors$cv.accndvi)
 
@@
 
-modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.2,]
-modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.2,]
+modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.3,]
+modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.3,]
 
@@
 
-```{r gls modelling, echo=TRUE, cache=FALSE}
-#short timescales
-gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.st)
-suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.st))
+```{r modelling, echo=TRUE, cache=FALSE}
 
-gls.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.phist,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long)) #remove ftype b/c only lakes
-summary(gls.phi.accndvi.st)
-suppressWarnings(dredge.phi.accndvi.st<-dredge(gls.phi.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.phi.accndvi.st))
+library(partykit)
 
-#long timescales
-gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.lt)
-suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.lt))
+cforest.st<-cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, data=modvars.accndvi)
+predcoh.st<-predict.cforest(cforest.st, newdata=modvars.accndvi)
+hist(predcoh.st)
+hist(modvars.accndvi$accndvicoh.ts1)
+plot(predcoh.st, modvars.accndvi$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
+     xlim=c(0,1), ylim=c(0,1))
+abline(a=0,b=1)
+cor.test(predcoh.st,modvars.accndvi$accndvicoh.ts1)
+varimp.coh.st<-varimp.cforest(cforest.st)
+print(varimp.coh.st)
 
-gls.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.philt,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.phi.accndvi.lt)
-suppressWarnings(dredge.phi.accndvi.lt<-dredge(gls.phi.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.phi.accndvi.lt))
-```
-That turned up astonishingly little, so now try breaking down by region. 
-The regions are: 1) Missouri; 2) Minnesota, Wisconsin, and Michigan; 3) Pennsylvania, New York, Rhode Island, Vermont, New Hampshire, Maine.
+cforest.lt<-cforest(accndvicoh.ts2 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, data=modvars.accndvi)
+predcoh.lt<-predict.cforest(cforest.lt, newdata=modvars.accndvi)
+hist(predcoh.lt)
+hist(modvars.accndvi$accndvicoh.ts2)
+plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long st",
+     xlim=c(0,1), ylim=c(0,1))
+abline(a=0,b=1)
+cor.test(predcoh.lt,modvars.accndvi$accndvicoh.ts2)
+varimp.coh.lt<-varimp.cforest(cforest.lt)
+print(varimp.coh.lt)
 
-```{r gls modeling r1, echo=TRUE, cache=FALSE}
-#Region 1: Missouri
+cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, 
+                        data=modvars.accndvi.phist)
+predphi.st<-predict.cforest(cforest.phi.st, newdata=modvars.accndvi.phist)
+hist(predphi.st)
+hist(cos(modvars.accndvi.phist$accndviphi.ts1))
+plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
+     xlim=c(-1,1), ylim=c(-1,1))
+abline(a=0,b=1)
+cor.test(predphi.st,cos(modvars.accndvi.phist$accndviphi.ts1))
+varimp.phi.st<-varimp.cforest(cforest.phi.st)
+print(varimp.phi.st)
 
-modvars.accndvi.r1<-modvars.accndvi[modvars.accndvi$state_name=="Missouri",]
-# modvars.accndvi.philt.r1<-modvars.accndvi.philt[modvars.accndvi.philt$state_name=="Missouri",]
-# modvars.accndvi.phist.r1<-modvars.accndvi.phist[modvars.accndvi.phist$state_name=="Missouri",]
-
-#short timescales
-gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r1,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.st)
-suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.st))
-
-#long timescales
-gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r1,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.lt)
-suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.lt))
+cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, 
+                        data=modvars.accndvi.philt)
+predphi.lt<-predict.cforest(cforest.phi.lt, newdata=modvars.accndvi.philt)
+hist(predphi.lt)
+hist(cos(modvars.accndvi.philt$accndviphi.ts2))
+plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
+     xlim=c(-1,1), ylim=c(-1,1))
+abline(a=0,b=1)
+cor.test(predphi.lt,cos(modvars.accndvi.philt$accndviphi.ts2))
+varimp.phi.lt<-varimp.cforest(cforest.phi.lt)
+print(varimp.phi.lt)
 
 ```
-
-```{r gls modeling r2, echo=TRUE, cache=FALSE}
-#Region 2: Minnesota, Wisconsin, Michigan
-
-modvars.accndvi.r2<-modvars.accndvi[modvars.accndvi$state_name %in% c("Minnesota","Wisconsin","Michigan"),]
-
-#short timescales
-gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r2,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.st)
-suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.st))
-
-#long timescales
-gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r2,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.lt)
-suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.lt))
-
-```
-```{r gls modeling r3, echo=TRUE, cache=FALSE}
-#Region 2: Minnesota, Wisconsin, Michigan
-
-modvars.accndvi.r3<-modvars.accndvi[modvars.accndvi$state_name %in% c("Pennsylvania","New York","Rhode Island","Vermont","New Hampshire","Maine"),]
-
-#short timescales
-gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r3,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.st)
-suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.st))
-
-#long timescales
-gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r3,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.lt)
-suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.lt))
-
-```

### 2019-06-12 R Package/aqts/R/cleanAnnualts.R

@@ -90,8 +90,12 @@ cleanAnnualts<-function(indat, ymin=20, maxNA=2, optim="chla", timespan=NULL, fi
       }
       if(sum(rle.opt$lengths[rle.opt$values])>(ymin-maxNA) & 
          sum(rle.opt$lengths[!rle.opt$values])<=maxNA &
-         sum(rle.opt$lenghts)>ymin &
          nacheck(rle.opt)){break}
+    }
+    
+    if(length(opt.out) < ymin){
+      droplakes<-c(droplakes, lind)
+      next
     }
     
     if(lind %in% droplakes){next}

### 2019-06-14 AnalysisCode/ms1_analyses_randforest.Rmd
random forest partial dependence plots

@@
 library(fields)
+#library(partykit)
+library(pdp)
+library(party)
 
@@
 
-```{r modelling, echo=TRUE, cache=FALSE}
+```{r modellingCoherence, echo=TRUE, cache=FALSE}
 
-library(partykit)
-
-cforest.st<-cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, data=modvars.accndvi)
-predcoh.st<-predict.cforest(cforest.st, newdata=modvars.accndvi)
+# cforest.st<-partykit::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
+#                     data=modvars.accndvi, ntree=20000)
+cforest.st<-party::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
+                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
+predcoh.st<-predict(cforest.st, newdata=modvars.accndvi,type="response")
 hist(predcoh.st)
@@
 cor.test(predcoh.st,modvars.accndvi$accndvicoh.ts1)
-varimp.coh.st<-varimp.cforest(cforest.st)
-print(varimp.coh.st)
+varimp.coh.st<-varimp(cforest.st)
+print(varimp.coh.st[order(varimp.coh.st, decreasing=T)])
 
-cforest.lt<-cforest(accndvicoh.ts2 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, data=modvars.accndvi)
-predcoh.lt<-predict.cforest(cforest.lt, newdata=modvars.accndvi)
-hist(predcoh.lt)
-hist(modvars.accndvi$accndvicoh.ts2)
+partial(cforest.st, pred.var="lake_perim_meters", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
+
+cforest.lt<-party::cforest(accndvicoh.ts2 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
+                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
+predcoh.lt<-predict(cforest.lt, newdata=modvars.accndvi)
+# hist(predcoh.lt)
+# hist(modvars.accndvi$accndvicoh.ts2)
 plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long st",
@@
 cor.test(predcoh.lt,modvars.accndvi$accndvicoh.ts2)
-varimp.coh.lt<-varimp.cforest(cforest.lt)
-print(varimp.coh.lt)
+varimp.coh.lt<-varimp(cforest.lt)
+print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)])
 
-cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, 
-                        data=modvars.accndvi.phist)
-predphi.st<-predict.cforest(cforest.phi.st, newdata=modvars.accndvi.phist)
+partial(cforest.lt, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="lake_perim_meters", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
+
+```
+
+```{r modellingPhase, echo=TRUE, cache=FALSE}
+
+cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
+                        data=modvars.accndvi.phist,controls=cforest_control(ntree=30000))
+predphi.st<-predict(cforest.phi.st, newdata=modvars.accndvi.phist)
 hist(predphi.st)
@@
 cor.test(predphi.st,cos(modvars.accndvi.phist$accndviphi.ts1))
-varimp.phi.st<-varimp.cforest(cforest.phi.st)
-print(varimp.phi.st)
+varimp.phi.st<-varimp(cforest.phi.st)
+print(varimp.phi.st[order(varimp.phi.st,decreasing=TRUE)])
 
-cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, 
-                        data=modvars.accndvi.philt)
-predphi.lt<-predict.cforest(cforest.phi.lt, newdata=modvars.accndvi.philt)
+partial(cforest.phi.st, pred.var="cv.accndvi", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="hu4_zoneid", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="pct.ag", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="lake_area_ha", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="lake_perim_meters", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="chla", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="tsi.cat", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="maxdepth", train=modvars.accndvi.phist, type="regression", plot=T)
+
+cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
+                        data=modvars.accndvi.philt,controls=cforest_control(ntree=30000))
+predphi.lt<-predict(cforest.phi.lt, newdata=modvars.accndvi.philt)
 hist(predphi.lt)
@@
 cor.test(predphi.lt,cos(modvars.accndvi.philt$accndviphi.ts2))
-varimp.phi.lt<-varimp.cforest(cforest.phi.lt)
-print(varimp.phi.lt)
+varimp.phi.lt<-varimp(cforest.phi.lt)
+print(varimp.phi.lt[order(varimp.phi.lt, decreasing=TRUE)])
+
+partial(cforest.phi.lt, pred.var="hu4_zoneid", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="lake_area_ha", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="lake_perim_meters", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="chla", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="cv.accndvi", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="maxdepth", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="pct.ag", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="tsi.cat", train=modvars.accndvi.philt, type="regression", plot=T)
 

### 2019-07-03 AnalysisCode/ms1_analyses_randforest.Rmd
analysis updates

--- 2019-06-12 AnalysisCode/ms1_analyses_randforest.Rmd
@@
 library(fields)
+#library(partykit)
+library(pdp)
+library(party)
+library(spatstat)
 
@@
 
-hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.2]/pi, main="Accumulated NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
+# hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.2]/pi, main="Accumulated NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
+rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian",
+     breaks=seq(0,2*pi,length.out=16))
 #hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<0.2]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
@@
 
-hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts2<0.2]/pi, main="Accumulated NDVI, long timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
+# hist(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.2]/pi, main="Accumulated NDVI, long timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
+rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian",
+     breaks=seq(0,2*pi,length.out=16))
+
 #hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvicoh.ts2>0.6]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
@@
 
+#Wetlands
+pct.wetlands<-lagosne_select(table="hu12.lulc", vars=c(c("hu12_zoneid","hu12_nlcd2001_pct_90","hu12_nlcd2006_pct_90",
+                                                         "hu12_nlcd2011_pct_90","hu12_nlcd2001_pct_95","hu12_nlcd2006_pct_95",
+                                                         "hu12_nlcd2011_pct_95")))
+pct.wetlands<-pct.wetlands[pct.wetlands$hu12_zoneid %in% analysislakes$lakeinfo$hu12_zoneid,]
+pct.wetlands$sum2001<-rowSums(pct.wetlands[,c(2,5)])
+pct.wetlands$sum2006<-rowSums(pct.wetlands[,c(3,6)])
+pct.wetlands$sum2011<-rowSums(pct.wetlands[,c(4,7)])
+pct.wetlands.avg<-data.frame(hu12_zoneid=pct.wetlands$hu12_zoneid, pct.wetlands=rowMeans(pct.wetlands[,8:10]))
+
 #depth
@@
 avg.chla<-aggregate(chla ~ lagoslakeid, data=gs.chla, FUN=mean, na.rm=T)
+
+#growing season DOC
+doc<-lagosne_select(table="epi_nutr", vars=c("lagoslakeid","samplemonth","doc"))
+doc<-doc[doc$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
+gs.doc<-doc[doc$samplemonth %in% 5:9,]
+avg.doc<-aggregate(doc ~ lagoslakeid, data=gs.doc, FUN=mean, na.rm=T)
 
@@
 
+#mean precipitation
+prcp.normal<-raster("~/Box Sync/NSF EAGER Synchrony/Data/PRISM Data/PRISM_ppt_30yr_normal_800mM2_annual_bil.bil")
+lakepts<-SpatialPoints(coords=cbind(analysislakes$lakeinfo$nhd_long,analysislakes$lakeinfo$nhd_lat))
+lake.prcp<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid, prcp.normal=raster::extract(prcp.normal,lakepts))
+
 #huc2 and huc4 watershed codes
@@
 predictors<-left_join(predictors, pct.ag.avg, by="hu12_zoneid")
+predictors<-left_join(predictors, pct.wetlands.avg, by="hu12_zoneid")
 predictors<-left_join(predictors, avg.chla, by="lagoslakeid")
@@
 predictors<-left_join(predictors, cv.accndvi, by="lagoslakeid")
+predictors<-left_join(predictors, avg.doc, by="lagoslakeid")
+predictors<-left_join(predictors, lake.prcp, by="lagoslakeid")
 #predictors<-left_join(predictors, huc_codes, by="hu4_zoneid")
@@
 hist(predictors$cv.accndvi)
+hist(predictors$pct.wetlands)
+hist(predictors$doc)
+hist(predictors$prcp.normal)
 
-predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha)
-predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
-predictors$log10_maxdepth<-log10(predictors$maxdepth)
-predictors$log10_pct.ag<-log10(predictors$pct.ag+1)
-predictors$log10_chla<-log10(predictors$chla)
+# predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha) #not necessary to transform with random forests
+# predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
+# predictors$log10_maxdepth<-log10(predictors$maxdepth)
+# predictors$log10_pct.ag<-log10(predictors$pct.ag+1)
+# predictors$log10_chla<-log10(predictors$chla)
 
@@
 
-```{r modelling, echo=TRUE, cache=FALSE}
+```{r modellingCoherence, echo=TRUE, cache=FALSE}
 
-library(partykit)
-
-cforest.st<-cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, data=modvars.accndvi)
-predcoh.st<-predict.cforest(cforest.st, newdata=modvars.accndvi)
+# cforest.st<-partykit::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
+#                     data=modvars.accndvi, ntree=20000)
+cforest.st<-party::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
+                             cv.accndvi + pct.wetlands + doc + prcp.normal,
+                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
+predcoh.st<-predict(cforest.st, newdata=modvars.accndvi,type="response")
 hist(predcoh.st)
@@
 cor.test(predcoh.st,modvars.accndvi$accndvicoh.ts1)
-varimp.coh.st<-varimp.cforest(cforest.st)
-print(varimp.coh.st)
+varimp.coh.st<-varimp(cforest.st)
+print(varimp.coh.st[order(varimp.coh.st, decreasing=T)])
 
-cforest.lt<-cforest(accndvicoh.ts2 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, data=modvars.accndvi)
-predcoh.lt<-predict.cforest(cforest.lt, newdata=modvars.accndvi)
-hist(predcoh.lt)
-hist(modvars.accndvi$accndvicoh.ts2)
+partial(cforest.st, pred.var="prcp.normal", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="lake_perim_meters", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="doc", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
+
+cforest.lt<-party::cforest(accndvicoh.ts2 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
+                             cv.accndvi+ pct.wetlands + doc + prcp.normal, 
+                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
+predcoh.lt<-predict(cforest.lt, newdata=modvars.accndvi)
+# hist(predcoh.lt)
+# hist(modvars.accndvi$accndvicoh.ts2)
 plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long st",
@@
 cor.test(predcoh.lt,modvars.accndvi$accndvicoh.ts2)
-varimp.coh.lt<-varimp.cforest(cforest.lt)
-print(varimp.coh.lt)
+varimp.coh.lt<-varimp(cforest.lt)
+print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)])
 
-cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, 
-                        data=modvars.accndvi.phist)
-predphi.st<-predict.cforest(cforest.phi.st, newdata=modvars.accndvi.phist)
-hist(predphi.st)
-hist(cos(modvars.accndvi.phist$accndviphi.ts1))
+partial(cforest.lt, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="doc", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="lake_perim_meters", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="prcp.normal", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
+
+```
+
+```{r modellingPhase, echo=TRUE, cache=FALSE}
+
+cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
+                          cv.accndvi+ pct.wetlands + doc + prcp.normal, 
+                        data=modvars.accndvi.phist,controls=cforest_control(ntree=40000))
+predphi.st<-predict(cforest.phi.st, newdata=modvars.accndvi.phist)
+# hist(predphi.st)
+# hist(cos(modvars.accndvi.phist$accndviphi.ts1))
 plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
@@
 cor.test(predphi.st,cos(modvars.accndvi.phist$accndviphi.ts1))
-varimp.phi.st<-varimp.cforest(cforest.phi.st)
-print(varimp.phi.st)
+varimp.phi.st<-varimp(cforest.phi.st)
+print(varimp.phi.st[order(varimp.phi.st,decreasing=TRUE)])
 
-cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, 
-                        data=modvars.accndvi.philt)
-predphi.lt<-predict.cforest(cforest.phi.lt, newdata=modvars.accndvi.philt)
-hist(predphi.lt)
-hist(cos(modvars.accndvi.philt$accndviphi.ts2))
+partial(cforest.phi.st, pred.var="maxdepth", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="lake_area_ha", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="lake_perim_meters", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="doc", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="cv.accndvi", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="pct.wetlands", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="prcp.normal", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="chla", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="pct.ag", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="tsi.cat", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="hu4_zoneid", train=modvars.accndvi.phist, type="regression", plot=T)
+
+cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
+                          cv.accndvi + pct.wetlands + doc + prcp.normal, 
+                        data=modvars.accndvi.philt,controls=cforest_control(ntree=40000))
+predphi.lt<-predict(cforest.phi.lt, newdata=modvars.accndvi.philt)
+# hist(predphi.lt)
+# hist(cos(modvars.accndvi.philt$accndviphi.ts2))
 plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
@@
 cor.test(predphi.lt,cos(modvars.accndvi.philt$accndviphi.ts2))
-varimp.phi.lt<-varimp.cforest(cforest.phi.lt)
-print(varimp.phi.lt)
+varimp.phi.lt<-varimp(cforest.phi.lt)
+print(varimp.phi.lt[order(varimp.phi.lt, decreasing=TRUE)])
+
+partial(cforest.phi.lt, pred.var="hu4_zoneid", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="lake_area_ha", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="prcp.normal", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="pct.wetlands", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="lake_perim_meters", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="doc", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="chla", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="cv.accndvi", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="maxdepth", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="pct.ag", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="tsi.cat", train=modvars.accndvi.philt, type="regression", plot=T)
 

### 2019-07-03 AnalysisCode/ThinkPiece/aboveSaylorville_analyses.R

@@ -137,7 +137,7 @@ no3Xflow<-bandtest(no3Xflow,b1)
 no3Xflow<-bandtest(no3Xflow,b2)
 no3Xflow<-bandtest(no3Xflow,b3)
 no3Xflow<-bandtest(no3Xflow,b4)
-print(no3Xflow$bandp) #why isn't long-timescale band significant?
+print(no3Xflow$bandp)
 
 plot(no3Xflow$timescales, Mod(no3Xflow$coher))
 

### 2019-07-03 AnalysisCode/ThinkPiece/calcofi_example.R

@@ -115,8 +115,8 @@ jetcolors <- c("#00007F", "blue", "#007FFF", "cyan",
                "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000")
 colorfill<-grDevices::colorRampPalette(jetcolors)
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/ThinkPiece/calcofi_example.tif",
-    units="in", height=5, width=6.5, res=300)
+# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/ThinkPiece/calcofi_example.tif",
+#     units="in", height=5, width=6.5, res=300)
 
 layout(laymat)
 
@@ -134,5 +134,5 @@ mtext("Time",1, outer=T, line=0.65)
 mtext(expression(paste("Larvae 10m"^"-2")),2,outer=T, line=0.5, at=0.75)
 mtext("Timescale (yr)",2, outer=T, line=0.5, at=0.25)
 
-dev.off()
+#dev.off()
 

### 2019-07-03 AnalysisCode/ThinkPiece/displayItems.R

@@ -27,47 +27,76 @@ y4<-rnorm(length(tt),0,sig)
 
 plot(tt,y1+y2+y3+y4, type="l")
 
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/ThinkPiece/superimposed_signals_v1.png", units="in",
+ycomp<-y1+y2+y3+y4
+
+df.lm2<-data.frame(x=seq(12.5,17.5,1), y=c(mean(ycomp[12:13]), mean(ycomp[13:14]), mean(ycomp[14:15]), mean(ycomp[15:16]),
+                                           mean(ycomp[16:17]), mean(ycomp[17:18])))
+
+lm1<-lm(ycomp[tt>=5 & tt<=10] ~ tt[tt>=5 & tt<=10])
+lm2<-lm(y~x, data=df.lm2)
+lm3<-lm(ycomp[tt>=20 & tt<=25] ~ tt[tt>=20 & tt<=25])
+
+
+png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/ThinkPiece/superimposed_signals_v2.png", units="in",
     height=5, width=3.25, res=300)
 
-par(mfrow=c(4,1), mar=c(2,4,0,1), xpd=T, oma=c(2,0,1,0))
-plot(tt,y1+y2+y3+y4, type="l",xaxt="n", xlab="")
+par(mfrow=c(4,1), mar=c(2,2,0,1), xpd=F, oma=c(2,0,1,0), mgp=c(1,1,0))
+plot(tt,y1+y2+y3+y4, type="l",xaxt="n", xlab="", yaxt="n", ylab="y1+y2+y3")
+rect(5,-4,10,4, col="skyblue2", xpd=F, border=NA)
+rect(12.5,-4,17.5,4,col="palegreen2",xpd=F,border=NA)
+rect(20,-4,25,4,col="gold",xpd=F,border=NA)
+lines(tt,y1+y2+y3+y4)
+lines(tt[tt>=5 & tt<=10], predict(lm1), col="royalblue3", lwd=3)
+lines(seq(12.5,17.5,1), predict(lm2), col="seagreen", lwd=3)
+lines(tt[tt>=20 & tt<=25], predict(lm3), col="goldenrod4", lwd=3)
 axis(1,at=c(1,5,10,15,20,25,30),labels=FALSE)
-plot(tt,y1,type="l",xaxt="n",xlab="")
[…]

### 2019-07-08 AnalysisCode/ms1_analyses_randforest.Rmd
Q1 analysis updates

--- 2019-06-12 AnalysisCode/ms1_analyses_randforest.Rmd
@@
 
-print(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<alpha]/pi) #only pattern is that lakes don't lead the landscape
-print(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<alpha]/pi)
+print(cbind(coh.chlaXaccndvi$lagoslakeid, coh.chlaXaccndvi$accndvip.ts1)[coh.chlaXaccndvi$accndvip.ts1<alpha,])
+print(cbind(coh.chlaXaccndvi$lagoslakeid, coh.chlaXaccndvi$accndvip.ts2)[coh.chlaXaccndvi$accndvip.ts2<alpha,])
+
+cor(coh.chlaXaccndvi$accndvicoh.ts1,coh.chlaXaccndvi$accndvicoh.ts2)
+
+# print(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<alpha]/pi) #only pattern is that lakes don't lead the landscape
+# print(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<alpha]/pi)
 
@@
 
+#shoreline development ratio
+sdev<-analysislakes$lakeinfo$lake_perim_meters/(2*sqrt(pi*analysislakes$lakeinfo$lake_area_ha*10000))
+shoredev<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid,shoredev=sdev)
+
 predictors<-analysislakes$lakeinfo
@@
 predictors<-left_join(predictors, cv.accndvi, by="lagoslakeid")
+predictors<-left_join(predictors, avg.doc, by="lagoslakeid")
+predictors<-left_join(predictors, lake.prcp, by="lagoslakeid")
+predictors<-left_join(predictors, shoredev, by="lagoslakeid")
 #predictors<-left_join(predictors, huc_codes, by="hu4_zoneid")
@@
 hist(predictors$cv.accndvi)
+hist(predictors$pct.wetlands)
+hist(predictors$doc)
+hist(predictors$prcp.normal)
+hist(predictors$shoredev)
 
-predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha)
-predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
-predictors$log10_maxdepth<-log10(predictors$maxdepth)
-predictors$log10_pct.ag<-log10(predictors$pct.ag+1)
-predictors$log10_chla<-log10(predictors$chla)
+# predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha) #not necessary to transform with random forests
+# predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
+# predictors$log10_maxdepth<-log10(predictors$maxdepth)
+# predictors$log10_pct.ag<-log10(predictors$pct.ag+1)
+# predictors$log10_chla<-log10(predictors$chla)
 
@@
 
-```{r modelling, echo=TRUE, cache=FALSE}
+```{r modellingCoherence, echo=TRUE, cache=FALSE}
 
-library(partykit)
-
-cforest.st<-cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, data=modvars.accndvi)
-predcoh.st<-predict.cforest(cforest.st, newdata=modvars.accndvi)
-hist(predcoh.st)
-hist(modvars.accndvi$accndvicoh.ts1)
+# cforest.st<-partykit::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
+#                     data=modvars.accndvi, ntree=20000)
+cforest.st<-party::cforest(accndvicoh.ts1 ~ shoredev + lake_area_ha +  maxdepth + pct.ag + chla + tsi.cat + 
+                             hu4_zoneid + cv.accndvi + pct.wetlands + doc + prcp.normal,
+                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
+predcoh.st<-predict(cforest.st, newdata=modvars.accndvi,type="response")
+#hist(predcoh.st)
+#hist(modvars.accndvi$accndvicoh.ts1)
 plot(predcoh.st, modvars.accndvi$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
@@
 cor.test(predcoh.st,modvars.accndvi$accndvicoh.ts1)
-varimp.coh.st<-varimp.cforest(cforest.st)
-print(varimp.coh.st)
+varimp.coh.st<-varimp(cforest.st)
+print(varimp.coh.st[order(varimp.coh.st, decreasing=T)])
 
-cforest.lt<-cforest(accndvicoh.ts2 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, data=modvars.accndvi)
-predcoh.lt<-predict.cforest(cforest.lt, newdata=modvars.accndvi)
-hist(predcoh.lt)
-hist(modvars.accndvi$accndvicoh.ts2)
+partial(cforest.st, pred.var="shoredev", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="prcp.normal", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="doc", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.st, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
+
+cforest.lt<-party::cforest(accndvicoh.ts2 ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid 
+                           + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
+                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
+predcoh.lt<-predict(cforest.lt, newdata=modvars.accndvi)
+# hist(predcoh.lt)
+# hist(modvars.accndvi$accndvicoh.ts2)
 plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long st",
@@
 cor.test(predcoh.lt,modvars.accndvi$accndvicoh.ts2)
-varimp.coh.lt<-varimp.cforest(cforest.lt)
-print(varimp.coh.lt)
+varimp.coh.lt<-varimp(cforest.lt)
+print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)])
 
-cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, 
-                        data=modvars.accndvi.phist)
-predphi.st<-predict.cforest(cforest.phi.st, newdata=modvars.accndvi.phist)
-hist(predphi.st)
-hist(cos(modvars.accndvi.phist$accndviphi.ts1))
+partial(cforest.lt, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="doc", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="prcp.normal", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="shoredev", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
+partial(cforest.lt, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
+
+```
+
+```{r modellingPhase, echo=TRUE, cache=FALSE}
+
+cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + 
+                          hu4_zoneid + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
+                        data=modvars.accndvi.phist,controls=cforest_control(ntree=40000))
+predphi.st<-predict(cforest.phi.st, newdata=modvars.accndvi.phist)
+# hist(predphi.st)
+# hist(cos(modvars.accndvi.phist$accndviphi.ts1))
 plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
@@
 cor.test(predphi.st,cos(modvars.accndvi.phist$accndviphi.ts1))
-varimp.phi.st<-varimp.cforest(cforest.phi.st)
-print(varimp.phi.st)
+varimp.phi.st<-varimp(cforest.phi.st)
+print(varimp.phi.st[order(varimp.phi.st,decreasing=TRUE)])
 
-cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi + hu4_zoneid + cv.accndvi, 
-                        data=modvars.accndvi.philt)
-predphi.lt<-predict.cforest(cforest.phi.lt, newdata=modvars.accndvi.philt)
-hist(predphi.lt)
-hist(cos(modvars.accndvi.philt$accndviphi.ts2))
+partial(cforest.phi.st, pred.var="maxdepth", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="lake_area_ha", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="doc", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="cv.accndvi", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="shoredev", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="pct.wetlands", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="prcp.normal", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="chla", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="pct.ag", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="tsi.cat", train=modvars.accndvi.phist, type="regression", plot=T)
+partial(cforest.phi.st, pred.var="hu4_zoneid", train=modvars.accndvi.phist, type="regression", plot=T)
+
+cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
+                          cv.accndvi + pct.wetlands + doc + prcp.normal, 
+                        data=modvars.accndvi.philt,controls=cforest_control(ntree=40000))
+predphi.lt<-predict(cforest.phi.lt, newdata=modvars.accndvi.philt)
+# hist(predphi.lt)
+# hist(cos(modvars.accndvi.philt$accndviphi.ts2))
 plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
@@
 cor.test(predphi.lt,cos(modvars.accndvi.philt$accndviphi.ts2))
-varimp.phi.lt<-varimp.cforest(cforest.phi.lt)
-print(varimp.phi.lt)
+varimp.phi.lt<-varimp(cforest.phi.lt)
+print(varimp.phi.lt[order(varimp.phi.lt, decreasing=TRUE)])
+
+partial(cforest.phi.lt, pred.var="hu4_zoneid", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="lake_area_ha", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="prcp.normal", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="pct.wetlands", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="doc", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="shoredev", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="chla", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="cv.accndvi", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="maxdepth", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="pct.ag", train=modvars.accndvi.philt, type="regression", plot=T)
+partial(cforest.phi.lt, pred.var="tsi.cat", train=modvars.accndvi.philt, type="regression", plot=T)
 

### 2019-10-04 AnalysisCode/ms1_analyses_gam.Rmd
analyses updates in progress

---
title: 'Q1: Are lake and terrestrial primary productivity coherent?'
author: "Jonathan Walter, Grace Wilkinson, Rachel Fleck, Michael Pace"
date: "4/17/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(aqts)
library(wsyn)
library(rgdal)
library(LAGOSNE)
library(raster)
library(MuMIn)
library(dplyr)
library(nlme)
library(lmerTest)
library(viridis)
library(fields)
#library(partykit)
# library(pdp)
# library(party)
library(mgcv)
library(MuMIn)
library(spatstat)

rm(list=ls())

```

This document organizes for openness and reproducibility analyses of the temporal coherence of interannual variation in lake primary productivity with terrestrial primary productivity in the landscape surrounding the lake.

# Data import

Data produced in 'ms1_prep.Rmd' are loaded.

```{r load workspace, echo=TRUE, cache=FALSE}

load("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873.RData")

```

```{r examine missing values, echo=TRUE, cache=FALSE}
any(sapply(analysislakes$lakedata, function(x){any(is.infinite(x))}))
any(sapply(analysislakes$lakedata, function(x){any(is.na(x))}))
which(sapply(analysislakes$lakedata, function(x){any(is.na(x))}))
analysislakes$lakeinfo[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))})),]

# image(accndvi)
# points(lakepts.prj[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))})),])

dbuff[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))}))]

analysislakes$lakeinfo<-analysislakes$lakeinfo[!sapply(analysislakes$lakedata, function(x){any(is.na(x))}),]
analysislakes$lakedata<-analysislakes$lakedata[!sapply(analysislakes$lakedata, function(x){any(is.na(x))})]

analysislakes$lakeinfo$tslength<-analysislakes$lakeinfo$end-analysislakes$lakeinfo$start+1
# analysislakes$lakedata<-analysislakes$lakedata[!analysislakes$lakeinfo$tslength < 20]
# analysislakes$lakeinfo<-analysislakes$lakeinfo[!analysislakes$lakeinfo$tslength < 20,]

```

```{r compute coherences, echo=TRUE, cache=FALSE}

source("~/GitHub/AquaTerrSynch/AnalysisCode/bandtest_coh.R")

tsranges<-rbind(c(2,4),c(4,Inf),c(2,Inf))

coh.chlaXaccndvi<-NULL
#coh.chlaXmaxndvi<-NULL

for(lind in 1:length(analysislakes$lakedata)){
  lakedat.ii<-cleandat(analysislakes$lakedata[[lind]], as.numeric(colnames(analysislakes$lakedata[[lind]])), clev=5)$cdat
  chlaXaccndvi<-coh(lakedat.ii[1,], lakedat.ii[2,], as.numeric(colnames(analysislakes$lakedata[[lind]])),
                    norm="powall", sigmethod="fast", nrand=10000)
#  chlaXmaxndvi<-coh(lakedat.ii[1,], lakedat.ii[3,], as.numeric(colnames(analysislakes$lakedata[[lind]])),
#                    norm="powall", sigmethod="fast", nrand=10000)
  for(rind in 1:nrow(tsranges)){
    chlaXaccndvi<-bandtest.coh(chlaXaccndvi, tsranges[rind,])
    #chlaXmaxndvi<-bandtest.coh(chlaXmaxndvi, tsranges[rind,])
  }
  coh.chlaXaccndvi<-rbind(coh.chlaXaccndvi, c(t(as.matrix(chlaXaccndvi$bandp[,3:5]))))
#  coh.chlaXmaxndvi<-rbind(coh.chlaXmaxndvi, c(t(as.matrix(chlaXmaxndvi$bandp[,3:5]))))

}

coh.chlaXaccndvi<-as.data.frame(coh.chlaXaccndvi)
#coh.chlaXmaxndvi<-as.data.frame(coh.chlaXmaxndvi)

colnames(coh.chlaXaccndvi)<-paste0("accndvi",c("p.ts1","phi.ts1","coh.ts1","p.ts2","phi.ts2","coh.ts2","p.ts3","phi.ts3","coh.ts3"))
#colnames(coh.chlaXmaxndvi)<-paste0("maxndvi",c("p.ts1","phi.ts1","coh.ts1","p.ts2","phi.ts2","coh.ts2","p.ts3","phi.ts3","coh.ts3"))

coh.chlaXaccndvi$lagoslakeid<-analysislakes$lakeinfo$lagoslakeid
#coh.chlaXmaxndvi$lagoslakeid<-analysislakes$lakeinfo$lagoslakeid

```

```{r pedagogical example, echo=TRUE, cache=FALSE}
#looking for especially coherent lakes did not return easy-to-interpret examples. Proceeding with simulated data

tmax=50
res=0.1
tt=seq(1,tmax,res)

p1<-2
sig1<-sin(seq(0,2*pi*tmax/p1,length.out=length(tt)))
p2<-10
sig2<-sin(seq(0,2*pi*tmax/p2,length.out=length(tt)))

comb1<-sig1+0.7*sig2+3.5
comb2<-sig1+-0.7*sig2

laymat<-matrix(1,nrow=2,ncol=3)
laymat[2,]<-2:4

sig3<-sig2[tt<=20]
sig4<-sig3*0.9
sig5<-sin(seq(-pi/2,2*pi*20/p2-(pi/2),length.out=length(tt[tt<=20])))
sig6<-sig3*-1

# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig1_pedagogical.tif", units="in",
#      res=300, width=6.5, height=4)
# 
# layout(laymat)
# par(mar=c(1.5,1.5,2,1.5), mgp=c(1,1,0), oma=c(2,2,0,0))
# 
# plot(NA,NA,ylim=c(-2,5.2),xlim=range(tt), xlab="", ylab="", xaxt="n",yaxt="n")
# lines(tt,comb1,lwd=2)
# lines(tt,comb2,lwd=2,col="red")
# axis(1, at=c(0,10,20,30,40,50),labels=NA)
# axis(2, at=c(-1,1.5,4), labels=NA)
# mtext("Timescale specific relationship",3,line=0.25)
# text(0.4,4.9,"a)",cex=1.2)
# 
# plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
# axis(1, at=c(0,10,20), labels=NA)
# axis(2, at=c(-1,0,1), labels=NA)
# lines(tt[tt<=20],sig3,lwd=2)
# lines(tt[tt<=20],sig4,lwd=2,col="red")
# mtext(expression(paste(phi," = 0")))
# text(1,0.9,"b)",cex=1.2)
# 
# plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
# axis(1, at=c(0,10,20), labels=NA)
# axis(2, at=c(-1,0,1), labels=NA)
# lines(tt[tt<=20],sig3,lwd=2)
# lines(tt[tt<=20],sig5,lwd=2,col="red")
# mtext(expression(paste(phi," = ",pi,"/2")))
# text(1,0.9,"c)",cex=1.2)
# 
# plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
# axis(1, at=c(0,10,20), labels=NA)
# axis(2, at=c(-1,0,1), labels=NA)
# lines(tt[tt<=20],sig3,lwd=2)
# lines(tt[tt<=20],sig6,lwd=2,col="red")
# mtext(expression(paste(phi," = ",pi)))
# text(1,0.9,"d)",cex=1.2)
# 
# 
# mtext("Time", 1, outer=T)
# mtext("Signal", 2, outer=T)
# 
# dev.off()

```

```{r summarize coherences, echo=TRUE, cache=FALSE}
#short timescales
hist(coh.chlaXaccndvi$accndvicoh.ts1, main="Accumulated NDVI, short timescales", xlab="Coherence", ylab="Frequency")
#hist(coh.chlaXmaxndvi$maxndvicoh.ts1, main="Maximum NDVI, short timescales", xlab="Coherence", ylab="Frequency")

quantile(coh.chlaXaccndvi$accndvicoh.ts1)
#quantile(coh.chlaXmaxndvi$maxndvicoh.ts1)

alpha=0.05
sum(coh.chlaXaccndvi$accndvip.ts1<alpha)/nrow(coh.chlaXaccndvi)
#sum(coh.chlaXmaxndvi$maxndvip.ts1<alpha)/nrow(coh.chlaXmaxndvi)

print(cbind(coh.chlaXaccndvi$lagoslakeid, coh.chlaXaccndvi$accndvip.ts1)[coh.chlaXaccndvi$accndvip.ts1<alpha,])
print(cbind(coh.chlaXaccndvi$lagoslakeid, coh.chlaXaccndvi$accndvip.ts2)[coh.chlaXaccndvi$accndvip.ts2<alpha,])

cor(coh.chlaXaccndvi$accndvicoh.ts1,coh.chlaXaccndvi$accndvicoh.ts2)

# print(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<alpha]/pi) #only pattern is that lakes don't lead the landscape
# print(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<alpha]/pi)

phicls<-c(-1,-.75,-0.25,0.25,0.75,1)

# hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.2]/pi, main="Accumulated NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian",
     breaks=seq(0,2*pi,length.out=16))
#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<0.2]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)

#long timescales
hist(coh.chlaXaccndvi$accndvicoh.ts2, main="Accumulated NDVI, long timescales", xlab="Coherence", ylab="Frequency")
#hist(coh.chlaXmaxndvi$maxndvicoh.ts2, main="Maximum NDVI, long timescales", xlab="Coherence", ylab="Frequency")

quantile(coh.chlaXaccndvi$accndvicoh.ts2)
#quantile(coh.chlaXmaxndvi$maxndvicoh.ts2)

alpha=0.05
sum(coh.chlaXaccndvi$accndvip.ts2<alpha)/nrow(coh.chlaXaccndvi)
#sum(coh.chlaXmaxndvi$maxndvip.ts2<alpha)/nrow(coh.chlaXmaxndvi)

print(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<alpha]/pi)
#print(coh.chlaXmaxndvi$maxndviphi.ts2[coh.chlaXmaxndvi$maxndvip.ts2<alpha]/pi)

# hist(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.2]/pi, main="Accumulated NDVI, long timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian",
     breaks=seq(0,2*pi,length.out=16))

#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvicoh.ts2>0.6]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
# 
# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions.tif", units="in",
#      res=300, width=6.5, height=6.5)
# 
# par(mar=c(3,3,2,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),cex.main=0.9)
# 
# hist(coh.chlaXaccndvi$accndvicoh.ts1, main="Short timescale coherence", xlab="Coherence", ylab="Frequency", col="lightgrey")
# text(par()$usr[1]+.05,0.95*par()$usr[4],"a)")
# hist(coh.chlaXaccndvi$accndvicoh.ts2, main="Long timescale coherence", xlab="Coherence", ylab="Frequency", col="lightgrey")
# text(par()$usr[1]+.05,0.95*par()$usr[4],"b)")
# 
# par(mar=c(1,1,2,1))
# rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian", col="lightgrey",
#      breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Short timescale phases",
#        at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
# text(0.9*par()$usr[1],0.95*par()$usr[4],"c)")
# rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian", col="lightgrey",
#      breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Long timescale phases",
#      at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
# text(0.9*par()$usr[1],0.95*par()$usr[4],"d)")
# 
# dev.off()

```

```{r mapping, echo=TRUE, cache=FALSE}

states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020.shp")
getstates<-c("Minnesota", "Iowa", "Wisconsin", "Illinois", "Missouri", "Michigan", "Indiana", "Ohio", "Pennsylvania", "New York", "New Jersey", "Connecticut", "New Hampshire", "Rhode Island", "Massachusetts", "Vermont", "Maine")
lagosstates<-states[states@data$STATE %in% getstates,]

plot(lagosstates, main="Lakes selected for analysis")
points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=16, cex=1, col="blue")

cohplotdata<-left_join(analysislakes$lakeinfo, coh.chlaXaccndvi, by="lagoslakeid")

pal<-viridis(100)

par(mar=c(1,0,2,0))

plot(lagosstates, main="Lakes by short timescale coherence")
par()$usr
points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)

plot(lagosstates, main="Lakes by long timescale coherence")
points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)

laymat=matrix(1,nrow=2,ncol=13)
laymat[2,]<-2
laymat[,13]<-3

# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_coherencemap.tif", units="in",
#      res=300, width=6.5, height=7.5)
# 
# layout(laymat)
# par(mar=c(0,0,1.5,0))
# 
# plot(lagosstates, main="Short timescale coherence")
# points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
# text(0.99*par()$usr[1],0.99*par()$usr[4],"a)",cex=1.5)
# 
# plot(lagosstates, main="Long timescale coherence")
# points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
# text(0.99*par()$usr[1],0.99*par()$usr[4],"b)",cex=1.5)
# 
# par(mar=c(5,1,5,1))
# image(matrix(1:100,nrow=1),col=pal,xaxt="n",yaxt="n")
# axis(2,at=seq(0,1,0.2))
# 
# dev.off()

```

```{r add vars for modelling, echo=TRUE, cache=FALSE}

#Need to add: depth, average growing season Chlorophyll-a, TSI(chla) categories, pct ag

#agriculture -- is 500m buffer best? Other options include 100m buffer (probably too small) and hu12 watershed
# pct.ag<-lagosne_select(table="buffer500m.lulc", vars=c("lagoslakeid","buffer500m_nlcd2001_pct_82","buffer500m_nlcd2006_pct_82","buffer500m_nlcd2011_pct_82"))
pct.ag<-lagosne_select(table="hu12.lulc", vars=c("hu12_zoneid","hu12_nlcd2001_pct_82","hu12_nlcd2006_pct_82","hu12_nlcd2011_pct_82"))
pct.ag<-pct.ag[pct.ag$hu12_zoneid %in% analysislakes$lakeinfo$hu12_zoneid,]
pct.ag.avg<-data.frame(hu12_zoneid=pct.ag$hu12_zoneid, pct.ag=rowMeans(pct.ag[,2:4]))

#Wetlands
pct.wetlands<-lagosne_select(table="hu12.lulc", vars=c(c("hu12_zoneid","hu12_nlcd2001_pct_90","hu12_nlcd2006_pct_90",
                                                         "hu12_nlcd2011_pct_90","hu12_nlcd2001_pct_95","hu12_nlcd2006_pct_95",
                                                         "hu12_nlcd2011_pct_95")))
pct.wetlands<-pct.wetlands[pct.wetlands$hu12_zoneid %in% analysislakes$lakeinfo$hu12_zoneid,]
pct.wetlands$sum2001<-rowSums(pct.wetlands[,c(2,5)])
pct.wetlands$sum2006<-rowSums(pct.wetlands[,c(3,6)])
pct.wetlands$sum2011<-rowSums(pct.wetlands[,c(4,7)])
pct.wetlands.avg<-data.frame(hu12_zoneid=pct.wetlands$hu12_zoneid, pct.wetlands=rowMeans(pct.wetlands[,8:10]))

#depth
depth<-lagosne_select(table="lakes_limno", vars=c("lagoslakeid","maxdepth"))
depth<-depth[depth$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,] #use max depth because it's more complete

#growing season Chlorophyll-a
chla<-lagosne_select(table="epi_nutr", vars=c("lagoslakeid","samplemonth","chla"))
chla<-chla[chla$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
gs.chla<-chla[chla$samplemonth %in% 5:9,]
avg.chla<-aggregate(chla ~ lagoslakeid, data=gs.chla, FUN=mean, na.rm=T)

#growing season DOC
doc<-lagosne_select(table="epi_nutr", vars=c("lagoslakeid","samplemonth","doc"))
doc<-doc[doc$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
gs.doc<-doc[doc$samplemonth %in% 5:9,]
avg.doc<-aggregate(doc ~ lagoslakeid, data=gs.doc, FUN=mean, na.rm=T)

#Chlorophyll-a TSI class
#TSI(CHL) = 9.81 ln(CHL) + 30.6
tsi.chl<-data.frame(lagoslakeid=avg.chla$lagoslakeid, tsi=9.81 * log(avg.chla$chla) + 30.6)
tsi.chl$tsi.cat<-rep("lake",nrow(tsi.chl))

tsi.chl$tsi.cat[tsi.chl$tsi < 40]<-"oligotrophic"
tsi.chl$tsi.cat[tsi.chl$tsi >=40 & tsi.chl$tsi < 50]<-"mesotrophic"
tsi.chl$tsi.cat[tsi.chl$tsi >=50 & tsi.chl$tsi < 70]<-"eutrophic"
tsi.chl$tsi.cat[tsi.chl$tsi >= 70] <-"hypereutrophic"

#CV of terrestrial NDVI
cv.accndvi<-NULL
for(lake in 1:length(analysislakes$lakedata)){
  tmp<-analysislakes$lakedata[[lake]][rownames(analysislakes$lakedata[[lake]])=="accndvi",]
  cv.accndvi<-c(cv.accndvi, sd(tmp)/mean(tmp))  
 # rm(tmp)
}
cv.accndvi<-data.frame(lagoslakeid=as.numeric(names(analysislakes$lakedata)), cv.accndvi=cv.accndvi)

#mean precipitation
prcp.normal<-raster("~/Box Sync/NSF EAGER Synchrony/Data/PRISM Data/PRISM_ppt_30yr_normal_800mM2_annual_bil.bil")
lakepts<-SpatialPoints(coords=cbind(analysislakes$lakeinfo$nhd_long,analysislakes$lakeinfo$nhd_lat))
lake.prcp<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid, prcp.normal=raster::extract(prcp.normal,lakepts))

#huc2 and huc4 watershed codes
huc_codes<-read.csv("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')

#state info
states<-lagosne_select(table="state", vars=c("state_zoneid","state_name"))

#shoreline development ratio
sdev<-analysislakes$lakeinfo$lake_perim_meters/(2*sqrt(pi*analysislakes$lakeinfo$lake_area_ha*10000))
shoredev<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid,shoredev=sdev)

predictors<-analysislakes$lakeinfo
predictors<-left_join(predictors, depth, by="lagoslakeid")
predictors<-left_join(predictors, pct.ag.avg, by="hu12_zoneid")
predictors<-left_join(predictors, pct.wetlands.avg, by="hu12_zoneid")
predictors<-left_join(predictors, avg.chla, by="lagoslakeid")
predictors<-left_join(predictors, tsi.chl, by="lagoslakeid")
predictors<-left_join(predictors, states, by="state_zoneid")
predictors<-left_join(predictors, cv.accndvi, by="lagoslakeid")
predictors<-left_join(predictors, avg.doc, by="lagoslakeid")
predictors<-left_join(predictors, lake.prcp, by="lagoslakeid")
predictors<-left_join(predictors, shoredev, by="lagoslakeid")
#predictors<-left_join(predictors, huc_codes, by="hu4_zoneid")

for(nn in 1:ncol(predictors)){

  if(is.factor(predictors[,nn])){
    predictors[,nn]<-factor(predictors[,nn])
  }

}

str(predictors)
hist(predictors$tslength)
hist(predictors$lake_area_ha)
hist(log10(predictors$lake_area_ha))
hist(predictors$lake_perim_meters)
hist(log10(predictors$lake_perim_meters))
table(predictors$nhd_fcode)
table(predictors$hu12_zoneid)
hist(predictors$elevation_m)
hist(predictors$maxdepth)
hist(log10(predictors$maxdepth))
hist(predictors$pct.ag)
hist(log10(predictors$pct.ag))
hist(predictors$chla)
hist(log10(predictors$chla))
hist(predictors$tsi)
table(predictors$tsi.cat)
hist(predictors$cv.accndvi)
hist(predictors$pct.wetlands)
hist(predictors$doc)
hist(predictors$prcp.normal)
hist(predictors$shoredev)

predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha) #not necessary to transform with random forests
# predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
# predictors$log10_maxdepth<-log10(predictors$maxdepth)
# predictors$log10_pct.ag<-log10(predictors$pct.ag+1)
# predictors$log10_chla<-log10(predictors$chla)

modvars.accndvi<-left_join(predictors, coh.chlaXaccndvi, by="lagoslakeid")
modvars.accndvi$nhd_ftype<-factor(modvars.accndvi$nhd_ftype)
modvars.accndvi$tsi.cat<-factor(modvars.accndvi$tsi.cat)
modvars.accndvi$tslength<-modvars.accndvi$end-modvars.accndvi$start + 1

modvars.accndvi<-modvars.accndvi[!is.na(modvars.accndvi$maxdepth),]
modvars.accndvi<-modvars.accndvi[!is.na(modvars.accndvi$pct.ag),]

modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.3,]
modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.3,]

```

```{r modellingCoherence, echo=TRUE, cache=FALSE}

# cforest.st<-partykit::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
# #                     data=modvars.accndvi, ntree=20000)
# cforest.st<-party::cforest(accndvicoh.ts1 ~ shoredev + lake_area_ha +  maxdepth + pct.ag + chla + tsi.cat + 
#                              hu4_zoneid + cv.accndvi + pct.wetlands + doc + prcp.normal,
#                     data=modvars.accndvi, controls=cforest_control(ntree=80000))

lwgt<-modvars.accndvi$tslength/mean(modvars.accndvi$tslength)

gam.cohst<-gam(accndvicoh.ts1 ~ s(shoredev) + s(prcp.normal) + s(log10(lake_area_ha)) + s(pct.ag),  weights=lwgt, data=modvars.accndvi, 
               gamma=1.4, na.action = "na.fail")
#dredge.cohst<-dredge(gam.cohst, evaluate=TRUE, m.lim=c(0,5))
#importance(dredge.cohst)
#modavg.cohst<-model.avg(dredge.cohst, fit=T)
summary(gam.cohst)

plot(modvars.accndvi$accndvicoh.ts1,predict(gam.cohst))

topmod.cohst<-gam(accndvicoh.ts1 ~ s(shoredev,k=3) + s(log10(lake_area_ha),k=3) + s(prcp.normal,k=3) + s(pct.ag,k=3), data=modvars.accndvi,
                  gamma=1)
summary(topmod.cohst)

gam.cohlt<-gam(accndvicoh.ts2 ~ s(shoredev,k=3) + s(log10(lake_area_ha),k=3) +  s(maxdepth,k=3) + s(pct.ag,k=3) + 
                 s(chla,k=3) + tsi.cat + hu4_zoneid + s(cv.accndvi,k=3) + s(pct.wetlands,k=3) +  #removed doc because of NAs
                 s(prcp.normal,k=3), data=modvars.accndvi, gamma=1,na.action = "na.fail")
dredge.cohlt<-dredge(gam.cohlt, evaluate=TRUE, m.lim=c(0,5))
importance(dredge.cohlt)
modavg.cohlt<-model.avg(dredge.cohlt, fit=T)

plot(modvars.accndvi$accndvicoh.ts1,predict(modavg.cohlt))

topmod.cohlt<-gam(accndvicoh.ts1 ~ s(pct.wetlands,k=3) + s(cv.accndvi,k=3) + s(prcp.normal,k=3) + s(maxdepth,k=3), data=modvars.accndvi,
                  gamma=1)
summary(topmod.cohlt)

predcoh.st<-predict(cforest.st, newdata=modvars.accndvi,type="response")
#hist(predcoh.st)
#hist(modvars.accndvi$accndvicoh.ts1)
plot(predcoh.st, modvars.accndvi$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
     xlim=c(0,1), ylim=c(0,1))
abline(a=0,b=1)
cor.test(predcoh.st,modvars.accndvi$accndvicoh.ts1)
varimp.coh.st<-varimp(cforest.st)
print(varimp.coh.st[order(varimp.coh.st, decreasing=T)])

pdp.shoredev.coh.st<-partial(cforest.st, pred.var="shoredev", train=modvars.accndvi, type="regression", plot=T)
pdp.prcp.coh.st<-partial(cforest.st, pred.var="prcp.normal", train=modvars.accndvi, type="regression", plot=T)
pdp.ag.coh.st<-partial(cforest.st, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
pdp.maxdepth.coh.st<-partial(cforest.st, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
pdp.lakearea.coh.st<-partial(cforest.st, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
pdp.chla.coh.st<-partial(cforest.st, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
pdp.doc.coh.st<-partial(cforest.st, pred.var="doc", train=modvars.accndvi, type="regression", plot=T)
pdp.cv.coh.st<-partial(cforest.st, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
pdp.wetlands.coh.st<-partial(cforest.st, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
pdp.region.coh.st<-partial(cforest.st, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
pdp.tsi.coh.st<-partial(cforest.st, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)

cforest.lt<-party::cforest(accndvicoh.ts2 ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid 
                           + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
predcoh.lt<-predict(cforest.lt, newdata=modvars.accndvi)
# hist(predcoh.lt)
# hist(modvars.accndvi$accndvicoh.ts2)
plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long st",
     xlim=c(0,1), ylim=c(0,1))
abline(a=0,b=1)
cor.test(predcoh.lt,modvars.accndvi$accndvicoh.ts2)
varimp.coh.lt<-varimp(cforest.lt)
print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)])

pdp.wetlands.coh.lt<-partial(cforest.lt, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
pdp.cv.coh.lt<-partial(cforest.lt, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
pdp.region.coh.lt<-partial(cforest.lt, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
pdp.tsi.coh.lt<-partial(cforest.lt, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
pdp.doc.coh.lt<-partial(cforest.lt, pred.var="doc", train=modvars.accndvi, type="regression", plot=T)
pdp.prcp.coh.lt<-partial(cforest.lt, pred.var="prcp.normal", train=modvars.accndvi, type="regression", plot=T)
pdp.lakearea.coh.lt<-partial(cforest.lt, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
pdp.chla.coh.lt<-partial(cforest.lt, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
pdp.shoredev.coh.lt<-partial(cforest.lt, pred.var="shoredev", train=modvars.accndvi, type="regression", plot=T)
pdp.ag.coh.lt<-partial(cforest.lt, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
pdp.maxdepth.coh.lt<-partial(cforest.lt, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)

```

```{r modellingPhase, echo=TRUE, cache=FALSE}

cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + 
                          hu4_zoneid + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
                        data=modvars.accndvi.phist,controls=cforest_control(ntree=40000))
predphi.st<-predict(cforest.phi.st, newdata=modvars.accndvi.phist)
# hist(predphi.st)
# hist(cos(modvars.accndvi.phist$accndviphi.ts1))
plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
     xlim=c(-1,1), ylim=c(-1,1))
abline(a=0,b=1)
cor.test(predphi.st,cos(modvars.accndvi.phist$accndviphi.ts1))
varimp.phi.st<-varimp(cforest.phi.st)
print(varimp.phi.st[order(varimp.phi.st,decreasing=TRUE)])

pdp.maxdepth.phi.st<-partial(cforest.phi.st, pred.var="maxdepth", train=modvars.accndvi.phist, type="regression", plot=T)
pdp.lakearea.phi.st<-partial(cforest.phi.st, pred.var="lake_area_ha", train=modvars.accndvi.phist, type="regression", plot=T)
pdp.doc.phi.st<-partial(cforest.phi.st, pred.var="doc", train=modvars.accndvi.phist, type="regression", plot=T)
pdp.cv.phi.st<-partial(cforest.phi.st, pred.var="cv.accndvi", train=modvars.accndvi.phist, type="regression", plot=T)
pdp.shoredev.phi.st<-partial(cforest.phi.st, pred.var="shoredev", train=modvars.accndvi.phist, type="regression", plot=T)
pdp.wetlands.phi.st<-partial(cforest.phi.st, pred.var="pct.wetlands", train=modvars.accndvi.phist, type="regression", plot=T)
pdp.prcp.phi.st<-partial(cforest.phi.st, pred.var="prcp.normal", train=modvars.accndvi.phist, type="regression", plot=T)
pdp.chla.phi.st<-partial(cforest.phi.st, pred.var="chla", train=modvars.accndvi.phist, type="regression", plot=T)
pdp.ag.phi.st<-partial(cforest.phi.st, pred.var="pct.ag", train=modvars.accndvi.phist, type="regression", plot=T)
pdp.tsi.phi.st<-partial(cforest.phi.st, pred.var="tsi.cat", train=modvars.accndvi.phist, type="regression", plot=T)
pdp.region.phi.st<-partial(cforest.phi.st, pred.var="hu4_zoneid", train=modvars.accndvi.phist, type="regression", plot=T)

cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
                          cv.accndvi + pct.wetlands + doc + prcp.normal, 
                        data=modvars.accndvi.philt,controls=cforest_control(ntree=40000))
predphi.lt<-predict(cforest.phi.lt, newdata=modvars.accndvi.philt)
# hist(predphi.lt)
# hist(cos(modvars.accndvi.philt$accndviphi.ts2))
plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
     xlim=c(-1,1), ylim=c(-1,1))
abline(a=0,b=1)
cor.test(predphi.lt,cos(modvars.accndvi.philt$accndviphi.ts2))
varimp.phi.lt<-varimp(cforest.phi.lt)
print(varimp.phi.lt[order(varimp.phi.lt, decreasing=TRUE)])

pdp.region.phi.lt<-partial(cforest.phi.lt, pred.var="hu4_zoneid", train=modvars.accndvi.philt, type="regression", plot=T)
pdp.lakearea.phi.lt<-partial(cforest.phi.lt, pred.var="lake_area_ha", train=modvars.accndvi.philt, type="regression", plot=T)
pdp.prsp.phi.lt<-partial(cforest.phi.lt, pred.var="prcp.normal", train=modvars.accndvi.philt, type="regression", plot=T)
pdp.wetlands.phi.lt<-partial(cforest.phi.lt, pred.var="pct.wetlands", train=modvars.accndvi.philt, type="regression", plot=T)
pdp.doc.phi.lt<-partial(cforest.phi.lt, pred.var="doc", train=modvars.accndvi.philt, type="regression", plot=T)
pdp.shoredev.phi.lt<-partial(cforest.phi.lt, pred.var="shoredev", train=modvars.accndvi.philt, type="regression", plot=T)
pdp.chla.phi.lt<-partial(cforest.phi.lt, pred.var="chla", train=modvars.accndvi.philt, type="regression", plot=T)
pdp.cv.phi.lt<-partial(cforest.phi.lt, pred.var="cv.accndvi", train=modvars.accndvi.philt, type="regression", plot=T)
pdp.maxdepth.phi.lt<-partial(cforest.phi.lt, pred.var="maxdepth", train=modvars.accndvi.philt, type="regression", plot=T)
pdp.ag.phi.lt<-partial(cforest.phi.lt, pred.var="pct.ag", train=modvars.accndvi.philt, type="regression", plot=T)
pdp.tsi.phi.lt<-partial(cforest.phi.lt, pred.var="tsi.cat", train=modvars.accndvi.philt, type="regression", plot=T)

save.image("~/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analyses_complete_20190729.RData")

```
```{r plot predictions, echo=TRUE, cache=FALSE}

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS1_predvsemp.tif", units="in",
     res=300, width=6.5, height=6.5)

par(mar=c(2.5,2.5,1.5,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),oma=c(1.2,1.2,0,0))

plot(predcoh.st, modvars.accndvi$accndvicoh.ts1, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="")
mtext("Short timescale coherence",line=0.2)
abline(a=0,b=1)

plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="")
mtext("Long timescale coherence",line=0.2)
abline(a=0,b=1)

plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlim=c(-1,1), ylim=c(-1,1), xlab="", ylab="")
mtext("Short timescale cos(phase)",line=0.2)
abline(a=0,b=1)

plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlim=c(-1,1), ylim=c(-1,1), xlab="", ylab="")
mtext("Short timescale cos(phase)",line=0.2)
abline(a=0,b=1)

mtext("Predicted",1,outer=T)
mtext("Empirical",2,outer=T)

dev.off()

```

```{r varimp plotting, echo=TRUE, cache=FALSE}
#fig 4: variable importance in rank order

cleannames<-function(dirtynames){
  out<-NULL
  for(ii in 1:length(dirtynames)){
    if(dirtynames[ii]=="shoredev"){out<-c(out,"Shore. devel.")}
    if(dirtynames[ii]=="lake_area_ha"){out<-c(out,"Lake area")}
    if(dirtynames[ii]=="maxdepth"){out<-c(out,"Depth")}
    if(dirtynames[ii]=="pct.ag"){out<-c(out,"% agriculture")}
    if(dirtynames[ii]=="chla"){out<-c(out,"Chlorophyll-a")}
    if(dirtynames[ii]=="tsi.cat"){out<-c(out,"TSI")}
    if(dirtynames[ii]=="hu4_zoneid"){out<-c(out,"HU4 watershed")}
    if(dirtynames[ii]=="cv.accndvi"){out<-c(out,"CV(NDVI)")}
    if(dirtynames[ii]=="pct.wetlands"){out<-c(out,"% wetlands")}
    if(dirtynames[ii]=="doc"){out<-c(out,"DOC")}
    if(dirtynames[ii]=="prcp.normal"){out<-c(out,"Precipitation")}
  }
  return(out)
}

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp.tif", units="in",
     res=300, width=6.5, height=6.5)

par(mar=c(6,3.8,1.5,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),oma=c(0,1.2,0,0))

barplot(varimp.coh.st[order(varimp.coh.st,decreasing=T)], names.arg=cleannames(names(varimp.coh.st)[order(varimp.coh.st,decreasing=T)]), las=2,
        cex.names=0.9)
mtext("a) Short timescale coherence", line=0.25, cex=0.9)
barplot(varimp.coh.lt[order(varimp.coh.lt,decreasing=T)], names.arg=cleannames(names(varimp.coh.lt)[order(varimp.coh.lt,decreasing=T)]), las=2,
        cex.names=0.9)
mtext("b) Long timescale coherence", line=0.25, cex=0.9)
barplot(varimp.phi.st[order(varimp.phi.st,decreasing=T)], names.arg=cleannames(names(varimp.phi.st)[order(varimp.phi.st,decreasing=T)]), las=2,
        cex.names=0.9)
mtext("c) Short timescale phase", line=0.25, cex=0.9)
barplot(varimp.phi.lt[order(varimp.phi.lt,decreasing=T)], names.arg=cleannames(names(varimp.phi.lt)[order(varimp.phi.lt,decreasing=T)]), las=2,
        cex.names=0.9)
mtext("d) Long timescale phase", line=0.25, cex=0.9)
mtext("Variable importance",2,outer=T)

dev.off()
#fig 5: top variable importances (9 total)

states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020.shp")
huc_bdys<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/huc4_watersheds.shp")
huc_codes<-read.csv("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
huc_codes<-huc_codes[huc_codes$hu4_zoneid %in% analysislakes$lakeinfo$hu4_zoneid,]

scale1_100<-function(x){
  x1<-x-min(x)+1/100
  x1<-round(x1/max(x1)*100)
  return(x1)
}

pdpdf.hu4.cohlt<-data.frame(hu4_zoneid=pdp.region.coh.lt$panel.args[[1]]$x, yhat=pdp.region.coh.lt$panel.args[[1]]$y)
pdpdf.hu4.cohlt<-left_join(pdpdf.hu4.cohlt, huc_codes)
huc_bdys1<-huc_bdys[huc_bdys$HUC4 %in% pdpdf.hu4.cohlt$huc4_code,]
huc_bdys1@data<-left_join(huc_bdys1@data, pdpdf.hu4.cohlt, by=c("HUC4"="huc4_code"))

pdpdf.hu4.philt<-data.frame(hu4_zoneid=pdp.region.phi.lt$panel.args[[1]]$x, yhat=pdp.region.phi.lt$panel.args[[1]]$y)
pdpdf.hu4.philt<-left_join(pdpdf.hu4.philt, huc_codes)
huc_bdys2<-huc_bdys[huc_bdys$HUC4 %in% pdpdf.hu4.philt$huc4_code,]
huc_bdys2@data<-left_join(huc_bdys2@data, pdpdf.hu4.philt, by=c("HUC4"="huc4_code"))

#make smaller images that we can insert into the main figure

png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5f_hu4_cohlt.png", units="in",
     res=300, width=6.5/3, height=8/3)
par(mar=c(0,0,0,0))
plot(huc_bdys1,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys1$yhat)])
lines(states)
par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys1$yhat), max(huc_bdys1$yhat), length.out=5),2), cex=0.8)
dev.off()

png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu4_philt.png", units="in",
     res=300, width=6.5/3, height=8/3)
par(mar=c(0,0,0,0))
plot(huc_bdys2,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys2$yhat)])
lines(states)
par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys2$yhat), max(huc_bdys2$yhat), length.out=5),2), cex=0.8)
dev.off()

laymat<-matrix(1:9,3,3,byrow=T)

library(png)
panel5f<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5f_hu4_cohlt.png")
panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu4_philt.png")

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_partialeffects.tif", units="in",
     res=300, width=6.5, height=8)
layout(laymat)
par(mar=c(3.6,2,1.5,1),mgp=c(1.7,0.5,0),oma=c(0,1.5,0,0))
#cohst ~ shoredev, precip, % ag
plot(pdp.shoredev.coh.st$panel.args[[1]]$x, pdp.shoredev.coh.st$panel.args[[1]]$y, type="l", xlab="Shore. devel.", ylab="")
mtext("a) Short timesecale coherence", line=0.25, cex=0.7)
plot(pdp.prcp.coh.st$panel.args[[1]]$x, pdp.prcp.coh.st$panel.args[[1]]$y, type="l", xlab="Precipitation (mm/yr)", ylab="")
mtext("b) Short timesecale coherence", line=0.25, cex=0.7)
plot(pdp.ag.coh.st$panel.args[[1]]$x, pdp.ag.coh.st$panel.args[[1]]$y, type="l", xlab="Partial effect", ylab="")
mtext("c) Short timesecale coherence", line=0.25, cex=0.7)
#cohlt ~ pct.wetlands, cv(ndvi), hu4_zoneid
plot(pdp.wetlands.coh.lt$panel.args[[1]]$x, pdp.wetlands.coh.lt$panel.args[[1]]$y, type="l", xlab="% Wetlands", ylab="")
mtext("d) Long timescale coherence", line=0.25, cex=0.7)
plot(pdp.cv.coh.lt$panel.args[[1]]$x, pdp.cv.coh.lt$panel.args[[1]]$y, type="l", xlab="CV(NDVI)", ylab="")
mtext("e) Long timescale coherence", line=0.25, cex=0.7)
plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HU4 watershed",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
rasterImage(image=panel5f,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
mtext("f) Long timescale coherence", line=0.25, cex=0.7)
#phist ~ depth, lake area
plot(pdp.maxdepth.phi.st$panel.args[[1]]$x, pdp.maxdepth.phi.st$panel.args[[1]]$y, type="l", xlab="Depth (m)", ylab="")
mtext("g) Short timescale phase", line=0.25, cex=0.7)
plot(pdp.lakearea.phi.st$panel.args[[1]]$x, pdp.lakearea.phi.st$panel.args[[1]]$y, type="l", xlab="Lake area (ha)", ylab="")
mtext("h) Short timescale phase", line=0.25, cex=0.7)
#philt ~ hu4_zoneid
plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HU4 watershed", xaxt="n",yaxt="n",mgp=c(1,0.5,0))
rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
mtext("i) Long timescale phase", line=0.25, cex=0.7)

mtext("Partial effect",side=2, outer=T, line=0.1)

dev.off()

```

### 2019-10-04 AnalysisCode/ms1_analyses_rf_testnewvars.Rmd
analyses updates in progress

--- 2019-10-04 AnalysisCode/ms1_analyses_gam.Rmd
@@
 ---
-title: 'Q1: Are lake and terrestrial primary productivity coherent?'
+title: "ms1_analyses_rf_testnewvars"
 author: "Jonathan Walter, Grace Wilkinson, Rachel Fleck, Michael Pace"
-date: "4/17/2019"
+date: "10/3/2019"
 output: pdf_document
@@
 #library(partykit)
-# library(pdp)
-# library(party)
-library(mgcv)
-library(MuMIn)
+library(pdp)
+library(party)
 library(spatstat)
+library(caret)
 
@@
 
-```{r pedagogical example, echo=TRUE, cache=FALSE}
-#looking for especially coherent lakes did not return easy-to-interpret examples. Proceeding with simulated data
-
-tmax=50
-res=0.1
-tt=seq(1,tmax,res)
-
-p1<-2
-sig1<-sin(seq(0,2*pi*tmax/p1,length.out=length(tt)))
-p2<-10
-sig2<-sin(seq(0,2*pi*tmax/p2,length.out=length(tt)))
-
-comb1<-sig1+0.7*sig2+3.5
-comb2<-sig1+-0.7*sig2
-
-laymat<-matrix(1,nrow=2,ncol=3)
-laymat[2,]<-2:4
-
-sig3<-sig2[tt<=20]
-sig4<-sig3*0.9
-sig5<-sin(seq(-pi/2,2*pi*20/p2-(pi/2),length.out=length(tt[tt<=20])))
-sig6<-sig3*-1
-
-# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig1_pedagogical.tif", units="in",
-#      res=300, width=6.5, height=4)
-# 
-# layout(laymat)
-# par(mar=c(1.5,1.5,2,1.5), mgp=c(1,1,0), oma=c(2,2,0,0))
-# 
-# plot(NA,NA,ylim=c(-2,5.2),xlim=range(tt), xlab="", ylab="", xaxt="n",yaxt="n")
-# lines(tt,comb1,lwd=2)
-# lines(tt,comb2,lwd=2,col="red")
-# axis(1, at=c(0,10,20,30,40,50),labels=NA)
-# axis(2, at=c(-1,1.5,4), labels=NA)
-# mtext("Timescale specific relationship",3,line=0.25)
-# text(0.4,4.9,"a)",cex=1.2)
-# 
-# plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
-# axis(1, at=c(0,10,20), labels=NA)
-# axis(2, at=c(-1,0,1), labels=NA)
-# lines(tt[tt<=20],sig3,lwd=2)
-# lines(tt[tt<=20],sig4,lwd=2,col="red")
-# mtext(expression(paste(phi," = 0")))
-# text(1,0.9,"b)",cex=1.2)
-# 
-# plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
-# axis(1, at=c(0,10,20), labels=NA)
-# axis(2, at=c(-1,0,1), labels=NA)
-# lines(tt[tt<=20],sig3,lwd=2)
-# lines(tt[tt<=20],sig5,lwd=2,col="red")
-# mtext(expression(paste(phi," = ",pi,"/2")))
-# text(1,0.9,"c)",cex=1.2)
-# 
-# plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
-# axis(1, at=c(0,10,20), labels=NA)
-# axis(2, at=c(-1,0,1), labels=NA)
-# lines(tt[tt<=20],sig3,lwd=2)
-# lines(tt[tt<=20],sig6,lwd=2,col="red")
-# mtext(expression(paste(phi," = ",pi)))
-# text(1,0.9,"d)",cex=1.2)
-# 
-# 
-# mtext("Time", 1, outer=T)
-# mtext("Signal", 2, outer=T)
-# 
-# dev.off()
-
-```
-
 ```{r summarize coherences, echo=TRUE, cache=FALSE}
@@
 #hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvicoh.ts2>0.6]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
-# 
+
 # tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions.tif", units="in",
@@
 # 
-# hist(coh.chlaXaccndvi$accndvicoh.ts1, main="Short timescale coherence", xlab="Coherence", ylab="Frequency", col="lightgrey")
+# hist(coh.chlaXaccndvi$accndvicoh.ts1, main="Short timescale coherence", xlab="Coherence", ylab="Frequency", col="lightgrey",xlim=c(0,1))
 # text(par()$usr[1]+.05,0.95*par()$usr[4],"a)")
-# hist(coh.chlaXaccndvi$accndvicoh.ts2, main="Long timescale coherence", xlab="Coherence", ylab="Frequency", col="lightgrey")
+# hist(coh.chlaXaccndvi$accndvicoh.ts2, main="Long timescale coherence", xlab="Coherence", ylab="Frequency", col="lightgrey",xlim=c(0,1))
 # text(par()$usr[1]+.05,0.95*par()$usr[4],"b)")
@@
 
-```{r mapping, echo=TRUE, cache=FALSE}
-
-states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020.shp")
-getstates<-c("Minnesota", "Iowa", "Wisconsin", "Illinois", "Missouri", "Michigan", "Indiana", "Ohio", "Pennsylvania", "New York", "New Jersey", "Connecticut", "New Hampshire", "Rhode Island", "Massachusetts", "Vermont", "Maine")
-lagosstates<-states[states@data$STATE %in% getstates,]
-
-plot(lagosstates, main="Lakes selected for analysis")
-points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=16, cex=1, col="blue")
-
-cohplotdata<-left_join(analysislakes$lakeinfo, coh.chlaXaccndvi, by="lagoslakeid")
-
-pal<-viridis(100)
-
-par(mar=c(1,0,2,0))
-
-plot(lagosstates, main="Lakes by short timescale coherence")
-par()$usr
-points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
-colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)
-
-plot(lagosstates, main="Lakes by long timescale coherence")
-points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
-colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)
-
-laymat=matrix(1,nrow=2,ncol=13)
-laymat[2,]<-2
-laymat[,13]<-3
-
-# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_coherencemap.tif", units="in",
-#      res=300, width=6.5, height=7.5)
-# 
-# layout(laymat)
-# par(mar=c(0,0,1.5,0))
-# 
-# plot(lagosstates, main="Short timescale coherence")
-# points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
-# text(0.99*par()$usr[1],0.99*par()$usr[4],"a)",cex=1.5)
-# 
-# plot(lagosstates, main="Long timescale coherence")
-# points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
-# text(0.99*par()$usr[1],0.99*par()$usr[4],"b)",cex=1.5)
-# 
-# par(mar=c(5,1,5,1))
-# image(matrix(1:100,nrow=1),col=pal,xaxt="n",yaxt="n")
-# axis(2,at=seq(0,1,0.2))
-# 
-# dev.off()
-
-```
-
 ```{r add vars for modelling, echo=TRUE, cache=FALSE}
 
-#Need to add: depth, average growing season Chlorophyll-a, TSI(chla) categories, pct ag
-
-#agriculture -- is 500m buffer best? Other options include 100m buffer (probably too small) and hu12 watershed
-# pct.ag<-lagosne_select(table="buffer500m.lulc", vars=c("lagoslakeid","buffer500m_nlcd2001_pct_82","buffer500m_nlcd2006_pct_82","buffer500m_nlcd2011_pct_82"))
-pct.ag<-lagosne_select(table="hu12.lulc", vars=c("hu12_zoneid","hu12_nlcd2001_pct_82","hu12_nlcd2006_pct_82","hu12_nlcd2011_pct_82"))
-pct.ag<-pct.ag[pct.ag$hu12_zoneid %in% analysislakes$lakeinfo$hu12_zoneid,]
-pct.ag.avg<-data.frame(hu12_zoneid=pct.ag$hu12_zoneid, pct.ag=rowMeans(pct.ag[,2:4]))
-
-#Wetlands
-pct.wetlands<-lagosne_select(table="hu12.lulc", vars=c(c("hu12_zoneid","hu12_nlcd2001_pct_90","hu12_nlcd2006_pct_90",
-                                                         "hu12_nlcd2011_pct_90","hu12_nlcd2001_pct_95","hu12_nlcd2006_pct_95",
-                                                         "hu12_nlcd2011_pct_95")))
-pct.wetlands<-pct.wetlands[pct.wetlands$hu12_zoneid %in% analysislakes$lakeinfo$hu12_zoneid,]
-pct.wetlands$sum2001<-rowSums(pct.wetlands[,c(2,5)])
-pct.wetlands$sum2006<-rowSums(pct.wetlands[,c(3,6)])
-pct.wetlands$sum2011<-rowSums(pct.wetlands[,c(4,7)])
-pct.wetlands.avg<-data.frame(hu12_zoneid=pct.wetlands$hu12_zoneid, pct.wetlands=rowMeans(pct.wetlands[,8:10]))
-
-#depth
-depth<-lagosne_select(table="lakes_limno", vars=c("lagoslakeid","maxdepth"))
-depth<-depth[depth$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,] #use max depth because it's more complete
-
-#growing season Chlorophyll-a
-chla<-lagosne_select(table="epi_nutr", vars=c("lagoslakeid","samplemonth","chla"))
-chla<-chla[chla$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
-gs.chla<-chla[chla$samplemonth %in% 5:9,]
-avg.chla<-aggregate(chla ~ lagoslakeid, data=gs.chla, FUN=mean, na.rm=T)
-
-#growing season DOC
-doc<-lagosne_select(table="epi_nutr", vars=c("lagoslakeid","samplemonth","doc"))
-doc<-doc[doc$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
-gs.doc<-doc[doc$samplemonth %in% 5:9,]
-avg.doc<-aggregate(doc ~ lagoslakeid, data=gs.doc, FUN=mean, na.rm=T)
-
-#Chlorophyll-a TSI class
-#TSI(CHL) = 9.81 ln(CHL) + 30.6
-tsi.chl<-data.frame(lagoslakeid=avg.chla$lagoslakeid, tsi=9.81 * log(avg.chla$chla) + 30.6)
-tsi.chl$tsi.cat<-rep("lake",nrow(tsi.chl))
-
-tsi.chl$tsi.cat[tsi.chl$tsi < 40]<-"oligotrophic"
-tsi.chl$tsi.cat[tsi.chl$tsi >=40 & tsi.chl$tsi < 50]<-"mesotrophic"
-tsi.chl$tsi.cat[tsi.chl$tsi >=50 & tsi.chl$tsi < 70]<-"eutrophic"
-tsi.chl$tsi.cat[tsi.chl$tsi >= 70] <-"hypereutrophic"
-
-#CV of terrestrial NDVI
-cv.accndvi<-NULL
-for(lake in 1:length(analysislakes$lakedata)){
-  tmp<-analysislakes$lakedata[[lake]][rownames(analysislakes$lakedata[[lake]])=="accndvi",]
-  cv.accndvi<-c(cv.accndvi, sd(tmp)/mean(tmp))  
- # rm(tmp)
-}
-cv.accndvi<-data.frame(lagoslakeid=as.numeric(names(analysislakes$lakedata)), cv.accndvi=cv.accndvi)
-
-#mean precipitation
-prcp.normal<-raster("~/Box Sync/NSF EAGER Synchrony/Data/PRISM Data/PRISM_ppt_30yr_normal_800mM2_annual_bil.bil")
-lakepts<-SpatialPoints(coords=cbind(analysislakes$lakeinfo$nhd_long,analysislakes$lakeinfo$nhd_lat))
-lake.prcp<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid, prcp.normal=raster::extract(prcp.normal,lakepts))
-
-#huc2 and huc4 watershed codes
-huc_codes<-read.csv("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
-
-#state info
-states<-lagosne_select(table="state", vars=c("state_zoneid","state_name"))
-
-#shoreline development ratio
-sdev<-analysislakes$lakeinfo$lake_perim_meters/(2*sqrt(pi*analysislakes$lakeinfo$lake_area_ha*10000))
-shoredev<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid,shoredev=sdev)
+dt<-lagosne_load("1.087.3")
+dt.conn<-dt$buffer500m.conn
+dt.chag<-dt$hu12.chag
 
 predictors<-analysislakes$lakeinfo
-predictors<-left_join(predictors, depth, by="lagoslakeid")
-predictors<-left_join(predictors, pct.ag.avg, by="hu12_zoneid")
-predictors<-left_join(predictors, pct.wetlands.avg, by="hu12_zoneid")
-predictors<-left_join(predictors, avg.chla, by="lagoslakeid")
-predictors<-left_join(predictors, tsi.chl, by="lagoslakeid")
-predictors<-left_join(predictors, states, by="state_zoneid")
-predictors<-left_join(predictors, cv.accndvi, by="lagoslakeid")
-predictors<-left_join(predictors, avg.doc, by="lagoslakeid")
-predictors<-left_join(predictors, lake.prcp, by="lagoslakeid")
-predictors<-left_join(predictors, shoredev, by="lagoslakeid")
-#predictors<-left_join(predictors, huc_codes, by="hu4_zoneid")
+predictors$tslength<-predictors$end-predictors$start + 1
+pred.conn<-left_join(predictors, dt.conn, by="lagoslakeid")
+pred.chag<-left_join(predictors, dt.chag, by="hu12_zoneid")
 
-for(nn in 1:ncol(predictors)){
+modvars.conn<-left_join(pred.conn, coh.chlaXaccndvi, by="lagoslakeid")
+modvars.chag<-left_join(pred.chag, coh.chlaXaccndvi, by="lagoslakeid")
 
-  if(is.factor(predictors[,nn])){
-    predictors[,nn]<-factor(predictors[,nn])
-  }
-
-}
-
-str(predictors)
-hist(predictors$tslength)
-hist(predictors$lake_area_ha)
-hist(log10(predictors$lake_area_ha))
-hist(predictors$lake_perim_meters)
-hist(log10(predictors$lake_perim_meters))
-table(predictors$nhd_fcode)
-table(predictors$hu12_zoneid)
-hist(predictors$elevation_m)
-hist(predictors$maxdepth)
-hist(log10(predictors$maxdepth))
-hist(predictors$pct.ag)
-hist(log10(predictors$pct.ag))
-hist(predictors$chla)
-hist(log10(predictors$chla))
-hist(predictors$tsi)
-table(predictors$tsi.cat)
-hist(predictors$cv.accndvi)
-hist(predictors$pct.wetlands)
-hist(predictors$doc)
-hist(predictors$prcp.normal)
-hist(predictors$shoredev)
-
-predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha) #not necessary to transform with random forests
-# predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
-# predictors$log10_maxdepth<-log10(predictors$maxdepth)
-# predictors$log10_pct.ag<-log10(predictors$pct.ag+1)
-# predictors$log10_chla<-log10(predictors$chla)
-
-modvars.accndvi<-left_join(predictors, coh.chlaXaccndvi, by="lagoslakeid")
-modvars.accndvi$nhd_ftype<-factor(modvars.accndvi$nhd_ftype)
-modvars.accndvi$tsi.cat<-factor(modvars.accndvi$tsi.cat)
-modvars.accndvi$tslength<-modvars.accndvi$end-modvars.accndvi$start + 1
-
-modvars.accndvi<-modvars.accndvi[!is.na(modvars.accndvi$maxdepth),]
-modvars.accndvi<-modvars.accndvi[!is.na(modvars.accndvi$pct.ag),]
-
-modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.3,]
-modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.3,]
+# modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.3,]
+# modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.3,]
 
@@
 
-# cforest.st<-partykit::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
-# #                     data=modvars.accndvi, ntree=20000)
-# cforest.st<-party::cforest(accndvicoh.ts1 ~ shoredev + lake_area_ha +  maxdepth + pct.ag + chla + tsi.cat + 
-#                              hu4_zoneid + cv.accndvi + pct.wetlands + doc + prcp.normal,
-#                     data=modvars.accndvi, controls=cforest_control(ntree=80000))
+dconn.st<-modvars.conn[,c(17:26,29)]
 
-lwgt<-modvars.accndvi$tslength/mean(modvars.accndvi$tslength)
-
-gam.cohst<-gam(accndvicoh.ts1 ~ s(shoredev) + s(prcp.normal) + s(log10(lake_area_ha)) + s(pct.ag),  weights=lwgt, data=modvars.accndvi, 
-               gamma=1.4, na.action = "na.fail")
-#dredge.cohst<-dredge(gam.cohst, evaluate=TRUE, m.lim=c(0,5))
-#importance(dredge.cohst)
-#modavg.cohst<-model.avg(dredge.cohst, fit=T)
-summary(gam.cohst)
-
-plot(modvars.accndvi$accndvicoh.ts1,predict(gam.cohst))
-
-topmod.cohst<-gam(accndvicoh.ts1 ~ s(shoredev,k=3) + s(log10(lake_area_ha),k=3) + s(prcp.normal,k=3) + s(pct.ag,k=3), data=modvars.accndvi,
-                  gamma=1)
-summary(topmod.cohst)
-
-gam.cohlt<-gam(accndvicoh.ts2 ~ s(shoredev,k=3) + s(log10(lake_area_ha),k=3) +  s(maxdepth,k=3) + s(pct.ag,k=3) + 
-                 s(chla,k=3) + tsi.cat + hu4_zoneid + s(cv.accndvi,k=3) + s(pct.wetlands,k=3) +  #removed doc because of NAs
-                 s(prcp.normal,k=3), data=modvars.accndvi, gamma=1,na.action = "na.fail")
-dredge.cohlt<-dredge(gam.cohlt, evaluate=TRUE, m.lim=c(0,5))
-importance(dredge.cohlt)
-modavg.cohlt<-model.avg(dredge.cohlt, fit=T)
-
-plot(modvars.accndvi$accndvicoh.ts1,predict(modavg.cohlt))
-
-topmod.cohlt<-gam(accndvicoh.ts1 ~ s(pct.wetlands,k=3) + s(cv.accndvi,k=3) + s(prcp.normal,k=3) + s(maxdepth,k=3), data=modvars.accndvi,
-                  gamma=1)
-summary(topmod.cohlt)
-
-predcoh.st<-predict(cforest.st, newdata=modvars.accndvi,type="response")
+cforest.st<-party::cforest(accndvicoh.ts1 ~ ., data=dconn.st,
+                           controls=cforest_control(ntree=50000,mincriterion =  0.9))
+predcoh.st<-predict(cforest.st, newdata=dconn.st,type="response")
 #hist(predcoh.st)
 #hist(modvars.accndvi$accndvicoh.ts1)
-plot(predcoh.st, modvars.accndvi$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
+plot(predcoh.st, dconn.st$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
      xlim=c(0,1), ylim=c(0,1))
 abline(a=0,b=1)
-cor.test(predcoh.st,modvars.accndvi$accndvicoh.ts1)
+cor.test(predcoh.st,dconn.st$accndvicoh.ts1)
 varimp.coh.st<-varimp(cforest.st)
@@
 
-pdp.shoredev.coh.st<-partial(cforest.st, pred.var="shoredev", train=modvars.accndvi, type="regression", plot=T)
-pdp.prcp.coh.st<-partial(cforest.st, pred.var="prcp.normal", train=modvars.accndvi, type="regression", plot=T)
-pdp.ag.coh.st<-partial(cforest.st, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
-pdp.maxdepth.coh.st<-partial(cforest.st, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
-pdp.lakearea.coh.st<-partial(cforest.st, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
-pdp.chla.coh.st<-partial(cforest.st, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
-pdp.doc.coh.st<-partial(cforest.st, pred.var="doc", train=modvars.accndvi, type="regression", plot=T)
-pdp.cv.coh.st<-partial(cforest.st, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
-pdp.wetlands.coh.st<-partial(cforest.st, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
-pdp.region.coh.st<-partial(cforest.st, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
-pdp.tsi.coh.st<-partial(cforest.st, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
+#pdp.shoredev.coh.st<-partial(cforest.st, pred.var="shoredev", train=modvars.accndvi, type="regression", plot=T)
 
-cforest.lt<-party::cforest(accndvicoh.ts2 ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid 
-                           + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
-                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
-predcoh.lt<-predict(cforest.lt, newdata=modvars.accndvi)
-# hist(predcoh.lt)
-# hist(modvars.accndvi$accndvicoh.ts2)
-plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long st",
+dchag.st<-modvars.chag[,c(17:158,161)]
+cforest.st<-party::cforest(accndvicoh.ts1 ~ ., data=dchag.st, 
+                           controls=cforest_control(ntree=50000,mincriterion =  0.9))
+predcoh.st<-predict(cforest.st, newdata=dchag.st,type="response")
+#hist(predcoh.st)
+#hist(modvars.accndvi$accndvicoh.ts1)
+plot(predcoh.st, dconn.st$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
      xlim=c(0,1), ylim=c(0,1))
 abline(a=0,b=1)
-cor.test(predcoh.lt,modvars.accndvi$accndvicoh.ts2)
+cor.test(predcoh.st,dconn.st$accndvicoh.ts1)
+varimp.coh.st<-varimp(cforest.st)
+print(varimp.coh.st[order(varimp.coh.st, decreasing=T)])
+
+### long timescales
+dconn.lt<-modvars.conn[,c(17:26,32)]
+
+cforest.lt<-party::cforest(accndvicoh.ts2 ~ ., data=dconn.lt,
+                           controls=cforest_control(ntree=50000,mincriterion =  0.9))
+predcoh.lt<-predict(cforest.lt, newdata=dconn.lt,type="response")
+#hist(predcoh.lt)
+#hist(modvars.accndvi$accndvicoh.ts1)
+plot(predcoh.lt, dconn.lt$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, short ts",
+     xlim=c(0,1), ylim=c(0,1))
+abline(a=0,b=1)
+cor.test(predcoh.lt,dconn.lt$accndvicoh.ts2)
 varimp.coh.lt<-varimp(cforest.lt)
@@
 
-pdp.wetlands.coh.lt<-partial(cforest.lt, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
-pdp.cv.coh.lt<-partial(cforest.lt, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
-pdp.region.coh.lt<-partial(cforest.lt, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
-pdp.tsi.coh.lt<-partial(cforest.lt, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
-pdp.doc.coh.lt<-partial(cforest.lt, pred.var="doc", train=modvars.accndvi, type="regression", plot=T)
-pdp.prcp.coh.lt<-partial(cforest.lt, pred.var="prcp.normal", train=modvars.accndvi, type="regression", plot=T)
-pdp.lakearea.coh.lt<-partial(cforest.lt, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
-pdp.chla.coh.lt<-partial(cforest.lt, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
-pdp.shoredev.coh.lt<-partial(cforest.lt, pred.var="shoredev", train=modvars.accndvi, type="regression", plot=T)
-pdp.ag.coh.lt<-partial(cforest.lt, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
-pdp.maxdepth.coh.lt<-partial(cforest.lt, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
+#pdp.shoredev.coh.lt<-partial(cforest.lt, pred.var="shoredev", train=modvars.accndvi, type="regression", plot=T)
+
+dchag.lt<-modvars.chag[,c(17:158,164)]
+cforest.lt<-party::cforest(accndvicoh.ts2 ~ ., data=dchag.lt, 
+                           controls=cforest_control(ntree=50000,mincriterion =  0.9))
+predcoh.lt<-predict(cforest.lt, newdata=dchag.lt,type="response")
+#hist(predcoh.lt)
+#hist(modvars.accndvi$accndvicoh.ts1)
+plot(predcoh.lt, dconn.lt$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, short ts",
+     xlim=c(0,1), ylim=c(0,1))
+abline(a=0,b=1)
+cor.test(predcoh.lt,dconn.lt$accndvicoh.ts2)
+varimp.coh.lt<-varimp(cforest.lt)
+print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)])
+
+# cforest.lt<-party::cforest(accndvicoh.ts2 ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid 
+#                            + cv.accndvi+ pct.wetlands + doc + prcp.normal,
+#                     data=modvars.accndvi, controls=cforest_control(ntree=50000,mincriterion = 0.9))
+# predcoh.lt<-predict(cforest.lt, newdata=modvars.accndvi)
+# # hist(predcoh.lt)
+# # hist(modvars.accndvi$accndvicoh.ts2)
+# plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long st",
+#      xlim=c(0,1), ylim=c(0,1))
+# abline(a=0,b=1)
+# cor.test(predcoh.lt,modvars.accndvi$accndvicoh.ts2)
+# varimp.coh.lt<-varimp(cforest.lt)
+# print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)])
+# 
+# 
+# #pdp.wetlands.coh.lt<-partial(cforest.lt, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
+#
 
 ```
-
-```{r modellingPhase, echo=TRUE, cache=FALSE}
-
-cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + 
-                          hu4_zoneid + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
-                        data=modvars.accndvi.phist,controls=cforest_control(ntree=40000))
-predphi.st<-predict(cforest.phi.st, newdata=modvars.accndvi.phist)
-# hist(predphi.st)
-# hist(cos(modvars.accndvi.phist$accndviphi.ts1))
-plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
-     xlim=c(-1,1), ylim=c(-1,1))
-abline(a=0,b=1)
-cor.test(predphi.st,cos(modvars.accndvi.phist$accndviphi.ts1))
-varimp.phi.st<-varimp(cforest.phi.st)
-print(varimp.phi.st[order(varimp.phi.st,decreasing=TRUE)])
-
-pdp.maxdepth.phi.st<-partial(cforest.phi.st, pred.var="maxdepth", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.lakearea.phi.st<-partial(cforest.phi.st, pred.var="lake_area_ha", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.doc.phi.st<-partial(cforest.phi.st, pred.var="doc", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.cv.phi.st<-partial(cforest.phi.st, pred.var="cv.accndvi", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.shoredev.phi.st<-partial(cforest.phi.st, pred.var="shoredev", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.wetlands.phi.st<-partial(cforest.phi.st, pred.var="pct.wetlands", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.prcp.phi.st<-partial(cforest.phi.st, pred.var="prcp.normal", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.chla.phi.st<-partial(cforest.phi.st, pred.var="chla", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.ag.phi.st<-partial(cforest.phi.st, pred.var="pct.ag", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.tsi.phi.st<-partial(cforest.phi.st, pred.var="tsi.cat", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.region.phi.st<-partial(cforest.phi.st, pred.var="hu4_zoneid", train=modvars.accndvi.phist, type="regression", plot=T)
-
-cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
-                          cv.accndvi + pct.wetlands + doc + prcp.normal, 
-                        data=modvars.accndvi.philt,controls=cforest_control(ntree=40000))
-predphi.lt<-predict(cforest.phi.lt, newdata=modvars.accndvi.philt)
-# hist(predphi.lt)
-# hist(cos(modvars.accndvi.philt$accndviphi.ts2))
-plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
-     xlim=c(-1,1), ylim=c(-1,1))
-abline(a=0,b=1)
-cor.test(predphi.lt,cos(modvars.accndvi.philt$accndviphi.ts2))
-varimp.phi.lt<-varimp(cforest.phi.lt)
-print(varimp.phi.lt[order(varimp.phi.lt, decreasing=TRUE)])
-
-pdp.region.phi.lt<-partial(cforest.phi.lt, pred.var="hu4_zoneid", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.lakearea.phi.lt<-partial(cforest.phi.lt, pred.var="lake_area_ha", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.prsp.phi.lt<-partial(cforest.phi.lt, pred.var="prcp.normal", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.wetlands.phi.lt<-partial(cforest.phi.lt, pred.var="pct.wetlands", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.doc.phi.lt<-partial(cforest.phi.lt, pred.var="doc", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.shoredev.phi.lt<-partial(cforest.phi.lt, pred.var="shoredev", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.chla.phi.lt<-partial(cforest.phi.lt, pred.var="chla", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.cv.phi.lt<-partial(cforest.phi.lt, pred.var="cv.accndvi", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.maxdepth.phi.lt<-partial(cforest.phi.lt, pred.var="maxdepth", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.ag.phi.lt<-partial(cforest.phi.lt, pred.var="pct.ag", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.tsi.phi.lt<-partial(cforest.phi.lt, pred.var="tsi.cat", train=modvars.accndvi.philt, type="regression", plot=T)
-
-save.image("~/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analyses_complete_20190729.RData")
-
-```
-```{r plot predictions, echo=TRUE, cache=FALSE}
-
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS1_predvsemp.tif", units="in",
-     res=300, width=6.5, height=6.5)
-
-par(mar=c(2.5,2.5,1.5,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),oma=c(1.2,1.2,0,0))
-
-plot(predcoh.st, modvars.accndvi$accndvicoh.ts1, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="")
-mtext("Short timescale coherence",line=0.2)
-abline(a=0,b=1)
-
-plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="")
-mtext("Long timescale coherence",line=0.2)
-abline(a=0,b=1)
-
-plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlim=c(-1,1), ylim=c(-1,1), xlab="", ylab="")
-mtext("Short timescale cos(phase)",line=0.2)
-abline(a=0,b=1)
-
-plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlim=c(-1,1), ylim=c(-1,1), xlab="", ylab="")
-mtext("Short timescale cos(phase)",line=0.2)
-abline(a=0,b=1)
-
-mtext("Predicted",1,outer=T)
-mtext("Empirical",2,outer=T)
-
-dev.off()
-
-```
-
-```{r varimp plotting, echo=TRUE, cache=FALSE}
-#fig 4: variable importance in rank order
-
-cleannames<-function(dirtynames){
-  out<-NULL
-  for(ii in 1:length(dirtynames)){
-    if(dirtynames[ii]=="shoredev"){out<-c(out,"Shore. devel.")}
-    if(dirtynames[ii]=="lake_area_ha"){out<-c(out,"Lake area")}
-    if(dirtynames[ii]=="maxdepth"){out<-c(out,"Depth")}
-    if(dirtynames[ii]=="pct.ag"){out<-c(out,"% agriculture")}
-    if(dirtynames[ii]=="chla"){out<-c(out,"Chlorophyll-a")}
-    if(dirtynames[ii]=="tsi.cat"){out<-c(out,"TSI")}
-    if(dirtynames[ii]=="hu4_zoneid"){out<-c(out,"HU4 watershed")}
-    if(dirtynames[ii]=="cv.accndvi"){out<-c(out,"CV(NDVI)")}
-    if(dirtynames[ii]=="pct.wetlands"){out<-c(out,"% wetlands")}
-    if(dirtynames[ii]=="doc"){out<-c(out,"DOC")}
-    if(dirtynames[ii]=="prcp.normal"){out<-c(out,"Precipitation")}
-  }
-  return(out)
-}
-
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp.tif", units="in",
-     res=300, width=6.5, height=6.5)
-
-par(mar=c(6,3.8,1.5,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),oma=c(0,1.2,0,0))
-
-barplot(varimp.coh.st[order(varimp.coh.st,decreasing=T)], names.arg=cleannames(names(varimp.coh.st)[order(varimp.coh.st,decreasing=T)]), las=2,
-        cex.names=0.9)
-mtext("a) Short timescale coherence", line=0.25, cex=0.9)
-barplot(varimp.coh.lt[order(varimp.coh.lt,decreasing=T)], names.arg=cleannames(names(varimp.coh.lt)[order(varimp.coh.lt,decreasing=T)]), las=2,
-        cex.names=0.9)
-mtext("b) Long timescale coherence", line=0.25, cex=0.9)
-barplot(varimp.phi.st[order(varimp.phi.st,decreasing=T)], names.arg=cleannames(names(varimp.phi.st)[order(varimp.phi.st,decreasing=T)]), las=2,
-        cex.names=0.9)
-mtext("c) Short timescale phase", line=0.25, cex=0.9)
-barplot(varimp.phi.lt[order(varimp.phi.lt,decreasing=T)], names.arg=cleannames(names(varimp.phi.lt)[order(varimp.phi.lt,decreasing=T)]), las=2,
-        cex.names=0.9)
-mtext("d) Long timescale phase", line=0.25, cex=0.9)
-mtext("Variable importance",2,outer=T)
-
-dev.off()
-#fig 5: top variable importances (9 total)
-
-states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020.shp")
-huc_bdys<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/huc4_watersheds.shp")
-huc_codes<-read.csv("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
-huc_codes<-huc_codes[huc_codes$hu4_zoneid %in% analysislakes$lakeinfo$hu4_zoneid,]
-
-scale1_100<-function(x){
-  x1<-x-min(x)+1/100
-  x1<-round(x1/max(x1)*100)
-  return(x1)
-}
-
-pdpdf.hu4.cohlt<-data.frame(hu4_zoneid=pdp.region.coh.lt$panel.args[[1]]$x, yhat=pdp.region.coh.lt$panel.args[[1]]$y)
-pdpdf.hu4.cohlt<-left_join(pdpdf.hu4.cohlt, huc_codes)
-huc_bdys1<-huc_bdys[huc_bdys$HUC4 %in% pdpdf.hu4.cohlt$huc4_code,]
-huc_bdys1@data<-left_join(huc_bdys1@data, pdpdf.hu4.cohlt, by=c("HUC4"="huc4_code"))
-
-pdpdf.hu4.philt<-data.frame(hu4_zoneid=pdp.region.phi.lt$panel.args[[1]]$x, yhat=pdp.region.phi.lt$panel.args[[1]]$y)
-pdpdf.hu4.philt<-left_join(pdpdf.hu4.philt, huc_codes)
-huc_bdys2<-huc_bdys[huc_bdys$HUC4 %in% pdpdf.hu4.philt$huc4_code,]
-huc_bdys2@data<-left_join(huc_bdys2@data, pdpdf.hu4.philt, by=c("HUC4"="huc4_code"))
-
-#make smaller images that we can insert into the main figure
-
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5f_hu4_cohlt.png", units="in",
-     res=300, width=6.5/3, height=8/3)
-par(mar=c(0,0,0,0))
-plot(huc_bdys1,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys1$yhat)])
-lines(states)
-par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
-image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
-axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys1$yhat), max(huc_bdys1$yhat), length.out=5),2), cex=0.8)
-dev.off()
-
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu4_philt.png", units="in",
-     res=300, width=6.5/3, height=8/3)
-par(mar=c(0,0,0,0))
-plot(huc_bdys2,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys2$yhat)])
-lines(states)
-par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
-image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
-axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys2$yhat), max(huc_bdys2$yhat), length.out=5),2), cex=0.8)
-dev.off()
-
-laymat<-matrix(1:9,3,3,byrow=T)
-
-library(png)
-panel5f<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5f_hu4_cohlt.png")
-panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu4_philt.png")
-
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_partialeffects.tif", units="in",
-     res=300, width=6.5, height=8)
-layout(laymat)
-par(mar=c(3.6,2,1.5,1),mgp=c(1.7,0.5,0),oma=c(0,1.5,0,0))
-#cohst ~ shoredev, precip, % ag
-plot(pdp.shoredev.coh.st$panel.args[[1]]$x, pdp.shoredev.coh.st$panel.args[[1]]$y, type="l", xlab="Shore. devel.", ylab="")
-mtext("a) Short timesecale coherence", line=0.25, cex=0.7)
-plot(pdp.prcp.coh.st$panel.args[[1]]$x, pdp.prcp.coh.st$panel.args[[1]]$y, type="l", xlab="Precipitation (mm/yr)", ylab="")
-mtext("b) Short timesecale coherence", line=0.25, cex=0.7)
-plot(pdp.ag.coh.st$panel.args[[1]]$x, pdp.ag.coh.st$panel.args[[1]]$y, type="l", xlab="Partial effect", ylab="")
-mtext("c) Short timesecale coherence", line=0.25, cex=0.7)
-#cohlt ~ pct.wetlands, cv(ndvi), hu4_zoneid
-plot(pdp.wetlands.coh.lt$panel.args[[1]]$x, pdp.wetlands.coh.lt$panel.args[[1]]$y, type="l", xlab="% Wetlands", ylab="")
-mtext("d) Long timescale coherence", line=0.25, cex=0.7)
-plot(pdp.cv.coh.lt$panel.args[[1]]$x, pdp.cv.coh.lt$panel.args[[1]]$y, type="l", xlab="CV(NDVI)", ylab="")
-mtext("e) Long timescale coherence", line=0.25, cex=0.7)
-plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HU4 watershed",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
-rasterImage(image=panel5f,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-mtext("f) Long timescale coherence", line=0.25, cex=0.7)
-#phist ~ depth, lake area
-plot(pdp.maxdepth.phi.st$panel.args[[1]]$x, pdp.maxdepth.phi.st$panel.args[[1]]$y, type="l", xlab="Depth (m)", ylab="")
-mtext("g) Short timescale phase", line=0.25, cex=0.7)
-plot(pdp.lakearea.phi.st$panel.args[[1]]$x, pdp.lakearea.phi.st$panel.args[[1]]$y, type="l", xlab="Lake area (ha)", ylab="")
-mtext("h) Short timescale phase", line=0.25, cex=0.7)
-#philt ~ hu4_zoneid
-plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HU4 watershed", xaxt="n",yaxt="n",mgp=c(1,0.5,0))
-rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-mtext("i) Long timescale phase", line=0.25, cex=0.7)
-
-mtext("Partial effect",side=2, outer=T, line=0.1)
-
-dev.off()
-
-```

### 2019-10-04 AnalysisCode/ms1_analyses_rf_to_gam.Rmd
analyses updates in progress

--- 2019-10-04 AnalysisCode/ms1_analyses_gam.Rmd
@@
 
-# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig1_pedagogical.tif", units="in",
-#      res=300, width=6.5, height=4)
-# 
-# layout(laymat)
-# par(mar=c(1.5,1.5,2,1.5), mgp=c(1,1,0), oma=c(2,2,0,0))
-# 
-# plot(NA,NA,ylim=c(-2,5.2),xlim=range(tt), xlab="", ylab="", xaxt="n",yaxt="n")
-# lines(tt,comb1,lwd=2)
-# lines(tt,comb2,lwd=2,col="red")
-# axis(1, at=c(0,10,20,30,40,50),labels=NA)
-# axis(2, at=c(-1,1.5,4), labels=NA)
-# mtext("Timescale specific relationship",3,line=0.25)
-# text(0.4,4.9,"a)",cex=1.2)
-# 
-# plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
-# axis(1, at=c(0,10,20), labels=NA)
-# axis(2, at=c(-1,0,1), labels=NA)
-# lines(tt[tt<=20],sig3,lwd=2)
-# lines(tt[tt<=20],sig4,lwd=2,col="red")
-# mtext(expression(paste(phi," = 0")))
-# text(1,0.9,"b)",cex=1.2)
-# 
-# plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
-# axis(1, at=c(0,10,20), labels=NA)
-# axis(2, at=c(-1,0,1), labels=NA)
-# lines(tt[tt<=20],sig3,lwd=2)
-# lines(tt[tt<=20],sig5,lwd=2,col="red")
-# mtext(expression(paste(phi," = ",pi,"/2")))
-# text(1,0.9,"c)",cex=1.2)
-# 
-# plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
-# axis(1, at=c(0,10,20), labels=NA)
-# axis(2, at=c(-1,0,1), labels=NA)
-# lines(tt[tt<=20],sig3,lwd=2)
-# lines(tt[tt<=20],sig6,lwd=2,col="red")
-# mtext(expression(paste(phi," = ",pi)))
-# text(1,0.9,"d)",cex=1.2)
-# 
-# 
-# mtext("Time", 1, outer=T)
-# mtext("Signal", 2, outer=T)
-# 
-# dev.off()
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig1_pedagogical.tif", units="in",
+     res=300, width=6.5, height=4)
+
+layout(laymat)
+par(mar=c(1.5,1.5,2,1.5), mgp=c(1,1,0), oma=c(2,2,0,0))
+
+plot(NA,NA,ylim=c(-2,5.2),xlim=range(tt), xlab="", ylab="", xaxt="n",yaxt="n")
+lines(tt,comb1,lwd=2)
+lines(tt,comb2,lwd=2,col="red")
+axis(1, at=c(0,10,20,30,40,50),labels=NA)
+axis(2, at=c(-1,1.5,4), labels=NA)
+mtext("Timescale specific relationship",3,line=0.25)
+text(0.4,4.9,"a)",cex=1.2)
+
+plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
+axis(1, at=c(0,10,20), labels=NA)
+axis(2, at=c(-1,0,1), labels=NA)
+lines(tt[tt<=20],sig3,lwd=2)
+lines(tt[tt<=20],sig4,lwd=2,col="red")
+mtext(expression(paste(phi," = 0")))
+text(1,0.9,"b)",cex=1.2)
+
+plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
+axis(1, at=c(0,10,20), labels=NA)
+axis(2, at=c(-1,0,1), labels=NA)
+lines(tt[tt<=20],sig3,lwd=2)
+lines(tt[tt<=20],sig5,lwd=2,col="red")
+mtext(expression(paste(phi," = ",pi,"/2")))
+text(1,0.9,"c)",cex=1.2)
+
+plot(NA,NA,ylim=c(-1,1),xlim=c(0,20),xaxt="n",yaxt="n",xlab="",ylab="")
+axis(1, at=c(0,10,20), labels=NA)
+axis(2, at=c(-1,0,1), labels=NA)
+lines(tt[tt<=20],sig3,lwd=2)
+lines(tt[tt<=20],sig6,lwd=2,col="red")
+mtext(expression(paste(phi," = ",pi)))
+text(1,0.9,"d)",cex=1.2)
+
+mtext("Time", 1, outer=T)
+mtext("Signal", 2, outer=T)
+
+dev.off()
 
@@
 #hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvicoh.ts2>0.6]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
-# 
-# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions.tif", units="in",
-#      res=300, width=6.5, height=6.5)
-# 
-# par(mar=c(3,3,2,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),cex.main=0.9)
-# 
-# hist(coh.chlaXaccndvi$accndvicoh.ts1, main="Short timescale coherence", xlab="Coherence", ylab="Frequency", col="lightgrey")
-# text(par()$usr[1]+.05,0.95*par()$usr[4],"a)")
-# hist(coh.chlaXaccndvi$accndvicoh.ts2, main="Long timescale coherence", xlab="Coherence", ylab="Frequency", col="lightgrey")
-# text(par()$usr[1]+.05,0.95*par()$usr[4],"b)")
-# 
-# par(mar=c(1,1,2,1))
-# rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian", col="lightgrey",
-#      breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Short timescale phases",
-#        at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
-# text(0.9*par()$usr[1],0.95*par()$usr[4],"c)")
-# rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian", col="lightgrey",
-#      breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Long timescale phases",
-#      at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
-# text(0.9*par()$usr[1],0.95*par()$usr[4],"d)")
-# 
-# dev.off()
+
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions.tif", units="in",
+     res=300, width=6.5, height=6.5)
+
+par(mar=c(3,3,2,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),cex.main=0.9)
+
+hist(coh.chlaXaccndvi$accndvicoh.ts1, main="Short timescale coherence", xlab="Coherence", ylab="Frequency", col="lightgrey",xlim=c(0,1))
+text(par()$usr[1]+.05,0.95*par()$usr[4],"a)")
+hist(coh.chlaXaccndvi$accndvicoh.ts2, main="Long timescale coherence", xlab="Coherence", ylab="Frequency", col="lightgrey",xlim=c(0,1))
+text(par()$usr[1]+.05,0.95*par()$usr[4],"b)")
+
+par(mar=c(1,1,2,1))
+rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian", col="lightgrey",
+     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Short timescale phases",
+       at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
+text(0.9*par()$usr[1],0.95*par()$usr[4],"c)")
+rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian", col="lightgrey",
+     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Long timescale phases",
+     at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
+text(0.9*par()$usr[1],0.95*par()$usr[4],"d)")
+
+dev.off()
 
@@
 
-# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_coherencemap.tif", units="in",
-#      res=300, width=6.5, height=7.5)
-# 
-# layout(laymat)
-# par(mar=c(0,0,1.5,0))
-# 
-# plot(lagosstates, main="Short timescale coherence")
-# points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
-# text(0.99*par()$usr[1],0.99*par()$usr[4],"a)",cex=1.5)
-# 
-# plot(lagosstates, main="Long timescale coherence")
-# points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
-# text(0.99*par()$usr[1],0.99*par()$usr[4],"b)",cex=1.5)
-# 
-# par(mar=c(5,1,5,1))
-# image(matrix(1:100,nrow=1),col=pal,xaxt="n",yaxt="n")
-# axis(2,at=seq(0,1,0.2))
-# 
-# dev.off()
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_coherencemap.tif", units="in",
+     res=300, width=6.5, height=7.5)
+
+layout(laymat)
+par(mar=c(0,0,1.5,0))
+
+plot(lagosstates, main="Short timescale coherence")
+points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
+text(0.99*par()$usr[1],0.99*par()$usr[4],"a)",cex=1.5)
+
+plot(lagosstates, main="Long timescale coherence")
+points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
+text(0.99*par()$usr[1],0.99*par()$usr[4],"b)",cex=1.5)
+
+par(mar=c(5,1,5,1))
+image(matrix(1:100,nrow=1),col=pal,xaxt="n",yaxt="n")
+axis(2,at=seq(0,1,0.2))
+
+dev.off()
 
@@
 
-#Need to add: depth, average growing season Chlorophyll-a, TSI(chla) categories, pct ag
+dt<-lagosne_load("1.087.3")
 
-#agriculture -- is 500m buffer best? Other options include 100m buffer (probably too small) and hu12 watershed
-# pct.ag<-lagosne_select(table="buffer500m.lulc", vars=c("lagoslakeid","buffer500m_nlcd2001_pct_82","buffer500m_nlcd2006_pct_82","buffer500m_nlcd2011_pct_82"))
-pct.ag<-lagosne_select(table="hu12.lulc", vars=c("hu12_zoneid","hu12_nlcd2001_pct_82","hu12_nlcd2006_pct_82","hu12_nlcd2011_pct_82"))
-pct.ag<-pct.ag[pct.ag$hu12_zoneid %in% analysislakes$lakeinfo$hu12_zoneid,]
-pct.ag.avg<-data.frame(hu12_zoneid=pct.ag$hu12_zoneid, pct.ag=rowMeans(pct.ag[,2:4]))
+dt.conn<-dt$buffer500m.conn
+dt.conn<-dt.conn[,!grepl("sum_lengthm",colnames(dt.conn))]
+dt.conn<-dt.conn[,colnames(dt.conn)!="buffer500m_nhdid"]
 
-#Wetlands
-pct.wetlands<-lagosne_select(table="hu12.lulc", vars=c(c("hu12_zoneid","hu12_nlcd2001_pct_90","hu12_nlcd2006_pct_90",
-                                                         "hu12_nlcd2011_pct_90","hu12_nlcd2001_pct_95","hu12_nlcd2006_pct_95",
-                                                         "hu12_nlcd2011_pct_95")))
-pct.wetlands<-pct.wetlands[pct.wetlands$hu12_zoneid %in% analysislakes$lakeinfo$hu12_zoneid,]
-pct.wetlands$sum2001<-rowSums(pct.wetlands[,c(2,5)])
-pct.wetlands$sum2006<-rowSums(pct.wetlands[,c(3,6)])
-pct.wetlands$sum2011<-rowSums(pct.wetlands[,c(4,7)])
-pct.wetlands.avg<-data.frame(hu12_zoneid=pct.wetlands$hu12_zoneid, pct.wetlands=rowMeans(pct.wetlands[,8:10]))
+dt.chag<-dt$hu12.chag
+dt.chag<-dt.chag[,!grepl("_min",colnames(dt.chag))]
+dt.chag<-dt.chag[,!grepl("_max",colnames(dt.chag))]
+
+dt.geo<-dt$lakes.geo
+dt.geo<-dt$lakes.geo[,!colnames(dt.geo) %in% c("state_zoneid","iws_zoneid","edu_zoneid")]
+
+dt.lulc<-dt$hu12.lulc
+dt.lulc<-dt.lulc[,!grepl("_ha_",colnames(dt.lulc))]
+dt.lulc<-dt.lulc[,!grepl("_nlcd1992_",colnames(dt.lulc))]
+dt.lulc<-dt.lulc[,!grepl("_nlcd2006_",colnames(dt.lulc))]
+dt.lulc<-dt.lulc[,!grepl("_nlcd2001_",colnames(dt.lulc))]
+dt.lulc<-dt.lulc[,colnames(dt.lulc)!="hu12_damdensity_pointsperha"]
 
@@
 avg.chla<-aggregate(chla ~ lagoslakeid, data=gs.chla, FUN=mean, na.rm=T)
-
-#growing season DOC
-doc<-lagosne_select(table="epi_nutr", vars=c("lagoslakeid","samplemonth","doc"))
-doc<-doc[doc$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
-gs.doc<-doc[doc$samplemonth %in% 5:9,]
-avg.doc<-aggregate(doc ~ lagoslakeid, data=gs.doc, FUN=mean, na.rm=T)
 
@@
 
-#mean precipitation
-prcp.normal<-raster("~/Box Sync/NSF EAGER Synchrony/Data/PRISM Data/PRISM_ppt_30yr_normal_800mM2_annual_bil.bil")
-lakepts<-SpatialPoints(coords=cbind(analysislakes$lakeinfo$nhd_long,analysislakes$lakeinfo$nhd_lat))
-lake.prcp<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid, prcp.normal=raster::extract(prcp.normal,lakepts))
+#shoreline development ratio
+sdev<-analysislakes$lakeinfo$lake_perim_meters/(2*sqrt(pi*analysislakes$lakeinfo$lake_area_ha*10000))
+shoredev<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid,shoredev=sdev)
+
+preds<-analysislakes$lakeinfo[,colnames(analysislakes$lakeinfo) %in% c("lagoslakeid","end","start")]
+preds$tslength<-preds$end-preds$start + 1
+preds<-left_join(preds, dt.geo, by="lagoslakeid")
+preds<-left_join(preds, dt.conn, by="lagoslakeid")
+preds<-left_join(preds, dt.chag, by="hu12_zoneid")
+preds<-left_join(preds, dt.lulc, by="hu12_zoneid")
+preds<-left_join(preds, avg.chla, by="lagoslakeid")
+preds<-left_join(preds, cv.accndvi, by="lagoslakeid")
+preds<-left_join(preds, depth, by="lagoslakeid")
+
+# modvars.conn<-left_join(pred.conn, coh.chlaXaccndvi, by="lagoslakeid")
+# modvars.chag<-left_join(pred.chag, coh.chlaXaccndvi, by="lagoslakeid")
 
@@
 
-#shoreline development ratio
-sdev<-analysislakes$lakeinfo$lake_perim_meters/(2*sqrt(pi*analysislakes$lakeinfo$lake_area_ha*10000))
-shoredev<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid,shoredev=sdev)
+for(nn in 1:ncol(preds)){
 
-predictors<-analysislakes$lakeinfo
-predictors<-left_join(predictors, depth, by="lagoslakeid")
-predictors<-left_join(predictors, pct.ag.avg, by="hu12_zoneid")
-predictors<-left_join(predictors, pct.wetlands.avg, by="hu12_zoneid")
-predictors<-left_join(predictors, avg.chla, by="lagoslakeid")
-predictors<-left_join(predictors, tsi.chl, by="lagoslakeid")
-predictors<-left_join(predictors, states, by="state_zoneid")
-predictors<-left_join(predictors, cv.accndvi, by="lagoslakeid")
-predictors<-left_join(predictors, avg.doc, by="lagoslakeid")
-predictors<-left_join(predictors, lake.prcp, by="lagoslakeid")
-predictors<-left_join(predictors, shoredev, by="lagoslakeid")
-#predictors<-left_join(predictors, huc_codes, by="hu4_zoneid")
-
-for(nn in 1:ncol(predictors)){
-
-  if(is.factor(predictors[,nn])){
-    predictors[,nn]<-factor(predictors[,nn])
+  if(is.factor(preds[,nn])){
+    preds[,nn]<-factor(preds[,nn])
   }
@@
 
-str(predictors)
-hist(predictors$tslength)
-hist(predictors$lake_area_ha)
-hist(log10(predictors$lake_area_ha))
-hist(predictors$lake_perim_meters)
-hist(log10(predictors$lake_perim_meters))
-table(predictors$nhd_fcode)
-table(predictors$hu12_zoneid)
-hist(predictors$elevation_m)
-hist(predictors$maxdepth)
-hist(log10(predictors$maxdepth))
-hist(predictors$pct.ag)
-hist(log10(predictors$pct.ag))
-hist(predictors$chla)
-hist(log10(predictors$chla))
-hist(predictors$tsi)
-table(predictors$tsi.cat)
-hist(predictors$cv.accndvi)
-hist(predictors$pct.wetlands)
-hist(predictors$doc)
-hist(predictors$prcp.normal)
-hist(predictors$shoredev)
+```
 
-predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha) #not necessary to transform with random forests
-# predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
-# predictors$log10_maxdepth<-log10(predictors$maxdepth)
-# predictors$log10_pct.ag<-log10(predictors$pct.ag+1)
-# predictors$log10_chla<-log10(predictors$chla)
+```{r rfCoherence_st, echo=TRUE, cache=FALSE}
 
-modvars.accndvi<-left_join(predictors, coh.chlaXaccndvi, by="lagoslakeid")
-modvars.accndvi$nhd_ftype<-factor(modvars.accndvi$nhd_ftype)
-modvars.accndvi$tsi.cat<-factor(modvars.accndvi$tsi.cat)
-modvars.accndvi$tslength<-modvars.accndvi$end-modvars.accndvi$start + 1
+rfdat.cohst<-left_join(coh.chlaXaccndvi[,c(10,3)], preds)
+rfdat.cohst<-rfdat.cohst[,!colnames(rfdat.cohst) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
+rfdat.cohst<-rfdat.cohst[,!grepl("borderhu12s",rfdat.cohst)]
 
-modvars.accndvi<-modvars.accndvi[!is.na(modvars.accndvi$maxdepth),]
-modvars.accndvi<-modvars.accndvi[!is.na(modvars.accndvi$pct.ag),]
+for(nn in 1:ncol(rfdat.cohst)){
+  if(is.character(rfdat.cohst[,nn])){
+    rfdat.cohst[,nn]<-as.factor(rfdat.cohst[,nn])
+  }
+}
 
-modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.3,]
-modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.3,]
+cf.cohst<-party::cforest(accndvicoh.ts1 ~ ., data=rfdat.cohst, controls=cforest_control(ntree=50000,mincriterion = 0.9))
+
+varimp.coh.st<-varimp(cf.cohst)
+print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:20])
+#hist(predcoh.st)
+#hist(modvars.accndvi$accndvicoh.ts1)
+predcoh.st<-predict(cf.cohst, newdata=rfdat.cohst,type="response")
+# plot(predcoh.st, rfdat.cohst$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
+#      xlim=c(0,1), ylim=c(0,1))
+# abline(a=0,b=1)
+cor.test(predcoh.st,rfdat.cohst$accndvicoh.ts1)
 
@@
 
-```{r modellingCoherence, echo=TRUE, cache=FALSE}
+```{r rfCoherence_lt, echo=TRUE, cache=FALSE}
+rfdat.cohlt<-left_join(coh.chlaXaccndvi[,c(10,6)], preds)
+rfdat.cohlt<-rfdat.cohlt[,!colnames(rfdat.cohlt) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
+rfdat.cohlt<-rfdat.cohlt[,!grepl("borderhu12s",rfdat.cohlt)]
 
-# cforest.st<-partykit::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
-# #                     data=modvars.accndvi, ntree=20000)
-# cforest.st<-party::cforest(accndvicoh.ts1 ~ shoredev + lake_area_ha +  maxdepth + pct.ag + chla + tsi.cat + 
-#                              hu4_zoneid + cv.accndvi + pct.wetlands + doc + prcp.normal,
-#                     data=modvars.accndvi, controls=cforest_control(ntree=80000))
+for(nn in 1:ncol(rfdat.cohlt)){
+  if(is.character(rfdat.cohlt[,nn])){
+    rfdat.cohlt[,nn]<-as.factor(rfdat.cohlt[,nn])
+  }
+}
 
-lwgt<-modvars.accndvi$tslength/mean(modvars.accndvi$tslength)
+cf.cohlt<-party::cforest(accndvicoh.ts2 ~ ., data=rfdat.cohlt, controls=cforest_control(ntree=50000,mincriterion = 0.9))
 
-gam.cohst<-gam(accndvicoh.ts1 ~ s(shoredev) + s(prcp.normal) + s(log10(lake_area_ha)) + s(pct.ag),  weights=lwgt, data=modvars.accndvi, 
-               gamma=1.4, na.action = "na.fail")
-#dredge.cohst<-dredge(gam.cohst, evaluate=TRUE, m.lim=c(0,5))
-#importance(dredge.cohst)
-#modavg.cohst<-model.avg(dredge.cohst, fit=T)
-summary(gam.cohst)
-
-plot(modvars.accndvi$accndvicoh.ts1,predict(gam.cohst))
-
-topmod.cohst<-gam(accndvicoh.ts1 ~ s(shoredev,k=3) + s(log10(lake_area_ha),k=3) + s(prcp.normal,k=3) + s(pct.ag,k=3), data=modvars.accndvi,
-                  gamma=1)
-summary(topmod.cohst)
-
-gam.cohlt<-gam(accndvicoh.ts2 ~ s(shoredev,k=3) + s(log10(lake_area_ha),k=3) +  s(maxdepth,k=3) + s(pct.ag,k=3) + 
-                 s(chla,k=3) + tsi.cat + hu4_zoneid + s(cv.accndvi,k=3) + s(pct.wetlands,k=3) +  #removed doc because of NAs
-                 s(prcp.normal,k=3), data=modvars.accndvi, gamma=1,na.action = "na.fail")
-dredge.cohlt<-dredge(gam.cohlt, evaluate=TRUE, m.lim=c(0,5))
-importance(dredge.cohlt)
-modavg.cohlt<-model.avg(dredge.cohlt, fit=T)
-
-plot(modvars.accndvi$accndvicoh.ts1,predict(modavg.cohlt))
-
-topmod.cohlt<-gam(accndvicoh.ts1 ~ s(pct.wetlands,k=3) + s(cv.accndvi,k=3) + s(prcp.normal,k=3) + s(maxdepth,k=3), data=modvars.accndvi,
-                  gamma=1)
-summary(topmod.cohlt)
-
-predcoh.st<-predict(cforest.st, newdata=modvars.accndvi,type="response")
+varimp.coh.st<-varimp(cf.cohlt)
+print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:20])
 #hist(predcoh.st)
 #hist(modvars.accndvi$accndvicoh.ts1)
-plot(predcoh.st, modvars.accndvi$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
+predcoh.lt<-predict(cf.cohlt, newdata=rfdat.cohlt,type="response")
+plot(predcoh.lt, rfdat.cohlt$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long ts",
      xlim=c(0,1), ylim=c(0,1))
 abline(a=0,b=1)
-cor.test(predcoh.st,modvars.accndvi$accndvicoh.ts1)
-varimp.coh.st<-varimp(cforest.st)
-print(varimp.coh.st[order(varimp.coh.st, decreasing=T)])
-
-pdp.shoredev.coh.st<-partial(cforest.st, pred.var="shoredev", train=modvars.accndvi, type="regression", plot=T)
-pdp.prcp.coh.st<-partial(cforest.st, pred.var="prcp.normal", train=modvars.accndvi, type="regression", plot=T)
-pdp.ag.coh.st<-partial(cforest.st, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
-pdp.maxdepth.coh.st<-partial(cforest.st, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
-pdp.lakearea.coh.st<-partial(cforest.st, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
-pdp.chla.coh.st<-partial(cforest.st, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
-pdp.doc.coh.st<-partial(cforest.st, pred.var="doc", train=modvars.accndvi, type="regression", plot=T)
-pdp.cv.coh.st<-partial(cforest.st, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
-pdp.wetlands.coh.st<-partial(cforest.st, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
-pdp.region.coh.st<-partial(cforest.st, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
-pdp.tsi.coh.st<-partial(cforest.st, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
-
-cforest.lt<-party::cforest(accndvicoh.ts2 ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid 
-                           + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
-                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
-predcoh.lt<-predict(cforest.lt, newdata=modvars.accndvi)
-# hist(predcoh.lt)
-# hist(modvars.accndvi$accndvicoh.ts2)
-plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long st",
-     xlim=c(0,1), ylim=c(0,1))
-abline(a=0,b=1)
-cor.test(predcoh.lt,modvars.accndvi$accndvicoh.ts2)
-varimp.coh.lt<-varimp(cforest.lt)
-print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)])
-
-pdp.wetlands.coh.lt<-partial(cforest.lt, pred.var="pct.wetlands", train=modvars.accndvi, type="regression", plot=T)
-pdp.cv.coh.lt<-partial(cforest.lt, pred.var="cv.accndvi", train=modvars.accndvi, type="regression", plot=T)
-pdp.region.coh.lt<-partial(cforest.lt, pred.var="hu4_zoneid", train=modvars.accndvi, type="regression", plot=T)
-pdp.tsi.coh.lt<-partial(cforest.lt, pred.var="tsi.cat", train=modvars.accndvi, type="regression", plot=T)
-pdp.doc.coh.lt<-partial(cforest.lt, pred.var="doc", train=modvars.accndvi, type="regression", plot=T)
-pdp.prcp.coh.lt<-partial(cforest.lt, pred.var="prcp.normal", train=modvars.accndvi, type="regression", plot=T)
-pdp.lakearea.coh.lt<-partial(cforest.lt, pred.var="lake_area_ha", train=modvars.accndvi, type="regression", plot=T)
-pdp.chla.coh.lt<-partial(cforest.lt, pred.var="chla", train=modvars.accndvi, type="regression", plot=T)
-pdp.shoredev.coh.lt<-partial(cforest.lt, pred.var="shoredev", train=modvars.accndvi, type="regression", plot=T)
-pdp.ag.coh.lt<-partial(cforest.lt, pred.var="pct.ag", train=modvars.accndvi, type="regression", plot=T)
-pdp.maxdepth.coh.lt<-partial(cforest.lt, pred.var="maxdepth", train=modvars.accndvi, type="regression", plot=T)
+cor.test(predcoh.st,rfdat.cohlt$accndvicoh.ts2)
 
@@
                           hu4_zoneid + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
-                        data=modvars.accndvi.phist,controls=cforest_control(ntree=40000))
+                        data=modvars.accndvi.phist,controls=cforest_control(ntree=50000))
 predphi.st<-predict(cforest.phi.st, newdata=modvars.accndvi.phist)
@@
 
-pdp.maxdepth.phi.st<-partial(cforest.phi.st, pred.var="maxdepth", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.lakearea.phi.st<-partial(cforest.phi.st, pred.var="lake_area_ha", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.doc.phi.st<-partial(cforest.phi.st, pred.var="doc", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.cv.phi.st<-partial(cforest.phi.st, pred.var="cv.accndvi", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.shoredev.phi.st<-partial(cforest.phi.st, pred.var="shoredev", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.wetlands.phi.st<-partial(cforest.phi.st, pred.var="pct.wetlands", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.prcp.phi.st<-partial(cforest.phi.st, pred.var="prcp.normal", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.chla.phi.st<-partial(cforest.phi.st, pred.var="chla", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.ag.phi.st<-partial(cforest.phi.st, pred.var="pct.ag", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.tsi.phi.st<-partial(cforest.phi.st, pred.var="tsi.cat", train=modvars.accndvi.phist, type="regression", plot=T)
-pdp.region.phi.st<-partial(cforest.phi.st, pred.var="hu4_zoneid", train=modvars.accndvi.phist, type="regression", plot=T)
-
 cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
                           cv.accndvi + pct.wetlands + doc + prcp.normal, 
-                        data=modvars.accndvi.philt,controls=cforest_control(ntree=40000))
+                        data=modvars.accndvi.philt,controls=cforest_control(ntree=50000))
 predphi.lt<-predict(cforest.phi.lt, newdata=modvars.accndvi.philt)
@@
 print(varimp.phi.lt[order(varimp.phi.lt, decreasing=TRUE)])
-
-pdp.region.phi.lt<-partial(cforest.phi.lt, pred.var="hu4_zoneid", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.lakearea.phi.lt<-partial(cforest.phi.lt, pred.var="lake_area_ha", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.prsp.phi.lt<-partial(cforest.phi.lt, pred.var="prcp.normal", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.wetlands.phi.lt<-partial(cforest.phi.lt, pred.var="pct.wetlands", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.doc.phi.lt<-partial(cforest.phi.lt, pred.var="doc", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.shoredev.phi.lt<-partial(cforest.phi.lt, pred.var="shoredev", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.chla.phi.lt<-partial(cforest.phi.lt, pred.var="chla", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.cv.phi.lt<-partial(cforest.phi.lt, pred.var="cv.accndvi", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.maxdepth.phi.lt<-partial(cforest.phi.lt, pred.var="maxdepth", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.ag.phi.lt<-partial(cforest.phi.lt, pred.var="pct.ag", train=modvars.accndvi.philt, type="regression", plot=T)
-pdp.tsi.phi.lt<-partial(cforest.phi.lt, pred.var="tsi.cat", train=modvars.accndvi.philt, type="regression", plot=T)
 
@@
 ```
-
-```{r varimp plotting, echo=TRUE, cache=FALSE}
-#fig 4: variable importance in rank order
-
-cleannames<-function(dirtynames){
-  out<-NULL
-  for(ii in 1:length(dirtynames)){
-    if(dirtynames[ii]=="shoredev"){out<-c(out,"Shore. devel.")}
-    if(dirtynames[ii]=="lake_area_ha"){out<-c(out,"Lake area")}
-    if(dirtynames[ii]=="maxdepth"){out<-c(out,"Depth")}
-    if(dirtynames[ii]=="pct.ag"){out<-c(out,"% agriculture")}
-    if(dirtynames[ii]=="chla"){out<-c(out,"Chlorophyll-a")}
-    if(dirtynames[ii]=="tsi.cat"){out<-c(out,"TSI")}
-    if(dirtynames[ii]=="hu4_zoneid"){out<-c(out,"HU4 watershed")}
-    if(dirtynames[ii]=="cv.accndvi"){out<-c(out,"CV(NDVI)")}
-    if(dirtynames[ii]=="pct.wetlands"){out<-c(out,"% wetlands")}
-    if(dirtynames[ii]=="doc"){out<-c(out,"DOC")}
-    if(dirtynames[ii]=="prcp.normal"){out<-c(out,"Precipitation")}
-  }
-  return(out)
-}
-
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp.tif", units="in",
-     res=300, width=6.5, height=6.5)
-
-par(mar=c(6,3.8,1.5,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),oma=c(0,1.2,0,0))
-
-barplot(varimp.coh.st[order(varimp.coh.st,decreasing=T)], names.arg=cleannames(names(varimp.coh.st)[order(varimp.coh.st,decreasing=T)]), las=2,
-        cex.names=0.9)
-mtext("a) Short timescale coherence", line=0.25, cex=0.9)
-barplot(varimp.coh.lt[order(varimp.coh.lt,decreasing=T)], names.arg=cleannames(names(varimp.coh.lt)[order(varimp.coh.lt,decreasing=T)]), las=2,
-        cex.names=0.9)
-mtext("b) Long timescale coherence", line=0.25, cex=0.9)
-barplot(varimp.phi.st[order(varimp.phi.st,decreasing=T)], names.arg=cleannames(names(varimp.phi.st)[order(varimp.phi.st,decreasing=T)]), las=2,
-        cex.names=0.9)
-mtext("c) Short timescale phase", line=0.25, cex=0.9)
-barplot(varimp.phi.lt[order(varimp.phi.lt,decreasing=T)], names.arg=cleannames(names(varimp.phi.lt)[order(varimp.phi.lt,decreasing=T)]), las=2,
-        cex.names=0.9)
-mtext("d) Long timescale phase", line=0.25, cex=0.9)
-mtext("Variable importance",2,outer=T)
-
-dev.off()
-#fig 5: top variable importances (9 total)
-
-states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020.shp")
-huc_bdys<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/huc4_watersheds.shp")
-huc_codes<-read.csv("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
-huc_codes<-huc_codes[huc_codes$hu4_zoneid %in% analysislakes$lakeinfo$hu4_zoneid,]
-
-scale1_100<-function(x){
-  x1<-x-min(x)+1/100
-  x1<-round(x1/max(x1)*100)
-  return(x1)
-}
-
-pdpdf.hu4.cohlt<-data.frame(hu4_zoneid=pdp.region.coh.lt$panel.args[[1]]$x, yhat=pdp.region.coh.lt$panel.args[[1]]$y)
-pdpdf.hu4.cohlt<-left_join(pdpdf.hu4.cohlt, huc_codes)
-huc_bdys1<-huc_bdys[huc_bdys$HUC4 %in% pdpdf.hu4.cohlt$huc4_code,]
-huc_bdys1@data<-left_join(huc_bdys1@data, pdpdf.hu4.cohlt, by=c("HUC4"="huc4_code"))
-
-pdpdf.hu4.philt<-data.frame(hu4_zoneid=pdp.region.phi.lt$panel.args[[1]]$x, yhat=pdp.region.phi.lt$panel.args[[1]]$y)
-pdpdf.hu4.philt<-left_join(pdpdf.hu4.philt, huc_codes)
-huc_bdys2<-huc_bdys[huc_bdys$HUC4 %in% pdpdf.hu4.philt$huc4_code,]
-huc_bdys2@data<-left_join(huc_bdys2@data, pdpdf.hu4.philt, by=c("HUC4"="huc4_code"))
-
-#make smaller images that we can insert into the main figure
-
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5f_hu4_cohlt.png", units="in",
-     res=300, width=6.5/3, height=8/3)
-par(mar=c(0,0,0,0))
-plot(huc_bdys1,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys1$yhat)])
-lines(states)
-par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
-image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
-axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys1$yhat), max(huc_bdys1$yhat), length.out=5),2), cex=0.8)
-dev.off()
-
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu4_philt.png", units="in",
-     res=300, width=6.5/3, height=8/3)
-par(mar=c(0,0,0,0))
-plot(huc_bdys2,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys2$yhat)])
-lines(states)
-par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
-image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
-axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys2$yhat), max(huc_bdys2$yhat), length.out=5),2), cex=0.8)
-dev.off()
-
-laymat<-matrix(1:9,3,3,byrow=T)
-
-library(png)
-panel5f<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5f_hu4_cohlt.png")
-panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu4_philt.png")
-
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_partialeffects.tif", units="in",
-     res=300, width=6.5, height=8)
-layout(laymat)
-par(mar=c(3.6,2,1.5,1),mgp=c(1.7,0.5,0),oma=c(0,1.5,0,0))
-#cohst ~ shoredev, precip, % ag
-plot(pdp.shoredev.coh.st$panel.args[[1]]$x, pdp.shoredev.coh.st$panel.args[[1]]$y, type="l", xlab="Shore. devel.", ylab="")
-mtext("a) Short timesecale coherence", line=0.25, cex=0.7)
-plot(pdp.prcp.coh.st$panel.args[[1]]$x, pdp.prcp.coh.st$panel.args[[1]]$y, type="l", xlab="Precipitation (mm/yr)", ylab="")
-mtext("b) Short timesecale coherence", line=0.25, cex=0.7)
-plot(pdp.ag.coh.st$panel.args[[1]]$x, pdp.ag.coh.st$panel.args[[1]]$y, type="l", xlab="Partial effect", ylab="")
-mtext("c) Short timesecale coherence", line=0.25, cex=0.7)
-#cohlt ~ pct.wetlands, cv(ndvi), hu4_zoneid
-plot(pdp.wetlands.coh.lt$panel.args[[1]]$x, pdp.wetlands.coh.lt$panel.args[[1]]$y, type="l", xlab="% Wetlands", ylab="")
-mtext("d) Long timescale coherence", line=0.25, cex=0.7)
-plot(pdp.cv.coh.lt$panel.args[[1]]$x, pdp.cv.coh.lt$panel.args[[1]]$y, type="l", xlab="CV(NDVI)", ylab="")
-mtext("e) Long timescale coherence", line=0.25, cex=0.7)
-plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HU4 watershed",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
-rasterImage(image=panel5f,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-mtext("f) Long timescale coherence", line=0.25, cex=0.7)
-#phist ~ depth, lake area
-plot(pdp.maxdepth.phi.st$panel.args[[1]]$x, pdp.maxdepth.phi.st$panel.args[[1]]$y, type="l", xlab="Depth (m)", ylab="")
-mtext("g) Short timescale phase", line=0.25, cex=0.7)
-plot(pdp.lakearea.phi.st$panel.args[[1]]$x, pdp.lakearea.phi.st$panel.args[[1]]$y, type="l", xlab="Lake area (ha)", ylab="")
-mtext("h) Short timescale phase", line=0.25, cex=0.7)
-#philt ~ hu4_zoneid
-plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HU4 watershed", xaxt="n",yaxt="n",mgp=c(1,0.5,0))
-rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-mtext("i) Long timescale phase", line=0.25, cex=0.7)
-
-mtext("Partial effect",side=2, outer=T, line=0.1)
-
-dev.off()
-
-```

### 2019-10-04 AnalysisCode/ms1_prep.Rmd
ms1 analysis updates
analyses updates in progress

@@
 
-```{r limno import and formatting, echo=TRUE, cache=TRUE}
+```{r limno import and formatting, echo=TRUE, cache=FALSE}
 
@@
                                                            "hu12_zoneid", "state_zoneid", "elevation_m"), tsvars=c("chla"), 
-                                  minmos=3, minobs=3, timespan=c(1989,2018))
+                                  minmos=3, minobs=3, timespan=c(1989,2018),lagosversion="1.087.3")
 lagoslakes.cln<-cleanAnnualts(lagoslakes.raw)
@@
 
-save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1.RData")
+save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873.RData")
 

### 2019-10-04 AnalysisCode/ThinkPiece/displayItems.R

@@ -4,71 +4,76 @@ rm(list=ls())
 
 ## 1. a real-ish timeseries with multi-annual dynamics
 
-tt = 1:30
+tmax=30
+res=0.01
+
+tt<-seq(1,tmax,by=res)
 
 #trend component
-b1<-0.1
+b1<-0.075
 y1<-b1*tt-mean(b1*tt)
 plot(y1,type="l")
 
-#10-year oscillation
-p1<-11
-y2<-sin(seq(0,2*pi*(max(tt)/p1),length.out=length(tt)))
-plot(y2, type="l")
+#seasonal oscillation
+p1<-0.5
+y2<-sin(seq(0,2*pi*(length(tt)/(p1/res)),length.out=length(tt)))
+plot(tt,y2, type="l")
 
 #4-year oscillation
-p2<-3
-y3<-sin(seq(0,2*pi*(max(tt)/p2),length.out=length(tt)))
-plot(y3, type="l")
+p2<-11
+y3<-sin(seq(0,2*pi*(length(tt)/(p2/res)),length.out=length(tt)))*0.7
+plot(tt,y3, type="l")
 
 #white noise
-sig<-0.1
+sig<-0.2
 y4<-rnorm(length(tt),0,sig)
 
 plot(tt,y1+y2+y3+y4, type="l")
 
 ycomp<-y1+y2+y3+y4
 
-df.lm2<-data.frame(x=seq(12.5,17.5,1), y=c(mean(ycomp[12:13]), mean(ycomp[13:14]), mean(ycomp[14:15]), mean(ycomp[15:16]),
-                                           mean(ycomp[16:17]), mean(ycomp[17:18])))
+#df.lm2<-data.frame(x=seq(12.5,17.5,1), y=c(mean(ycomp[12:13]), mean(ycomp[13:14]), mean(ycomp[14:15]), mean(ycomp[15:16]),
+#                                           mean(ycomp[16:17]), mean(ycomp[17:18])))
 
 lm1<-lm(ycomp[tt>=5 & tt<=10] ~ tt[tt>=5 & tt<=10])
-lm2<-lm(y~x, data=df.lm2)
+#lm2<-lm(y~x, data=df.lm2)
+lm2<-lm(ycomp[tt>=12.5 & tt <=17.5] ~ tt[tt>=12.5 & tt<=17.5])
[…]

### 2019-10-04 AnalysisCode/test_kfoldcv.R

@@ -1,0 +1,19 @@
+train.control <- trainControl(method="cv", number = 10)
+# Train the model
+test <- train(accndvicoh.ts2 ~ shoredev + lake_area_ha +  maxdepth + pct.ag + chla + tsi.cat + 
+              hu4_zoneid + cv.accndvi + pct.wetlands + prcp.normal,
+              data = modvars.accndvi, method = "cforest",
+              trControl = train.control)
+print(test)
+
+ttree<-ctree(accndvicoh.ts1 ~ shoredev + lake_area_ha +  maxdepth + pct.ag + chla + tsi.cat + doc +
+               hu4_zoneid + cv.accndvi + pct.wetlands + prcp.normal,
+             data = modvars.accndvi, controls=ctree_control(mincriterion = 0.9))
+
+plot(ttree)
+
+predtest<-predict(ttree,newdata=modvars.accndvi)
+
+cor.test(modvars.accndvi$accndvicoh.ts1,predtest)
+
+plot(predtest,modvars.accndvi$accndvicoh.ts1)

### 2019-10-07 AnalysisCode/ms1_analyses_rf_to_gam.Rmd
q1 analysis udpdates

@@
 library(caret)
+library(mgcv)
 
@@
 
-load("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873.RData")
+load("~/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873.RData")
 
@@
 dt.chag<-dt.chag[,!grepl("_max",colnames(dt.chag))]
+dt.chag<-dt.chag[,!grepl("_ha",colnames(dt.chag))]
+dt.chag<-dt.chag[,!colnames(dt.chag)=="borderhu12s"]
+dt.chag$hu12_dep_no3_tavg_mean<-rowMeans(dt.chag[,grepl("hu12_dep_no3",colnames(dt.chag)) & 
+                                                   grepl("_mean",colnames(dt.chag))])
+dt.chag$hu12_dep_no3_tavg_std<-rowMeans(dt.chag[,grepl("hu12_dep_no3",colnames(dt.chag)) & 
+                                                   grepl("_std",colnames(dt.chag))])
+dt.chag$hu12_dep_so4_tavg_mean<-rowMeans(dt.chag[,grepl("hu12_dep_so4",colnames(dt.chag)) &
+                                                    grepl("_mean", colnames(dt.chag))])
+dt.chag$hu12_dep_so4_tavg_std<-rowMeans(dt.chag[,grepl("hu12_dep_so4",colnames(dt.chag)) &
+                                                    grepl("_std", colnames(dt.chag))])
+dt.chag$hu12_dep_totaln_tavg_mean<-rowMeans(dt.chag[,grepl("hu12_dep_totaln",colnames(dt.chag)) &
+                                                      grepl("_mean", colnames(dt.chag))])
+dt.chag$hu12_dep_totaln_tavg_std<-rowMeans(dt.chag[,grepl("hu12_dep_totaln",colnames(dt.chag)) &
+                                                      grepl("_std", colnames(dt.chag))])
+dt.chag<-dt.chag[,!(grepl("hu12_dep",colnames(dt.chag)) & grepl("_19",colnames(dt.chag)))]
+dt.chag<-dt.chag[,!(grepl("hu12_dep",colnames(dt.chag)) & grepl("_20",colnames(dt.chag)))]
 
@@
 dt.lulc<-dt.lulc[,colnames(dt.lulc)!="hu12_damdensity_pointsperha"]
+dt.lulc<-dt.lulc[,colnames(dt.lulc)!="hu12_damdensity_pointcount"]
+dt.lulc<-dt.lulc[,colnames(dt.lulc)!="hu12_roaddensity_sum_lengthm"]
+dt.lulc<-dt.lulc[,!grepl("_min",colnames(dt.lulc))]
+dt.lulc<-dt.lulc[,!grepl("_max",colnames(dt.lulc))]
 
@@
 #huc2 and huc4 watershed codes
-huc_codes<-read.csv("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
+huc_codes<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
 
@@
 rfdat.cohst<-rfdat.cohst[,!colnames(rfdat.cohst) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
-rfdat.cohst<-rfdat.cohst[,!grepl("borderhu12s",rfdat.cohst)]
+rfdat.cohst<-rfdat.cohst[,!grepl("borderhu12s",colnames(rfdat.cohst))]
 
@@
 cor.test(predcoh.st,rfdat.cohst$accndvicoh.ts1)
+
+```
+```{r gam_cohst, echo=TRUE, cache=FALSE}
+lwgt<-preds$tslength/mean(preds$tslength)
+
+gam.cohst<-gam(accndvicoh.ts1 ~ s(buffer500m_streamdensity_midreaches_density_mperha) + s(hu12_nlcd2011_pct_31 ) +
+               s(buffer500m_streamdensity_streams_density_mperha) + s(hu12_baseflowindex_mean) + 
+                 s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean), data=rfdat.cohst, gamma=1, weights=lwgt)
+gam.check(gam.cohst)
+concurvity(gam.cohst)
+summary(gam.cohst)
+plot(rfdat.cohst$accndvicoh.ts1, predict(gam.cohst, rfdat.cohst))
 
@@
 abline(a=0,b=1)
-cor.test(predcoh.st,rfdat.cohlt$accndvicoh.ts2)
+cor.test(predcoh.lt,rfdat.cohlt$accndvicoh.ts2)
+
+```
+```{r gam_cohlt, echo=TRUE, cache=FALSE}
+lwgt<-preds$tslength/mean(preds$tslength)
+
+gam.cohlt<-gam(accndvicoh.ts2 ~ s(hu12_nlcd2011_pct_90 ) + s(hu12_canopy2001_mean) + s(cv.accndvi) + 
+                 s(hu12_dep_totaln_tavg_mean) + hu6_zoneid, data=rfdat.cohlt, gamma=1, weights=lwgt)
+gam.check(gam.cohlt)
+concurvity(gam.cohlt)
+summary(gam.cohlt)
+plot(rfdat.cohlt$accndvicoh.ts2, predict(gam.cohlt, rfdat.cohlt))
 
@@
 
-```{r modellingPhase, echo=TRUE, cache=FALSE}
+```{r rfPhase_st, echo=TRUE, cache=FALSE}
 
-cforest.phi.st<-cforest(cos(accndviphi.ts1) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + 
-                          hu4_zoneid + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
-                        data=modvars.accndvi.phist,controls=cforest_control(ntree=50000))
-predphi.st<-predict(cforest.phi.st, newdata=modvars.accndvi.phist)
-# hist(predphi.st)
-# hist(cos(modvars.accndvi.phist$accndviphi.ts1))
-plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
-     xlim=c(-1,1), ylim=c(-1,1))
-abline(a=0,b=1)
-cor.test(predphi.st,cos(modvars.accndvi.phist$accndviphi.ts1))
-varimp.phi.st<-varimp(cforest.phi.st)
-print(varimp.phi.st[order(varimp.phi.st,decreasing=TRUE)])
+rfdat.phist<-left_join(coh.chlaXaccndvi[,c(10,2)], preds)
+rfdat.phist<-rfdat.phist[,!colnames(rfdat.phist) %in% 
+                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
+rfdat.phist<-rfdat.phist[,!grepl("borderhu12s",colnames(rfdat.phist))]
 
-cforest.phi.lt<-cforest(cos(accndviphi.ts2) ~ shoredev + lake_area_ha + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + 
-                          cv.accndvi + pct.wetlands + doc + prcp.normal, 
-                        data=modvars.accndvi.philt,controls=cforest_control(ntree=50000))
-predphi.lt<-predict(cforest.phi.lt, newdata=modvars.accndvi.philt)
-# hist(predphi.lt)
-# hist(cos(modvars.accndvi.philt$accndviphi.ts2))
-plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlab="predicted", ylab="empirical", main="cos(phase), short ts",
-     xlim=c(-1,1), ylim=c(-1,1))
-abline(a=0,b=1)
-cor.test(predphi.lt,cos(modvars.accndvi.philt$accndviphi.ts2))
-varimp.phi.lt<-varimp(cforest.phi.lt)
-print(varimp.phi.lt[order(varimp.phi.lt, decreasing=TRUE)])
+rfdat.phist<-rfdat.phist[coh.chlaXaccndvi$accndvip.ts1<0.3,]
 
-save.image("~/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analyses_complete_20190729.RData")
+for(nn in 1:ncol(rfdat.phist)){
+  if(is.character(rfdat.phist[,nn])){
+    rfdat.phist[,nn]<-as.factor(rfdat.phist[,nn])
+  }
+}
+
+cf.phist<-party::cforest(cos(accndviphi.ts1) ~ ., data=rfdat.phist, 
+                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
+
+varimp.phi.st<-varimp(cf.phist)
+print(varimp.phi.st[order(varimp.phi.st, decreasing=T)][1:20])
+predphi.st<-predict(cf.phist, newdata=rfdat.phist,type="response")
+cor.test(predphi.st,cos(rfdat.phist$accndviphi.ts1))
 
 ```
-```{r plot predictions, echo=TRUE, cache=FALSE}
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS1_predvsemp.tif", units="in",
-     res=300, width=6.5, height=6.5)
+```{r gam_phist, echo=TRUE, cache=FALSE}
+lwgt<-preds$tslength[coh.chlaXaccndvi$accndvip.ts1<0.3]/mean(preds$tslength[coh.chlaXaccndvi$accndvip.ts1<0.3])
 
-par(mar=c(2.5,2.5,1.5,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),oma=c(1.2,1.2,0,0))
-
-plot(predcoh.st, modvars.accndvi$accndvicoh.ts1, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="")
-mtext("Short timescale coherence",line=0.2)
-abline(a=0,b=1)
-
-plot(predcoh.lt, modvars.accndvi$accndvicoh.ts2, xlim=c(0,1), ylim=c(0,1), xlab="", ylab="")
-mtext("Long timescale coherence",line=0.2)
-abline(a=0,b=1)
-
-plot(predphi.st, cos(modvars.accndvi.phist$accndviphi.ts1), xlim=c(-1,1), ylim=c(-1,1), xlab="", ylab="")
-mtext("Short timescale cos(phase)",line=0.2)
-abline(a=0,b=1)
-
-plot(predphi.lt, cos(modvars.accndvi.philt$accndviphi.ts2), xlim=c(-1,1), ylim=c(-1,1), xlab="", ylab="")
-mtext("Short timescale cos(phase)",line=0.2)
-abline(a=0,b=1)
-
-mtext("Predicted",1,outer=T)
-mtext("Empirical",2,outer=T)
-
-dev.off()
+gam.phist<-gam(cos(accndviphi.ts1) ~ s(maxdepth) + s(upstream_lakes_4ha_count) + 
+                 s(wlconnections_openwaterwetlands_contributing_area_), 
+               data=rfdat.phist, gamma=1, weights=lwgt)
+gam.check(gam.phist)
+concurvity(gam.phist)
+summary(gam.phist)
+plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.phist, rfdat.phist))
 
 ```
+
+```{r rfPhase_lt, echo=TRUE, cache=FALSE}
+
+rfdat.philt<-left_join(coh.chlaXaccndvi[,c(10,5)], preds)
+rfdat.philt<-rfdat.philt[,!colnames(rfdat.philt) %in% 
+                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
+rfdat.philt<-rfdat.philt[,!grepl("borderhu12s",colnames(rfdat.philt))]
+
+rfdat.philt<-rfdat.philt[coh.chlaXaccndvi$accndvip.ts2<0.3,]
+
+for(nn in 1:ncol(rfdat.philt)){
+  if(is.character(rfdat.philt[,nn])){
+    rfdat.philt[,nn]<-as.factor(rfdat.philt[,nn])
+  }
+}
+
+cf.philt<-party::cforest(cos(accndviphi.ts2) ~ ., data=rfdat.philt,
+                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
+
+varimp.phi.lt<-varimp(cf.philt)
+print(varimp.phi.lt[order(varimp.phi.lt, decreasing=T)][1:20])
+predphi.lt<-predict(cf.philt, newdata=rfdat.philt,type="response")
+cor.test(predphi.lt,cos(rfdat.philt$accndviphi.ts2))
+
+```
+
+```{r gam_philt, echo=TRUE, cache=FALSE}
+lwgt<-preds$tslength[coh.chlaXaccndvi$accndvip.ts2<0.3]/mean(preds$tslength[coh.chlaXaccndvi$accndvip.ts2<0.3])
+
+gam.philt<-gam(cos(accndviphi.ts2) ~ hu4_zoneid + s(hu12_tri_mean) + 
+                 s(buffer500m_streamdensity_headwaters_density_mperha), 
+               data=rfdat.philt, gamma=1, weights=lwgt)
+gam.check(gam.philt)
+concurvity(gam.philt)
+summary(gam.philt)
+plot(cos(rfdat.philt$accndviphi.ts2), predict(gam.philt, rfdat.philt))
+
+```

### 2019-10-07 R Package/aqts/R/makeMNMPCAannualts.R

@@ -117,4 +117,4 @@ makeMNMPCAannualts<-function(dir, tsvars="Chlorophyll a, corrected for pheophyti
   return(list(lakeinfo=lakeinfo, lakedata=lakedata))  
 }
 
-test<-makeMNMPCAannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/MN_MPCA")
+#test<-makeMNMPCAannualts(dir="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/LAGOS Extended/MN_MPCA")

### 2019-11-01 AnalysisCode/ms1_analyses_rf_to_gam.Rmd
q1 rough gam plots
analysis fixes and updates

@@
 
-load("~/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873.RData")
+load("~/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873_2.RData")
 
@@
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions.tif", units="in",
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions_20191031.tif", units="in",
      res=300, width=6.5, height=6.5)
@@
 dt.chag<-dt.chag[,!(grepl("hu12_dep",colnames(dt.chag)) & grepl("_20",colnames(dt.chag)))]
+dt.chag<-dt.chag[,!(grepl("_std",colnames(dt.chag)))]
+dt.chag<-dt.chag[,!grepl("surficialgeology",colnames(dt.chag))]
 
 dt.geo<-dt$lakes.geo
-dt.geo<-dt$lakes.geo[,!colnames(dt.geo) %in% c("state_zoneid","iws_zoneid","edu_zoneid")]
+dt.geo<-dt$lakes.geo[,!colnames(dt.geo) %in% c("state_zoneid","iws_zoneid","edu_zoneid","county_zoneid")]
+dt.geo<-dt.geo[,!grepl("_count",colnames(dt.geo))]
 
@@
 dt.lulc<-dt.lulc[,!grepl("_max",colnames(dt.lulc))]
+dt.lulc<-dt.lulc[,!grepl("_std",colnames(dt.lulc))]
 
@@
 for(lake in 1:length(analysislakes$lakedata)){
-  tmp<-analysislakes$lakedata[[lake]][rownames(analysislakes$lakedata[[lake]])=="accndvi",]
+  tmp<-analysislakes$lakedata[[lake]][rownames(analysislakes$lakedata[[lake]])=="avhrrdata",]
+
   cv.accndvi<-c(cv.accndvi, sd(tmp)/mean(tmp))  
@@
 preds<-left_join(preds, depth, by="lagoslakeid")
+preds<-left_join(preds, shoredev, by="lagoslakeid")
+
+#remove any variables that don't vary in this dataset
+# for(nn in 1:ncol(preds)){
+#   print(colnames(preds)[nn])
+#   print(unique(preds[,nn]))
+# }
+
+preds<-preds[,!colnames(preds) %in% c("hu12_surficialgeology_beach_pct",
+                                      "hu12_surficialgeology_colluv_pct",
+                                      "hu12_surficialgeology_grus_pct",
+                                      "hu12_surficialgeology_other_pct",
+                                      "hu12_surficialgeology_solif_pct",
+                                      "hu12_surficialgeology_till_oth_pct",
+                                      "hu12_nlcd2011_pct_0")]
 
@@
 varimp.coh.st<-varimp(cf.cohst)
-print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:20])
+print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10])
 #hist(predcoh.st)
@@
 
-gam.cohst<-gam(accndvicoh.ts1 ~ s(buffer500m_streamdensity_midreaches_density_mperha) + s(hu12_nlcd2011_pct_31 ) +
-               s(buffer500m_streamdensity_streams_density_mperha) + s(hu12_baseflowindex_mean) + 
-                 s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean), data=rfdat.cohst, gamma=1, weights=lwgt)
+gam.cohst<-gam(accndvicoh.ts1 ~ s(cv.accndvi) + hu8_zoneid + s(hu12_dep_totaln_tavg_mean) +
+               s(hu12_nlcd2011_pct_90) + s(hu12_nlcd2011_pct_95), data=rfdat.cohst, gamma=1, weights=lwgt)
 gam.check(gam.cohst)
@@
 rfdat.cohlt<-rfdat.cohlt[,!colnames(rfdat.cohlt) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
-rfdat.cohlt<-rfdat.cohlt[,!grepl("borderhu12s",rfdat.cohlt)]
+rfdat.cohlt<-rfdat.cohlt[,!grepl("borderhu12s",colnames(rfdat.cohlt))]
 
@@
 
-varimp.coh.st<-varimp(cf.cohlt)
-print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:20])
+varimp.coh.lt<-varimp(cf.cohlt)
+print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10])
 #hist(predcoh.st)
@@
 predcoh.lt<-predict(cf.cohlt, newdata=rfdat.cohlt,type="response")
-plot(predcoh.lt, rfdat.cohlt$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long ts",
-     xlim=c(0,1), ylim=c(0,1))
-abline(a=0,b=1)
+# plot(predcoh.lt, rfdat.cohlt$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long ts",
+#      xlim=c(0,1), ylim=c(0,1))
+# abline(a=0,b=1)
 cor.test(predcoh.lt,rfdat.cohlt$accndvicoh.ts2)
@@
 
-gam.cohlt<-gam(accndvicoh.ts2 ~ s(hu12_nlcd2011_pct_90 ) + s(hu12_canopy2001_mean) + s(cv.accndvi) + 
-                 s(hu12_dep_totaln_tavg_mean) + hu6_zoneid, data=rfdat.cohlt, gamma=1, weights=lwgt)
+gam.cohlt<-gam(accndvicoh.ts2 ~ hu8_zoneid + s(hu12_nlcd2011_pct_52) + s(cv.accndvi) + 
+                 s(wlconnections_forestedwetlands_shoreline_km) + 
+                 s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean), data=rfdat.cohlt, gamma=1, weights=lwgt)
 gam.check(gam.cohlt)
@@
 varimp.phi.st<-varimp(cf.phist)
-print(varimp.phi.st[order(varimp.phi.st, decreasing=T)][1:20])
+print(varimp.phi.st[order(varimp.phi.st, decreasing=T)][1:10])
 predphi.st<-predict(cf.phist, newdata=rfdat.phist,type="response")
@@
 
-gam.phist<-gam(cos(accndviphi.ts1) ~ s(maxdepth) + s(upstream_lakes_4ha_count) + 
-                 s(wlconnections_openwaterwetlands_contributing_area_), 
+gam.phist<-gam(cos(accndviphi.ts1) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
+                 s(buffer500m_streamdensity_headwaters_density_mperha) + 
+                 s(chla), 
                data=rfdat.phist, gamma=1, weights=lwgt)
@@
 varimp.phi.lt<-varimp(cf.philt)
-print(varimp.phi.lt[order(varimp.phi.lt, decreasing=T)][1:20])
+print(varimp.phi.lt[order(varimp.phi.lt, decreasing=T)][1:10])
 predphi.lt<-predict(cf.philt, newdata=rfdat.philt,type="response")
@@
 gam.philt<-gam(cos(accndviphi.ts2) ~ hu4_zoneid + s(hu12_tri_mean) + 
-                 s(buffer500m_streamdensity_headwaters_density_mperha), 
+                 s(hu12_nlcd2011_pct_41), 
                data=rfdat.philt, gamma=1, weights=lwgt)
@@
 ```
+
+```{r roughGAMplotting, echo=TRUE, cache=FALSE}
+
+# plot(gam.cohst, main="coherence, short")
+# plot(gam.cohlt, main="coherence, long")
+# plot(gam.phist, main="cos(phase), short")
+# plot(gam.philt, main="cos(phase), long")
+
+```
+```{r plot varimp}
+
+print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10])
+ltxt.st<-c("cv(NDVI)","HUC-8 sub-basin","total N deposition","% woody wetlands","% herbaceous wetlands",
+           "shrub wetlands shoreline","all wetlands shoreline","slope","topographic roughness","forested wetlands shoreline")
+
+print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10])
+ltxt.lt<-c("HUC-8 sub-basin","% shrub/scrub","cv(NDVI)","annual precipitation","all wetlands contrib. area",
+           "forested wetlands shoreline","% woody wetlands","all wetlands shoreline","sulfate deposition",
+           "groundwater recharge")
+
+print(varimp.phi.st[order(varimp.phi.st, decreasing = T)][1:10])
+ltxt.phist<-c("open wetlands shoreline","headwaters density","mean chlorophyll-a","stream density",
+              "open wetlands contrib. area","% developed open space","nitrate deposition", "road density",
+              "% developed low intensity","all wetlands contrib. area")
+
+print(varimp.phi.lt[order(varimp.phi.lt, decreasing = T)][1:10])
+ltxt.philt<-c("HUC-4 subregion","HUC-6 basin","slope","topographic roughness","% deciduous forest","% woody wetlands",
+               "headwaters density","total N deposition","HUC-8 sub-basin","stream density")
+
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10.tif",units="in",res=300,width=6.5, height=6.5)
+
+par(mfrow=c(2,2), mar=c(5,11,1,1), cex.main=0.9, cex.axis=0.9)
+
+barplot(rev(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10]),names.arg=rev(ltxt.st),las=2,main="Short timescale coher.", horiz=T)
+
+barplot(rev(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.lt),las=2,main="Long timescale coher.", horiz=T)
+
+barplot(rev(varimp.phi.st[order(varimp.phi.st, decreasing=T)][1:10]),names.arg=rev(ltxt.phist),las=2,main="Short timescale phase", horiz=T)
+
+barplot(rev(varimp.phi.lt[order(varimp.phi.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.philt),las=2,main="Long timescale phase", horiz=T)
+
+dev.off()
+
+```
+
+```{r plot_gameffects}
+
+mar1<-c(3,1.5,0.5,1)
+#mar2<-c(2.5,1.5,1,1)
+fudge=1/40
+
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits.tif",units="in",res=300,width=6.5, height=6.5)
+
+par(mfrow=c(4,5),mgp=c(1.5,0.5,0),oma=c(0,2.5,0,0),mar=mar1)
+
+plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence")
+plot(NA,NA,xlab="HUC-8 sub-basin",xlim=c(0,1),ylim=c(0,1))
+plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="")
+plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="")
+plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% herbaceous wetld.",ylab="")
+
+plot(gam.phist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetlands shoreline",ylab="short phase")
+plot(gam.phist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
+plot(gam.phist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
+plot.new()
+plot.new()
+
+plot(NA,NA,xlab="HUC-8 sub-basin",xlim=c(0,1),ylim=c(0,1))
+plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-1,1))
+plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="",ylim=c(-1,1))
+plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="annual precipitation",ylab="")
+plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetld. contrib. area",ylab="",ylim=c(-1,1))
+
+plot(NA,NA,xlab="HUC-4 subregion",xlim=c(0,1),ylim=c(0,1),ylab="long phase")
+plot(gam.philt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="slope",ylab="")
+plot(gam.philt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% deciduous forest",ylab="")
+
+mtext("Partial residuals",2,outer=T,line=1.2,cex=0.8)
+mtext("cos(long phase)",2,at=1/8+fudge,outer=T,line=0,cex=0.7)
+mtext("long coherence)",2,at=1/8+1/4+fudge,outer=T,line=0,cex=0.7)
+mtext("cos(short phase)",2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)
+mtext("short coherence",2,at=1/8+3/4+fudge,outer=T,line=0,cex=0.7)
+
+dev.off()
+
+```

### 2019-11-01 R Package/aqts/R/addAVHRRannualts.R

@@ -48,14 +48,15 @@ addAVHRRannualts<-function(lakelist, avhrrdata, buffdist=5000, aggfun="mean"){
   #loop through lakes and extract AVHRR time series
   for(ii in 1:nrow(lakeinfo)){
     lakebuffer.ii<-buffer(lakepts.prj[ii,], width=buffdist[ii], dissolve=FALSE)
-    #avhrrstack.ii<-mask(avhrrdata,lakebuffer.ii)
+    #plot(lakebuffer.ii)
+    avhrrstack.ii<-mask(avhrrdata,lakebuffer.ii)
     
     if(!aggfun %in% c("mean","median")){stop("aggfun argument must be 'mean' or 'median'.")}
     else if(aggfun=="mean"){
-      ts.ii<-cellStats(avhrrdata, mean, na.rm=TRUE)
+      ts.ii<-cellStats(avhrrstack.ii, mean, na.rm=TRUE)
     }
     else if(aggfun=="median"){
-      ts.ii<-cellStats(avhrrdata, median, na.rm=TRUE)
+      ts.ii<-cellStats(avhrrstack.ii, median, na.rm=TRUE)
     }
 
     lakeyrs<-lakeinfo$start[ii]:lakeinfo$end[ii]

### 2019-11-13 AnalysisCode/ms1_analyses_rf_to_gam.Rmd
add sin(phi) analyses

@@
 }
-
-cf.phist<-party::cforest(cos(accndviphi.ts1) ~ ., data=rfdat.phist, 
+#cosine
+cf.cosphist<-party::cforest(cos(accndviphi.ts1) ~ ., data=rfdat.phist, 
                          controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
 
-varimp.phi.st<-varimp(cf.phist)
+varimp.phi.st<-varimp(cf.cosphist)
 print(varimp.phi.st[order(varimp.phi.st, decreasing=T)][1:10])
-predphi.st<-predict(cf.phist, newdata=rfdat.phist,type="response")
-cor.test(predphi.st,cos(rfdat.phist$accndviphi.ts1))
+pred.cosphi.st<-predict(cf.cosphist, newdata=rfdat.phist,type="response")
+cor.test(pred.cosphi.st,cos(rfdat.phist$accndviphi.ts1))
+
+#sine
+cf.sinphist<-party::cforest(sin(accndviphi.ts1) ~ ., data=rfdat.phist, 
+                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
+
+varimp.phi.st<-varimp(cf.sinphist)
+print(varimp.phi.st[order(varimp.phi.st, decreasing=T)][1:10])
+pred.sinphi.st<-predict(cf.sinphist, newdata=rfdat.phist,type="response")
+cor.test(pred.sinphi.st,sin(rfdat.phist$accndviphi.ts1))
 
@@
 
-gam.phist<-gam(cos(accndviphi.ts1) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
+#cosine
+gam.cosphist<-gam(cos(accndviphi.ts1) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
                  s(buffer500m_streamdensity_headwaters_density_mperha) + 
@@
                data=rfdat.phist, gamma=1, weights=lwgt)
-gam.check(gam.phist)
-concurvity(gam.phist)
-summary(gam.phist)
-plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.phist, rfdat.phist))
+gam.check(gam.cosphist)
+concurvity(gam.cosphist)
+summary(gam.cosphist)
+plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.cosphist, rfdat.phist))
+
+#sine
+gam.sinphist<-gam(sin(accndviphi.ts1) ~ s(buffer500m_streamdensity_headwaters_density_mperha) + 
+                 s(hu12_dep_so4_tavg_mean ) + 
+                 s(buffer500m_streamdensity_streams_density_mperha), 
+               data=rfdat.phist, gamma=1, weights=lwgt)
+gam.check(gam.sinphist)
+concurvity(gam.sinphist)
+summary(gam.sinphist)
+plot(sin(rfdat.phist$accndviphi.ts1), predict(gam.sinphist, rfdat.phist))
 
@@
 
-cf.philt<-party::cforest(cos(accndviphi.ts2) ~ ., data=rfdat.philt,
+#cosine
+cf.cosphilt<-party::cforest(cos(accndviphi.ts2) ~ ., data=rfdat.philt,
                          controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
 
-varimp.phi.lt<-varimp(cf.philt)
-print(varimp.phi.lt[order(varimp.phi.lt, decreasing=T)][1:10])
-predphi.lt<-predict(cf.philt, newdata=rfdat.philt,type="response")
-cor.test(predphi.lt,cos(rfdat.philt$accndviphi.ts2))
+varimp.cosphi.lt<-varimp(cf.cosphilt)
+print(varimp.cosphi.lt[order(varimp.cosphi.lt, decreasing=T)][1:10])
+pred.cosphi.lt<-predict(cf.cosphilt, newdata=rfdat.philt,type="response")
+cor.test(pred.cosphi.lt,cos(rfdat.cosphilt$accndviphi.ts2))
+
+#sine
+cf.sinphilt<-party::cforest(sin(accndviphi.ts2) ~ ., data=rfdat.philt,
+                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
+
+varimp.sinphi.lt<-varimp(cf.sinphilt)
+print(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing=T)][1:10])
+pred.sinphi.lt<-predict(cf.sinphilt, newdata=rfdat.philt,type="response")
+cor.test(pred.sinphi.lt,sin(rfdat.philt$accndviphi.ts2))
 
@@
 
-gam.philt<-gam(cos(accndviphi.ts2) ~ hu4_zoneid + s(hu12_tri_mean) + 
+#cosine
+gam.cosphilt<-gam(cos(accndviphi.ts2) ~ hu4_zoneid + s(hu12_tri_mean) + 
                  s(hu12_nlcd2011_pct_41), 
                data=rfdat.philt, gamma=1, weights=lwgt)
-gam.check(gam.philt)
-concurvity(gam.philt)
-summary(gam.philt)
-plot(cos(rfdat.philt$accndviphi.ts2), predict(gam.philt, rfdat.philt))
+gam.check(gam.cosphilt)
+concurvity(gam.cosphilt)
+summary(gam.cosphilt)
+plot(cos(rfdat.cosphilt$accndviphi.ts2), predict(gam.cosphilt, rfdat.philt))
+
+#sine
+gam.sinphilt<-gam(sin(accndviphi.ts2) ~ hu4_zoneid + s(hu12_nlcd2011_pct_82) + 
+                 s(hu12_nlcd2011_pct_21), 
+               data=rfdat.philt, gamma=1, weights=lwgt)
+gam.check(gam.sinphilt)
+concurvity(gam.sinphilt)
+summary(gam.sinphilt)
+plot(sin(rfdat.philt$accndviphi.ts2), predict(gam.sinphilt, rfdat.philt))
 
@@
 
-```{r roughGAMplotting, echo=TRUE, cache=FALSE}
+```{r saveResults, echo=TRUE, cache=FALSE}
 
-# plot(gam.cohst, main="coherence, short")
-# plot(gam.cohlt, main="coherence, long")
-# plot(gam.phist, main="cos(phase), short")
-# plot(gam.philt, main="cos(phase), long")
-
+save.image(file="~/Box Sync/NSF EAGER Synchrony/Data/results_20191106.RData")
 ```

### 2019-11-29 AnalysisCode/Q1_coherenceSpatialVariation/ms1_analyses.Rmd
thinkPiece R1 and reorganization

--- 2019-06-05 AnalysisCode/ms1_analyses.Rmd
@@
 analysislakes$lakedata<-analysislakes$lakedata[!sapply(analysislakes$lakedata, function(x){any(is.na(x))})]
+
+analysislakes$lakeinfo$tslength<-analysislakes$lakeinfo$end-analysislakes$lakeinfo$start+1
+# analysislakes$lakedata<-analysislakes$lakedata[analysislakes$lakeinfo$tslength >= 20]
+# analysislakes$lakeinfo<-analysislakes$lakeinfo[analysislakes$lakeinfo$tslength >= 20,]
+
 ```
@@
 
-hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.2]/pi, main="Accumulated NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
+hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3]/pi, main="Accumulated NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
 #hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<0.2]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
@@
 
-hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts2<0.2]/pi, main="Accumulated NDVI, long timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
+hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts2<0.3]/pi, main="Accumulated NDVI, long timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
 #hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvicoh.ts2>0.6]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
@@
 
-modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.2,]
-modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.2,]
+modvars.accndvi.phist<-modvars.accndvi[modvars.accndvi$accndvip.ts1<0.3,]
+modvars.accndvi.philt<-modvars.accndvi[modvars.accndvi$accndvip.ts2<0.3,]
+
+modvars.accndvi[modvars.accndvi$tslength < 20,]
 
@@
 #short timescales
-gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
                         data=modvars.accndvi,
@@
 summary(gls.coh.accndvi.st)
+
+hist(predict(gls.coh.accndvi.st))
+plot(predict(gls.coh.accndvi.st), modvars.accndvi$accndvicoh.ts1, ylim=c(0,1), xlim=c(0,1),
+     ylab="empirical", xlab="predicted", main="Coherence, short ts")
+abline(a=0,b=1)
+cor.test(predict(gls.coh.accndvi.st),modvars.accndvi$accndvicoh.ts1)
+
 suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
@@
 
-gls.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+modavg.coh.accndvi.st<-model.avg(dredge.coh.accndvi.st, fit=T)
+modavg.coh.accndvi.st$importance
+
+hist(predict(modavg.coh.accndvi.st))
+plot(predict(modavg.coh.accndvi.st), modvars.accndvi$accndvicoh.ts1, ylim=c(0,1), xlim=c(0,1),
+     ylab="empirical", xlab="predicted", main="Coherence, short ts")
+abline(a=0,b=1)
+cor.test(predict(modavg.coh.accndvi.st),modvars.accndvi$accndvicoh.ts1)
+
+gls.phi.accndvi.st<-gls(cos(accndviphi.ts1) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
                         data=modvars.accndvi.phist,
@@
 #long timescales
-gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
                         data=modvars.accndvi,
@@
 
-gls.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
+gls.phi.accndvi.lt<-gls(cos(accndviphi.ts2) ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
                         data=modvars.accndvi.philt,
@@
 ```
-That turned up astonishingly little, so now try breaking down by region. 
+Early iterations of this made us wonder of things differed by region, so we tested these relationships broken down into 3 regions.
 The regions are: 1) Missouri; 2) Minnesota, Wisconsin, and Michigan; 3) Pennsylvania, New York, Rhode Island, Vermont, New Hampshire, Maine.
@@
 ```{r gls modeling r1, echo=TRUE, cache=FALSE}
-#Region 1: Missouri
-
-modvars.accndvi.r1<-modvars.accndvi[modvars.accndvi$state_name=="Missouri",]
-# modvars.accndvi.philt.r1<-modvars.accndvi.philt[modvars.accndvi.philt$state_name=="Missouri",]
-# modvars.accndvi.phist.r1<-modvars.accndvi.phist[modvars.accndvi.phist$state_name=="Missouri",]
-
-#short timescales
-gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r1,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.st)
-suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.st))
-
-#long timescales
-gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r1,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.lt)
-suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.lt))
+# #Region 1: Missouri
+# 
+# modvars.accndvi.r1<-modvars.accndvi[modvars.accndvi$state_name=="Missouri",]
+# # modvars.accndvi.philt.r1<-modvars.accndvi.philt[modvars.accndvi.philt$state_name=="Missouri",]
+# # modvars.accndvi.phist.r1<-modvars.accndvi.phist[modvars.accndvi.phist$state_name=="Missouri",]
+# 
+# #short timescales
+# gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
+#                         data=modvars.accndvi.r1,
+#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
+# summary(gls.coh.accndvi.st)
+# suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
+# print(head(dredge.coh.accndvi.st))
+# 
+# #long timescales
+# gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
+#                         data=modvars.accndvi.r1,
+#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
+# summary(gls.coh.accndvi.lt)
+# suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
+# print(head(dredge.coh.accndvi.lt))
 
@@
 ```{r gls modeling r2, echo=TRUE, cache=FALSE}
-#Region 2: Minnesota, Wisconsin, Michigan
-
-modvars.accndvi.r2<-modvars.accndvi[modvars.accndvi$state_name %in% c("Minnesota","Wisconsin","Michigan"),]
-
-#short timescales
-gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r2,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.st)
-suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.st))
-
-#long timescales
-gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r2,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.lt)
-suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.lt))
+# #Region 2: Minnesota, Wisconsin, Michigan
+# 
+# modvars.accndvi.r2<-modvars.accndvi[modvars.accndvi$state_name %in% c("Minnesota","Wisconsin","Michigan"),]
+# 
+# #short timescales
+# gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
+#                         data=modvars.accndvi.r2,
+#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
+# summary(gls.coh.accndvi.st)
+# suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
+# print(head(dredge.coh.accndvi.st))
+# 
+# #long timescales
+# gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
+#                         data=modvars.accndvi.r2,
+#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
+# summary(gls.coh.accndvi.lt)
+# suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
+# print(head(dredge.coh.accndvi.lt))
 
@@
 ```{r gls modeling r3, echo=TRUE, cache=FALSE}
-#Region 2: Minnesota, Wisconsin, Michigan
-
-modvars.accndvi.r3<-modvars.accndvi[modvars.accndvi$state_name %in% c("Pennsylvania","New York","Rhode Island","Vermont","New Hampshire","Maine"),]
-
-#short timescales
-gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r3,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.st)
-suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.st))
-
-#long timescales
-gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat, 
-                        data=modvars.accndvi.r3,
-                        correlation=corExp(form = ~ nhd_lat + nhd_long))
-summary(gls.coh.accndvi.lt)
-suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
-print(head(dredge.coh.accndvi.lt))
+# #Region 2: Minnesota, Wisconsin, Michigan
+# 
+# modvars.accndvi.r3<-modvars.accndvi[modvars.accndvi$state_name %in% c("Pennsylvania","New York","Rhode Island","Vermont","New Hampshire","Maine"),]
+# 
+# #short timescales
+# gls.coh.accndvi.st<-gls(accndvicoh.ts1 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
+#                         data=modvars.accndvi.r3,
+#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
+# summary(gls.coh.accndvi.st)
+# suppressWarnings(dredge.coh.accndvi.st<-dredge(gls.coh.accndvi.st, beta="sd")) #intercept only is best model. Disappointing.
+# print(head(dredge.coh.accndvi.st))
+# 
+# #long timescales
+# gls.coh.accndvi.lt<-gls(accndvicoh.ts2 ~ log10_maxdepth + log10_lake_area_ha + log10_pct.ag + log10_chla + tsi.cat + cv.accndvi, 
+#                         data=modvars.accndvi.r3,
+#                         correlation=corExp(form = ~ nhd_lat + nhd_long))
+# summary(gls.coh.accndvi.lt)
+# suppressWarnings(dredge.coh.accndvi.lt<-dredge(gls.coh.accndvi.lt, beta="sd")) #intercept only is best model. Disappointing.
+# print(head(dredge.coh.accndvi.lt))
 

### 2019-11-29 AnalysisCode/Q1_coherenceSpatialVariation/ms1_analyses_randforest.Rmd
thinkPiece R1 and reorganization

--- 2019-10-04 AnalysisCode/ms1_analyses_gam.Rmd
@@
 
-predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha) #not necessary to transform with random forests
+# predictors$log10_lake_area_ha<-log10(predictors$lake_area_ha) #not necessary to transform with random forests
 # predictors$log10_lake_perim_meters<-log10(predictors$lake_perim_meters)
@@
 # cforest.st<-partykit::cforest(accndvicoh.ts1 ~ lake_area_ha + lake_perim_meters + maxdepth + pct.ag + chla + tsi.cat + hu4_zoneid + cv.accndvi, 
-# #                     data=modvars.accndvi, ntree=20000)
-# cforest.st<-party::cforest(accndvicoh.ts1 ~ shoredev + lake_area_ha +  maxdepth + pct.ag + chla + tsi.cat + 
-#                              hu4_zoneid + cv.accndvi + pct.wetlands + doc + prcp.normal,
-#                     data=modvars.accndvi, controls=cforest_control(ntree=80000))
-
-lwgt<-modvars.accndvi$tslength/mean(modvars.accndvi$tslength)
-
-gam.cohst<-gam(accndvicoh.ts1 ~ s(shoredev) + s(prcp.normal) + s(log10(lake_area_ha)) + s(pct.ag),  weights=lwgt, data=modvars.accndvi, 
-               gamma=1.4, na.action = "na.fail")
-#dredge.cohst<-dredge(gam.cohst, evaluate=TRUE, m.lim=c(0,5))
-#importance(dredge.cohst)
-#modavg.cohst<-model.avg(dredge.cohst, fit=T)
-summary(gam.cohst)
-
-plot(modvars.accndvi$accndvicoh.ts1,predict(gam.cohst))
-
-topmod.cohst<-gam(accndvicoh.ts1 ~ s(shoredev,k=3) + s(log10(lake_area_ha),k=3) + s(prcp.normal,k=3) + s(pct.ag,k=3), data=modvars.accndvi,
-                  gamma=1)
-summary(topmod.cohst)
-
-gam.cohlt<-gam(accndvicoh.ts2 ~ s(shoredev,k=3) + s(log10(lake_area_ha),k=3) +  s(maxdepth,k=3) + s(pct.ag,k=3) + 
-                 s(chla,k=3) + tsi.cat + hu4_zoneid + s(cv.accndvi,k=3) + s(pct.wetlands,k=3) +  #removed doc because of NAs
-                 s(prcp.normal,k=3), data=modvars.accndvi, gamma=1,na.action = "na.fail")
-dredge.cohlt<-dredge(gam.cohlt, evaluate=TRUE, m.lim=c(0,5))
-importance(dredge.cohlt)
-modavg.cohlt<-model.avg(dredge.cohlt, fit=T)
-
-plot(modvars.accndvi$accndvicoh.ts1,predict(modavg.cohlt))
-
-topmod.cohlt<-gam(accndvicoh.ts1 ~ s(pct.wetlands,k=3) + s(cv.accndvi,k=3) + s(prcp.normal,k=3) + s(maxdepth,k=3), data=modvars.accndvi,
-                  gamma=1)
-summary(topmod.cohlt)
-
+#                     data=modvars.accndvi, ntree=20000)
+cforest.st<-party::cforest(accndvicoh.ts1 ~ shoredev + lake_area_ha +  maxdepth + pct.ag + chla + tsi.cat + 
+                             hu4_zoneid + cv.accndvi + pct.wetlands + doc + prcp.normal,
+                    data=modvars.accndvi, controls=cforest_control(ntree=50000,mincriterion = 0.9))
 predcoh.st<-predict(cforest.st, newdata=modvars.accndvi,type="response")
@@
                            + cv.accndvi+ pct.wetlands + doc + prcp.normal, 
-                    data=modvars.accndvi, controls=cforest_control(ntree=80000))
+                    data=modvars.accndvi, controls=cforest_control(ntree=50000,mincriterion = 0.9))
 predcoh.lt<-predict(cforest.lt, newdata=modvars.accndvi)
@@
                           cv.accndvi + pct.wetlands + doc + prcp.normal, 
-                        data=modvars.accndvi.philt,controls=cforest_control(ntree=40000))
+                        data=modvars.accndvi.philt,controls=cforest_control(ntree=50000))
 predphi.lt<-predict(cforest.phi.lt, newdata=modvars.accndvi.philt)

### 2019-11-29 AnalysisCode/ThinkPiece/allFigsAnalyses_R1.R

@@ -1,0 +1,266 @@
+# Think Piece Analysis and Figures
+
+rm(list=ls())
+
+library(lubridate)
+library(wsyn)
+
+##--------------------------------------------------------------
+## Figure 1: Des Moines River Nitrate
+
+##Data preparation
+
+dat1<-read.csv("~/Box Sync/NSF EAGER Synchrony/Data/Iowa Lakes Data/DesMoinesRiver_Site1_AllData.csv", stringsAsFactors = F)
+dat2<-read.csv("~/Box Sync/NSF EAGER Synchrony/Data/Iowa Lakes Data/ACE_Site1_TempFlow.csv", stringsAsFactors = F)
+
+dat<-rbind(dat1,dat2)
+
+dat$parameter<-rep(NA, nrow(dat))
+
+dat$parameter[dat$PARAM_NUM==4]<-"turbidity_ntu"
+dat$parameter[dat$PARAM_NUM==7]<-"tss_mgL"
+dat$parameter[dat$PARAM_NUM==13]<-"toc_mgL"
+dat$parameter[dat$PARAM_NUM==16]<-"bod_mgL"
+dat$parameter[dat$PARAM_NUM==20]<-"nitrate_mgL"
+dat$parameter[dat$PARAM_NUM==32]<-"tp_mgL"
+dat$parameter[dat$PARAM_NUM==2]<-"flow_"  #Ask Grace about units for flow and temp
+dat$parameter[dat$PARAM_NUM==3]<-"temp_"
+
+
+dat$sampleDate<-as.POSIXct(dat$DATE_OF_SAMPLE, format="%d-%b-%y")
+
+for(ii in 1:nrow(dat)){
+  if(year(dat$sampleDate[ii])==2067){year(dat$sampleDate[ii])<-1967}
+  if(year(dat$sampleDate[ii])==2068){year(dat$sampleDate[ii])<-1968}
+}
+
+params<-c("nitrate_mgL","tss_mgL","flow_","temp_")
+years<-1968:2016
+months<-1:12
+monthyear<-expand.grid(months, years)
+
+param.monthly<-matrix(NA, nrow=length(params), ncol=12*length(years))
+
+for(pp in 1:length(params)){
+  for(yy in 1:length(years)){
+    for(mm in months){
[…]

### 2019-11-29 AnalysisCode/ThinkPiece/old/displayItems.R

@@ -45,7 +45,7 @@ png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/ThinkPiece/superimposed_signals_
     height=5, width=3.25, res=300)
 
 par(mfrow=c(4,1), mar=c(2,2,0,1), xpd=F, oma=c(2,2,1,0), mgp=c(1,1,0))
-plot(tt,y1+y2+y3+y4, type="l",xaxt="n", xlab="", yaxt="n", ylab="Integrated")
+plot(tt,y1+y2+y3+y4, type="l",xaxt="n", xlab="", yaxt="n", ylab="Integrated",ylim=c(-3,3))
 rect(5,-4,10,4, col="skyblue2", xpd=F, border=NA)
 rect(12.5,-4,17.5,4,col="palegreen2",xpd=F,border=NA)
 rect(20,-4,25,4,col="gold",xpd=F,border=NA)
@@ -55,22 +55,22 @@ lines(tt[tt>=12.5 & tt<=17.5], predict(lm2), col="seagreen", lwd=3)
 lines(tt[tt>=20 & tt<=25], predict(lm3), col="goldenrod4", lwd=3)
 axis(1,at=c(1,5,10,15,20,25,30),labels=FALSE)
 axis(2,at=pretty(ycomp,5),labels=FALSE, xpd=F)
-text(0.5,2.6,"A")
+text(0.55,2.7,"A")
 
-plot(tt,y2,type="l",xaxt="n",xlab="", yaxt="n", ylab="Seasonal")
+plot(tt,y2,type="l",xaxt="n",xlab="", yaxt="n", ylab="Seasonal",ylim=c(-3,3))
 axis(1,at=c(1,5,10,15,20,25,30),labels=FALSE)
-axis(2,at=pretty(y2,5),labels=FALSE,xpd=F)
-text(0.5,0.85,"B")
+axis(2,at=pretty(ycomp,5),labels=FALSE,xpd=F)
+text(0.55,2.7,"B")
 
-plot(tt,y3,type="l",xaxt="n",xlab="", yaxt="n", ylab="Multi-annual")
+plot(tt,y3,type="l",xaxt="n",xlab="", yaxt="n", ylab="Multi-annual",ylim=c(-3,3))
 axis(1,at=c(1,5,10,15,20,25,30),labels=FALSE)
-axis(2,at=pretty(y3,5),labels=FALSE,xpd=F)
-text(0.5,0.65,"C")
[…]

### 2019-12-01 AnalysisCode/ThinkPiece/allFigsAnalyses_R1.R
Update allFigsAnalyses_R1.R

@@ -84,7 +84,7 @@ no3Xflow<-bandtest(no3Xflow,b4)
 print(no3Xflow$bandp)
 
 ## trend from 1980:1990
-lmx<-lm(no3[dec.time>=1980&dec.time<1991]~dec.time[dec.time>=1980&dec.time<1991])
+lmx<-lm(no3[dec.time>=1981&dec.time<1990]~dec.time[dec.time>=1981&dec.time<1990])
 summary(lmx)
 ## plotting function--this is modified from the 'wsyn' function by Reuman et al.
 
@@ -134,13 +134,13 @@ plotmag.JW<-function(object,zlims=NULL,neat=TRUE,colorfill=NULL,colorbar=TRUE,ti
   if (!colorbar)
   {
     graphics::image(x=times,y=log2(timescales),z=wav,xlab="",zlim=zlims,
-                    ylab="Timescale",axes=F,col=colorfill(100),main=title,...)
+                    ylab="Timescale (years)",axes=F,col=colorfill(100),main=title,...)
     graphics::axis(1,at = xlocs,labels=xlabs)
     graphics::axis(2,at = log2(ylocs),labels = ylabs)
   }else
   {
     fields::image.plot(x=times,y=log2(timescales),z=wav,xlab="",zlim=zlims,
-                       ylab="Timescale",axes=F,col=colorfill(100),main=title,...)
+                       ylab="Timescale (years)",axes=F,col=colorfill(100),main=title,...)
     graphics::axis(1,at = xlocs,labels=xlabs)
     graphics::axis(2,at = log2(ylocs),labels = ylabs)
   }
@@ -169,11 +169,11 @@ tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/ThinkPiece/dmr_example.tif",
 layout(laymat)
 par(mar=c(2.1,3.5,1.1,1.1),oma=c(2.1,0,0,0),mgp=c(2.2,0.8,0))
 
-plot(no3, type="l", xlab="", ylab=expression("NO"[3]*~(mu*"gL"^-1)), xaxt="n")
-lines((1:length(no3))[dec.time>=1980&dec.time<1991],
-      predict(lmx,data.frame(dec.time[dec.time>=1980&dec.time<1991])),col="red")
[…]

### 2019-12-10 AnalysisCode/Q2_ClimateCoherence/ms2_analyses.Rmd
q2 updates in progress

---
title: 'Q2: Does climate drive lake-landscape coherence?'
author: "Jonathan Walter, Grace Wilkinson, Rachel Fleck, Michael Pace"
date: "12/9/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(aqts)
library(wsyn)
library(rgdal)
library(rgeos)
library(LAGOSNE)
library(raster)
library(dplyr)
library(viridis)

rm(list=ls())

```

This document organizes for openness and reproducibility analyses of the influence of climate .

# Data import

In the Q1 manuscript, we output time series from coherent lake-landscape pairs. These are loaded here. We also load time series of three major climate indices (ENSO, PDO, NAO) and local temperature and precipitation.

```{r load and format data, echo=TRUE, cache=FALSE}

#load coherent lakes data
load("~/Box Sync/NSF EAGER Synchrony/Data/RData files/q2_coherent_lakes.RData")
#load climate index time series
mei.raw<-read.csv("/Users/jonathanwalter/Documents/Research/DATA/ClimateIndices/mei_monthly_1979_2019.csv")#MEI
pdo.raw<-read.csv("/Users/jonathanwalter/Documents/Research/DATA/ClimateIndices/pdo_monthly_1950_2019.csv")#PDO
nao.raw<-read.csv("/Users/jonathanwalter/Documents/Research/DATA/ClimateIndices/nao_monthly_1950_2019.csv")#NAO

mei.gs<-mei.raw[mei.raw$mm >=5 & mei.raw$mm <=9,]
pdo.gs<-pdo.raw[pdo.raw$mm >=5 & pdo.raw$mm <=9,]
nao.gs<-nao.raw[nao.raw$mm >=5 & nao.raw$mm <=9,]

mei.gs<-aggregate(mei.gs$mei,list(mei.gs$yyyy),FUN="mean")
names(mei.gs)<-c("year","mei")
pdo.gs<-aggregate(pdo.gs$PDO,list(pdo.gs$yyyy),FUN="mean")
names(pdo.gs)<-c("year","pdo")
nao.gs<-aggregate(nao.gs$NAO,list(nao.gs$yyyy),FUN="mean")
names(nao.gs)<-c("year","nao")

for(ii in 1:length(coherentlakes.st$lakedata)){
  coherentlakes.st$lakedata[[ii]]<-rbind(coherentlakes.st$lakedata[[ii]],
                                         mei.gs$mei[mei.gs$year %in% colnames(coherentlakes.st$lakedata[[ii]])],
                                         pdo.gs$pdo[pdo.gs$year %in% colnames(coherentlakes.st$lakedata[[ii]])],
                                         nao.gs$nao[nao.gs$year %in% colnames(coherentlakes.st$lakedata[[ii]])])
  rownames(coherentlakes.st$lakedata[[ii]])<-c("chla","ndvi","mei","pdo","nao")
}

for(ii in 1:length(coherentlakes.lt$lakedata)){
  coherentlakes.lt$lakedata[[ii]]<-rbind(coherentlakes.lt$lakedata[[ii]],
                                         mei.gs$mei[mei.gs$year %in% colnames(coherentlakes.lt$lakedata[[ii]])],
                                         pdo.gs$pdo[pdo.gs$year %in% colnames(coherentlakes.lt$lakedata[[ii]])],
                                         nao.gs$nao[nao.gs$year %in% colnames(coherentlakes.lt$lakedata[[ii]])])
  rownames(coherentlakes.lt$lakedata[[ii]])<-c("chla","ndvi","mei","pdo","nao")
}
#add local weather --  write a function to do this.

```

# Analyses

a) Are lakes and landscapes coherent with the same climate variables? b) Do climate variables explain a similar amount of variability in coherent lakes as the landscape does? c) does this differ by timescale?

First, do coherences with climate variables
```{r climate coherence, echo=TRUE, cache=FALSE}

```

Second, find out how much variability in lakes is explained by coherence with the landscape
```{r wlms lake v landscape, echo=TRUE, cache=FALSE}

```

Third, find out how much variability in lakes is explained by coherence with variables the landscape is coherent with
```{r wlms lake v climate, echo=TRUE, cache=FALSE}

```

### 2019-12-10 AnalysisCode/ms1_analyses_rf_to_gam.Rmd
q2 updates in progress

--- 2019-11-01 AnalysisCode/ms1_analyses_rf_to_gam.Rmd
@@
 library(rgdal)
+library(rgeos)
 library(LAGOSNE)
@@
 #library(partykit)
-library(pdp)
+#library(pdp)
+library(png)
 library(party)
@@
 
-# image(accndvi)
-# points(lakepts.prj[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))})),])
-
 dbuff[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))}))]
@@
 analysislakes$lakeinfo$tslength<-analysislakes$lakeinfo$end-analysislakes$lakeinfo$start+1
-# analysislakes$lakedata<-analysislakes$lakedata[!analysislakes$lakeinfo$tslength < 20]
-# analysislakes$lakeinfo<-analysislakes$lakeinfo[!analysislakes$lakeinfo$tslength < 20,]
 
@@
 coh.chlaXaccndvi<-NULL
-#coh.chlaXmaxndvi<-NULL
 
@@
                     norm="powall", sigmethod="fast", nrand=10000)
-#  chlaXmaxndvi<-coh(lakedat.ii[1,], lakedat.ii[3,], as.numeric(colnames(analysislakes$lakedata[[lind]])),
-#                    norm="powall", sigmethod="fast", nrand=10000)
   for(rind in 1:nrow(tsranges)){
     chlaXaccndvi<-bandtest.coh(chlaXaccndvi, tsranges[rind,])
-    #chlaXmaxndvi<-bandtest.coh(chlaXmaxndvi, tsranges[rind,])
   }
   coh.chlaXaccndvi<-rbind(coh.chlaXaccndvi, c(t(as.matrix(chlaXaccndvi$bandp[,3:5]))))
-#  coh.chlaXmaxndvi<-rbind(coh.chlaXmaxndvi, c(t(as.matrix(chlaXmaxndvi$bandp[,3:5]))))
-
 }
@@
 coh.chlaXaccndvi<-as.data.frame(coh.chlaXaccndvi)
-#coh.chlaXmaxndvi<-as.data.frame(coh.chlaXmaxndvi)
 
 colnames(coh.chlaXaccndvi)<-paste0("accndvi",c("p.ts1","phi.ts1","coh.ts1","p.ts2","phi.ts2","coh.ts2","p.ts3","phi.ts3","coh.ts3"))
-#colnames(coh.chlaXmaxndvi)<-paste0("maxndvi",c("p.ts1","phi.ts1","coh.ts1","p.ts2","phi.ts2","coh.ts2","p.ts3","phi.ts3","coh.ts3"))
 
 coh.chlaXaccndvi$lagoslakeid<-analysislakes$lakeinfo$lagoslakeid
-#coh.chlaXmaxndvi$lagoslakeid<-analysislakes$lakeinfo$lagoslakeid
+
+```
+
+```{r export coherent lakes, echo=FALSE, cache=FALSE}
+
+coherentlakes.st<-analysislakes
+coherentlakes.st$lakeinfo<-coherentlakes.st$lakeinfo[coherentlakes.st$lakeinfo$lagoslakeid %in%
+                                                       coh.chlaXaccndvi$lagoslakeid[coh.chlaXaccndvi$accndvip.ts1<0.05],]
+coherentlakes.st$lakedata<-coherentlakes.st$lakedata[names(coherentlakes.st$lakedata) %in%
+                                                       coh.chlaXaccndvi$lagoslakeid[coh.chlaXaccndvi$accndvip.ts1<0.05]]
+
+coherentlakes.lt<-analysislakes
+coherentlakes.lt$lakeinfo<-coherentlakes.lt$lakeinfo[coherentlakes.lt$lakeinfo$lagoslakeid %in%
+                                                       coh.chlaXaccndvi$lagoslakeid[coh.chlaXaccndvi$accndvip.ts2<0.05],]
+coherentlakes.lt$lakedata<-coherentlakes.lt$lakedata[names(coherentlakes.lt$lakedata) %in%
+                                                       coh.chlaXaccndvi$lagoslakeid[coh.chlaXaccndvi$accndvip.ts2<0.05]]
+
+save(list=c("coherentlakes.st","coherentlakes.lt"),
+     file="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/q2_coherent_lakes.RData")
 
@@
 ```{r pedagogical example, echo=TRUE, cache=FALSE}
-#looking for especially coherent lakes did not return easy-to-interpret examples. Proceeding with simulated data
 
@@
 #short timescales
-hist(coh.chlaXaccndvi$accndvicoh.ts1, main="Accumulated NDVI, short timescales", xlab="Coherence", ylab="Frequency")
-#hist(coh.chlaXmaxndvi$maxndvicoh.ts1, main="Maximum NDVI, short timescales", xlab="Coherence", ylab="Frequency")
-
 quantile(coh.chlaXaccndvi$accndvicoh.ts1)
-#quantile(coh.chlaXmaxndvi$maxndvicoh.ts1)
 
@@
 sum(coh.chlaXaccndvi$accndvip.ts1<alpha)/nrow(coh.chlaXaccndvi)
-#sum(coh.chlaXmaxndvi$maxndvip.ts1<alpha)/nrow(coh.chlaXmaxndvi)
 
@@
 
-# print(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<alpha]/pi) #only pattern is that lakes don't lead the landscape
-# print(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<alpha]/pi)
-
-phicls<-c(-1,-.75,-0.25,0.25,0.75,1)
-
-# hist(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.2]/pi, main="Accumulated NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
-rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian",
-     breaks=seq(0,2*pi,length.out=16))
-#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvip.ts1<0.2]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
-
 #long timescales
-hist(coh.chlaXaccndvi$accndvicoh.ts2, main="Accumulated NDVI, long timescales", xlab="Coherence", ylab="Frequency")
-#hist(coh.chlaXmaxndvi$maxndvicoh.ts2, main="Maximum NDVI, long timescales", xlab="Coherence", ylab="Frequency")
-
 quantile(coh.chlaXaccndvi$accndvicoh.ts2)
-#quantile(coh.chlaXmaxndvi$maxndvicoh.ts2)
 
@@
 sum(coh.chlaXaccndvi$accndvip.ts2<alpha)/nrow(coh.chlaXaccndvi)
-#sum(coh.chlaXmaxndvi$maxndvip.ts2<alpha)/nrow(coh.chlaXmaxndvi)
 
 print(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<alpha]/pi)
-#print(coh.chlaXmaxndvi$maxndviphi.ts2[coh.chlaXmaxndvi$maxndvip.ts2<alpha]/pi)
 
-# hist(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.2]/pi, main="Accumulated NDVI, long timescales", xlab="Phase (pi)", ylab="Frequency", breaks=phicls)
-rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian",
-     breaks=seq(0,2*pi,length.out=16))
-
-#hist(coh.chlaXmaxndvi$maxndviphi.ts1[coh.chlaXmaxndvi$maxndvicoh.ts2>0.6]/pi, main="Maximum NDVI, short timescales", xlab="Phase (pi)", ylab="Frequency", breaks=5)
-
+#plotting
 tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions_20191031.tif", units="in",
@@
 
-states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020.shp")
+states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020_nolakes.shp")
 getstates<-c("Minnesota", "Iowa", "Wisconsin", "Illinois", "Missouri", "Michigan", "Indiana", "Ohio", "Pennsylvania", "New York", "New Jersey", "Connecticut", "New Hampshire", "Rhode Island", "Massachusetts", "Vermont", "Maine")
@@
 
-plot(lagosstates, main="Lakes selected for analysis")
-points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=16, cex=1, col="blue")
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_map.tif",units="in",
+     res=300, width=3.25, height=2.75)
+par(mar=rep(0,4))
+plot(lagosstates, main="",bty="o")
+points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=21, cex=0.45, col="black",bg="grey")
+legend("bottomright",pch=c(0,21),col="black",pt.bg="grey",legend=c("States in LAGOS-NE","Selected lakes"),inset=c(0.025,0.01),bty="n")
+dev.off()
 
@@
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_coherencemap.tif", units="in",
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS1_coherencemap.tif", units="in",
      res=300, width=6.5, height=7.5)
@@
 
-#remove any variables that don't vary in this dataset
-# for(nn in 1:ncol(preds)){
-#   print(colnames(preds)[nn])
-#   print(unique(preds[,nn]))
-# }
+conpreds<-preds[,sapply(preds, is.numeric)]
+cor.conpreds<-cor(conpreds,use="pairwise.complete.obs")
 
@@
 
-# modvars.conn<-left_join(pred.conn, coh.chlaXaccndvi, by="lagoslakeid")
-# modvars.chag<-left_join(pred.chag, coh.chlaXaccndvi, by="lagoslakeid")
-
 #huc2 and huc4 watershed codes
@@
 for(nn in 1:ncol(preds)){
-
   if(is.factor(preds[,nn])){
@@
   }
+}
 
-}
+#write.csv(colnames(preds),file="~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/predictorlist.csv")
 
@@
 print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10])
-#hist(predcoh.st)
-#hist(modvars.accndvi$accndvicoh.ts1)
 predcoh.st<-predict(cf.cohst, newdata=rfdat.cohst,type="response")
-# plot(predcoh.st, rfdat.cohst$accndvicoh.ts1, xlab="predicted", ylab="empirical", main="Coherence, short ts",
-#      xlim=c(0,1), ylim=c(0,1))
-# abline(a=0,b=1)
 cor.test(predcoh.st,rfdat.cohst$accndvicoh.ts1)
@@
 gam.check(gam.cohst)
-concurvity(gam.cohst)
+concurvity(gam.cohst,full=F)$estimate
 summary(gam.cohst)
@@
 print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10])
-#hist(predcoh.st)
-#hist(modvars.accndvi$accndvicoh.ts1)
 predcoh.lt<-predict(cf.cohlt, newdata=rfdat.cohlt,type="response")
-# plot(predcoh.lt, rfdat.cohlt$accndvicoh.ts2, xlab="predicted", ylab="empirical", main="Coherence, long ts",
-#      xlim=c(0,1), ylim=c(0,1))
-# abline(a=0,b=1)
 cor.test(predcoh.lt,rfdat.cohlt$accndvicoh.ts2)
@@
 gam.cohlt<-gam(accndvicoh.ts2 ~ hu8_zoneid + s(hu12_nlcd2011_pct_52) + s(cv.accndvi) + 
-                 s(wlconnections_forestedwetlands_shoreline_km) + 
-                 s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean), data=rfdat.cohlt, gamma=1, weights=lwgt)
+                 s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean) + 
+                 s(wlconnections_allwetlands_contributing_area_ha), data=rfdat.cohlt, gamma=1, weights=lwgt)
 gam.check(gam.cohlt)
-concurvity(gam.cohlt)
+concurvity(gam.cohlt,full=F)$estimate
 summary(gam.cohlt)
@@
 
-cf.phist<-party::cforest(cos(accndviphi.ts1) ~ ., data=rfdat.phist, 
+#cosine
+cf.cosphist<-party::cforest(cos(accndviphi.ts1) ~ ., data=rfdat.phist, 
                          controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
+varimp.cosphi.st<-varimp(cf.cosphist)
+print(varimp.cosphi.st[order(varimp.cosphi.st, decreasing=T)][1:10])
+pred.cosphi.st<-predict(cf.cosphist, newdata=rfdat.phist,type="response")
+cor.test(pred.cosphi.st,cos(rfdat.phist$accndviphi.ts1))
 
-varimp.phi.st<-varimp(cf.phist)
-print(varimp.phi.st[order(varimp.phi.st, decreasing=T)][1:10])
-predphi.st<-predict(cf.phist, newdata=rfdat.phist,type="response")
-cor.test(predphi.st,cos(rfdat.phist$accndviphi.ts1))
+#sine
+cf.sinphist<-party::cforest(sin(accndviphi.ts1) ~ ., data=rfdat.phist, 
+                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
+varimp.sinphi.st<-varimp(cf.sinphist)
+print(varimp.sinphi.st[order(varimp.sinphi.st, decreasing=T)][1:10])
+pred.sinphi.st<-predict(cf.sinphist, newdata=rfdat.phist,type="response")
+cor.test(pred.sinphi.st,sin(rfdat.phist$accndviphi.ts1))
 
@@
                data=rfdat.phist, gamma=1, weights=lwgt)
-gam.check(gam.phist)
-concurvity(gam.phist)
-summary(gam.phist)
-plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.phist, rfdat.phist))
+gam.check(gam.cosphist)
+concurvity(gam.cosphist, full=F)$estimate
+summary(gam.cosphist)
+plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.cosphist, rfdat.phist))
+
+#sine -- ignored in main text
+gam.sinphist<-gam(sin(accndviphi.ts1) ~ s(buffer500m_streamdensity_headwaters_density_mperha) + 
+                 s(hu12_dep_so4_tavg_mean) + 
+                 s(hu12_damdensity_pointspersqkm), 
+               data=rfdat.phist, gamma=1, weights=lwgt)
+gam.check(gam.sinphist)
+concurvity(gam.sinphist,full=F)$estimate
+summary(gam.sinphist)
+plot(sin(rfdat.phist$accndviphi.ts1), predict(gam.sinphist, rfdat.phist))
 
@@
 
-cf.philt<-party::cforest(cos(accndviphi.ts2) ~ ., data=rfdat.philt,
+#cosine
+cf.cosphilt<-party::cforest(cos(accndviphi.ts2) ~ ., data=rfdat.philt,
                          controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
 
-varimp.phi.lt<-varimp(cf.philt)
-print(varimp.phi.lt[order(varimp.phi.lt, decreasing=T)][1:10])
-predphi.lt<-predict(cf.philt, newdata=rfdat.philt,type="response")
-cor.test(predphi.lt,cos(rfdat.philt$accndviphi.ts2))
+varimp.cosphi.lt<-varimp(cf.cosphilt)
+print(varimp.cosphi.lt[order(varimp.cosphi.lt, decreasing=T)][1:10])
+pred.cosphi.lt<-predict(cf.cosphilt, newdata=rfdat.philt,type="response")
+cor.test(pred.cosphi.lt,cos(rfdat.philt$accndviphi.ts2))
+
+#sine
+cf.sinphilt<-party::cforest(sin(accndviphi.ts2) ~ ., data=rfdat.philt,
+                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
+
+varimp.sinphi.lt<-varimp(cf.sinphilt)
+print(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing=T)][1:10])
+pred.sinphi.lt<-predict(cf.sinphilt, newdata=rfdat.philt,type="response")
+cor.test(pred.sinphi.lt,sin(rfdat.philt$accndviphi.ts2))
 
@@
 
-gam.philt<-gam(cos(accndviphi.ts2) ~ hu4_zoneid + s(hu12_tri_mean) + 
-                 s(hu12_nlcd2011_pct_41), 
+#cosine
+gam.cosphilt<-gam(cos(accndviphi.ts2) ~ hu4_zoneid + s(hu12_slope_mean) + 
+                 s(hu12_nlcd2011_pct_90), 
                data=rfdat.philt, gamma=1, weights=lwgt)
-gam.check(gam.philt)
-concurvity(gam.philt)
-summary(gam.philt)
-plot(cos(rfdat.philt$accndviphi.ts2), predict(gam.philt, rfdat.philt))
+gam.check(gam.cosphilt)
+concurvity(gam.cosphilt,full=F)$estimate
+summary(gam.cosphilt)
+plot(cos(rfdat.philt$accndviphi.ts2), predict(gam.cosphilt, rfdat.philt))
+
+#sine
+gam.sinphilt<-gam(sin(accndviphi.ts2) ~ hu4_zoneid + s(hu12_nlcd2011_pct_82) + 
+                 s(hu12_nlcd2011_pct_21), 
+               data=rfdat.philt, gamma=1, weights=lwgt)
+gam.check(gam.sinphilt)
+concurvity(gam.sinphilt,full=F)$estimate
+summary(gam.sinphilt)
+plot(sin(rfdat.philt$accndviphi.ts2), predict(gam.sinphilt, rfdat.philt))
 
@@
 
-```{r roughGAMplotting, echo=TRUE, cache=FALSE}
+```{r saveResults, echo=TRUE, cache=FALSE}
+# save.image(file="~/Box Sync/NSF EAGER Synchrony/Data/results_20191106.RData")
+```
 
-# plot(gam.cohst, main="coherence, short")
-# plot(gam.cohlt, main="coherence, long")
-# plot(gam.phist, main="cos(phase), short")
-# plot(gam.philt, main="cos(phase), long")
-
-```
 ```{r plot varimp}
@@
 
-print(varimp.phi.st[order(varimp.phi.st, decreasing = T)][1:10])
-ltxt.phist<-c("open wetlands shoreline","headwaters density","mean chlorophyll-a","stream density",
-              "open wetlands contrib. area","% developed open space","nitrate deposition", "road density",
-              "% developed low intensity","all wetlands contrib. area")
+print(varimp.cosphi.st[order(varimp.cosphi.st, decreasing = T)][1:10])
+ltxt.cosphist<-c("open wetlands shoreline","headwaters density","stream density","mean chlorophyll-a",
+              "% developed open space","open wetlands contrib. area","all wetlands contrib. area", "road density","nitrate deposition",
+              "% pasture/hay")
 
-print(varimp.phi.lt[order(varimp.phi.lt, decreasing = T)][1:10])
-ltxt.philt<-c("HUC-4 subregion","HUC-6 basin","slope","topographic roughness","% deciduous forest","% woody wetlands",
-               "headwaters density","total N deposition","HUC-8 sub-basin","stream density")
+print(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing = T)][1:10])
+ltxt.sinphilt<-c("HUC-4 subregion","HUC-6 basin","% cultivated crops","HUC-8 sub-basin","% developed open space",
+                 "open wetlands contrib. area","all wetlands contrib. area","% open water","all wetlands shoreline","shrub wetladns contrib. area")
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10.tif",units="in",res=300,width=6.5, height=6.5)
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10.tif",units="in",res=300,width=6.5, height=5)
 
-par(mfrow=c(2,2), mar=c(5,11,1,1), cex.main=0.9, cex.axis=0.9)
+par(mfrow=c(2,2), mar=c(4,11,1,1), cex.main=0.9, cex.axis=0.9)
 
-barplot(rev(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10]),names.arg=rev(ltxt.st),las=2,main="Short timescale coher.", horiz=T)
+barplot(rev(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10]),names.arg=rev(ltxt.st),las=2,main="a) Short timescale coher.", horiz=T,font.main=1)
 
-barplot(rev(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.lt),las=2,main="Long timescale coher.", horiz=T)
+barplot(rev(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.lt),las=2,main="c) Long timescale coher.", horiz=T, font.main=1)
 
-barplot(rev(varimp.phi.st[order(varimp.phi.st, decreasing=T)][1:10]),names.arg=rev(ltxt.phist),las=2,main="Short timescale phase", horiz=T)
+barplot(rev(varimp.cosphi.st[order(varimp.cosphi.st, decreasing=T)][1:10]),names.arg=rev(ltxt.cosphist),las=2,
+        main=expression(paste("b) Short timescale cosine(",phi,")",sep="")), horiz=T)
 
-barplot(rev(varimp.phi.lt[order(varimp.phi.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.philt),las=2,main="Long timescale phase", horiz=T)
+barplot(rev(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.sinphilt),las=2,
+        main=expression(paste("d) Long timescale sine(",phi,")",sep="")), horiz=T)
 
@@
 
-mar1<-c(3,1.5,0.5,1)
-#mar2<-c(2.5,1.5,1,1)
-fudge=1/40
+## Make geographic variation images 
+huc4_bdys<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/HU4.shp")
+huc8_bdys<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/HU8.shp")
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits.tif",units="in",res=300,width=6.5, height=6.5)
+cohst_huc8<-data.frame(ZoneID=names(gam.cohst$coefficients)[grepl("hu8_zoneid",names(gam.cohst$coefficients))],
+                      coeff=gam.cohst$coefficients[grepl("hu8_zoneid",names(gam.cohst$coefficients))])
+rownames(cohst_huc8)<-c()
+cohst_huc8$ZoneID<-substring(cohst_huc8$ZoneID,11)
 
-par(mfrow=c(4,5),mgp=c(1.5,0.5,0),oma=c(0,2.5,0,0),mar=mar1)
+cohlt_huc8<-data.frame(ZoneID=names(gam.cohlt$coefficients)[grepl("hu8_zoneid",names(gam.cohlt$coefficients))],
+                      coeff=gam.cohlt$coefficients[grepl("hu8_zoneid",names(gam.cohlt$coefficients))])
+rownames(cohlt_huc8)<-c()
+cohlt_huc8$ZoneID<-substring(cohlt_huc8$ZoneID,11)
+
+sinphilt_huc4<-data.frame(ZoneID=names(gam.sinphilt$coefficients)[grepl("hu4_zoneid",names(gam.sinphilt$coefficients))],
+                      coeff=gam.sinphilt$coefficients[grepl("hu4_zoneid",names(gam.sinphilt$coefficients))])
+rownames(sinphilt_huc4)<-c()
+sinphilt_huc4$ZoneID<-substring(sinphilt_huc4$ZoneID,11)
+
+# lagosstates_outline<-lagosstates
+# lagosstates_outline@data$dissolve<-rep(1,length(lagosstates_outline))
+# lagosstates_outline<-gUnaryUnion(lagosstates_outline,id=lagosstates_outline@data$dissolve)
+# huc4_bdys<-raster::intersect(huc4_bdys,lagosstates_outline)
+# huc8_bdys<-raster::intersect(huc8_bdys,lagosstates_outline)
+
+# huc_codes<-read.csv("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
+# huc_codes<-huc_codes[huc_codes$hu4_zoneid %in% analysislakes$lakeinfo$hu4_zoneid,]
+
+huc_bdys_cohst<-huc8_bdys[huc8_bdys$ZoneID %in% cohst_huc8$ZoneID,]
+huc_bdys_cohst@data<-left_join(huc_bdys_cohst@data, cohst_huc8)
+
+huc_bdys_cohlt<-huc8_bdys[huc8_bdys$ZoneID %in% cohlt_huc8$ZoneID,]
+huc_bdys_cohlt@data<-left_join(huc_bdys_cohlt@data, cohlt_huc8)
+
+huc_bdys_sinphilt<-huc4_bdys[huc4_bdys$ZoneID %in% sinphilt_huc4$ZoneID,]
+huc_bdys_sinphilt@data<-left_join(huc_bdys_sinphilt@data, sinphilt_huc4)
+
+scale1_100<-function(x){
+  x1<-x-min(x)+1/100
+  x1<-round(x1/max(x1)*100)
+  return(x1)
+}
+#make smaller images that we can insert into the main figure
+
+bight=6.5
+bigwd=6.5
+
+lagosstates_prj<-spTransform(lagosstates, proj4string(huc8_bdys))
+
+# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst.png", units="in",
+#      res=300, width=bigwd/5, height=bight/4)
+# par(mar=c(0,0,2,0))
+# plot(huc_bdys_cohst,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohst$coeff)],xlim=c(-91837,2260000),lwd=0.5)
+# lines(lagosstates_prj,lwd=0.5)
+# par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
+# image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
+# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohst$coeff), max(huc_bdys_cohst$coeff), length.out=5),2), cex=0.5)
+# dev.off()
+# 
+# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt.png", units="in",
+#      res=300, width=bigwd/5, height=bight/4)
+# par(mar=c(0,0,2,0))
+# plot(huc_bdys_cohlt,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohlt$coeff)],xlim=c(-91837,2260000),lwd=0.5)
+# lines(lagosstates_prj,lwd=0.5)
+# par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
+# image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
+# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohlt$coeff), max(huc_bdys_cohlt$coeff), length.out=5),2), cex=0.5)
+# dev.off()
+# 
+# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt.png", units="in",
+#      res=300, width=bigwd/5, height=bight/4)
+# par(mar=c(0,0,2,0))
+# plot(huc_bdys_sinphilt,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys_sinphilt$coeff)],xlim=c(-91837,2260000),lwd=0.5)
+# lines(lagosstates_prj,lwd=0.5)
+# par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
+# image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
+# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_sinphilt$coeff), max(huc_bdys_sinphilt$coeff), length.out=5),2), cex=0.5)
+# dev.off()
+# 
+# 
+# panel5b<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst.png")
+# panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt.png")
+# panel5n<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt.png")
+# 
+# mar1<-c(3,1.5,0.5,1)
+# fudge=1/40
+# 
+# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits.tif",units="in",res=300,width=bigwd, height=bight)
+# 
+# par(mfrow=c(4,5),mgp=c(1.5,0.5,0),oma=c(0,2.5,0,0),mar=mar1)
+# 
+# plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence")
+# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
+# rasterImage(image=panel5b,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+# plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="")
+# plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="")
+# plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% herbaceous wetld.",ylab="")
+# 
+# plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetlands shoreline",ylab="short phase")
+# plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
+# plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
+# plot.new()
+# plot.new()
+# 
+# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
+# rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+# plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-1,1))
+# plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="",ylim=c(-1,1))
+# plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="annual precipitation",ylab="")
+# plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetld. contrib. area",ylab="",ylim=c(-1,1))
+# 
+# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-4 sub-region",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
+# rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+# plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% pasture",ylab="")
+# plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% developed-open space",ylab="")
+# 
+# mtext("Partial residuals",2,outer=T,line=1.2,cex=0.8)
+# mtext("sin(long phase)",2,at=1/8+fudge,outer=T,line=0,cex=0.7)
+# mtext("long coherence",2,at=1/8+1/4+fudge,outer=T,line=0,cex=0.7)
+# mtext("cos(short phase)",2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)
+# mtext("short coherence",2,at=1/8+3/4+fudge,outer=T,line=0,cex=0.7)
+# 
+# dev.off()
+
+## try out landscape orientation
+
+bight=5.5
+bigwd=9
+
+lagosstates_prj<-spTransform(lagosstates, proj4string(huc8_bdys))
+
+png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png", units="in",
+     res=300, width=bigwd/5, height=bight/4)
+par(mar=c(0,0,1,0))
+plot(huc_bdys_cohst,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohst$coeff)],xlim=c(-91837,2260000),
+     ylim=c(1454000,3012981),lwd=0.5)
+lines(lagosstates_prj,lwd=0.5)
+par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
+image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
+axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohst$coeff), max(huc_bdys_cohst$coeff), length.out=5),2), cex.axis=0.7)
+dev.off()
+
+png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png", units="in",
+     res=300, width=bigwd/5, height=bight/4)
+par(mar=c(0,0,1,0))
+plot(huc_bdys_cohlt,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohlt$coeff)],xlim=c(-91837,2260000),
+     ylim=c(1454000,3012981),lwd=0.5)
+lines(lagosstates_prj,lwd=0.5)
+par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
+image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
+axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohlt$coeff), max(huc_bdys_cohlt$coeff), length.out=5),2), cex.axis=0.7)
+dev.off()
+
+png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png", units="in",
+     res=300, width=bigwd/5, height=bight/4)
+par(mar=c(0,0,1,0))
+plot(huc_bdys_sinphilt,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys_sinphilt$coeff)],xlim=c(-91837,2260000),
+     ylim=c(1454000,3012981),lwd=0.5)
+lines(lagosstates_prj,lwd=0.5)
+par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
+image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
+axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_sinphilt$coeff), max(huc_bdys_sinphilt$coeff), length.out=5),2), cex.axis=0.7)
+dev.off()
+
+panel5b<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png")
+panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png")
+panel5n<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png")
+
+mar1<-c(3,1.5,0.5,0.2)
+fudge=1/34
+
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_landscape.tif",units="in",res=300,width=bigwd, height=bight)
+
+par(mfrow=c(4,5),mgp=c(1.5,0.5,0), oma=c(0,2.5,0,0.5),mar=mar1,tcl=-0.3)
 
 plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence")
-plot(NA,NA,xlab="HUC-8 sub-basin",xlim=c(0,1),ylim=c(0,1))
+plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
+rasterImage(image=panel5b,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
 plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="")
@@
 
-plot(gam.phist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetlands shoreline",ylab="short phase")
-plot(gam.phist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
-plot(gam.phist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
+plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetlands shoreline",ylab="short phase")
+plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
+plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
 plot.new()
@@
 
-plot(NA,NA,xlab="HUC-8 sub-basin",xlim=c(0,1),ylim=c(0,1))
+plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
+rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
 plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-1,1))
@@
 
-plot(NA,NA,xlab="HUC-4 subregion",xlim=c(0,1),ylim=c(0,1),ylab="long phase")
-plot(gam.philt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="slope",ylab="")
-plot(gam.philt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% deciduous forest",ylab="")
+plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-4 sub-region",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
+rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% pasture",ylab="")
+plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% developed-open space",ylab="")
 
 mtext("Partial residuals",2,outer=T,line=1.2,cex=0.8)
-mtext("cos(long phase)",2,at=1/8+fudge,outer=T,line=0,cex=0.7)
-mtext("long coherence)",2,at=1/8+1/4+fudge,outer=T,line=0,cex=0.7)
-mtext("cos(short phase)",2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)
+mtext(expression(paste("long sin(",phi,")",sep="")),2,at=1/8+fudge,outer=T,line=0,cex=0.7)
+mtext("long coherence",2,at=1/8+1/4+fudge,outer=T,line=0,cex=0.7)
+mtext(expression(paste("short cos(",phi,")",sep="")),2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)
 mtext("short coherence",2,at=1/8+3/4+fudge,outer=T,line=0,cex=0.7)

### 2019-12-10 R Package/aqts/R/addPRISMts.R

@@ -1,0 +1,70 @@
+#' Add terrestrial AVHRR time series to limnological time series
+#' 
+#' \code{addPRISMts} extracts PRISM time series and appends them to limnological time series produced by,
+#' e.g., \code{makeLAGOSannualts}.
+#' 
+#' @param lakelist a list containing \code{lakeinfo} and \code{lakedata}, as output from \code{makeLAGOSannualts}.
+#' @param prismdata a raster stack of annual AVHRR metrics
+#' 
+#' @return \code{addPRISMts} returns an object of class \code{list}. Slots are:
+#' \item{lakeinfo}{A data frame of lake information.}
+#' \item{lakedata}{A list of data frames containing the lake data. The PRISM data are appended here.}
+#' 
+#' @details Extracts the PRISM data using latitude-longitude coordinates provided by LAGOS
+#' 
+#' @author Jonathan Walter, \email{jaw3es@@virginia.edu}
+#' 
+#' @seealso \code{\link{addAVHRRannualts}}, \code{\link{makeIowaALMannualts}}
+#' 
+#' @examples
+#' #need to add some
+#' 
+#' @export
+
+addAVHRRannualts<-function(lakelist, avhrrdata, buffdist=5000, aggfun="mean"){
+  
+  library(raster)
+  library(rgdal)
+  library(sp)
+  
+  lakeinfo<-lakelist$lakeinfo
+  lakedata<-lakelist$lakedata
+  
+  if(length(buffdist)==1){buffdist<-rep(buffdist, nrow(lakelist$lakeinfo))}
+  if(length(buffdist)!=nrow(lakelist$lakeinfo)){
+    stop("length(buffdist) must be 1 or equal to the number of lakes")
+  }
+  
+  #make lake points 
+  lakepts<-SpatialPoints(coords=data.frame(x=lakeinfo$nhd_long,y=lakeinfo$nhd_lat),
+                            proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs"))
+  avhrrproj<-crs(avhrrdata)
+  lakepts.prj<-spTransform(lakepts, avhrrproj)
+  
+  
+  #loop through lakes and extract AVHRR time series
+  for(ii in 1:nrow(lakeinfo)){
[…]

### 2019-12-10 R Package/aqts/R/addWeatherts.R

@@ -1,0 +1,73 @@
+#' Add terrestrial AVHRR time series to limnological time series
+#' 
+#' \code{addAVHRRannualts} extracts terrestrial AVHRR time series and appends them to limnological time series produced by,
+#' e.g., \code{makeLAGOSannualts}.
+#' 
+#' @param lakelist a list containing \code{lakeinfo} and \code{lakedata}, as output from \code{makeLAGOSannualts}.
+#' @param avhrrdata a raster stack of annual AVHRR metrics
+#' @param buffdist the distance (in meters) of the radius around each lake to draw terrestrial productivity information from.
+#' @param aggfun a string indicating how to aggregate values from multiple satellite measurements within the buffer. Defaults to "mean",
+#' "median" is also available.
+#' 
+#' @return \code{addAVHRRannualts} returns an object of class \code{list}. Slots are:
+#' \item{lakeinfo}{A data frame of lake information.}
+#' \item{lakedata}{A list of data frames containing the lake data. The avhrr data are appended here.}
+#' 
+#' @details Nope.
+#' 
+#' @author Jonathan Walter, \email{jaw3es@@virginia.edu}
+#' 
+#' @seealso \code{\link{addAVHRRnnualts}}, \code{\link{makeIowaALMannualts}}
+#' 
+#' @examples
+#' #need to add some
+#' 
+#' @export
+
+addAVHRRannualts<-function(lakelist, avhrrdata, buffdist=5000, aggfun="mean"){
+  
+  library(raster)
+  library(rgdal)
+  library(sp)
+  
+  lakeinfo<-lakelist$lakeinfo
+  lakedata<-lakelist$lakedata
+  
+  if(length(buffdist)==1){buffdist<-rep(buffdist, nrow(lakelist$lakeinfo))}
+  if(length(buffdist)!=nrow(lakelist$lakeinfo)){
+    stop("length(buffdist) must be 1 or equal to the number of lakes")
+  }
+  
+  #make lake points 
+  lakepts<-SpatialPoints(coords=data.frame(x=lakeinfo$nhd_long,y=lakeinfo$nhd_lat),
+                            proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs"))
+  avhrrproj<-crs(avhrrdata)
[…]

### 2019-12-10 AnalysisCode/Q1_coherenceSpatialVariation/ms1_prep.Rmd

--- 2019-10-04 AnalysisCode/ms1_prep.Rmd
@@
 accndvi<-mask(accndvi,watermask,maskvalue=0) #mask out pixels that have too much water in them
-maxndvi<-mask(maxndvi,watermask,maskvalue=0)
+#maxndvi<-mask(maxndvi,watermask,maskvalue=0)
 
 analysislakes<-addAVHRRannualts(analysislakes, accndvi, dbuff)
-analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)
+#analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)
 
-save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873.RData")
+save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873_2.RData")
 

### 2019-12-11 AnalysisCode/Q1_CoherenceVariation/ms1_analyses_randforest.Rmd
q2 analyses updates

--- 2019-11-29 AnalysisCode/Q1_coherenceSpatialVariation/ms1_analyses_randforest.Rmd
@@
 #library(partykit)
-library(pdp)
+#library(pdp)
 library(party)
@@
 library(caret)
+library(png)
 

### 2019-12-11 AnalysisCode/Q2_ClimateCoherence/ms2_analyses.Rmd
q2 analyses updates

@@
 
+source("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/Q2_ClimateCoherence/bandtest_coh.R")
+
 ```
@@
 
-```{r load and format data, echo=TRUE, cache=FALSE}
+```{r load and format data, echo=TRUE, cache=TRUE}
 
@@
 }
-#add local weather --  write a function to do this.
 
+#add local weather
+ppt.files<-paste0("/Users/jonathanwalter/Documents/Research/DATA/PRISM_4km2_gridded/ppt/PRISM_ppt_stable_4kmM3_",
+                  rep(1989:2018,each=5),
+                  rep(c("05","06","07","08","09"),times=30),
+                  "_bil.bil")
+ppt<-stack(ppt.files)
+
+tavg.files<-c(paste0("/Users/jonathanwalter/Documents/Research/DATA/PRISM_4km2_gridded/tmean/PRISM_tmean_stable_4kmM2_",
+                  rep(1989:2016,each=5),
+                  rep(c("05","06","07","08","09"),times=28),
+                  "_bil.bil"),
+              paste0("/Users/jonathanwalter/Documents/Research/DATA/PRISM_4km2_gridded/tmean/PRISM_tmean_stable_4kmM3_",
+                  rep(2017:2018,each=5),
+                  rep(c("05","06","07","08","09"),times=2),
+                  "_bil.bil"))
+tavg<-stack(tavg.files)
+
+coherentlakes.st<-addPRISMts(coherentlakes.st, ppt, var="ppt")
+coherentlakes.st<-addPRISMts(coherentlakes.st, tavg, var="tmean")
+coherentlakes.lt<-addPRISMts(coherentlakes.lt, ppt, var="ppt")
+coherentlakes.lt<-addPRISMts(coherentlakes.lt, tavg, var="tmean")
 ```
@@
 ```{r climate coherence, echo=TRUE, cache=FALSE}
+lakeXclim.st<-data.frame(lagoslakeid=names(coherentlakes.st$lakedata),
+                         mei.coh=rep(NA, length(coherentlakes.st$lakedata)),
+                         mei.p=rep(NA, length(coherentlakes.st$lakedata)),
+                         mei.phi=rep(NA, length(coherentlakes.st$lakedata)),
+                         nao.coh=rep(NA, length(coherentlakes.st$lakedata)),
+                         nao.p=rep(NA, length(coherentlakes.st$lakedata)),
+                         nao.phi=rep(NA, length(coherentlakes.st$lakedata)),
+                         pdo.coh=rep(NA, length(coherentlakes.st$lakedata)),
+                         pdo.p=rep(NA, length(coherentlakes.st$lakedata)),
+                         pdo.phi=rep(NA, length(coherentlakes.st$lakedata)),
+                         ppt.coh=rep(NA, length(coherentlakes.st$lakedata)),
+                         ppt.p=rep(NA, length(coherentlakes.st$lakedata)),
+                         ppt.phi=rep(NA, length(coherentlakes.st$lakedata)),
+                         tavg.coh=rep(NA, length(coherentlakes.st$lakedata)),
+                         tavg.p=rep(NA, length(coherentlakes.st$lakedata)),
+                         tavg.phi=rep(NA, length(coherentlakes.st$lakedata)))
+landXclim.st<-lakeXclim.st
+
+lakeXclim.lt<-data.frame(lagoslakeid=names(coherentlakes.lt$lakedata),
+                         mei.coh=rep(NA, length(coherentlakes.lt$lakedata)),
+                         mei.p=rep(NA, length(coherentlakes.lt$lakedata)),
+                         mei.phi=rep(NA, length(coherentlakes.lt$lakedata)),
+                         nao.coh=rep(NA, length(coherentlakes.lt$lakedata)),
+                         nao.p=rep(NA, length(coherentlakes.lt$lakedata)),
+                         nao.phi=rep(NA, length(coherentlakes.lt$lakedata)),
+                         pdo.coh=rep(NA, length(coherentlakes.lt$lakedata)),
+                         pdo.p=rep(NA, length(coherentlakes.lt$lakedata)),
+                         pdo.phi=rep(NA, length(coherentlakes.lt$lakedata)),
+                         ppt.coh=rep(NA, length(coherentlakes.lt$lakedata)),
+                         ppt.p=rep(NA, length(coherentlakes.lt$lakedata)),
+                         ppt.phi=rep(NA, length(coherentlakes.lt$lakedata)),
+                         tavg.coh=rep(NA, length(coherentlakes.lt$lakedata)),
+                         tavg.p=rep(NA, length(coherentlakes.lt$lakedata)),
+                         tavg.phi=rep(NA, length(coherentlakes.lt$lakedata)))
+landXclim.lt<-lakeXclim.lt
+
+# lakes, short timescales
+NN=length(coherentlakes.st$lakedata)
+ts=c(2,4)
+for(ii in 1:NN){
+  vars<-rownames(coherentlakes.st$lakedata[[ii]])
+  yy<-as.numeric(colnames(coherentlakes.st$lakedata[[ii]]))
+  clnd<-cleandat(coherentlakes.st$lakedata[[ii]],yy,clev=5)$cdat
+
+  cohXmei<-coh(clnd[vars=="chla",], clnd[vars=="mei"], yy, norm="powall", sigmethod="fast")
+  cohXnao<-coh(clnd[vars=="chla",], clnd[vars=="nao"], yy, norm="powall", sigmethod="fast")
+  cohXpdo<-coh(clnd[vars=="chla",], clnd[vars=="pdo"], yy, norm="powall", sigmethod="fast")
+  cohXppt<-coh(clnd[vars=="chla",], clnd[vars=="ppt"], yy, norm="powall", sigmethod="fast")
+  cohXtavg<-coh(clnd[vars=="chla",], clnd[vars=="tavg"], yy, norm="powall", sigmethod="fast")
+
+  cohXmei<-bandtest.coh(cohXmei,ts)
+  cohXnao<-bandtest.coh(cohXnao,ts)
+  cohXpdo<-bandtest.coh(cohXpdo,ts)
+  cohXppt<-bandtest.coh(cohXppt,ts)
+  cohXtavg<-bandtest.coh(cohXtavg,ts)
+
+  lakeXclim.st$mei.coh[ii]<-cohXmei$bandp$mn_coh
+  lakeXclim.st$mei.p[ii]<-cohXmei$bandp$p_val
+  lakeXclim.st$mei.phi[ii]<-cohXmei$bandp$mn_phs
+  lakeXclim.st$nao.coh[ii]<-cohXnao$bandp$mn_coh
+  lakeXclim.st$nao.p[ii]<-cohXnao$bandp$p_val
+  lakeXclim.st$nao.phi[ii]<-cohXnao$bandp$mn_phs
+  lakeXclim.st$pdo.coh[ii]<-cohXpdo$bandp$mn_coh
+  lakeXclim.st$pdo.p[ii]<-cohXpdo$bandp$p_val
+  lakeXclim.st$pdo.phi[ii]<-cohXpdo$bandp$mn_phs
+  lakeXclim.st$ppt.coh[ii]<-cohXppt$bandp$mn_coh
+  lakeXclim.st$ppt.p[ii]<-cohXppt$bandp$p_val
+  lakeXclim.st$ppt.phi[ii]<-cohXppt$bandp$mn_phs
+  lakeXclim.st$tavg.coh[ii]<-cohXtavg$bandp$mn_coh
+  lakeXclim.st$tavg.p[ii]<-cohXtavg$bandp$p_val
+  lakeXclim.st$tavg.phi[ii]<-cohXtavg$bandp$mn_phs
+}
+
+#land, short timescales
+NN=length(coherentlakes.st$lakedata)
+ts=c(2,4)
+for(ii in 1:NN){
+  vars<-rownames(coherentlakes.st$lakedata[[ii]])
+  yy<-as.numeric(colnames(coherentlakes.st$lakedata[[ii]]))
+  clnd<-cleandat(coherentlakes.st$lakedata[[ii]],yy,clev=5)$cdat
+
+  cohXmei<-coh(clnd[vars=="ndvi",], clnd[vars=="mei"], yy, norm="powall", sigmethod="fast")
+  cohXnao<-coh(clnd[vars=="ndvi",], clnd[vars=="nao"], yy, norm="powall", sigmethod="fast")
+  cohXpdo<-coh(clnd[vars=="ndvi",], clnd[vars=="pdo"], yy, norm="powall", sigmethod="fast")
+  cohXppt<-coh(clnd[vars=="ndvi",], clnd[vars=="ppt"], yy, norm="powall", sigmethod="fast")
+  cohXtavg<-coh(clnd[vars=="ndvi",], clnd[vars=="tavg"], yy, norm="powall", sigmethod="fast")
+
+  cohXmei<-bandtest.coh(cohXmei,ts)
+  cohXnao<-bandtest.coh(cohXnao,ts)
+  cohXpdo<-bandtest.coh(cohXpdo,ts)
+  cohXppt<-bandtest.coh(cohXppt,ts)
+  cohXtavg<-bandtest.coh(cohXtavg,ts)
+
+  landXclim.st$mei.coh[ii]<-cohXmei$bandp$mn_coh
+  landXclim.st$mei.p[ii]<-cohXmei$bandp$p_val
+  landXclim.st$mei.phi[ii]<-cohXmei$bandp$mn_phs
+  landXclim.st$nao.coh[ii]<-cohXnao$bandp$mn_coh
+  landXclim.st$nao.p[ii]<-cohXnao$bandp$p_val
+  landXclim.st$nao.phi[ii]<-cohXnao$bandp$mn_phs
+  landXclim.st$pdo.coh[ii]<-cohXpdo$bandp$mn_coh
+  landXclim.st$pdo.p[ii]<-cohXpdo$bandp$p_val
+  landXclim.st$pdo.phi[ii]<-cohXpdo$bandp$mn_phs
+  landXclim.st$ppt.coh[ii]<-cohXppt$bandp$mn_coh
+  landXclim.st$ppt.p[ii]<-cohXppt$bandp$p_val
+  landXclim.st$ppt.phi[ii]<-cohXppt$bandp$mn_phs
+  landXclim.st$tavg.coh[ii]<-cohXtavg$bandp$mn_coh
+  landXclim.st$tavg.p[ii]<-cohXtavg$bandp$p_val
+  landXclim.st$tavg.phi[ii]<-cohXtavg$bandp$mn_phs
+}
+
+#lakes, long timescales
+NN=length(coherentlakes.lt$lakedata)
+ts=c(4,Inf)
+for(ii in 1:NN){
+  vars<-rownames(coherentlakes.lt$lakedata[[ii]])
+  yy<-as.numeric(colnames(coherentlakes.lt$lakedata[[ii]]))
+  clnd<-cleandat(coherentlakes.lt$lakedata[[ii]],yy,clev=5)$cdat
+
+  cohXmei<-coh(clnd[vars=="chla",], clnd[vars=="mei"], yy, norm="powall", sigmethod="fast")
+  cohXnao<-coh(clnd[vars=="chla",], clnd[vars=="nao"], yy, norm="powall", sigmethod="fast")
+  cohXpdo<-coh(clnd[vars=="chla",], clnd[vars=="pdo"], yy, norm="powall", sigmethod="fast")
+  cohXppt<-coh(clnd[vars=="chla",], clnd[vars=="ppt"], yy, norm="powall", sigmethod="fast")
+  cohXtavg<-coh(clnd[vars=="chla",], clnd[vars=="tavg"], yy, norm="powall", sigmethod="fast")
+
+  cohXmei<-bandtest.coh(cohXmei,ts)
+  cohXnao<-bandtest.coh(cohXnao,ts)
+  cohXpdo<-bandtest.coh(cohXpdo,ts)
+  cohXppt<-bandtest.coh(cohXppt,ts)
+  cohXtavg<-bandtest.coh(cohXtavg,ts)
+
+  lakeXclim.lt$mei.coh[ii]<-cohXmei$bandp$mn_coh
+  lakeXclim.lt$mei.p[ii]<-cohXmei$bandp$p_val
+  lakeXclim.lt$mei.phi[ii]<-cohXmei$bandp$mn_phs
+  lakeXclim.lt$nao.coh[ii]<-cohXnao$bandp$mn_coh
+  lakeXclim.lt$nao.p[ii]<-cohXnao$bandp$p_val
+  lakeXclim.lt$nao.phi[ii]<-cohXnao$bandp$mn_phs
+  lakeXclim.lt$pdo.coh[ii]<-cohXpdo$bandp$mn_coh
+  lakeXclim.lt$pdo.p[ii]<-cohXpdo$bandp$p_val
+  lakeXclim.lt$pdo.phi[ii]<-cohXpdo$bandp$mn_phs
+  lakeXclim.lt$ppt.coh[ii]<-cohXppt$bandp$mn_coh
+  lakeXclim.lt$ppt.p[ii]<-cohXppt$bandp$p_val
+  lakeXclim.lt$ppt.phi[ii]<-cohXppt$bandp$mn_phs
+  lakeXclim.lt$tavg.coh[ii]<-cohXtavg$bandp$mn_coh
+  lakeXclim.lt$tavg.p[ii]<-cohXtavg$bandp$p_val
+  lakeXclim.lt$tavg.phi[ii]<-cohXtavg$bandp$mn_phs
+}
+
+#land, long timescales
+NN=length(coherentlakes.lt$lakedata)
+ts=c(4,Inf)
+for(ii in 1:NN){
+  vars<-rownames(coherentlakes.lt$lakedata[[ii]])
+  yy<-as.numeric(colnames(coherentlakes.lt$lakedata[[ii]]))
+  clnd<-cleandat(coherentlakes.lt$lakedata[[ii]],yy,clev=5)$cdat
+
+  cohXmei<-coh(clnd[vars=="ndvi",], clnd[vars=="mei"], yy, norm="powall", sigmethod="fast")
+  cohXnao<-coh(clnd[vars=="ndvi",], clnd[vars=="nao"], yy, norm="powall", sigmethod="fast")
+  cohXpdo<-coh(clnd[vars=="ndvi",], clnd[vars=="pdo"], yy, norm="powall", sigmethod="fast")
+  cohXppt<-coh(clnd[vars=="ndvi",], clnd[vars=="ppt"], yy, norm="powall", sigmethod="fast")
+  cohXtavg<-coh(clnd[vars=="ndvi",], clnd[vars=="tavg"], yy, norm="powall", sigmethod="fast")
+
+  cohXmei<-bandtest.coh(cohXmei,ts)
+  cohXnao<-bandtest.coh(cohXnao,ts)
+  cohXpdo<-bandtest.coh(cohXpdo,ts)
+  cohXppt<-bandtest.coh(cohXppt,ts)
+  cohXtavg<-bandtest.coh(cohXtavg,ts)
+
+  landXclim.lt$mei.coh[ii]<-cohXmei$bandp$mn_coh
+  landXclim.lt$mei.p[ii]<-cohXmei$bandp$p_val
+  landXclim.lt$mei.phi[ii]<-cohXmei$bandp$mn_phs
+  landXclim.lt$nao.coh[ii]<-cohXnao$bandp$mn_coh
+  landXclim.lt$nao.p[ii]<-cohXnao$bandp$p_val
+  landXclim.lt$nao.phi[ii]<-cohXnao$bandp$mn_phs
+  landXclim.lt$pdo.coh[ii]<-cohXpdo$bandp$mn_coh
+  landXclim.lt$pdo.p[ii]<-cohXpdo$bandp$p_val
+  landXclim.lt$pdo.phi[ii]<-cohXpdo$bandp$mn_phs
+  landXclim.lt$ppt.coh[ii]<-cohXppt$bandp$mn_coh
+  landXclim.lt$ppt.p[ii]<-cohXppt$bandp$p_val
+  landXclim.lt$ppt.phi[ii]<-cohXppt$bandp$mn_phs
+  landXclim.lt$tavg.coh[ii]<-cohXtavg$bandp$mn_coh
+  landXclim.lt$tavg.p[ii]<-cohXtavg$bandp$p_val
+  landXclim.lt$tavg.phi[ii]<-cohXtavg$bandp$mn_phs
+}
+
+# test correlation between coherence of lakes and coherence of land
+cor.test(lakeXclim.st$mei.coh,landXclim.st$mei.coh)
+cor.test(lakeXclim.st$nao.coh,landXclim.st$nao.coh)
+cor.test(lakeXclim.st$pdo.coh,landXclim.st$pdo.coh)
+cor.test(lakeXclim.st$ppt.coh,landXclim.st$ppt.coh)
+cor.test(lakeXclim.st$tavg.coh,landXclim.st$tavg.coh)
+# no significant correlations at short timescales
+
+cor.test(lakeXclim.lt$mei.coh,landXclim.lt$mei.coh)
+cor.test(lakeXclim.lt$nao.coh,landXclim.lt$nao.coh)
+cor.test(lakeXclim.lt$pdo.coh,landXclim.lt$pdo.coh)
+cor.test(lakeXclim.lt$ppt.coh,landXclim.lt$ppt.coh)
+cor.test(lakeXclim.lt$tavg.coh,landXclim.lt$tavg.coh)
+# mostly significant correlations at long timescales
 
 ```
+Coherence with climate variables was essentially uncorrelated between lakes and the landscape at short timescales, albeit with a small (n=9) number of lakes.
+However, at long timescales coherence with climate variables tended to be significantly and positively correlated between lakes and the landscape.
 
@@
 ```{r wlms lake v landscape, echo=TRUE, cache=FALSE}
+
+## Short timescales
+
+#2851 - Walloon Lake
+yy<-as.numeric(colnames(coherentlakes.st$lakedata$`2851`))
+dat<-list(cleandat(coherentlakes.st$lakedata$`2851`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.st$lakedata$`2851`[2,],yy,clev=5)$cdat)
+wlm.lakeland.2851<-wlm(dat,yy,1,2,norm="powall")
+syncexpl(wlm.lakeland.2851)
 

### 2019-12-11 AnalysisCode/Q2_ClimateCoherence/bandtest_coh.R

@@ -1,0 +1,116 @@
+#' Aggregate significance across a timescale band
+#' 
+#' This is essentially a duplicate of 'bandtest' in package \code{'wsyn'} with minor functionality additions.
+#' 
+#' Computes the aggregate significance of coherence (\code{coh}) across a timescale band, 
+#' accounting for non-independence of timescales. Also gets the 
+#' average phase and average coherence across the band.
+#' 
+#' @param object An object of class \code{coh}, must have a non-\code{NA} 
+#' \code{signif} slot
+#' @param band A length-two numeric vector indicating a timescale band
+#' @param ... Passed from the generic to specific methods. Not currently used.
+#' 
+#' @return \code{bandtest.coh} returns an object of the same class as its first input but with a
+#' \code{bandp} slot added. Or if there was already a \code{bandp} slot, the output has a 
+#' \code{bandp} slot with an additional row. For a \code{coh} object, the \code{bandp} slot 
+#' is a data frame with four columns, the first two indicating the timescale band and the third 
+#' an associated p-value for the test of coherence over that band. The fourth column is the 
+#' average phase over the band.
+#' 
+#' @author Thomas Anderson, \email{anderstl@@gmail.com}, Jon Walter, \email{jaw3es@@virginia.edu}; Lawrence 
+#' Sheppard, \email{lwsheppard@@ku.edu}; Daniel Reuman, \email{reuman@@ku.edu}
+#' 
+#' @references 
+#' Sheppard, L.W., et al. (2016) Changes in large-scale climate alter spatial synchrony of aphid 
+#' pests. Nature Climate Change. DOI: 10.1038/nclimate2881
+#' 
+#' @seealso \code{\link{coh}},
+#' 
+#' @examples 
+#' #Example for a coh object
+#' times<-(-3:100)
+#' ts1<-sin(2*pi*times/10)
+#' ts2<-5*sin(2*pi*times/3)
+#' artsig_x<-matrix(NA,11,length(times)) #the driver
+#' for (counter in 1:11)
+#' {
+#'   artsig_x[counter,]=ts1+ts2+rnorm(length(times),mean=0,sd=1.5)
+#' }
+#' times<-0:100
[…]

### 2019-12-11 R Package/aqts/R/addPRISMts.R

@@ -5,6 +5,7 @@
 #' 
 #' @param lakelist a list containing \code{lakeinfo} and \code{lakedata}, as output from \code{makeLAGOSannualts}.
 #' @param prismdata a raster stack of annual AVHRR metrics
+#' @param var what variable is being handled? currently, ppt and tmean are accepted.
 #' 
 #' @return \code{addPRISMts} returns an object of class \code{list}. Slots are:
 #' \item{lakeinfo}{A data frame of lake information.}
@@ -21,47 +22,48 @@
 #' 
 #' @export
 
-addAVHRRannualts<-function(lakelist, avhrrdata, buffdist=5000, aggfun="mean"){
+addPRISMts<-function(lakelist, prismdata, var){
   
   library(raster)
   library(rgdal)
   library(sp)
   
+  if(!var %in% c("ppt","tmean")){stop("var must be ppt or tmean")}
+  
   lakeinfo<-lakelist$lakeinfo
   lakedata<-lakelist$lakedata
-  
-  if(length(buffdist)==1){buffdist<-rep(buffdist, nrow(lakelist$lakeinfo))}
-  if(length(buffdist)!=nrow(lakelist$lakeinfo)){
-    stop("length(buffdist) must be 1 or equal to the number of lakes")
-  }
   
   #make lake points 
   lakepts<-SpatialPoints(coords=data.frame(x=lakeinfo$nhd_long,y=lakeinfo$nhd_lat),
                             proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs"))
-  avhrrproj<-crs(avhrrdata)
-  lakepts.prj<-spTransform(lakepts, avhrrproj)
+  prismproj<-crs(prismdata)
+  lakepts.prj<-spTransform(lakepts, prismproj)
   
   
   #loop through lakes and extract AVHRR time series
   for(ii in 1:nrow(lakeinfo)){
-    lakebuffer.ii<-buffer(lakepts.prj[ii,], width=buffdist[ii], dissolve=FALSE)
-    #plot(lakebuffer.ii)
-    avhrrstack.ii<-mask(avhrrdata,lakebuffer.ii)
+    lake.ii<-lakepts.prj[ii,]
+    lakeweather<-prismdata[lake.ii]
+    if(var=="ppt"){
+      df<-data.frame(year=substr(colnames(lakeweather),24,27),
[…]

### 2019-12-11 R Package/aqts/R/addWeatherts.R

@@ -1,73 +1,0 @@
-#' Add terrestrial AVHRR time series to limnological time series
-#' 
-#' \code{addAVHRRannualts} extracts terrestrial AVHRR time series and appends them to limnological time series produced by,
-#' e.g., \code{makeLAGOSannualts}.
-#' 
-#' @param lakelist a list containing \code{lakeinfo} and \code{lakedata}, as output from \code{makeLAGOSannualts}.
-#' @param avhrrdata a raster stack of annual AVHRR metrics
-#' @param buffdist the distance (in meters) of the radius around each lake to draw terrestrial productivity information from.
-#' @param aggfun a string indicating how to aggregate values from multiple satellite measurements within the buffer. Defaults to "mean",
-#' "median" is also available.
-#' 
-#' @return \code{addAVHRRannualts} returns an object of class \code{list}. Slots are:
-#' \item{lakeinfo}{A data frame of lake information.}
-#' \item{lakedata}{A list of data frames containing the lake data. The avhrr data are appended here.}
-#' 
-#' @details Nope.
-#' 
-#' @author Jonathan Walter, \email{jaw3es@@virginia.edu}
-#' 
-#' @seealso \code{\link{addAVHRRnnualts}}, \code{\link{makeIowaALMannualts}}
-#' 
-#' @examples
-#' #need to add some
-#' 
-#' @export
-
-addAVHRRannualts<-function(lakelist, avhrrdata, buffdist=5000, aggfun="mean"){
-  
-  library(raster)
-  library(rgdal)
-  library(sp)
-  
-  lakeinfo<-lakelist$lakeinfo
-  lakedata<-lakelist$lakedata
-  
-  if(length(buffdist)==1){buffdist<-rep(buffdist, nrow(lakelist$lakeinfo))}
-  if(length(buffdist)!=nrow(lakelist$lakeinfo)){
-    stop("length(buffdist) must be 1 or equal to the number of lakes")
-  }
-  
-  #make lake points 
-  lakepts<-SpatialPoints(coords=data.frame(x=lakeinfo$nhd_long,y=lakeinfo$nhd_lat),
-                            proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs"))
-  avhrrproj<-crs(avhrrdata)
[…]

### 2019-12-11 R Package/aqts/build.R

@@ -4,10 +4,9 @@ library(devtools)
 
 setwd("~/GitHub/AquaTerrSynch/R package")
 
-build("aqts")   # need a folder named 'Reumannplatz', in which a file named DESCRIPTION and a sub-folder named 'R'. This will creat a zip file
+build("aqts")   # need a folder named 'aqts, in which a file named DESCRIPTION and a sub-folder named 'R'. This will creat a zip file
 document("aqts") # this will create a file 'NAMESPACE' and a folder 'man'
 check("aqts")
 install("aqts")
-#install_github("reumandc/reumannplatz",force=T)
 library("aqts")
 

### 2019-12-18 AnalysisCode/Q2_ClimateCoherence/ms2_analyses.Rmd
q2 analysis updates

@@
 coherentlakes.lt<-addPRISMts(coherentlakes.lt, tavg, var="tmean")
+```
+Make some maps to see where we are
+```{r mapping, echo=T, cache=T}
+states<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/statesp020_nolakes.shp")
+getstates<-c("Minnesota", "Iowa", "Wisconsin", "Illinois", "Missouri", "Michigan", "Indiana", "Ohio", "Pennsylvania", "New York", "New Jersey", "Connecticut", "New Hampshire", "Rhode Island", "Massachusetts", "Vermont", "Maine")
+lagosstates<-states[states@data$STATE %in% getstates,]
+
+plot(lagosstates, main="Coherent lakes, short timescales")
+points(coherentlakes.st$lakeinfo$nhd_long, coherentlakes.st$lakeinfo$nhd_lat, pch=16, col="blue")
+
+plot(lagosstates, main="Coherent lakes, long timescales")
+points(coherentlakes.lt$lakeinfo$nhd_long, coherentlakes.lt$lakeinfo$nhd_lat, pch=16, col="blue")
+
 ```
@@
 However, at long timescales coherence with climate variables tended to be significantly and positively correlated between lakes and the landscape.
+```{r biplots, echo=TRUE, cahce=FALSE}
+par(mfrow=c(2,3),mar=c(3.1,3.1,1,1),mgp=c(1.7,0.5,0))
+plot(landXclim.st$mei.coh, lakeXclim.st$mei.coh, xlim=c(0,1), ylim=c(0,1), xlab="land", ylab="lake",main="mei")
+abline(a=0,b=1)
+plot(landXclim.st$nao.coh, lakeXclim.st$nao.coh, xlim=c(0,1), ylim=c(0,1), xlab="land", ylab="lake",main="nao")
+abline(a=0,b=1)
+plot(landXclim.st$pdo.coh, lakeXclim.st$pdo.coh, xlim=c(0,1), ylim=c(0,1), xlab="land", ylab="lake",main="pdo")
+abline(a=0,b=1)
+plot(landXclim.st$ppt.coh, lakeXclim.st$ppt.coh, xlim=c(0,1), ylim=c(0,1), xlab="land", ylab="lake",main="ppt")
+abline(a=0,b=1)
+plot(landXclim.st$tavg.coh, lakeXclim.st$tavg.coh, xlim=c(0,1), ylim=c(0,1), xlab="land", ylab="lake",main="tavg")
+abline(a=0,b=1)
+
+par(mfrow=c(2,3),mar=c(3.1,3.1,1,1),mgp=c(1.7,0.5,0))
+plot(landXclim.lt$mei.coh, lakeXclim.lt$mei.coh, xlim=c(0,1), ylim=c(0,1), xlab="land", ylab="lake",main="mei")
+abline(a=0,b=1)
+plot(landXclim.lt$nao.coh, lakeXclim.lt$nao.coh, xlim=c(0,1), ylim=c(0,1), xlab="land", ylab="lake",main="nao")
+abline(a=0,b=1)
+plot(landXclim.lt$pdo.coh, lakeXclim.lt$pdo.coh, xlim=c(0,1), ylim=c(0,1), xlab="land", ylab="lake",main="pdo")
+abline(a=0,b=1)
+plot(landXclim.lt$ppt.coh, lakeXclim.lt$ppt.coh, xlim=c(0,1), ylim=c(0,1), xlab="land", ylab="lake",main="ppt")
+abline(a=0,b=1)
+plot(landXclim.lt$tavg.coh, lakeXclim.lt$tavg.coh, xlim=c(0,1), ylim=c(0,1), xlab="land", ylab="lake",main="tavg")
+abline(a=0,b=1)
+
+```
 
 Second, find out how much variability in lakes is explained by coherence with the landscape
-```{r wlms lake v landscape, echo=TRUE, cache=FALSE}
+```{r wlms lake v landscape, echo=TRUE, cache=TRUE}
 
-## Short timescales
+## Short timescales------------------------------------------------------------
+varexpl.land_v_clim.st<-data.frame(lagoslakeid=names(coherentlakes.st$lakedata),
+                                   varexpl.land=rep(NA, length(names(coherentlakes.st$lakedata))),
+                                   varexpl.clim=rep(NA, length(names(coherentlakes.st$lakedata))))
 
@@
 wlm.lakeland.2851<-wlm(dat,yy,1,2,norm="powall")
-syncexpl(wlm.lakeland.2851)
+varexpl.land_v_clim.st$varexpl.land[1]<-mean(syncexpl(wlm.lakeland.2851)$syncexpl[syncexpl(wlm.lakeland.2851)$timescales < 4])
+
+#3370 - White Lake
+yy<-as.numeric(colnames(coherentlakes.st$lakedata$`3370`))
+dat<-list(cleandat(coherentlakes.st$lakedata$`3370`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.st$lakedata$`3370`[2,],yy,clev=5)$cdat)
+wlm.lakeland.3370<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.st$varexpl.land[2]<-mean(syncexpl(wlm.lakeland.3370)$syncexpl[syncexpl(wlm.lakeland.3370)$timescales < 4])
+
+#6075 - Fellows Lake
+yy<-as.numeric(colnames(coherentlakes.st$lakedata$`6075`))
+dat<-list(cleandat(coherentlakes.st$lakedata$`6075`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.st$lakedata$`6075`[2,],yy,clev=5)$cdat)
+wlm.lakeland.6075<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.st$varexpl.land[3]<-mean(syncexpl(wlm.lakeland.6075)$syncexpl[syncexpl(wlm.lakeland.6075)$timescales < 4])
+
+#6547 - Lake Moraine
+yy<-as.numeric(colnames(coherentlakes.st$lakedata$`6547`))
+dat<-list(cleandat(coherentlakes.st$lakedata$`6547`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.st$lakedata$`6547`[2,],yy,clev=5)$cdat)
+wlm.lakeland.6547<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.st$varexpl.land[4]<-mean(syncexpl(wlm.lakeland.6547)$syncexpl[syncexpl(wlm.lakeland.6547)$timescales < 4])
+
+#7523 - Annabessacook Lake
+yy<-as.numeric(colnames(coherentlakes.st$lakedata$`7523`))
+dat<-list(cleandat(coherentlakes.st$lakedata$`7523`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.st$lakedata$`7523`[2,],yy,clev=5)$cdat)
+wlm.lakeland.7523<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.st$varexpl.land[5]<-mean(syncexpl(wlm.lakeland.7523)$syncexpl[syncexpl(wlm.lakeland.7523)$timescales < 4])
+
+#28836 - Higginsville Old City Lake
+yy<-as.numeric(colnames(coherentlakes.st$lakedata$`28836`))
+dat<-list(cleandat(coherentlakes.st$lakedata$`28836`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.st$lakedata$`28836`[2,],yy,clev=5)$cdat)
+wlm.lakeland.28836<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.st$varexpl.land[6]<-mean(syncexpl(wlm.lakeland.28836)$syncexpl[syncexpl(wlm.lakeland.28836)$timescales < 4])
+
+#72641 - Lake Wallenpaupack
+yy<-as.numeric(colnames(coherentlakes.st$lakedata$`72641`))
+dat<-list(cleandat(coherentlakes.st$lakedata$`72641`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.st$lakedata$`72641`[2,],yy,clev=5)$cdat)
+wlm.lakeland.72641<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.st$varexpl.land[7]<-mean(syncexpl(wlm.lakeland.72641)$syncexpl[syncexpl(wlm.lakeland.72641)$timescales < 4])
+
+#133500 - Kraut run lake
+yy<-as.numeric(colnames(coherentlakes.st$lakedata$`133500`))
+dat<-list(cleandat(coherentlakes.st$lakedata$`133500`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.st$lakedata$`133500`[2,],yy,clev=5)$cdat)
+wlm.lakeland.133500<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.st$varexpl.land[8]<-mean(syncexpl(wlm.lakeland.133500)$syncexpl[syncexpl(wlm.lakeland.133500)$timescales < 4])
+
+#4909 - Annabelle lake
+yy<-as.numeric(colnames(coherentlakes.st$lakedata$`4909`))
+dat<-list(cleandat(coherentlakes.st$lakedata$`4909`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.st$lakedata$`4909`[2,],yy,clev=5)$cdat)
+wlm.lakeland.4909<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.st$varexpl.land[9]<-mean(syncexpl(wlm.lakeland.4909)$syncexpl[syncexpl(wlm.lakeland.4909)$timescales < 4])
+
+## Long timescales ------------------------------------------------------------
+varexpl.land_v_clim.lt<-data.frame(lagoslakeid=names(coherentlakes.lt$lakedata),
+                                   varexpl.land=rep(NA, length(names(coherentlakes.lt$lakedata))),
+                                   varexpl.clim=rep(NA, length(names(coherentlakes.lt$lakedata))))
+# 3370 - White Lake
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`3370`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`3370`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`3370`[2,],yy,clev=5)$cdat)
+wlm.lakeland.3370<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[1]<-mean(syncexpl(wlm.lakeland.3370)$syncexpl[syncexpl(wlm.lakeland.3370)$timescales > 4])
+
+# 3834 - Hasbrook Lake
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`3834`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`3834`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`3834`[2,],yy,clev=5)$cdat)
+wlm.lakeland.3834<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[2]<-mean(syncexpl(wlm.lakeland.3834)$syncexpl[syncexpl(wlm.lakeland.3834)$timescales > 4])
+
+# 4243 - unnamed
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`4243`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`4243`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`4243`[2,],yy,clev=5)$cdat)
+wlm.lakeland.4243<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[3]<-mean(syncexpl(wlm.lakeland.4243)$syncexpl[syncexpl(wlm.lakeland.4243)$timescales > 4])
+
+# 4416 - Green Lake
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`4416`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`4416`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`4416`[2,],yy,clev=5)$cdat)
+wlm.lakeland.4416<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[4]<-mean(syncexpl(wlm.lakeland.4416)$syncexpl[syncexpl(wlm.lakeland.4416)$timescales > 4])
+
+# 4434 - Kangaroo Lake
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`4434`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`4434`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`4434`[2,],yy,clev=5)$cdat)
+wlm.lakeland.4434<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[5]<-mean(syncexpl(wlm.lakeland.4434)$syncexpl[syncexpl(wlm.lakeland.4434)$timescales > 4])
+
+# 5895 - Lake Sunapee
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`5895`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`5895`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`5895`[2,],yy,clev=5)$cdat)
+wlm.lakeland.5895<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[6]<-mean(syncexpl(wlm.lakeland.5895)$syncexpl[syncexpl(wlm.lakeland.5895)$timescales > 4])
+
+# 6199 - unnamed
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`6199`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`6199`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`6199`[2,],yy,clev=5)$cdat)
+wlm.lakeland.6199<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[7]<-mean(syncexpl(wlm.lakeland.6199)$syncexpl[syncexpl(wlm.lakeland.6199)$timescales > 4])
+
+# 7523 - Annabessacook Lake
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`7523`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`7523`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`7523`[2,],yy,clev=5)$cdat)
+wlm.lakeland.7523<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[8]<-mean(syncexpl(wlm.lakeland.7523)$syncexpl[syncexpl(wlm.lakeland.7523)$timescales > 4])
+
+# 8369 - unnamed
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`8369`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`8369`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`8369`[2,],yy,clev=5)$cdat)
+wlm.lakeland.8369<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[9]<-mean(syncexpl(wlm.lakeland.8369)$syncexpl[syncexpl(wlm.lakeland.8369)$timescales > 4])
+
+# 39489 - Ashokan Reservoir West Basin
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`39489`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`39489`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`39489`[2,],yy,clev=5)$cdat)
+wlm.lakeland.39489<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[10]<-mean(syncexpl(wlm.lakeland.39489)$syncexpl[syncexpl(wlm.lakeland.39489)$timescales > 4])
+
+# 115040 - Ashokan Reservoir East Basin
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`115040`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`115040`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`115040`[2,],yy,clev=5)$cdat)
+wlm.lakeland.115040<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[11]<-mean(syncexpl(wlm.lakeland.115040)$syncexpl[syncexpl(wlm.lakeland.115040)$timescales > 4])
+
+# 133500 - Kraut Run Lake
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`133500`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`133500`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`133500`[2,],yy,clev=5)$cdat)
+wlm.lakeland.133500<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[12]<-mean(syncexpl(wlm.lakeland.133500)$syncexpl[syncexpl(wlm.lakeland.133500)$timescales > 4])
+
+# 14815 - unnamed
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`14815`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`14815`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`14815`[2,],yy,clev=5)$cdat)
+wlm.lakeland.14815<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[13]<-mean(syncexpl(wlm.lakeland.14815)$syncexpl[syncexpl(wlm.lakeland.14815)$timescales > 4])
+
+# 102115 - Wilkinson Lake
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`102115`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`102115`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`102115`[2,],yy,clev=5)$cdat)
+wlm.lakeland.102115<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[14]<-mean(syncexpl(wlm.lakeland.102115)$syncexpl[syncexpl(wlm.lakeland.102115)$timescales > 4])
+
+# 5463 - Pearl Lake
+yy<-as.numeric(colnames(coherentlakes.lt$lakedata$`5463`))
+dat<-list(cleandat(coherentlakes.lt$lakedata$`5463`[1,],yy,clev=5)$cdat,
+          cleandat(coherentlakes.lt$lakedata$`5463`[2,],yy,clev=5)$cdat)
+wlm.lakeland.5463<-wlm(dat,yy,1,2,norm="powall")
+varexpl.land_v_clim.lt$varexpl.land[15]<-mean(syncexpl(wlm.lakeland.5463)$syncexpl[syncexpl(wlm.lakeland.5463)$timescales > 4])
 
@@
 
+is.coh_land.lt<-landXclim.lt[colnames(landXclim.lt) %in% 
+                               c("lagoslakeid","mei.p","nao.p","pdo.p","ppt.p","tavg.p")]
+is.coh_land.lt$mei.p<-ifelse(is.coh_land.lt$mei.p<0.1,1,0)
+is.coh_land.lt$nao.p<-ifelse(is.coh_land.lt$nao.p<0.1,1,0)
+is.coh_land.lt$pdo.p<-ifelse(is.coh_land.lt$pdo.p<0.1,1,0)
+is.coh_land.lt$ppt.p<-ifelse(is.coh_land.lt$ppt.p<0.1,1,0)
+is.coh_land.lt$tavg.p<-ifelse(is.coh_land.lt$tavg.p<0.1,1,0)
+
 ```

### 2020-01-07 AnalysisCode/Q1_CoherenceVariation/ms1_analyses_rf_to_gam.Rmd
update figure for manuscript

--- 2019-12-10 AnalysisCode/ms1_analyses_rf_to_gam.Rmd
@@
 
-source("~/GitHub/AquaTerrSynch/AnalysisCode/bandtest_coh.R")
+source("~/GitHub/AquaTerrSynch/AnalysisCode/Q1_CoherenceVariation/bandtest_coh.R")
 
@@
 
+print(cbind(coh.chlaXaccndvi$lagoslakeid, coh.chlaXaccndvi$accndvip.ts1)[coh.chlaXaccndvi$accndvip.ts1>0.9,])
+print(cbind(coh.chlaXaccndvi$lagoslakeid, coh.chlaXaccndvi$accndvip.ts2)[coh.chlaXaccndvi$accndvip.ts2>0.9,])
+
 cor(coh.chlaXaccndvi$accndvicoh.ts1,coh.chlaXaccndvi$accndvicoh.ts2)
@@
 #plotting
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_distributions_20191031.tif", units="in",
-     res=300, width=6.5, height=6.5)
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_distributions_20191031.tif", units="in",
+     res=300, width=6.5, height=5)
+layout(matrix(1:4,2,2,byrow=T),heights=c(0.4,0.4,0.6,0.6))
 
-par(mar=c(3,3,2,1),mgp=c(1.7,0.5,0),mfrow=c(2,2),cex.main=0.9)
+par(mar=c(3,3,2,1),mgp=c(1.7,0.5,0),cex.main=0.9)
 
@@
 rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian", col="lightgrey",
-     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Short timescale phases",
+     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Short timescale phase",
        at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
@@
 rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian", col="lightgrey",
-     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Long timescale phases",
+     breaks=c(0,pi/4,pi/2,3*pi/4,pi,5*pi/4,3*pi/2,7*pi/4,2*pi), main="Long timescale phase",
      at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
@@
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_map.tif",units="in",
-     res=300, width=3.25, height=2.75)
+cohid<-3370
+incohid<-4386
+
+bgcol<-rep("grey",length(lakedata))
+bgcol[names(lakedata)=="3370"]<-"red"
+bgcol[names(lakedata)=="4386"]<-"blue"
+
+laymat<-matrix(c(1,1,2,3),2,2)
+
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_map_plus.tif",units="in",
+     res=300, width=6.5, height=2.75)
+
+layout(laymat, width=c(0.6,0.4,0.4))
+
 par(mar=rep(0,4))
 plot(lagosstates, main="",bty="o")
-points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=21, cex=0.45, col="black",bg="grey")
-legend("bottomright",pch=c(0,21),col="black",pt.bg="grey",legend=c("States in LAGOS-NE","Selected lakes"),inset=c(0.025,0.01),bty="n")
+points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=21, cex=0.55, col="black",bg=bgcol)
+legend("bottomright",pch=c(0,21,21,21),col="black",pt.bg=c("grey","grey","red","blue"),
+       legend=c("States in LAGOS-NE","Selected lakes","Coherent lake","Non-coherent lake"),inset=c(0.025,0.01),bty="n")
+text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.06*diff(par("usr")[3:4]),"a)")
+
+par(mar=c(2.6,1.1,1.1,0.9), mgp=c(1.4,0.4,0), tcl=-0.3, cex.axis=0.8, cex.lab=0.8)
+plot(as.numeric(colnames(lakedata[[paste0(cohid)]])),scale(lakedata[[paste0(cohid)]][1,]),type="l", col="blue", ylim=c(-3,3.5),
+     ylab="",xlab="Year",yaxt="n")
+lines(as.numeric(colnames(lakedata[[paste0(cohid)]])),scale(lakedata[[paste0(cohid)]][2,]), col="green")
+mtext("Coherent lake and landscape", cex=0.8)
+legend("topright", lty=1, col=c("blue","green"), legend=c("lake","land"), bty="n", cex=0.8, horiz=T)
+text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.1*diff(par("usr")[3:4]),"b)")
+
+plot(as.numeric(colnames(lakedata[[paste0(incohid)]])),scale(lakedata[[paste0(incohid)]][1,]),type="l", col="blue", ylim=c(-2,3.3),
+     ylab="",xlab="Year", yaxt="n")
+lines(as.numeric(colnames(lakedata[[paste0(incohid)]])),scale(lakedata[[paste0(incohid)]][2,]), col="green")
+mtext("Non-coherent lake and landscape", cex=0.8)
+text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.1*diff(par("usr")[3:4]),"c)")
+
 dev.off()
@@
 #huc2 and huc4 watershed codes
-huc_codes<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
+huc_codes<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/Q1_CoherenceVariation/match_huc_codes.csv", colClasses = 'character')
 
@@
 ## try out landscape orientation
+# 
+# bight=5.5
+# bigwd=9
+# 
+# lagosstates_prj<-spTransform(lagosstates, proj4string(huc8_bdys))
+# 
+# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png", units="in",
+#      res=300, width=bigwd/5, height=bight/4)
+# par(mar=c(0,0,1,0))
+# plot(huc_bdys_cohst,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohst$coeff)],xlim=c(-91837,2260000),
+#      ylim=c(1454000,3012981),lwd=0.5)
+# lines(lagosstates_prj,lwd=0.5)
+# par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
+# image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
+# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohst$coeff), max(huc_bdys_cohst$coeff), length.out=5),2), cex.axis=0.7)
+# dev.off()
+# 
+# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png", units="in",
+#      res=300, width=bigwd/5, height=bight/4)
+# par(mar=c(0,0,1,0))
+# plot(huc_bdys_cohlt,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohlt$coeff)],xlim=c(-91837,2260000),
+#      ylim=c(1454000,3012981),lwd=0.5)
+# lines(lagosstates_prj,lwd=0.5)
+# par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
+# image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
+# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohlt$coeff), max(huc_bdys_cohlt$coeff), length.out=5),2), cex.axis=0.7)
+# dev.off()
+# 
+# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png", units="in",
+#      res=300, width=bigwd/5, height=bight/4)
+# par(mar=c(0,0,1,0))
+# plot(huc_bdys_sinphilt,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys_sinphilt$coeff)],xlim=c(-91837,2260000),
+#      ylim=c(1454000,3012981),lwd=0.5)
+# lines(lagosstates_prj,lwd=0.5)
+# par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
+# image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
+# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_sinphilt$coeff), max(huc_bdys_sinphilt$coeff), length.out=5),2), cex.axis=0.7)
+# dev.off()
+# 
+# 
+# panel5b<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png")
+# panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png")
+# panel5n<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png")
+# 
+# mar1<-c(3,1.5,0.5,0.2)
+# fudge=1/34
+# 
+# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_landscape.tif",units="in",res=300,width=bigwd, height=bight)
+# 
+# par(mfrow=c(4,5),mgp=c(1.5,0.5,0), oma=c(0,2.5,0,0.5),mar=mar1,tcl=-0.3)
+# 
+# plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence")
+# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
+# rasterImage(image=panel5b,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+# plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="")
+# plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="")
+# plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% herbaceous wetld.",ylab="")
+# 
+# plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetlands shoreline",ylab="short phase")
+# plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
+# plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
+# plot.new()
+# plot.new()
+# 
+# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
+# rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+# plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-1,1))
+# plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="",ylim=c(-1,1))
+# plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="annual precipitation",ylab="")
+# plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetld. contrib. area",ylab="",ylim=c(-1,1))
+# 
+# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-4 sub-region",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
+# rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+# plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% pasture",ylab="")
+# plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% developed-open space",ylab="")
+# 
+# mtext("Partial residuals",2,outer=T,line=1.2,cex=0.8)
+# mtext(expression(paste("long sin(",phi,")",sep="")),2,at=1/8+fudge,outer=T,line=0,cex=0.7)
+# mtext("long coherence",2,at=1/8+1/4+fudge,outer=T,line=0,cex=0.7)
+# mtext(expression(paste("short cos(",phi,")",sep="")),2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)
+# mtext("short coherence",2,at=1/8+3/4+fudge,outer=T,line=0,cex=0.7)
+# 
+# dev.off()
 
-bight=5.5
-bigwd=9
+## try out portrait orientation by column
+
+bight=8
+bigwd=6.5
 
@@
 
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png", units="in",
-     res=300, width=bigwd/5, height=bight/4)
+png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_bycol.png", units="in",
+     res=300, width=bigwd/4, height=bight/5)
 par(mar=c(0,0,1,0))
@@
 
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png", units="in",
-     res=300, width=bigwd/5, height=bight/4)
+png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_bycol.png", units="in",
+     res=300, width=bigwd/4, height=bight/5)
 par(mar=c(0,0,1,0))
@@
 
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png", units="in",
-     res=300, width=bigwd/5, height=bight/4)
+png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_bycol.png", units="in",
+     res=300, width=bigwd/4, height=bight/5)
 par(mar=c(0,0,1,0))
@@
 
-panel5b<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png")
-panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png")
-panel5n<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png")
+panel5b<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_bycol.png")
+panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_bycol.png")
+panel5n<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_bycol.png")
 
-mar1<-c(3,1.5,0.5,0.2)
-fudge=1/34
+mar1<-c(3,1.5,0.3,0.2)
+fudge=1/60
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_landscape.tif",units="in",res=300,width=bigwd, height=bight)
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_bycolumn.tif",units="in",res=300,width=bigwd, height=bight)
 
-par(mfrow=c(4,5),mgp=c(1.5,0.5,0), oma=c(0,2.5,0,0.5),mar=mar1,tcl=-0.3)
+par(mfcol=c(5,4),mgp=c(1.5,0.5,0), oma=c(0,1.5,1.5,0.5),mar=mar1,tcl=-0.3)
 
 plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"a)")
 plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
 rasterImage(image=panel5b,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"b)")
 plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"c)")
 plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"d)")
 plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% herbaceous wetld.",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"e)")
 
-plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetlands shoreline",ylab="short phase")
+plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetld. shoreline",ylab="short phase")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"f)")
 plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"g)")
 plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"h)")
 plot.new()
@@
 rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"i)")
 plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-1,1))
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"j)")
 plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="",ylim=c(-1,1))
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"k)")
 plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="annual precipitation",ylab="")
-plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetld. contrib. area",ylab="",ylim=c(-1,1))
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"l)")
+plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetld. contrib. area",ylab="",ylim=c(-0.5,1.5))
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"m)")
 
@@
 rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"n)")
 plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% pasture",ylab="")
-plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% developed-open space",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"o)")
+plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% devel.-open space",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"p)")
 
-mtext("Partial residuals",2,outer=T,line=1.2,cex=0.8)
-mtext(expression(paste("long sin(",phi,")",sep="")),2,at=1/8+fudge,outer=T,line=0,cex=0.7)
-mtext("long coherence",2,at=1/8+1/4+fudge,outer=T,line=0,cex=0.7)
-mtext(expression(paste("short cos(",phi,")",sep="")),2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)
-mtext("short coherence",2,at=1/8+3/4+fudge,outer=T,line=0,cex=0.7)
+mtext("Partial residuals",2,outer=T,line=0.1,cex=1)
+mtext("short coherence",3,at=1/8+fudge,outer=T,line=0,cex=0.8)
+mtext(expression(paste("short cos(",phi,")",sep="")),3,at=1/8+1/4+fudge,outer=T,line=-0.2,cex=0.8)
+mtext("long coherence",3,at=1/8+2/4+fudge,outer=T,line=0,cex=0.8)
+mtext(expression(paste("long sin(",phi,")",sep="")),3,at=1/8+3/4+fudge,outer=T,line=-0.2,cex=0.8)
 

### 2020-07-01 AnalysisCode/Q1_CoherenceVariation/ms1_analyses_rf_to_gam_IWSnotHU12.Rmd
revisions post review

--- 2019-12-10 AnalysisCode/ms1_analyses_rf_to_gam.Rmd
@@
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_map.tif",units="in",
-     res=300, width=3.25, height=2.75)
+cohid<-3370
+incohid<-4386
+
+bgcol<-rep("grey",length(lakedata))
+bgcol[names(lakedata)=="3370"]<-"red"
+bgcol[names(lakedata)=="4386"]<-"cyan3"
+
+laymat<-matrix(c(1,1,2,3),2,2)
+
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_map_plus.tif",units="in",
+     res=300, width=6.5, height=2.75)
+
+layout(laymat, width=c(0.6,0.4,0.4))
+
 par(mar=rep(0,4))
 plot(lagosstates, main="",bty="o")
-points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=21, cex=0.45, col="black",bg="grey")
-legend("bottomright",pch=c(0,21),col="black",pt.bg="grey",legend=c("States in LAGOS-NE","Selected lakes"),inset=c(0.025,0.01),bty="n")
+points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=21, cex=0.7, col="black",bg=bgcol)
+legend("bottomright",pch=c(0,21,21,21),col="black",pt.bg=c("grey","grey","red","cyan3"),
+       legend=c("States in LAGOS-NE","Selected lakes","Coherent lake","Non-coherent lake"),inset=c(0.025,0.01),bty="n")
+text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.06*diff(par("usr")[3:4]),"a)")
+
+par(mar=c(2.6,1.1,1.1,0.9), mgp=c(1.4,0.4,0), tcl=-0.3, cex.axis=0.8, cex.lab=0.8)
+plot(as.numeric(colnames(lakedata[[paste0(cohid)]])),scale(lakedata[[paste0(cohid)]][1,]),type="l", col="blue", ylim=c(-3,3.5),
+     ylab="",xlab="Year",yaxt="n")
+lines(as.numeric(colnames(lakedata[[paste0(cohid)]])),scale(lakedata[[paste0(cohid)]][2,]), col="green")
+mtext("Coherent lake and landscape", cex=0.8)
+legend("topright", lty=1, col=c("blue","green"), legend=c("lake","land"), bty="n", cex=0.8, horiz=T)
+text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.1*diff(par("usr")[3:4]),"b)")
+
+plot(as.numeric(colnames(lakedata[[paste0(incohid)]])),scale(lakedata[[paste0(incohid)]][1,]),type="l", col="blue", ylim=c(-2,3.3),
+     ylab="",xlab="Year", yaxt="n")
+lines(as.numeric(colnames(lakedata[[paste0(incohid)]])),scale(lakedata[[paste0(incohid)]][2,]), col="green")
+mtext("Non-coherent lake and landscape", cex=0.8)
+text(par("usr")[1]+0.04*diff(par("usr")[1:2]), par("usr")[4]-0.1*diff(par("usr")[3:4]),"c)")
+
 dev.off()
@@
 
-dt.conn<-dt$buffer500m.conn
+dt.conn<-dt$iws.conn
 dt.conn<-dt.conn[,!grepl("sum_lengthm",colnames(dt.conn))]
-dt.conn<-dt.conn[,colnames(dt.conn)!="buffer500m_nhdid"]
+dt.conn<-dt.conn[,!grepl("_avgsize_ha",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("_count",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("_overlapping_area_ha",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("_contributing_area",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("_isolated",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("_lakes_",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("canalditchdensity",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("streamdensity_midreaches",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("streamdensity_rivers",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("regimea",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("regimeg",colnames(dt.conn))]
+dt.conn<-dt.conn[,!grepl("regimeh",colnames(dt.conn))]
+dt.conn<-dt.conn[,!colnames(dt.conn) %in% c("iws_zoneid","borderiws","iws_nwiexclusions","iws_nhdid")]
 
@@
 dt.geo<-dt.geo[,!grepl("_count",colnames(dt.geo))]
+dt.geo<-dt.geo[,!grepl("contributing_area",colnames(dt.geo))]
 
-dt.lulc<-dt$hu12.lulc
+dt.lulc<-dt$iws.lulc
 dt.lulc<-dt.lulc[,!grepl("_ha_",colnames(dt.lulc))]
@@
 dt.lulc<-dt.lulc[,!grepl("_nlcd2001_",colnames(dt.lulc))]
-dt.lulc<-dt.lulc[,colnames(dt.lulc)!="hu12_damdensity_pointsperha"]
-dt.lulc<-dt.lulc[,colnames(dt.lulc)!="hu12_damdensity_pointcount"]
-dt.lulc<-dt.lulc[,colnames(dt.lulc)!="hu12_roaddensity_sum_lengthm"]
+dt.lulc<-dt.lulc[,!grepl("_damdensity",colnames(dt.lulc))]
+dt.lulc<-dt.lulc[,colnames(dt.lulc)!="_roaddensity_sum_lengthm"]
 dt.lulc<-dt.lulc[,!grepl("_min",colnames(dt.lulc))]
@@
 dt.lulc<-dt.lulc[,!grepl("_std",colnames(dt.lulc))]
+dt.lulc<-dt.lulc[,!colnames(dt.lulc) %in% c("iws_zoneid","borderiws","iws_nwiexclusions","iws_nhdid")]
 
@@
 avg.chla<-aggregate(chla ~ lagoslakeid, data=gs.chla, FUN=mean, na.rm=T)
+
+#drainage ratio
+dr<-lagosne_select(table="iws", vars=c("lagoslakeid","iws_ha","iws_lakeareaha"))
+dr$drainage_ratio<-dr$iws_ha/dr$iws_lakeareaha
+dr<-dr[,colnames(dr) %in% c("lagoslakeid","drainage_ratio")]
 
@@
 preds<-left_join(preds, dt.chag, by="hu12_zoneid")
-preds<-left_join(preds, dt.lulc, by="hu12_zoneid")
+preds<-left_join(preds, dt.lulc, by="lagoslakeid")
 preds<-left_join(preds, avg.chla, by="lagoslakeid")
@@
 preds<-left_join(preds, shoredev, by="lagoslakeid")
+preds<-left_join(preds, dr, by="lagoslakeid")
 
@@
                                       "hu12_surficialgeology_till_oth_pct",
-                                      "hu12_nlcd2011_pct_0")]
+                                      "iws_nlcd2011_pct_0",
+                                      "hu8_zoneid",
+                                      "hu6_zoneid")]
+
+preds<-preds[,!grepl("scrubshrubwetlands",colnames(preds))]
+preds<-preds[,!grepl("otherwetlands",colnames(preds))]
+
+conpreds<-preds[,sapply(preds, is.numeric)]
+cor.conpreds<-cor(conpreds,use="pairwise.complete.obs")
 
 #huc2 and huc4 watershed codes
-huc_codes<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
+huc_codes<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/Q1_CoherenceVariation/match_huc_codes.csv", colClasses = 'character')
 
@@
 
-#write.csv(colnames(preds),file="~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/predictorlist.csv")
+write.csv(colnames(preds),file="~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/predictorlist_iws.csv")
 
@@
 ```
-```{r gam_cohst, echo=TRUE, cache=FALSE}
-lwgt<-preds$tslength/mean(preds$tslength)
-
-gam.cohst<-gam(accndvicoh.ts1 ~ s(cv.accndvi) + hu8_zoneid + s(hu12_dep_totaln_tavg_mean) +
-               s(hu12_nlcd2011_pct_90) + s(hu12_nlcd2011_pct_95), data=rfdat.cohst, gamma=1, weights=lwgt)
-gam.check(gam.cohst)
-concurvity(gam.cohst,full=F)$estimate
-summary(gam.cohst)
-plot(rfdat.cohst$accndvicoh.ts1, predict(gam.cohst, rfdat.cohst))
-
-```
 
@@
 ```
-```{r gam_cohlt, echo=TRUE, cache=FALSE}
-lwgt<-preds$tslength/mean(preds$tslength)
-
-gam.cohlt<-gam(accndvicoh.ts2 ~ hu8_zoneid + s(hu12_nlcd2011_pct_52) + s(cv.accndvi) + 
-                 s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean) + 
-                 s(wlconnections_allwetlands_contributing_area_ha), data=rfdat.cohlt, gamma=1, weights=lwgt)
-gam.check(gam.cohlt)
-concurvity(gam.cohlt,full=F)$estimate
-summary(gam.cohlt)
-plot(rfdat.cohlt$accndvicoh.ts2, predict(gam.cohlt, rfdat.cohlt))
-
-```
 
@@
 rfdat.phist<-rfdat.phist[,!colnames(rfdat.phist) %in% 
-                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
+                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","hu4_zoneid")]
 rfdat.phist<-rfdat.phist[,!grepl("borderhu12s",colnames(rfdat.phist))]
@@
 #sine
-cf.sinphist<-party::cforest(sin(accndviphi.ts1) ~ ., data=rfdat.phist, 
-                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
-varimp.sinphi.st<-varimp(cf.sinphist)
-print(varimp.sinphi.st[order(varimp.sinphi.st, decreasing=T)][1:10])
-pred.sinphi.st<-predict(cf.sinphist, newdata=rfdat.phist,type="response")
-cor.test(pred.sinphi.st,sin(rfdat.phist$accndviphi.ts1))
-
-```
-
-```{r gam_phist, echo=TRUE, cache=FALSE}
-lwgt<-preds$tslength[coh.chlaXaccndvi$accndvip.ts1<0.3]/mean(preds$tslength[coh.chlaXaccndvi$accndvip.ts1<0.3])
-
-#cosine
-gam.cosphist<-gam(cos(accndviphi.ts1) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
-                 s(buffer500m_streamdensity_headwaters_density_mperha) + 
-                 s(chla), 
-               data=rfdat.phist, gamma=1, weights=lwgt)
-gam.check(gam.cosphist)
-concurvity(gam.cosphist, full=F)$estimate
-summary(gam.cosphist)
-plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.cosphist, rfdat.phist))
-
-#sine -- ignored in main text
-gam.sinphist<-gam(sin(accndviphi.ts1) ~ s(buffer500m_streamdensity_headwaters_density_mperha) + 
-                 s(hu12_dep_so4_tavg_mean) + 
-                 s(hu12_damdensity_pointspersqkm), 
-               data=rfdat.phist, gamma=1, weights=lwgt)
-gam.check(gam.sinphist)
-concurvity(gam.sinphist,full=F)$estimate
-summary(gam.sinphist)
-plot(sin(rfdat.phist$accndviphi.ts1), predict(gam.sinphist, rfdat.phist))
+# cf.sinphist<-party::cforest(sin(accndviphi.ts1) ~ ., data=rfdat.phist, 
+#                          controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
+# varimp.sinphi.st<-varimp(cf.sinphist)
+# print(varimp.sinphi.st[order(varimp.sinphi.st, decreasing=T)][1:10])
+# pred.sinphi.st<-predict(cf.sinphist, newdata=rfdat.phist,type="response")
+# cor.test(pred.sinphi.st,sin(rfdat.phist$accndviphi.ts1))
 
@@
 rfdat.philt<-rfdat.philt[,!colnames(rfdat.philt) %in% 
-                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
+                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","hu4_zoneid")]
 rfdat.philt<-rfdat.philt[,!grepl("borderhu12s",colnames(rfdat.philt))]
@@
 
-#cosine
-cf.cosphilt<-party::cforest(cos(accndviphi.ts2) ~ ., data=rfdat.philt,
-                         controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
-
-varimp.cosphi.lt<-varimp(cf.cosphilt)
-print(varimp.cosphi.lt[order(varimp.cosphi.lt, decreasing=T)][1:10])
-pred.cosphi.lt<-predict(cf.cosphilt, newdata=rfdat.philt,type="response")
-cor.test(pred.cosphi.lt,cos(rfdat.philt$accndviphi.ts2))
+# #cosine
+# cf.cosphilt<-party::cforest(cos(accndviphi.ts2) ~ ., data=rfdat.philt,
+#                          controls=cforest_control(ntree=50000,mincriterion = 0.9,mtry=3))
+# 
+# varimp.cosphi.lt<-varimp(cf.cosphilt)
+# print(varimp.cosphi.lt[order(varimp.cosphi.lt, decreasing=T)][1:10])
+# pred.cosphi.lt<-predict(cf.cosphilt, newdata=rfdat.philt,type="response")
+# cor.test(pred.cosphi.lt,cos(rfdat.philt$accndviphi.ts2))
 
@@
 ```
-
-```{r gam_philt, echo=TRUE, cache=FALSE}
-lwgt<-preds$tslength[coh.chlaXaccndvi$accndvip.ts2<0.3]/mean(preds$tslength[coh.chlaXaccndvi$accndvip.ts2<0.3])
-
-#cosine
-gam.cosphilt<-gam(cos(accndviphi.ts2) ~ hu4_zoneid + s(hu12_slope_mean) + 
-                 s(hu12_nlcd2011_pct_90), 
-               data=rfdat.philt, gamma=1, weights=lwgt)
-gam.check(gam.cosphilt)
-concurvity(gam.cosphilt,full=F)$estimate
-summary(gam.cosphilt)
-plot(cos(rfdat.philt$accndviphi.ts2), predict(gam.cosphilt, rfdat.philt))
-
-#sine
-gam.sinphilt<-gam(sin(accndviphi.ts2) ~ hu4_zoneid + s(hu12_nlcd2011_pct_82) + 
-                 s(hu12_nlcd2011_pct_21), 
-               data=rfdat.philt, gamma=1, weights=lwgt)
-gam.check(gam.sinphilt)
-concurvity(gam.sinphilt,full=F)$estimate
-summary(gam.sinphilt)
-plot(sin(rfdat.philt$accndviphi.ts2), predict(gam.sinphilt, rfdat.philt))
-
-```
-
-```{r saveResults, echo=TRUE, cache=FALSE}
-# save.image(file="~/Box Sync/NSF EAGER Synchrony/Data/results_20191106.RData")
-```
-
 ```{r plot varimp}
@@
 print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10])
-ltxt.st<-c("cv(NDVI)","HUC-8 sub-basin","total N deposition","% woody wetlands","% herbaceous wetlands",
-           "shrub wetlands shoreline","all wetlands shoreline","slope","topographic roughness","forested wetlands shoreline")
+ltxt.st<-c("total N deposition","cv(NDVI)","% woody wetlands","all wetlands shoreline","mean runoff",
+           "% developed open space","% regime c wetlands","forest wetlands shoreline","mean annual precipitation",
+           "shoreline development ratio")
 
 print(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10])
-ltxt.lt<-c("HUC-8 sub-basin","% shrub/scrub","cv(NDVI)","annual precipitation","all wetlands contrib. area",
-           "forested wetlands shoreline","% woody wetlands","all wetlands shoreline","sulfate deposition",
-           "groundwater recharge")
+ltxt.lt<-c("% shrub/scrub","cv(NDVI)","% regime f wetlands","mean annual precipitation","forest wetlands shoreline",
+           "% cultivated crops","headwaters density","% mixed forest", "wetland shoreline", "% developed low intensity")
 
 print(varimp.cosphi.st[order(varimp.cosphi.st, decreasing = T)][1:10])
-ltxt.cosphist<-c("open wetlands shoreline","headwaters density","stream density","mean chlorophyll-a",
-              "% developed open space","open wetlands contrib. area","all wetlands contrib. area", "road density","nitrate deposition",
-              "% pasture/hay")
+ltxt.cosphist<-c("open wetlands shoreline","% open wetlands area","mean chlorophyll-a","% shrub/scrub",
+              "% cultivated crops","% developed open space","% developed high intensity","nitrate deposition",
+              "groundwater recharge","% open water")
 
 print(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing = T)][1:10])
-ltxt.sinphilt<-c("HUC-4 subregion","HUC-6 basin","% cultivated crops","HUC-8 sub-basin","% developed open space",
-                 "open wetlands contrib. area","all wetlands contrib. area","% open water","all wetlands shoreline","shrub wetladns contrib. area")
+ltxt.sinphilt<-c("open wetlands shoreline", "all wetlands shoreline","% cultivated crops","% regime f wetlands",
+                 "% evergreen forest","forested wetlands shoreline", "% open wetlands area","% barren land",
+                 "max depth","lake connection type")
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10.tif",units="in",res=300,width=6.5, height=5)
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10_iws.tif",units="in",
+     res=300,width=6.5, height=5)
 
-par(mfrow=c(2,2), mar=c(4,11,1,1), cex.main=0.9, cex.axis=0.9)
+par(mfrow=c(2,2), mar=c(3.5,10,1.5,1), cex.main=0.9, cex.axis=0.9, mgp=c(1,0.5,0), tcl=-0.3)
 
@@
 
+```{r gam_cohst, echo=TRUE, cache=FALSE}
+lwgt<-preds$tslength/mean(preds$tslength)
+
+gam.cohst<-gam(accndvicoh.ts1 ~ s(hu12_dep_totaln_tavg_mean) + s(cv.accndvi) + s(iws_nlcd2011_pct_90,k=3)
+               #+ s(wlconnections_allwetlands_shoreline_km) + s(hu12_runoff_mean)
+               , data=rfdat.cohst, gamma=1, weights=lwgt)
+gam.check(gam.cohst)
+concurvity(gam.cohst,full=F)$estimate
+summary(gam.cohst)
+plot(rfdat.cohst$accndvicoh.ts1, predict(gam.cohst, rfdat.cohst))
+
+```
+
+```{r gam_cohlt, echo=TRUE, cache=FALSE}
+lwgt<-preds$tslength/mean(preds$tslength)
+
+gam.cohlt<-gam(accndvicoh.ts2 ~ s(iws_nlcd2011_pct_52) + s(cv.accndvi) + 
+                 s(iws_wl_regimefwetlandsundissolved_overlapping_area_pct) 
+               #+  s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean) + s(wlconnections_forestedwetlands_shoreline_km)
+               , data=rfdat.cohlt, gamma=1, weights=lwgt)
+gam.check(gam.cohlt)
+concurvity(gam.cohlt,full=F)$estimate
+summary(gam.cohlt)
+plot(rfdat.cohlt$accndvicoh.ts2, predict(gam.cohlt, rfdat.cohlt))
+
+```
+
+```{r gam_phist, echo=TRUE, cache=FALSE}
+lwgt<-preds$tslength[coh.chlaXaccndvi$accndvip.ts1<0.3]/mean(preds$tslength[coh.chlaXaccndvi$accndvip.ts1<0.3])
+
+#cosine
+gam.cosphist<-gam(cos(accndviphi.ts1) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
+                  s(chla) + s(iws_nlcd2011_pct_52,k=3), data=rfdat.phist, gamma=1, weights=lwgt)
+gam.check(gam.cosphist)
+concurvity(gam.cosphist, full=F)$estimate
+summary(gam.cosphist)
+plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.cosphist, rfdat.phist))
+
+# #sine -- ignored in main text
+# gam.sinphist<-gam(sin(accndviphi.ts1) ~ s(buffer500m_streamdensity_headwaters_density_mperha) + 
+#                  s(hu12_dep_so4_tavg_mean) + 
+#                  s(hu12_damdensity_pointspersqkm), 
+#                data=rfdat.phist, gamma=1, weights=lwgt)
+# gam.check(gam.sinphist)
+# concurvity(gam.sinphist,full=F)$estimate
+# summary(gam.sinphist)
+# plot(sin(rfdat.phist$accndviphi.ts1), predict(gam.sinphist, rfdat.phist))
+
+```
+
+```{r gam_philt, echo=TRUE, cache=FALSE}
+lwgt<-preds$tslength[coh.chlaXaccndvi$accndvip.ts2<0.3]/mean(preds$tslength[coh.chlaXaccndvi$accndvip.ts2<0.3])
+
+# #cosine
+# gam.cosphilt<-gam(cos(accndviphi.ts2) ~ hu4_zoneid + s(hu12_slope_mean) + 
+#                  s(hu12_nlcd2011_pct_90), 
+#                data=rfdat.philt, gamma=1, weights=lwgt)
+# gam.check(gam.cosphilt)
+# concurvity(gam.cosphilt,full=F)$estimate
+# summary(gam.cosphilt)
+# plot(cos(rfdat.philt$accndviphi.ts2), predict(gam.cosphilt, rfdat.philt))
+
+#sine
+gam.sinphilt<-gam(sin(accndviphi.ts2) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
+                 s(iws_nlcd2011_pct_82) + s(iws_wl_regimefwetlandsundissolved_overlapping_area_pct), 
+               data=rfdat.philt, gamma=1, weights=lwgt)
+gam.check(gam.sinphilt)
+concurvity(gam.sinphilt,full=F)$estimate
+summary(gam.sinphilt)
+plot(sin(rfdat.philt$accndviphi.ts2), predict(gam.sinphilt, rfdat.philt))
+
+```
+
+```{r saveResults, echo=TRUE, cache=FALSE}
+# save.image(file="~/Box Sync/NSF EAGER Synchrony/Data/results_20191106.RData")
+```
+
 ```{r plot_gameffects}
 
-## Make geographic variation images 
-huc4_bdys<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/HU4.shp")
-huc8_bdys<-readOGR("~/Box Sync/NSF EAGER Synchrony/Data/HU8.shp")
-
-cohst_huc8<-data.frame(ZoneID=names(gam.cohst$coefficients)[grepl("hu8_zoneid",names(gam.cohst$coefficients))],
-                      coeff=gam.cohst$coefficients[grepl("hu8_zoneid",names(gam.cohst$coefficients))])
-rownames(cohst_huc8)<-c()
-cohst_huc8$ZoneID<-substring(cohst_huc8$ZoneID,11)
-
-cohlt_huc8<-data.frame(ZoneID=names(gam.cohlt$coefficients)[grepl("hu8_zoneid",names(gam.cohlt$coefficients))],
-                      coeff=gam.cohlt$coefficients[grepl("hu8_zoneid",names(gam.cohlt$coefficients))])
-rownames(cohlt_huc8)<-c()
-cohlt_huc8$ZoneID<-substring(cohlt_huc8$ZoneID,11)
-
-sinphilt_huc4<-data.frame(ZoneID=names(gam.sinphilt$coefficients)[grepl("hu4_zoneid",names(gam.sinphilt$coefficients))],
-                      coeff=gam.sinphilt$coefficients[grepl("hu4_zoneid",names(gam.sinphilt$coefficients))])
-rownames(sinphilt_huc4)<-c()
-sinphilt_huc4$ZoneID<-substring(sinphilt_huc4$ZoneID,11)
-
-# lagosstates_outline<-lagosstates
-# lagosstates_outline@data$dissolve<-rep(1,length(lagosstates_outline))
-# lagosstates_outline<-gUnaryUnion(lagosstates_outline,id=lagosstates_outline@data$dissolve)
-# huc4_bdys<-raster::intersect(huc4_bdys,lagosstates_outline)
-# huc8_bdys<-raster::intersect(huc8_bdys,lagosstates_outline)
-
-# huc_codes<-read.csv("/Users/jonathanwalter/GitHub/AquaTerrSynch/AnalysisCode/match_huc_codes.csv", colClasses = 'character')
-# huc_codes<-huc_codes[huc_codes$hu4_zoneid %in% analysislakes$lakeinfo$hu4_zoneid,]
-
-huc_bdys_cohst<-huc8_bdys[huc8_bdys$ZoneID %in% cohst_huc8$ZoneID,]
-huc_bdys_cohst@data<-left_join(huc_bdys_cohst@data, cohst_huc8)
-
-huc_bdys_cohlt<-huc8_bdys[huc8_bdys$ZoneID %in% cohlt_huc8$ZoneID,]
-huc_bdys_cohlt@data<-left_join(huc_bdys_cohlt@data, cohlt_huc8)
-
-huc_bdys_sinphilt<-huc4_bdys[huc4_bdys$ZoneID %in% sinphilt_huc4$ZoneID,]
-huc_bdys_sinphilt@data<-left_join(huc_bdys_sinphilt@data, sinphilt_huc4)
-
-scale1_100<-function(x){
-  x1<-x-min(x)+1/100
-  x1<-round(x1/max(x1)*100)
-  return(x1)
-}
-#make smaller images that we can insert into the main figure
-
-bight=6.5
+bight=5
 bigwd=6.5
 
-lagosstates_prj<-spTransform(lagosstates, proj4string(huc8_bdys))
+mar1<-c(3,1.5,0.3,0.2)
+fudge=1/60
 
-# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst.png", units="in",
-#      res=300, width=bigwd/5, height=bight/4)
-# par(mar=c(0,0,2,0))
-# plot(huc_bdys_cohst,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohst$coeff)],xlim=c(-91837,2260000),lwd=0.5)
-# lines(lagosstates_prj,lwd=0.5)
-# par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
-# image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
-# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohst$coeff), max(huc_bdys_cohst$coeff), length.out=5),2), cex=0.5)
-# dev.off()
-# 
-# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt.png", units="in",
-#      res=300, width=bigwd/5, height=bight/4)
-# par(mar=c(0,0,2,0))
-# plot(huc_bdys_cohlt,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohlt$coeff)],xlim=c(-91837,2260000),lwd=0.5)
-# lines(lagosstates_prj,lwd=0.5)
-# par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
-# image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
-# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohlt$coeff), max(huc_bdys_cohlt$coeff), length.out=5),2), cex=0.5)
-# dev.off()
-# 
-# png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt.png", units="in",
-#      res=300, width=bigwd/5, height=bight/4)
-# par(mar=c(0,0,2,0))
-# plot(huc_bdys_sinphilt,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys_sinphilt$coeff)],xlim=c(-91837,2260000),lwd=0.5)
-# lines(lagosstates_prj,lwd=0.5)
-# par(fig=c(0.2,0.8,0.875,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
-# image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
-# axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_sinphilt$coeff), max(huc_bdys_sinphilt$coeff), length.out=5),2), cex=0.5)
-# dev.off()
-# 
-# 
-# panel5b<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst.png")
-# panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt.png")
-# panel5n<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt.png")
-# 
-# mar1<-c(3,1.5,0.5,1)
-# fudge=1/40
-# 
-# tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits.tif",units="in",res=300,width=bigwd, height=bight)
-# 
-# par(mfrow=c(4,5),mgp=c(1.5,0.5,0),oma=c(0,2.5,0,0),mar=mar1)
-# 
-# plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence")
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_bycolumn_iws.tif",units="in",res=300,width=bigwd, height=bight)
+
+par(mfcol=c(3,4),mgp=c(1.5,0.5,0), oma=c(0,1.5,1.5,0.5),mar=mar1,tcl=-0.3)
+
 # plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
-# rasterImage(image=panel5b,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-# plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="")
-# plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="")
-# plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% herbaceous wetld.",ylab="")
-# 
-# plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetlands shoreline",ylab="short phase")
-# plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
-# plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
+# rasterImage(image=panel5a,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
+plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="short coherence", ylim=c(-.6,.6))
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"a)")
+plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence", ylim=c(-.6,.6))
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"b)")
+plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="",ylim=c(-.6,.6))
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"c)")
+#plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetlands shoreline",ylab="",ylim=c(-.6,.6))
+# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"d)")
+# plot(gam.cohst,select=5,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean runoff",ylab="",ylim=c(-.6,.6))
+# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"e)")
+
+plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetld. shoreline",ylab="short phase")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"d)")
+plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"e)")
+plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"f)")
 # plot.new()
 # plot.new()
-# 
+
 # plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
 # rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-# plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-1,1))
-# plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="",ylim=c(-1,1))
-# plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="annual precipitation",ylab="")
-# plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetld. contrib. area",ylab="",ylim=c(-1,1))
-# 
+plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-.6,.6))
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"g)")
+plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="long coherence",ylim=c(-.6,.6))
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"h)")
+plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% regime f wetlands",ylab="",ylim=c(-.6,.6))
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"i)")
+# plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean annual precipitation",ylab="", ylim=c(-.6,.6))
+# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"l)")
+# plot(gam.cohlt,select=5,residuals=T,rug=FALSE,shade=T,cex=2,xlab="forest wetlands shoreline",ylab="",ylim=c(-.6,.6))
+# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"m)")
+
 # plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-4 sub-region",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
 # rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-# plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% pasture",ylab="")
-# plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% developed-open space",ylab="")
-# 
-# mtext("Partial residuals",2,outer=T,line=1.2,cex=0.8)
-# mtext("sin(long phase)",2,at=1/8+fudge,outer=T,line=0,cex=0.7)
-# mtext("long coherence",2,at=1/8+1/4+fudge,outer=T,line=0,cex=0.7)
-# mtext("cos(short phase)",2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)
-# mtext("short coherence",2,at=1/8+3/4+fudge,outer=T,line=0,cex=0.7)
-# 
-# dev.off()
+plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetld. shoreline",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"j)")
+plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% cultivated crops",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"k)")
+plot(gam.sinphilt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% regime f wetlands",ylab="")
+text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"l)")
 
-## try out landscape orientation
-
-bight=5.5
-bigwd=9
-
-lagosstates_prj<-spTransform(lagosstates, proj4string(huc8_bdys))
-
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png", units="in",
-     res=300, width=bigwd/5, height=bight/4)
-par(mar=c(0,0,1,0))
-plot(huc_bdys_cohst,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohst$coeff)],xlim=c(-91837,2260000),
-     ylim=c(1454000,3012981),lwd=0.5)
-lines(lagosstates_prj,lwd=0.5)
-par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
-image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
-axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohst$coeff), max(huc_bdys_cohst$coeff), length.out=5),2), cex.axis=0.7)
-dev.off()
-
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png", units="in",
-     res=300, width=bigwd/5, height=bight/4)
-par(mar=c(0,0,1,0))
-plot(huc_bdys_cohlt,bty="o",xlab="HU8 watershed", col=pal[scale1_100(huc_bdys_cohlt$coeff)],xlim=c(-91837,2260000),
-     ylim=c(1454000,3012981),lwd=0.5)
-lines(lagosstates_prj,lwd=0.5)
-par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.05,0))
-image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
-axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_cohlt$coeff), max(huc_bdys_cohlt$coeff), length.out=5),2), cex.axis=0.7)
-dev.off()
-
-png("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png", units="in",
-     res=300, width=bigwd/5, height=bight/4)
-par(mar=c(0,0,1,0))
-plot(huc_bdys_sinphilt,bty="o",xlab="HU4 watershed", col=pal[scale1_100(huc_bdys_sinphilt$coeff)],xlim=c(-91837,2260000),
-     ylim=c(1454000,3012981),lwd=0.5)
-lines(lagosstates_prj,lwd=0.5)
-par(fig=c(0.25,0.75,0.855,1), new=T,mar=c(.5,0,0.2,0), tcl=-0.15, mgp=c(1,0.2,0))
-image(matrix(1:100,ncol=1),col=pal[1:100], xaxt="n", yaxt="n")
-axis(1,at=c(0,0.25,0.5,0.75,1),labels=round(seq(min(huc_bdys_sinphilt$coeff), max(huc_bdys_sinphilt$coeff), length.out=5),2), cex.axis=0.7)
-dev.off()
-
-panel5b<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5b_hu8_cohst_lscp.png")
-panel5i<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5i_hu8_cohlt_lscp.png")
-panel5n<-readPNG("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5n_hu4_sinphilt_lscp.png")
-
-mar1<-c(3,1.5,0.5,0.2)
-fudge=1/34
-
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_landscape.tif",units="in",res=300,width=bigwd, height=bight)
-
-par(mfrow=c(4,5),mgp=c(1.5,0.5,0), oma=c(0,2.5,0,0.5),mar=mar1,tcl=-0.3)
-
-plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence")
-plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
-rasterImage(image=panel5b,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="")
-plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="")
-plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% herbaceous wetld.",ylab="")
-
-plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetlands shoreline",ylab="short phase")
-plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="headwaters density",ylab="")
-plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
-plot.new()
-plot.new()
-
-plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
-rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-1,1))
-plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="",ylim=c(-1,1))
-plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="annual precipitation",ylab="")
-plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetld. contrib. area",ylab="",ylim=c(-1,1))
-
-plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-4 sub-region",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
-rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% pasture",ylab="")
-plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% developed-open space",ylab="")
-
-mtext("Partial residuals",2,outer=T,line=1.2,cex=0.8)
-mtext(expression(paste("long sin(",phi,")",sep="")),2,at=1/8+fudge,outer=T,line=0,cex=0.7)
-mtext("long coherence",2,at=1/8+1/4+fudge,outer=T,line=0,cex=0.7)
-mtext(expression(paste("short cos(",phi,")",sep="")),2,at=1/8+2/4+fudge,outer=T,line=0,cex=0.7)
-mtext("short coherence",2,at=1/8+3/4+fudge,outer=T,line=0,cex=0.7)
+mtext("Partial residuals",2,outer=T,line=0.1,cex=1,at=0.537)
+mtext("short coherence",3,at=1/8+fudge,outer=T,line=0,cex=0.8)
+mtext(expression(paste("short cos(",phi,")",sep="")),3,at=1/8+1/4+fudge,outer=T,line=-0.2,cex=0.8)
+mtext("long coherence",3,at=1/8+2/4+fudge,outer=T,line=0,cex=0.8)
+mtext(expression(paste("long sin(",phi,")",sep="")),3,at=1/8+3/4+fudge,outer=T,line=-0.2,cex=0.8)
 

### 2020-07-01 AnalysisCode/Q1_CoherenceVariation/ms1_analyses_rf_to_gam_IWSnotHU12_20200312.Rmd
revisions post review

--- 2020-07-01 AnalysisCode/Q1_CoherenceVariation/ms1_analyses_rf_to_gam_IWSnotHU12.Rmd
@@
 
-gam.cohst<-gam(accndvicoh.ts1 ~ s(hu12_dep_totaln_tavg_mean) + s(cv.accndvi) + s(iws_nlcd2011_pct_90,k=3)
+gam.cohst<-gam(accndvicoh.ts1 ~ s(hu12_dep_totaln_tavg_mean) + s(log10(cv.accndvi)) + s(iws_nlcd2011_pct_90,k=3)
                #+ s(wlconnections_allwetlands_shoreline_km) + s(hu12_runoff_mean)
-               , data=rfdat.cohst, gamma=1, weights=lwgt)
+               , data=rfdat.cohst, gamma=1, weights=lwgt, family=betar)
 gam.check(gam.cohst)
@@
 
-gam.cohlt<-gam(accndvicoh.ts2 ~ s(iws_nlcd2011_pct_52) + s(cv.accndvi) + 
+gam.cohlt<-gam(accndvicoh.ts2 ~ s(iws_nlcd2011_pct_52) + s(log10(cv.accndvi)) + 
                  s(iws_wl_regimefwetlandsundissolved_overlapping_area_pct) 
                #+  s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean) + s(wlconnections_forestedwetlands_shoreline_km)
-               , data=rfdat.cohlt, gamma=1, weights=lwgt)
+               , data=rfdat.cohlt, gamma=1, weights=lwgt, family="betar")
 gam.check(gam.cohlt)
@@
 #cosine
-gam.cosphist<-gam(cos(accndviphi.ts1) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
-                  s(chla) + s(iws_nlcd2011_pct_52,k=3), data=rfdat.phist, gamma=1, weights=lwgt)
+gam.cosphist<-gam(cos(accndviphi.ts1) ~ s(sqrt(wlconnections_openwaterwetlands_shoreline_km),k=3) + 
+                  s(log10(chla)) + s(iws_nlcd2011_pct_52,k=3), data=rfdat.phist, gamma=1, weights=lwgt)
 gam.check(gam.cosphist)
@@
 #sine
-gam.sinphilt<-gam(sin(accndviphi.ts2) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
-                 s(iws_nlcd2011_pct_82) + s(iws_wl_regimefwetlandsundissolved_overlapping_area_pct), 
+gam.sinphilt<-gam(sin(accndviphi.ts2) ~ s(sqrt(wlconnections_openwaterwetlands_shoreline_km)) + 
+                 s(iws_nlcd2011_pct_82) + s(sqrt(iws_wl_regimefwetlandsundissolved_overlapping_area_pct)), 
                data=rfdat.philt, gamma=1, weights=lwgt)
@@
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_bycolumn_iws.tif",units="in",res=300,width=bigwd, height=bight)
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_bycolumn_iws_v2.tif",units="in",res=300,width=bigwd, height=bight)
 
@@
 # rasterImage(image=panel5a,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="short coherence", ylim=c(-.6,.6))
+plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="total N deposition",ylab="short coherence", ylim=c(-2,3.2))
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"a)")
-plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence", ylim=c(-.6,.6))
+plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab=expression(paste("log"[10],"(cv(NDVI))",sep="")),ylab="short coherence", ylim=c(-2,3.2))
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"b)")
-plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="",ylim=c(-.6,.6))
+plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="% woody wetlands",ylab="",ylim=c(-2,3.2))
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"c)")
@@
 
-plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetld. shoreline",ylab="short phase")
+plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="sqrt(open wetld. shoreline)",ylab="short phase")
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"d)")
-plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
+plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab=expression(paste("log"[10],"(mean chlorophyll-a)",sep="")),ylab="")
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"e)")
-plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="")
+plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="% shrub/scrub",ylab="")
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"f)")
@@
 # rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-.6,.6))
+plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-2.5,2.2))
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"g)")
-plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="long coherence",ylim=c(-.6,.6))
+plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab=expression(paste("log"[10],"(cv(NDVI))",sep="")),ylab="long coherence",ylim=c(-2.5,2.2))
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"h)")
-plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% regime f wetlands",ylab="",ylim=c(-.6,.6))
+plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="% regime f wetlands",ylab="",ylim=c(-2.5,2.2))
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"i)")
@@
 # rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
-plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetld. shoreline",ylab="")
+plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="sqrt(open wetld. shoreline)",ylab="")
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"j)")
-plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% cultivated crops",ylab="")
+plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="% cultivated crops",ylab="")
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"k)")
-plot(gam.sinphilt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% regime f wetlands",ylab="")
+plot(gam.sinphilt,select=3,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="sqrt(% regime f wetlands)",ylab="")
 text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"l)")

### 2020-07-01 AnalysisCode/Q1_CoherenceVariation/ms1_analyses_rf_to_gam_IWSnotHU12_20200323.Rmd
revisions post review

--- 2020-07-01 AnalysisCode/Q1_CoherenceVariation/ms1_analyses_rf_to_gam_IWSnotHU12.Rmd
@@
 
-dbuff[which(sapply(analysislakes$lakedata, function(x){any(is.na(x))}))]
-
 analysislakes$lakeinfo<-analysislakes$lakeinfo[!sapply(analysislakes$lakedata, function(x){any(is.na(x))}),]
@@
 coh.chlaXaccndvi<-NULL
+# surrog.coh<-NULL
+# ar1.chla<-NULL
+# ar1.ndvi<-NULL
 
@@
                     norm="powall", sigmethod="fast", nrand=10000)
+  # ar1.chla<-c(ar1.chla, arima(lakedat.ii[1,], order=c(1,0,0))$coef[1])
+  # ar1.ndvi<-c(ar1.ndvi, arima(lakedat.ii[2,], order=c(1,0,0))$coef[1])
+
   for(rind in 1:nrow(tsranges)){
@@
   coh.chlaXaccndvi<-rbind(coh.chlaXaccndvi, c(t(as.matrix(chlaXaccndvi$bandp[,3:5]))))
+  ## this following is wrong, need to take Mod after mean
+  # surrog.coh<-rbind(surrog.coh,
+  #                   cbind(apply(Mod(chlaXaccndvi$signif$scoher[,chlaXaccndvi$timescales<4]),1,mean)
+  #                   ,apply(Mod(chlaXaccndvi$signif$scoher[,chlaXaccndvi$timescales>4]),1,mean)
+  #                          ))
 }
@@
 save(list=c("coherentlakes.st","coherentlakes.lt"),
-     file="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/q2_coherent_lakes.RData")
+     file="/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/q2_coherent_lakes_byWatershed.RData")
 
@@
 plot(NA,NA,ylim=c(-2,5.2),xlim=range(tt), xlab="", ylab="", xaxt="n",yaxt="n")
-lines(tt,comb1,lwd=2)
-lines(tt,comb2,lwd=2,col="red")
+lines(tt,comb1,lwd=2,col="royalblue")
+lines(tt,comb2,lwd=2,col="forestgreen")
 axis(1, at=c(0,10,20,30,40,50),labels=NA)
 axis(2, at=c(-1,1.5,4), labels=NA)
-mtext("Timescale specific relationship",3,line=0.25)
+mtext("Timescale-specific relationship",3,line=0.25)
 text(0.4,4.9,"a)",cex=1.2)
@@
 axis(2, at=c(-1,0,1), labels=NA)
-lines(tt[tt<=20],sig3,lwd=2)
-lines(tt[tt<=20],sig4,lwd=2,col="red")
-mtext(expression(paste(phi," = 0")))
+lines(tt[tt<=20],sig3,lwd=2, col="royalblue")
+lines(tt[tt<=20],sig4,lwd=2,col="forestgreen")
+mtext(expression(paste("in-phase (",phi," = 0)")))
 text(1,0.9,"b)",cex=1.2)
@@
 axis(2, at=c(-1,0,1), labels=NA)
-lines(tt[tt<=20],sig3,lwd=2)
-lines(tt[tt<=20],sig5,lwd=2,col="red")
-mtext(expression(paste(phi," = ",pi,"/2")))
+lines(tt[tt<=20],sig3,lwd=2, col="forestgreen")
+lines(tt[tt<=20],sig5,lwd=2,col="royalblue")
+mtext(expression(paste("lagged (",phi," = ",pi,"/2)")))
 text(1,0.9,"c)",cex=1.2)
@@
 axis(2, at=c(-1,0,1), labels=NA)
-lines(tt[tt<=20],sig3,lwd=2)
-lines(tt[tt<=20],sig6,lwd=2,col="red")
-mtext(expression(paste(phi," = ",pi)))
+lines(tt[tt<=20],sig3,lwd=2, col="royalblue")
+lines(tt[tt<=20],sig6,lwd=2,col="forestgreen")
+mtext(expression(paste("anti-phase (",phi," = ",pi,")")))
 text(1,0.9,"d)",cex=1.2)
@@
 
+# ## ar1 comparison
+# coef.chla<-mean(ar1.chla)
+# coef.ndvi<-mean(ar1.ndvi)
+# tslen<-ceiling(mean(analysislakes$lakeinfo$tslength))
+# 
+# nreps=1000
+
+# ar1.coh<-NULL
+# for(ii in 1:nreps){
+# 
+#   y1<-cleandat(arima.sim(list(ar=coef.chla), n=tslen, n.start=500),1:tslen,5)$cdat
+#   y2<-cleandat(arima.sim(list(ar=coef.ndvi), n=tslen, n.start=500),1:tslen,5)$cdat
+#   zz<-coh(y1,y2,1:tslen,norm="powall")
+#   ar1.coh<-rbind(ar1.coh,cbind(Mod(mean(zz$coher[zz$timescales<4]))
+#                  ,Mod(mean(zz$coher[zz$timescales>4]))))
+# 
+# }
+# 
+# hist(ar1.coh[,1])
+# hist(ar1.coh[,2])
 #plotting
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_distributions_20191031.tif", units="in",
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig3_distributions_20200609.tif", units="in",
      res=300, width=6.5, height=5)
-layout(matrix(1:4,2,2,byrow=T),heights=c(0.4,0.4,0.6,0.6))
+layout(matrix(1:4,2,2,byrow=T),heights=c(0.45,0.6,0.45,0.6))
 
@@
 
-par(mar=c(1,1,2,1))
+par(mar=c(2,2,3,2))
 rose(coh.chlaXaccndvi$accndviphi.ts1[coh.chlaXaccndvi$accndvip.ts1<0.3], unit="radian", col="lightgrey",
@@
        at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
-text(0.9*par()$usr[1],0.95*par()$usr[4],"c)")
+text(0.9*par()$usr[1],0.9*par()$usr[4],"c)")
+mtext("lagged positive",1,col="grey",cex=0.75)
+mtext("negative (anti-phase)",2,col="grey",cex=0.75, line=-1.8)
+mtext("lagged negative",3,col="grey",cex=0.75)
+mtext("positive (in-phase)",4,col="grey",cex=0.75, line=-2)
+
 rose(coh.chlaXaccndvi$accndviphi.ts2[coh.chlaXaccndvi$accndvip.ts2<0.3], unit="radian", col="lightgrey",
@@
      at=c(0,pi/4,pi/2,3*pi/4,pi,-3*pi/4,-pi/2,-pi/4))
-text(0.9*par()$usr[1],0.95*par()$usr[4],"d)")
+text(0.9*par()$usr[1],0.9*par()$usr[4],"d)")
+mtext("lagged positive",1,col="grey",cex=0.75)
+mtext("negative (anti-phase)",2,col="grey",cex=0.75, line=-1.8)
+mtext("lagged negative",3,col="grey",cex=0.75)
+mtext("positive (in-phase)",4,col="grey",cex=0.75, line=-2)
 
@@
 
+mapdata<-data.frame(lagoslakeid=analysislakes$lakeinfo$lagoslakeid
+                    ,gnis_name=analysislakes$lakeinfo$gnis_name
+                    ,nhd_lat=analysislakes$lakeinfo$nhd_lat
+                    ,nhd_long=analysislakes$lakeinfo$nhd_long)
+mapdata<-left_join(mapdata, coh.chlaXaccndvi, by="lagoslakeid")
+
 cohid<-3370
@@
 
-bgcol<-rep("grey",length(lakedata))
-bgcol[names(lakedata)=="3370"]<-"red"
-bgcol[names(lakedata)=="4386"]<-"cyan3"
+mapdata$bgcol<-rep("grey",nrow(mapdata))
+mapdata$bgcol[mapdata$lagoslakeid==cohid]<-"red"
+mapdata$bgcol[mapdata$lagoslakeid==incohid]<-"cyan3"
+
+mapdata$pchar.st<-rep(16,nrow(mapdata))
+mapdata$pchar.st[mapdata$accndvip.ts1<0.05]<-21
+
+mapdata$pchar.lt<-rep(16,nrow(mapdata))
+mapdata$pchar.lt[mapdata$accndvip.ts2<0.05]<-21
+
+mapdata$ptcex<-rep(0.7, nrow(mapdata))
+mapdata$ptcex[mapdata$lagoslakeid==cohid | mapdata$lagoslakeid==incohid]<-1.2
 
@@
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_map_plus.tif",units="in",
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS1_map_plus.tif",units="in",
      res=300, width=6.5, height=2.75)
@@
 plot(lagosstates, main="",bty="o")
-points(analysislakes$lakeinfo$nhd_long, analysislakes$lakeinfo$nhd_lat, pch=21, cex=0.7, col="black",bg=bgcol)
+points(mapdata$nhd_long, mapdata$nhd_lat, pch=21, cex=mapdata$ptcex, col="black",bg=mapdata$bgcol)
 legend("bottomright",pch=c(0,21,21,21),col="black",pt.bg=c("grey","grey","red","cyan3"),
@@
 
-cohplotdata<-left_join(analysislakes$lakeinfo, coh.chlaXaccndvi, by="lagoslakeid")
+#cohplotdata<-left_join(analysislakes$lakeinfo, coh.chlaXaccndvi, by="lagoslakeid")
 
@@
 par()$usr
-points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
+points(mapdata$nhd_long[mapdata$accndvip.ts1 >=0.05], mapdata$nhd_lat[mapdata$accndvip.ts1 >=0.05], pch=16, cex=1, 
+       col=pal[round(mapdata$accndvicoh.ts1[mapdata$accndvip.ts1 >=0.05],2)*100])
+points(mapdata$nhd_long[mapdata$accndvip.ts1 <0.05], mapdata$nhd_lat[mapdata$accndvip.ts1 <0.05], pch=21, cex=1, 
+       bg=pal[round(mapdata$accndvicoh.ts1[mapdata$accndvip.ts1 <0.05],2)*100])
 colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)
@@
 plot(lagosstates, main="Lakes by long timescale coherence")
-points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
+points(mapdata$nhd_long, mapdata$nhd_lat, pch=16, cex=1, col=pal[round(mapdata$accndvicoh.ts2,2)*100])
 colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)
@@
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS1_coherencemap.tif", units="in",
-     res=300, width=6.5, height=7.5)
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig2_coherencemap_st.tif", units="in",
+     res=300, width=6.5, height=3.75)
 
-layout(laymat)
-par(mar=c(0,0,1.5,0))
+# layout(laymat)
+par(mar=c(0.1,0.1,0.1,0.1))
 
-plot(lagosstates, main="Short timescale coherence")
-points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts1,2)*100])
-text(0.99*par()$usr[1],0.99*par()$usr[4],"a)",cex=1.5)
+plot(lagosstates, main="")
+points(mapdata$nhd_long[mapdata$accndvip.ts1 >=0.05], mapdata$nhd_lat[mapdata$accndvip.ts1 >=0.05], pch=16, cex=1.5, 
+       col=pal[round(mapdata$accndvicoh.ts1[mapdata$accndvip.ts1 >=0.05],2)*100])
+points(mapdata$nhd_long[mapdata$accndvip.ts1 <0.05], mapdata$nhd_lat[mapdata$accndvip.ts1 <0.05], pch=21, cex=1.5, 
+       bg=pal[round(mapdata$accndvicoh.ts1[mapdata$accndvip.ts1 <0.05],2)*100], lwd=1.5)
+#colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)
+#text(0.99*par()$usr[1],0.99*par()$usr[4],"a)",cex=1.5)
 
-plot(lagosstates, main="Long timescale coherence")
-points(cohplotdata$nhd_long, cohplotdata$nhd_lat, pch=16, cex=1.5, col=pal[round(cohplotdata$accndvicoh.ts2,2)*100])
-text(0.99*par()$usr[1],0.99*par()$usr[4],"b)",cex=1.5)
-
-par(mar=c(5,1,5,1))
-image(matrix(1:100,nrow=1),col=pal,xaxt="n",yaxt="n")
-axis(2,at=seq(0,1,0.2))
+ext<-par("usr")
+par(new=T, mar=c(1.5,0.1,1.5,0.1), plt=c(0.45, 0.95, 0.08,0.13), tcl=-0.3, mgp=c(1,0.5,0))
+image(matrix(1:100,ncol=1),col=pal,xaxt="n",yaxt="n")
+axis(1,at=seq(0,1,0.2))
+mtext(3,"Coherence",line=0)
 
 dev.off()
+
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/figS2_coherencemap_lt.tif", units="in",
+     res=300, width=6.5, height=3.75)
+
+par(mar=c(0.1,0.1,0.1,0.1))
+
+plot(lagosstates, main="")
+points(mapdata$nhd_long[mapdata$accndvip.ts2 >=0.05], mapdata$nhd_lat[mapdata$accndvip.ts2 >=0.05], pch=16, cex=1.5, 
+       col=pal[round(mapdata$accndvicoh.ts2[mapdata$accndvip.ts2 >=0.05],2)*100])
+points(mapdata$nhd_long[mapdata$accndvip.ts2 <0.05], mapdata$nhd_lat[mapdata$accndvip.ts2 <0.05], pch=21, cex=1.5, 
+       bg=pal[round(mapdata$accndvicoh.ts2[mapdata$accndvip.ts2 <0.05],2)*100], lwd=1.5)
+
+ext<-par("usr")
+par(new=T, mar=c(1.5,0.1,0.1,0.1), plt=c(0.45, 0.95, 0.08,0.13), tcl=-0.3, mgp=c(1,0.5,0))
+image(matrix(1:100,ncol=1),col=pal,xaxt="n",yaxt="n")
+axis(1,at=seq(0,1,0.2))
+mtext(3,"Coherence")
+
+dev.off()
+#colorbar.plot(x=mean(par("usr")[1:2]),y=par("usr")[3],strip=1:100,col=pal,horizontal = T)
+#axis(1,at=c(1,100),labels=c(0,1))
+#text(0.99*par()$usr[1],0.99*par()$usr[4],"b)",cex=1.5)
+
+# par(mar=c(5,1,5,1))
+# image(matrix(1:100,nrow=1),col=pal,xaxt="n",yaxt="n")
+# axis(2,at=seq(0,1,0.2))
 
@@
 
+# dt.type<-dt$locus
+# dt.type<-dt.type[,colnames(dt.type) %in% c("lagoslakeid","nhd_fcode","nhd_ftype")]
+# dt.type<-dt.type[dt.type$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
+#125 of 126 lakes are non-reservoirs
+
 #depth
-depth<-lagosne_select(table="lakes_limno", vars=c("lagoslakeid","maxdepth"))
+depth<-lagosne_select(table="lakes_limno", vars=c("lagoslakeid","maxdepth","meandepth"))
 depth<-depth[depth$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,] #use max depth because it's more complete
@@
 
-preds<-analysislakes$lakeinfo[,colnames(analysislakes$lakeinfo) %in% c("lagoslakeid","end","start")]
+preds<-analysislakes$lakeinfo[,colnames(analysislakes$lakeinfo) %in% c("lagoslakeid","end","start","nhd_lat")]
 preds$tslength<-preds$end-preds$start + 1
@@
 rfdat.cohst<-left_join(coh.chlaXaccndvi[,c(10,3)], preds)
-rfdat.cohst<-rfdat.cohst[,!colnames(rfdat.cohst) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
+rfdat.cohst<-rfdat.cohst[,!colnames(rfdat.cohst) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","nhd_lat")]
 rfdat.cohst<-rfdat.cohst[,!grepl("borderhu12s",colnames(rfdat.cohst))]
@@
 rfdat.cohlt<-left_join(coh.chlaXaccndvi[,c(10,6)], preds)
-rfdat.cohlt<-rfdat.cohlt[,!colnames(rfdat.cohlt) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid")]
+rfdat.cohlt<-rfdat.cohlt[,!colnames(rfdat.cohlt) %in% c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","nhd_lat")]
 rfdat.cohlt<-rfdat.cohlt[,!grepl("borderhu12s",colnames(rfdat.cohlt))]
@@
 rfdat.phist<-rfdat.phist[,!colnames(rfdat.phist) %in% 
-                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","hu4_zoneid")]
+                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","hu4_zoneid","nhd_lat")]
 rfdat.phist<-rfdat.phist[,!grepl("borderhu12s",colnames(rfdat.phist))]
@@
 rfdat.philt<-rfdat.philt[,!colnames(rfdat.philt) %in% 
-                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","hu4_zoneid")]
+                           c("lagoslakeid","start","end","lakes_nhdid","hu12_zoneid","tslength","county_zoneid","hu4_zoneid","nhd_lat")]
 rfdat.philt<-rfdat.philt[,!grepl("borderhu12s",colnames(rfdat.philt))]
@@
 
+## atmosphere/climate is white; land productivity is green; lake productivity is blue; wetlands are brown;
+## crops are yellow; other is grey.
+
 print(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10])
 ltxt.st<-c("total N deposition","cv(NDVI)","% woody wetlands","all wetlands shoreline","mean runoff",
-           "% developed open space","% regime c wetlands","forest wetlands shoreline","mean annual precipitation",
+           "% developed-open space","% regime c wetlands","forest wetlands shoreline","mean annual precipitation",
            "shoreline development ratio")
+barcol.st<-c("white","forestgreen","saddlebrown","saddlebrown","white","grey","saddlebrown","saddlebrown","white","royalblue")
 
@@
 ltxt.lt<-c("% shrub/scrub","cv(NDVI)","% regime f wetlands","mean annual precipitation","forest wetlands shoreline",
-           "% cultivated crops","headwaters density","% mixed forest", "wetland shoreline", "% developed low intensity")
+           "% cultivated crops","headwaters density","% mixed forest", "all wetland shoreline", "% developed-low intensity")
+barcol.lt<-c("grey","forestgreen","saddlebrown","white","saddlebrown","forestgreen","grey","forestgreen","saddlebrown","grey")
 
 print(varimp.cosphi.st[order(varimp.cosphi.st, decreasing = T)][1:10])
-ltxt.cosphist<-c("open wetlands shoreline","% open wetlands area","mean chlorophyll-a","% shrub/scrub",
-              "% cultivated crops","% developed open space","% developed high intensity","nitrate deposition",
-              "groundwater recharge","% open water")
+ltxt.cosphist<-c("open wetlands shoreline","% open wetlands","mean chlorophyll-a","% shrub/scrub",
+              "% cultivated crops","% developed-open space","% developed-high intensity",
+              "nitrate deposition","groundwater recharge", "% open water")
+barcol.st2<-c("saddlebrown","saddlebrown","royalblue","grey","forestgreen","grey","grey","white","royalblue","royalblue")
 
@@
 ltxt.sinphilt<-c("open wetlands shoreline", "all wetlands shoreline","% cultivated crops","% regime f wetlands",
-                 "% evergreen forest","forested wetlands shoreline", "% open wetlands area","% barren land",
-                 "max depth","lake connection type")
+                 "% evergreen forest","forested wetlands shoreline", "% open wetlands","% barren land",
+                 "lake max depth","lake connection type")
+barcol.lt2<-c("saddlebrown","saddlebrown","forestgreen","saddlebrown","forestgreen","saddlebrown","saddlebrown","grey"
+              ,"royalblue","royalblue")
 
-tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10_iws.tif",units="in",
+tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig4_varimp_top10_iws_20200609.tif",units="in",
      res=300,width=6.5, height=5)
@@
 
-barplot(rev(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10]),names.arg=rev(ltxt.st),las=2,main="a) Short timescale coher.", horiz=T,font.main=1)
+barplot(rev(varimp.coh.st[order(varimp.coh.st, decreasing=T)][1:10]), col=rev(barcol.st),
+        names.arg=rev(ltxt.st),las=2,main="a) Short timescale coher.", horiz=T,font.main=1)
 
-barplot(rev(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.lt),las=2,main="c) Long timescale coher.", horiz=T, font.main=1)
+barplot(rev(varimp.coh.lt[order(varimp.coh.lt, decreasing=T)][1:10]), col=rev(barcol.lt),
+        names.arg=rev(ltxt.lt),las=2,main="c) Long timescale coher.", horiz=T, font.main=1)
 
 barplot(rev(varimp.cosphi.st[order(varimp.cosphi.st, decreasing=T)][1:10]),names.arg=rev(ltxt.cosphist),las=2,
-        main=expression(paste("b) Short timescale cosine(",phi,")",sep="")), horiz=T)
+        col=rev(barcol.st2), main=expression(paste("b) Short timescale cosine(",phi,")",sep="")), horiz=T)
 
 barplot(rev(varimp.sinphi.lt[order(varimp.sinphi.lt, decreasing=T)][1:10]),names.arg=rev(ltxt.sinphilt),las=2,
-        main=expression(paste("d) Long timescale sine(",phi,")",sep="")), horiz=T)
+        col=rev(barcol.lt2), main=expression(paste("d) Long timescale sine(",phi,")",sep="")), horiz=T)
 

### 2020-07-01 AnalysisCode/Q1_CoherenceVariation/ms1_prep_bywatershed.Rmd
revisions post review

--- 2019-12-10 AnalysisCode/Q1_coherenceSpatialVariation/ms1_prep.Rmd
@@
 
+source("~/GitHub/AquaTerrSynch/AnalysisCode/Q1_CoherenceVariation/addAVHRRannualts_bywatershed.R")
+
 ```
@@
 
-lakes_to_get<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/lakes20yrs_chla.csv")$x
+lakes_to_get<-read.csv("~/GitHub/AquaTerrSynch/AnalysisCode/Q1_CoherenceVariation/lakes20yrs_chla.csv")$x
 
@@
 
-dbuff<-calcBufferDist(sa=analysislakes$lakeinfo$lake_area_ha, ltype=analysislakes$lakeinfo$nhd_ftype, minbuff=2500)
+#dbuff<-calcBufferDist(sa=analysislakes$lakeinfo$lake_area_ha, ltype=analysislakes$lakeinfo$nhd_ftype, minbuff=2500)
 
 accndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/accvi1989_2018.img")
-maxndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/mxvi1989_2018.img")
+#maxndvi<-stack("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/SatelliteData/mxvi1989_2018.img")
 
@@
 
-analysislakes<-addAVHRRannualts(analysislakes, accndvi, dbuff)
+lagosIWS<-readOGR("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/IWS/IWS.shp", stringsAsFactors = F)
+colnames(lagosIWS@data)[12]<-"lagoslakeid"
+lagosIWS<-lagosIWS[lagosIWS$lagoslakeid %in% analysislakes$lakeinfo$lagoslakeid,]
+lagosIWS<-spTransform(lagosIWS, crs(accndvi))
+
+analysislakes<-addAVHRRannualts_byWatershed(analysislakes, accndvi, watersheds=lagosIWS)
 #analysislakes<-addAVHRRannualts(analysislakes, maxndvi, dbuff)
 
-save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873_2.RData")
+save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873_byWatershed.RData")
 

### 2020-07-01 AnalysisCode/Q1_CoherenceVariation/addAVHRRannualts_bywatershed.R

@@ -1,0 +1,72 @@
+#' Add terrestrial AVHRR time series to limnological time series
+#' 
+#' \code{addAVHRRannualts} extracts terrestrial AVHRR time series and appends them to limnological time series produced by,
+#' e.g., \code{makeLAGOSannualts}.
+#' 
+#' @param lakelist a list containing \code{lakeinfo} and \code{lakedata}, as output from \code{makeLAGOSannualts}.
+#' @param avhrrdata a raster stack of annual AVHRR metrics
+#' @param buffdist the distance (in meters) of the radius around each lake to draw terrestrial productivity information from.
+#' @param aggfun a string indicating how to aggregate values from multiple satellite measurements within the buffer. Defaults to "mean",
+#' "median" is also available.
+#' 
+#' @return \code{addAVHRRannualts} returns an object of class \code{list}. Slots are:
+#' \item{lakeinfo}{A data frame of lake information.}
+#' \item{lakedata}{A list of data frames containing the lake data. The avhrr data are appended here.}
+#' 
+#' @details Nope.
+#' 
+#' @author Jonathan Walter, \email{jaw3es@@virginia.edu}
+#' 
+#' @seealso \code{\link{addAVHRRnnualts}}, \code{\link{makeIowaALMannualts}}
+#' 
+#' @examples
+#' #need to add some
+#' 
+#' @export
+
+addAVHRRannualts_byWatershed<-function(lakelist, avhrrdata, watersheds, aggfun="mean"){
+  
+  library(raster)
+  library(rgdal)
+  library(sp)
+  
+  lakeinfo<-lakelist$lakeinfo
+  lakedata<-lakelist$lakedata
+  
+
+  #loop through lakes and extract AVHRR time series
+  for(ii in 1:nrow(lakeinfo)){
+    lakeyrs<-lakeinfo$start[ii]:lakeinfo$end[ii]
+    watershed.ii<-watersheds[watersheds$lagoslakeid == lakeinfo$lagoslakeid[ii],]
+    if(length(watershed.ii)==0){
+      ts.ii<-rep(NA, length(lakeyrs))
+    }
+    else{
+      avhrrstack.ii<-crop(avhrrdata, watershed.ii)
+      avhrrstack.ii<-mask(avhrrstack.ii, watershed.ii)
+      
[…]

### 2020-07-01 R Package/aqts/build.R

@@ -9,4 +9,3 @@ document("aqts") # this will create a file 'NAMESPACE' and a folder 'man'
 check("aqts")
 install("aqts")
 library("aqts")
-
